### 2018-07-16 misc/thesis-hardbound/Appendices/AppendixA.tex
Update 16/7/2018

% Appendix A

\chapter{Calculating Sun Position from Earth's Surface} % Main appendix title
\label{append:sunposition} % For referencing this appendix elsewhere, use \ref{append:motor}

\lhead{Appendix A. \emph{Calculating Sun Position}} % This is for the header on each page - perhaps a shortened title

The position of the sun from the earth's surface is generally measured using two entities---elevation angle and zenith angle. The angle projected from the sun with reference to the horizon is called the elevation angle. The compass angle of the sun from the $0^{\circ}$ N direction is called the azimuth angle. We use the Jean Meeus algorithm~\cite{SPA} that has an error of $\pm 3\cdot 10^{-4}$ degrees. This is one of the most popular algorithms, as its implementation is available in various platforms. It consists of an online web version~\footnote{\url{https://www.nrel.gov/midc/solpos/spa.html}}; also it is available in Python~\footnote{\url{http://pysolar.org/}} and MATLAB~\footnote{\url{http://pvpmc.org/pv-lib/}} programming languages.

### 2018-07-16 misc/thesis-hardbound/Appendices/AppendixB.tex
Update 16/7/2018

% Appendix B

\chapter{Calculating the Position of Sun Blocker} % Main appendix title
\label{append:motor} % For referencing this appendix elsewhere, use \ref{append:motor}

\lhead{Appendix B. \emph{Calculating the Position of Sun Blocker}} % This is for the header on each page - perhaps a shortened title

In order to block the light coming directly from the sun, the sun blocker head should intersect the ray from the sun to the camera. We use the Jean Meeus algorithm~\cite{SPA} to compute the azimuth and elevation angles of this ray, which we call $\xi$ and $\varepsilon$ respectively. The algorithm has an error of $\pm 3\cdot 10^{-4}$ degrees. The various lengths and angles required for the computations are shown in Fig.~\ref{fig:SideTopWSI_sub}. $L_{1}$ represents the length of the main arm. $L_{2}$ is the distance of the motor shift between the blocker and the arm.  $L_{3}$ denotes the length of the stem under the blocker head. $L_{4}$ denotes the length between the camera center and the arm motor axis. The two unknowns are $\tilde{\theta}$ which measures the arm angle measured from the horizon and $\alpha$ which measures the stem angle measured from the east direction. The following trigonometric equations are used:

\begin{gather}
a=L_{1}\sin\tilde{\theta} +L_{2}\cos\tilde{\theta} +L_{3}(\sin\alpha)(\sin\tilde{\theta})-L_{4},\\
c=L_{3}\cos\alpha,\\
d=L_{1}\cos\tilde{\theta}-L_{2}\sin\tilde{\theta}+L_{3}(\sin\alpha)(\cos\tilde{\theta}),\\
tan(\varepsilon)=\left(\frac{a\sin(\xi)}{c} \right)^2,\\
\sin(\xi)=-\left(\frac{c}{d}\right)
\end{gather}

\begin{figure}[H]
\centering
\subfloat[Side and top views]{\includegraphics[clip=true, trim={0cm 0cm 0cm 0cm},height=8cm]{SideTopWSI_3010_v2.pdf}}\quad
\subfloat[3D view]{\includegraphics[clip=true,  width=0.4\textwidth]{3d_view.pdf}}
\caption{Representation of WAHRSIS with the lengths and angles required for the computation of the motor angles.\label{fig:SideTopWSI_sub}}
\end{figure}

The arm angle $\tilde{\theta}$ can range from $45$ to $135$ degrees, whereas the stem angle $\alpha$ can range from $0$ to $180$ degrees. Combinations of $\tilde{\theta}$ and $\alpha$ with increments of $0.5$ are used to compute the related $\xi$ and $\varepsilon$ sun ray angles values. The combination leading to the smallest difference between those values and the ones obtained by the Jean Meeus algorithm is used.

### 2018-07-16 misc/thesis-hardbound/Appendices/AppendixC.tex
Update 16/7/2018

% Appendix C

\chapter{Derivation of Normalization Factor} % Main appendix title
\label{append:solarestimation} % For referencing this appendix elsewhere, use \ref{append:motor}

\lhead{Appendix C. \emph{Derivation of Normalization Factor}} % This is for the header on each page - perhaps a shortened title

Let us suppose that $a_1$, $a_2$, \ldots, $a_{\bar{t}}$ be the weather station records for $\bar{t}$ number of time stamps. The luminance values computed for each of the corresponding weather station points are represented by ${l}_1$, ${l}_2$, \ldots, ${l}_{\bar{t}}$. We attempt to estimate the conversion factor $x$, such that the objective function $f(x)$ representing the inter-sample distances between weather station and computed luminance value is minimized.

We represent objective function $f(x)$ as:

\noindent
\begin{align*}
   f(x) &= (xl_1 - a_1)^2 + (xl_2 - a_2)^2 + \ldots + (xl_{\bar{t}} - a_{\bar{t}})^2 & \\
              &= \sum_{i=1}^{\bar{t}} (xl_i - a_i)^2
\end{align*}

We equate $f'(x)$ to $0$, and the normalization factor $x$ is found as $x = \frac{\sum_{i=1}^{\bar{t}} a_{i}l_{i} }{\sum_{i=1}^{\bar{t}} l_i^2}$.

### 2018-07-16 misc/thesis-hardbound/Appendices/AppendixD.tex
Update 16/7/2018

% Appendix D
\chapter{Computation of Geometrical Bounds in a Multi-camera Setup} % Main appendix title
\label{append:multicamera} % For referencing this appendix elsewhere, use \ref{append:motor}

\lhead{Appendix D. \emph{Computation of Geometrical Bounds}} % This is for the header on each page - perhaps a shortened title

We formulate the geometrical limits for other scenarios as well. %, with noise in X co-ordinate of the camera positions.

% Part 1
\section{Noise in X- coordinate}

\subsection{Scenario - II}

\subsubsection{Upper Bound}

\begin{minipage}[t]{0.5\textwidth}
\includegraphics[width=0.7\textwidth,bb=0 0 600 600]{X-2a.pdf}
\captionof{figure}{Determination of upper bound for the translation of camera in X-direction (Scenario II).}
\end{minipage}
\begin{minipage}[t]{0.5\textwidth}
\vspace{-2in}
\begin{equation*}
\centering
\begin{aligned}
ZC_x = r\cos(\theta) \\
Z'C_y = r\sin(\theta) \\
ZC_x = \frac{r\sin(\theta)}{\tan(\theta_5)}\\
Z'Z = \frac{r\sin(\theta)}{\tan(\theta_5)} - r\cos(\theta)\\
\end{aligned}
\end{equation*}
\end{minipage}

\subsubsection{Lower Bound}

\begin{minipage}[t]{0.5\textwidth}
\includegraphics[width=0.9\textwidth,bb=0 0 600 600]{X-2b.pdf} 
\captionof{figure}{Determination of lower bound for the translation of camera in X-direction (Scenario II).}
\end{minipage}
\begin{minipage}[t]{0.5\textwidth}
\vspace{-2in}
\begin{equation*}
\centering
\begin{aligned}
ZC_x = r\cos(\theta) \\
ZC_y =  C_{x}C = r\sin(\theta) \\
Z'C_x =\frac{r\sin(\theta)}{\tan(\theta_4)}\\
Z'Z = \frac{r\sin(\theta)}{\tan(\theta_4)} - r\cos(\theta)\\
\end{aligned}
\end{equation*}
\end{minipage}

Therefore, the two geometrical bounds - lower and upper are $-(\frac{r\sin(\theta)}{\tan(\theta_4)} - r\cos(\theta))$ and $-(\frac{r\sin(\theta)}{\tan(\theta_5)} - r\cos(\theta))$ respectively.

\subsection{Scenario - III}

\subsubsection{Upper Bound}

\begin{minipage}[t]{0.5\textwidth}
\includegraphics[width=0.65\textwidth,bb=0 0 600 600]{X-3a.pdf} 
\captionof{figure}{Determination of upper bound for the translation of camera in X-direction (Scenario III).}
\end{minipage}
\begin{minipage}[t]{0.5\textwidth}
\vspace{-2in}
\begin{equation*}
\centering
\begin{aligned}
\sin(180-\theta) = \frac{CC_x}{CZ}\\
\implies CC_x = r\sin(\theta) \\ \\
\tan(\theta_5) = \frac{CC_x}{Z'C_x}\\
\implies Z'C_x = \frac{r\sin(\theta)}{\tan(\theta_5)}\\\\
\cos(180-\theta) = \frac{C_{x}Z}{CZ}\\
\implies C_{x}Z = -r\cos(\theta)\\ \\
Z'Z = \frac{r\sin(\theta)}{\tan(\theta_5)} + r\cos(\theta)
\end{aligned}
\end{equation*}
\end{minipage}

\subsubsection{Lower Bound}

\begin{minipage}[t]{0.5\textwidth}
\includegraphics[width=0.65\textwidth,bb=0 0 600 600]{X-3b.pdf} 
\captionof{figure}{Determination of upper bound for the translation of camera in X-direction (Scenario III).}
\end{minipage}
\begin{minipage}[t]{0.5\textwidth}
\vspace{-2in}
\begin{equation*}
\centering
\begin{aligned}
\sin(180-\theta) = \frac{CC_x}{CZ}\\
\implies CC_x = r\sin(\theta) \\ \\
\tan(\theta_4) = \frac{CC_x}{Z'C_x}\\
\implies Z'C_x = \frac{r\sin(\theta)}{\tan(\theta_4)}\\\\
\cos(180-\theta) = \frac{C_{x}Z}{CZ}\\
\implies C_{x}Z = -r\cos(\theta)\\ \\
Z'Z = \frac{r\sin(\theta)}{\tan(\theta_4)} + r\cos(\theta)
\end{aligned}
\end{equation*}
\end{minipage}

Therefore, the two geometrical limits - lower and upper are given by $-(\frac{r\sin(\theta)}{\tan(\theta_4)} + r\cos(\theta))$ and $-(\frac{r\sin(\theta)}{\tan(\theta_5)} + r\cos(\theta))$ respectively.

\subsection{Scenario - IV}
In this scenario, \emph{no} possible translation of camera in X-direction can contain the point in the active region. Therefore, the probability of a point to belong to active region is \emph{null}.

\begin{figure}[H]
\centering
\includegraphics[width=0.45\textwidth,bb=0 0 600 600]{X-4.pdf} 
\caption{Probability is $0$ for the translation of camera in X-direction (Scenario IV).}
\label{fig:SWIM-images}
\end{figure}

\subsection{Scenario - V}
In this scenario, \emph{no} possible translation of camera in X-direction can contain the point in the active region. Therefore, the probability of a point to belong to active region is \emph{null}.

\begin{figure}[htb]
\centering
\includegraphics[width=0.45\textwidth,bb=0 0 600 600]{X-5.pdf} 
\caption{Probability is $0$ for the translation of camera in X-direction (Scenario V).}
\label{fig:SWIM-images}
\end{figure}

\subsection{Scenario - VI}

\begin{minipage}[t]{0.5\textwidth}
\includegraphics[width=0.65\textwidth,bb=0 0 600 600]{X-6a.pdf}
\captionof{figure}{Determination of lower bound for the translation of camera in X-direction (Scenario VI).}
\end{minipage}
\begin{minipage}[t]{0.5\textwidth}
\vspace{-2in}
\begin{equation*}
\centering
\begin{aligned}
ZC_x = r\cos(\theta) \\
ZC_y = r\sin(\theta) \\
Z'C_x = \frac{r\sin(\theta)}{\tan(\theta_4)}\\
ZZ' = r\cos(\theta) - \frac{r\sin(\theta)}{\tan(\theta_4)}
\end{aligned}
\end{equation*}
\end{minipage}

\subsubsection{Upper Bound}

\begin{minipage}[t]{0.5\textwidth}
\includegraphics[width=0.65\textwidth,bb=0 0 600 600]{X-6b.pdf} 
\captionof{figure}{Determination of upper bound for the translation of camera in X-direction (Scenario VI).}
\end{minipage}
\begin{minipage}[t]{0.5\textwidth}
\vspace{-2in}
\begin{equation*}
\centering
\begin{aligned}
ZC_x = r\cos(\theta) \\
ZC_y = r\sin(\theta) \\
Z'C_x = \frac{r\sin(\theta)}{\tan(\theta_5)}\\
ZZ' = r\cos(\theta) - \frac{r\sin(\theta)}{\tan(\theta_5)}
\end{aligned}
\end{equation*}
\end{minipage}

Therefore, the two geometrical limits - lower and upper are $+(r\cos(\theta) - \frac{r\sin(\theta)}{\tan(\theta_4)})$ and $r\cos(\theta) - \frac{r\sin(\theta)}{\tan(\theta_5)}$ respectively.

% Part 2
\section{Noise in Y- coordinate}

\subsection{Scenario - II}

\subsubsection{Lower Bound}

\begin{minipage}[t]{0.5\textwidth}
\includegraphics[width=0.65\textwidth,bb=0 0 600 600]{Y-2a.pdf}  
\captionof{figure}{Determination of lower bound for the translation of camera in Y-direction (Scenario II).}
\end{minipage}
\begin{minipage}[t]{0.5\textwidth}
\vspace{-2in}
\begin{equation*}
\centering
\begin{aligned}
\cos(90-\theta)=\frac{C_{y}Z}{CZ}\\
\implies C_{y}Z=r\sin(\theta)\\
\sin(90-\theta) = \frac{C_{y}C}{CZ}\\
\implies C_{y}C = r\cos(\theta)\\
\tan(90-\theta_5) = \frac{C_{y}C}{C_{y}Z'}\\
\implies C_{y}Z' = \frac{r\cos(\theta)}{\cot(\theta_5)}\\
ZZ' =  r\sin(\theta) - \frac{r\cos(\theta)}{\cot(\theta_5)}
\end{aligned}
\end{equation*}
\end{minipage}

\subsubsection{Upper Bound}

\begin{minipage}[t]{0.5\textwidth}
\includegraphics[width=0.65\textwidth,bb=0 0 600 600]{Y-2b.pdf}  
\captionof{figure}{Determination of upper bound for the translation of camera in Y-direction (Scenario II).}
\end{minipage}
\begin{minipage}[t]{0.5\textwidth}
\vspace{-2in}
\begin{equation*}
\centering
\begin{aligned}
\cos(90-\theta)=\frac{C_{y}P}{CP}\\
\implies C_{y}P=r\sin(\theta)\\
\sin(90-\theta) = \frac{C_{y}C}{CP}\\
\implies C_{y}C = r\cos(\theta)\\
\tan(90-\theta_4) = \frac{C_{y}C}{C_{y}P'}\\
\implies C_{y}P' = \frac{r\cos(\theta)}{\cot(\theta_4)}\\
PP' =  r\sin(\theta) - \frac{r\cos(\theta)}{\cot(\theta_4)}
\end{aligned}
\end{equation*}
\end{minipage}

\subsection{Scenario - III}

\begin{figure}[H]
	\centering
	\includegraphics[width=0.4\textwidth,bb=0 0 600 600]{Y-3.pdf} 
	\caption{Probability of the point C is $0$ for the translation of camera in Y-direction (Scenario III).}
	\label{fig:SWIM-images}
\end{figure}

\subsection{Scenario - IV}

\begin{figure}[H]
	\centering
	\includegraphics[width=0.4\textwidth,bb=0 0 600 600]{Y-4.pdf} 
	\caption{Probability of the point C is $0$ for the translation of camera in Y-direction (Scenario IV).}
	\label{fig:SWIM-images}
\end{figure}

\subsection{Scenario - V}

\subsubsection{Lower Bound}

\begin{minipage}[t]{0.5\textwidth}
\includegraphics[width=0.55\textwidth,bb=0 0 600 600]{Y-5a.pdf}  
\captionof{figure}{Determination of lower bound for the translation of camera in Y-direction (Scenario V).}
\end{minipage}
\begin{minipage}[t]{0.5\textwidth}
\vspace{-2in}
\begin{equation*}
\centering
\begin{aligned}
\alpha = 90 - (360 - \theta)\\
\implies \alpha = \theta - 270 \\
\sin(\alpha) = \frac{CC_y}{CP}\\
CC_y = r\sin(\theta - 270)\\
\cos(\alpha) = \frac{PC_y}{CP}\\
\implies PC_y = r\cos(\theta - 270)\\
\tan(90 - \theta_5) = \frac{CC_y}{C_{y}P'}\\
\implies C_{y}P' = \frac{r\sin(\theta - 270)}{\cot(\theta_4)}\\
PP' = r\cos(\theta - 270) +  \frac{r\sin(\theta - 270)}{\cot(\theta_4)}
\end{aligned}
\end{equation*}
\end{minipage}

\subsubsection{Upper Bound}

\begin{minipage}[t]{0.5\textwidth}
\includegraphics[width=0.55\textwidth,bb=0 0 600 600]{Y-5b.pdf}  
\captionof{figure}{Determination of upper bound for the translation of camera in Y-direction (Scenario V).}
\end{minipage}
\begin{minipage}[t]{0.5\textwidth}
\vspace{-2in}
\begin{equation*}
\centering
\begin{aligned}
\alpha = 90 - (360 - \theta)\\
\implies \alpha = \theta - 270 \\
\sin(\alpha) = \frac{CC_y}{CP}\\
CC_y = r\sin(\theta - 270)\\
\cos(\alpha) = \frac{PC_y}{CP}\\
\implies PC_y = r\cos(\theta - 270)\\
\tan(90 - \theta_4) = \frac{CC_y}{C_{y}P'}\\
\implies C_{y}P' = \frac{r\sin(\theta - 270)}{\cot(\theta_4)}\\
PP' = r\cos(\theta - 270) +  \frac{r\sin(\theta - 270)}{\cot(\theta_4)}
\end{aligned}
\end{equation*}
\end{minipage}

\subsection{Scenario - VI}

\subsubsection{Upper Bound}

\begin{minipage}[t]{0.5\textwidth}
\includegraphics[width=0.55\textwidth,bb=0 0 600 600]{Y-6a.pdf}  
\captionof{figure}{Determination of upper bound for the translation of camera in Y-direction (Scenario VI).}
\end{minipage}
\begin{minipage}[t]{0.5\textwidth}
\vspace{-2in}
\begin{equation*}
\centering
\begin{aligned}
\cos(90-\theta)=\frac{C_{y}P}{CP}\\
\implies C_{y}P=r\sin(\theta)\\
\sin(90-\theta) = \frac{C_{y}C}{CP}\\
\implies C_{y}C = r\cos(\theta)\\
\tan(90-\theta_4) = \frac{C_{y}C}{C_{y}P'}\\
\implies C_{y}P' = \frac{r\cos(\theta)}{\cot(\theta_4)}\\
PP' = \frac{r\cos(\theta)}{\cot(\theta_4)} - r\sin(\theta)
\end{aligned}
\end{equation*}
\end{minipage}

\subsubsection{Lower Bound}

\begin{minipage}[t]{0.5\textwidth}
\includegraphics[width=0.75\textwidth]{demo3.pdf}   
\captionof{figure}{Determination of lower bound for the translation of camera in Y-direction (Scenario VI).}
\end{minipage}
\begin{minipage}[t]{0.5\textwidth}
\vspace{-2in}
\begin{equation*}
\centering
\begin{aligned}
\cos(90-\theta)=\frac{C_{y}P}{CP}\\
\implies C_{y}P=r\sin(\theta)\\
\sin(90-\theta) = \frac{C_{y}C}{CP}\\
\implies C_{y}C = r\cos(\theta)\\
\tan(90-\theta_5) = \frac{C_{y}C}{C_{y}P'}\\
\implies C_{y}P' = \frac{r\cos(\theta)}{\cot(\theta_5)}\\
PP' = \frac{r\cos(\theta)}{\cot(\theta_5)} - r\sin(\theta)
\end{aligned}
\end{equation*}
\end{minipage}

% Part 3
\section{Noise in view angle}

\subsection{Scenario - II}

\subsubsection{Lower Bound}

\begin{minipage}[t]{0.5\textwidth}
\includegraphics[width=0.9\textwidth]{theta-2a.pdf}   
\captionof{figure}{Determination of lower bound of view angle for the rotation of camera (Scenario II).}
\end{minipage}
\begin{minipage}[t]{0.5\textwidth}
\vspace{-1in}
\begin{equation*}
\centering
\begin{aligned}
\theta_5^{'} = \theta_5 + (\theta - \theta_5)\\
\Theta + \delta_5 = \theta \\
\implies \Theta = \theta - \delta_5
\end{aligned}
\end{equation*}
\end{minipage}

\subsubsection{Upper Bound}

\begin{minipage}[t]{0.5\textwidth}
\includegraphics[width=0.85\textwidth]{theta-2b.pdf}   
\captionof{figure}{Determination of upper bound of view angle for the rotation of camera (Scenario II).}
\end{minipage}
\begin{minipage}[t]{0.5\textwidth}
\vspace{-1in}
\begin{equation*}
\centering
\begin{aligned}
\theta_5^{'} = \theta_5 + (\theta - \theta_4)\\
\Theta + \delta_5 = \theta_5 + (\theta - \theta_4)\\
\implies \Theta = \theta_5 + (\theta - \theta_4) - \delta_5
\end{aligned}
\end{equation*}
\end{minipage}

\subsection{Scenario - III}

\subsubsection{Lower Bound}

\begin{minipage}[t]{0.5\textwidth}
\includegraphics[width=0.85\textwidth]{theta-3a.pdf}  
\captionof{figure}{Determination of lower bound of view angle for the rotation of camera (Scenario III).}
\end{minipage}
\begin{minipage}[t]{0.5\textwidth}
\vspace{-1in}
\begin{equation*}
\centering
\begin{aligned}
\theta_5^{'} = \theta_5 + (\theta - \theta_5)\\
\Theta + \delta_5 = \theta \\
\implies \Theta = \theta - \delta_5
\end{aligned}
\end{equation*}
\end{minipage}

\subsubsection{Upper Bound}

\begin{minipage}[t]{0.5\textwidth}
\includegraphics[width=0.85\textwidth]{theta-3b.pdf}  
\captionof{figure}{Determination of upper bound of view angle for the rotation of camera (Scenario III).}
\end{minipage}
\begin{minipage}[t]{0.5\textwidth}
\vspace{-1in}
\begin{equation*}
\centering
\begin{aligned}
\theta_5^{'} = \theta_5 + (\theta - \theta_4)\\
\Theta + \delta_5 = \theta_5 + (\theta - \theta_4)\\
\implies \Theta = \theta_5 + (\theta - \theta_4) - \delta_5
\end{aligned}
\end{equation*}
\end{minipage}

\subsection{Scenario - IV}

\begin{figure}[H]
	\centering
	\includegraphics[width=0.4\textwidth]{theta-4.pdf} 
	\caption{Probability of the point C is $0$ for the rotation of camera (Scenario IV).}
	\label{fig:SWIM-images}
\end{figure}

\subsection{Scenario - V}

\subsubsection{Upper Bound}

\begin{minipage}[t]{0.5\textwidth}
\includegraphics[width=0.85\textwidth]{theta-5a.pdf} 
\captionof{figure}{Determination of upper bound of view angle for the rotation of camera (Scenario V).}
\end{minipage}
\begin{minipage}[t]{0.5\textwidth}
\vspace{-1in}
\begin{equation*}
\centering
\begin{aligned}
\theta_4^{'} = \theta_4 - (\theta_4 + 360 -\theta)\\
\implies \theta_4^{'} = \theta - 360 \\
\Theta + \delta_4 = \theta - 360 \\
\implies \Theta = \theta - 360 - \delta_4
\end{aligned}
\end{equation*}
\end{minipage}

\subsubsection{Lower Bound}

\begin{minipage}[t]{0.5\textwidth}
\includegraphics[width=0.85\textwidth]{theta-5b.pdf} 
\captionof{figure}{Determination of lower bound of view angle for the rotation of camera (Scenario V).}
\end{minipage}
\begin{minipage}[t]{0.5\textwidth}
\vspace{-1in}
\begin{equation*}
\centering
\begin{aligned}
\theta_4^{'} = \theta_4 - (\theta_5 + 360 -\theta)\\
\implies \theta_4^{'} = \theta_4 - \theta_5 - 360 + \theta \\
\Theta + \delta_4 = \theta_4 - \theta_5 - 360 + \theta \\
\implies \Theta = \theta_4 - \theta_5 - 360 + \theta - \delta_4 
\end{aligned}
\end{equation*}
\end{minipage}

\subsection{Scenario - VI}

\subsubsection{Upper Bound}

\begin{minipage}[t]{0.5\textwidth}
\includegraphics[width=0.85\textwidth]{theta-6a.pdf}  
\captionof{figure}{Determination of upper bound of view angle for the rotation of camera (Scenario VI).}
\end{minipage}
\begin{minipage}[t]{0.5\textwidth}
\vspace{-1in}
\begin{equation*}
\centering
\begin{aligned}
\theta_4^{'} = \theta_4 - (\theta_4 - \theta)\\
\Theta + \delta_4 = \theta \\
\implies \Theta = \theta - \delta_4
\end{aligned}
\end{equation*}
\end{minipage}

\subsubsection{Lower Bound}

\begin{minipage}[t]{0.5\textwidth}
\includegraphics[width=0.85\textwidth]{theta-6b.pdf}  
\captionof{figure}{Determination of lower bound of view angle for the rotation of camera (Scenario VI).}
\end{minipage}
\begin{minipage}[t]{0.5\textwidth}
\vspace{-1in}
\begin{equation*}
\centering
\begin{aligned}
\theta_4^{'} = \theta_4 - (\theta_5 - \theta)\\
\Theta + \delta_4 = \theta_4 - \theta_5 + \theta\\
\implies \Theta = \theta_4 - \theta_5 + \theta - \delta_4
\end{aligned}
\end{equation*}
\end{minipage}

### 2018-07-16 misc/thesis-hardbound/Chapters/Chapter1.tex
Update 16/7/2018

\chapter{Introduction}
\label{chap:intro}

\definecolor{Light}{gray}{.95}
\newcommand\tab[1][0.5cm]{\hspace*{#1}}

\lhead{Chapter 1. \emph{Introduction}}

\section{Background and Motivation}

The study of clouds in the earth's atmosphere is becoming popular amongst the remote sensing community for a variety of applications and domains---aviation, weather prediction, and solar energy. Furthermore, ground-to-satellite or ground-to-air communication signals suffer from substantial attenuation because of clouds in the atmosphere. Rain, clouds, atmospheric particles, and water vapor along the signal path affect communication links in various ways.

Sky pictures are commonly used in the analysis and prediction of signal attenuation due to clouds. Imaging the cloud in the atmosphere can be performed in different ways. Satellite imagery~\cite{PALSAR,sat_reg} and aerial photographs~\cite{air1} are popular in particular for large-scale surveys; airborne light detection and ranging (LiDAR) data are extensively used for aerial surveys~\cite{LIDAR1}. However, these techniques rarely provide sufficient temporal and/or spatial resolution for localized and short-term cloud analysis over a particular area. This is where ground-based whole sky imagers (WSIs) offer a compelling alternative~\cite{WAHRSIS}. The images obtained from these devices provide high-resolution data about local cloud formation, movement, and other atmospheric phenomena.

With the rapid advancement in photogrammetric techniques, high resolution cameras are now extensively used for almost all applications. The existence of ubiquitous cameras around us generate a huge amount of data, which can be effectively used to solve most of the fundamental problems in the field of remote sensing. Extracting valuable information from the huge amount of image data by detecting and analyzing the various entities in these images is challenging. In this thesis, we attempt to answer some of the fundamental questions in the cloud imaging by connecting the remote sensing and computer vision communities.

\begin{figure}[htb]
\begin{center}
\includegraphics[width=0.7\textwidth]{cloud_att_demo_v2.pdf}
\caption[Illustration of cloud attenuation in satellite communication links.]{Attenuation: The effects of the atmosphere on signal transmitted from geo-stationary satellites. The rain, cloud and the other atmospheric particles contributes a noise signature that ultimately degrades the fidelity of the satellite signals. Image is archived from NASA, Glenn Research Center.
\label{fig:cloud_att}}
\end{center}
\end{figure}

Our objective is to use whole sky imagers to provide an analysis of the effect of clouds in signal strength attenuation during satellite and military communications. Satellite communication links suffer from appreciable attenuation in the space to ground communication because of the rain, cloud, atmospheric particles, water vapor particles in its signal path~\cite{site_diversity,GammaDrop}. Figure~\ref{fig:cloud_att} shows a satellite slant path which is affected by propagation impairments. The images obtained from the whole sky imagers will help us to detect and identify different type of clouds, analyze the small-scale movement which will subsequently help us in deriving a model for signal attenuation of satellite and air-to-ground communication links.

We aim to understand the effects of clouds on communications using ground-based whole sky imagers. These ground-based devices capture the entire sky at regular intervals of time. The resulting images are of higher resolution than what can be obtained from satellites, and the upwards pointing nature of the camera makes it easy to capture low-lying clouds.

The objectives of this thesis can be clearly defined as:
\begin{itemize}
\item To design and build low-cost and high image resolution sky cameras.
\item To identify the best color channels for cloud detection.
\item To propose a color-based image segmentation algorithm.
\item To classify cloud types into various categories, as identified by World Meteorological Organization (WMO).
\item To estimate various weather parameters using ground-based sky imagers.
\item To analyze point localization error in a multi-camera set-up and to localize cloud base using stereo cameras.
\end{itemize}
The current approaches for such problems lack a systematic analysis, proper benchmarking in public databases and better performance. Therefore, we have identified these problems and propose the following solutions for these various tasks.

We present the design of the first low-cost, high image resolution sky camera designed for tropical countries like Singapore. We name our imagers \textbf{WAHRSIS}, that stands for \textbf{W}ide \textbf{A}ngle \textbf{H}igh \textbf{R}esolution \textbf{S}ky \textbf{I}maging \textbf{S}ystem. We present three models of WAHRSIS.

Using several statistical tools viz.\ Principal Component Analysis (PCA), bimodality analysis and clustering techniques, we present a structured and systematic analysis of the various existing color channels. We propose a rough-set based color channel selection method that accurately estimates the efficiency of different color channels for cloud detection. Our method is the first that employs rough-set based techniques to solve this problem of color channel selection. Such rough-set methods provide us with mathematical tools to define the \emph{approximate} ground-truth maps of sky/cloud images.

We introduce the first large-scale, publicly available sky/cloud image database with manually annotated segmentation masks. We refer to this database as \textbf{SWIMSEG}: \textbf{S}ingapore \textbf{W}hole sky \textbf{IM}aging \textbf{SEG}mentation database. Unlike the conventional binary segmentation algorithms, we propose a probabilistic segmentation method. In our method, instead of \emph{hard} labeling, we assign a \emph{probability} to a pixel to belong to cloud category. We also benchmark with the state-of-the-art cloud segmentation algorithms.

We also propose a robust cloud classification framework for identifying and recognizing cloud types in tropical regions like Singapore. We propose a filter-bank based cloud classification framework that systematically integrates both \emph{color} and \emph{texture} cues of sky/cloud images, and benchmark with other existing algorithms. We also release the first large-scale cloud categorization database to the research community. We refer to this database as \textbf{SWIMCAT}, that stands for \textbf{S}ingapore \textbf{W}hole sky \textbf{IM}aging \textbf{CAT}egories database.

We propose a model to estimate the instantaneous solar radiation from the corresponding ground-based sky/cloud images. Extensive benchmarking w.r.t.\ other existing solar estimation algorithms show the efficacy of our approach. We also propose a method to detect the onset of precipitation from sky/cloud images. Finally, we present a methodology to perform short-term cloud forecasts using optical flow techniques.

Finally, we present a localization algorithm in a multiple-camera setup, under the assumption of error-free matching and noisy camera poses. We benchmark our algorithm with other state-of-the-art point localization algorithms. We present a framework for estimating the cloud-base height, using a pair of sky cameras.

\section{Thesis Outline \& Main Contributions}
\forceindent \textbf{Chapter~\ref{chap:intro}: Introduction} \tab We discuss the objectives and motivation of the thesis in this chapter. We also describe the outline of the thesis, and briefly highlight the main contributions which were offered throughout this thesis.

\textbf{Chapter~\ref{chap:litreview}: Literature Review} \tab In this chapter, we provide a thorough literature review of the various aspects of this thesis. We give a general account of the current state-of-the-art practices, and also aim to identify a few research gaps in the current literature.

\textbf{Chapter~\ref{chap:wsi}: Whole Sky Imager} \tab The central theme of this thesis involves the use of high-resolution, ground-based sky imagers for continuous monitoring of the earth's atmosphere. Unlike conventional satellite images, ground-based sky cameras have high temporal and spatial resolutions. In this chapter, we discuss the methodology for spatial-, color- and luminance- calibration for our custom-built, low-cost sky imagers. Moreover, the images captured by regular sky cameras are often saturated because of the direct glare from the sun. In this chapter, we show how High Dynamic Range Imaging (HDRI) techniques can solve this problem of over-saturation.

\textbf{Chapter~\ref{chap:colorchannels}: Color Spaces and Components} \tab Our ground-based imagers called WAHRSIS (cf.\ Chapter~\ref{chap:wsi}) captures the images of the atmosphere at regular intervals of time, and stores the captured images in a server. The first task of cloud analysis is to accurately detect the cloud pixels in sky/cloud images. This is an extremely challenging task, as clouds are non-rigid and do not have specific shape or size. Therefore, \emph{color} is used as the most discriminatory feature for cloud detection. This chapter deals with a structured review of the various color spaces and components that are generally used in cloud analyis.

\textbf{Chapter~\ref{chap:segmentation}: Color-based Image Segmentation} \tab A structured and systematic analysis of the various color channels of sky/cloud images assist us in identifying the most discriminatory color channels. In this chapter, we use the identified discriminatory color channel and discuss the approach of our color-based image segmentation algorithm.

\textbf{Chapter~\ref{chap:classification}: Texture-based Image Classification} \tab One of the important tasks after successful cloud detection, is to identify and categorize the different cloud types. In this chapter, we deal with multi-class classification of sky/cloud image patches. We perform a systematic analysis of various image features that were designed specifically for this task.

\textbf{Chapter~\ref{chap:solar}: Weather Parameters Estimation from Images} \tab In the previous chapters, we discussed our proposed methodology to perform color-based segmentation and texture-based classification on sky/cloud images. In this chapter, we discuss about the impact of clouds on solar and renewable energy generation. In tropical regions like Singapore, the weather phenomenon is highly localized and clouds often block the sun. This greatly impacts the incoming solar radiation falling on the earth's surface. Therefore, the generated solar energy drops drastically in a short span of time. Such scenarios are not conducive for Photo Voltaic (PV) power generation. It is extremely difficult to model these sharp variations of the incoming solar radiation. In this chapter, we analyze the impact of clouds on such incoming solar radiation and also discuss our current works on cloud tracking and detecting rainfall onset.

\textbf{Chapter~\ref{chap:localize}: 3D Scene Analysis Using Multiple Cameras} The earlier chapters deal with the study and analysis of images, captured from a single camera. In this chapter, we extend our discussion to the task of scene analysis using multiple cameras. The first part of this chapter deals with the introduction of a novel localization algorithm in the setup of multiple cameras, having finite pixel dimension and noisy camera poses. The remaining part of this chapter discusses a practical application of point localization task. We use scene flow techniques on stereo images captured by ground-based sky cameras to localize cloud mass.

\textbf{Chapter~\ref{chap:conclusion}: Conclusion \& Future Work} \tab We conclude the thesis in this chapter. Future works using ground-based sky camera are also discussed. Following this chapter, we provide a detailed list of the various notations that were used throughout this thesis, for easy reference.

### 2018-07-16 misc/thesis-hardbound/Chapters/Chapter2.tex
Update 16/7/2018

\chapter{Literature Review}
\label{chap:litreview}

\lhead{Chapter 2. \emph{Literature Review}}
In this chapter, we provide a thorough literature review of the various aspects of this thesis. As mentioned in the previous chapter, this thesis involves the use of camera(s) to understand a scene better, and learn important cues of its surroundings. In most cases, we apply our proposed algorithms and frameworks in the context of cloud imaging using ground-based whole sky imagers. In this chapter, we describe the existing works of this particular field. We attempt to identify a few existing research gaps in the literature and bridge most of them by proposing state-of-the-algorithms and best practices.

\section{Ground-based Imaging Instrument}
\label{sec:lit-wsi}
Satellite images are commonly used to monitor the earth and analyze its various phenomena. They provide remote sensing analysts with accurate information about various earth's events. Satellite images are available in different spatial and temporal resolutions and also across various ranges of the electromagnetic spectrum, including visible, near- and far-infrared regions. For example, multi-temporal satellite images are extensively used for monitoring forest canopy changes~\cite{forest} or evaluating sea ice concentrations~\cite{ice2008}.

The presence of clouds plays a very important role in the analysis of satellite images. NASA's Ice, Cloud, and land Elevation Satellite (ICESat) has demonstrated that $70\%$ of the world's atmosphere is covered with clouds~\cite{NASA-cloud}. Therefore, there has been renewed interest amongst the remote sensing community to further study clouds and their effects on the earth.

Satellite images are a good starting point for monitoring the earth's atmosphere. However, they have either high temporal resolution (e.g.\ geostationary satellites) or high spatial resolution (e.g.\ low-orbit satellites), but never both. In many applications like solar energy production~\cite{solar_irr_pred}, local weather prediction, tracking contrails at high altitudes~\cite{contrail_WSI}, studying aerosol properties~\cite{fuse_AOD}, attenuation of communication signals~\cite{cloud_model_compare,radiosonde2014}, we need data with high spatial \emph{and} temporal resolution. This is why ground-based sky imagers have become popular and are now widely used in such applications. The ready availability of high-resolution cameras at a low cost facilitated the development of various models of sky imagers. These sky cameras are popularly known as Whole Sky Imagers (WSIs), as they capture the whole sky scene with its wide-angled lens. In geographical small countries like Singapore, ground-based whole sky imagers offer remote sensing analysts a fantastic alternative, as compared to satellite images. These sky cameras have high temporal and spatial resolutions. However, conventional sky cameras are expensive, have limited flexibilities and low image resolutions. We address this in Chapter~\ref{chap:wsi}, and present custom-built sky cameras.

A WSI consists of an imaging system placed inside a weather-proof enclosure that captures the sky at user-defined intervals. A number of WSI models have been developed over the years.

\begin{table}[htb]
\footnotesize
\centering
\begin{tabular}{ p{1.7in}|p{1.8in}|l|p{1in} }
\hline 
\textbf{Application}  & \textbf{Organization} & \textbf{Country} &  \textbf{WSI Model}  \\
\hline
Air traffic control~\cite{infrared_UK} & Campbell Scientific Ltd. & United Kingdom & IR NEC TS9230  \\   
Cloud characterization~\cite{sky_imager2008}& Atmospheric Physics Group & Spain & GFAT All-sky imager\\ 
Cloud classification~\cite{Sylvio} & Brazilian Institute for Space Research & Brazil & TSI-440\\
Cloud classification~\cite{Kazantzidis2012} & Laboratory of Atmospheric Physics & Greece & Canon IXUS II with FOV $180^{\circ}$   \\ 
Cloud macrophysical properties~\cite{Long} & Pacific Northwest National Laboratory & United States & Hemispheric Sky Imager\\ 
Cloud track wind data monitoring~\cite{synerg} & Laboratoire de M\'et\'eorologie Dynamique & France & Nikon D100 with FOV $63^{\circ}$\\ 
Convection~\cite{orograph2007}& Creighton University & United States & Digital Camera   \\ 
Radiation balance~\cite{uwe2000}& Lindenberg Meteorological Observatory & Germany & VIS/NIR 7   \\  
Solar power forecasting~\cite{Ghonima2012}& Solar Resource Assessment \& Forecasting Laboratory & United States & TSI-440 \\ 
Weather monitoring~\cite{TSI880} & Pacific Northwest National Laboratory & United States & TSI-880\\ 
Weather reporting~\cite{how_weather}& Ecole Polytechnique F\'ed\'erale de Lausanne & Switzerland & Panorama Camera\\ 
\hline  
\end{tabular}
\caption{Overview of various ground-based whole sky imagers and their intended applications.}
\label{tab:diff-database}
\end{table}

A commercial WSI (\mbox{TSI-440}, \mbox{TSI-880}) manufactured by Yankee Environmental Systems (YES) is used by many researchers~\cite{Long,Souza,Ghonima2012}. Owing to the high cost and limited flexibility of commercial sky imagers, many research groups have built their own WSI models \cite{Sylvio,sky_imager2008,Kazantzidis2012,synerg,orograph2007,uwe2000,infrared_UK,how_weather}. For example, the Scripps Institution of Oceanography at the University of California San Diego has been developing and using WSIs as part of their work for many years~\cite{WSI_UCSD}. Table~\ref{tab:diff-database} provides an overview of the types of ground-based sky cameras used by various organizations around the world, and their primary applications.

These ground-based sky cameras capture images at regular intervals of time, and stores them in local or remote server. The captured sky/cloud images are subsequently analyzed for various applications. The segmentation of clouds from these images is one of the fundamental tasks---existing works on cloud detection are discussed in the subsequent Section~\ref{sec:lit-segment} of this chapter.

\section{Image Segmentation}
\label{sec:lit-segment}
Segmentation is one of the first steps in sky/cloud image analysis. It remains a challenging task because of the non-rigid, feature-less, and poorly-defined structure of clouds. Also, the shape of clouds also changes continuously over time. Thus, classical image segmentation approaches based on shape priors~\cite{wrapper_Jain} are not suitable. Furthermore, the wide range of lighting conditions (direct sunlight to completely covered skies) adds to the difficulty.

As color is the most discriminating feature in sky/cloud images, most works in the literature use color for cloud segmentation. Long et al.\ \cite{Long} showed that the ratio of red and blue channels from RGB color space is a good candidate for segmentation and tuned corresponding thresholds to create binary masks. Calb{\'{o}} and Sabburg~\cite{Calbo2008} use the same ($R/B$) ratio to derive statistical features (mean, standard deviation, entropy etc.) of the clouds and subsequently classify the sky/cloud images into different cloud types.
Heinle et al.\ \cite{Heinle2010} exploited the difference of red and blue channels for successful detection and subsequent labeling of pixels. Liu et al.\ \cite{LiuSP2015} also used the difference of red and blue channels in their superpixel-based cloud segmentation framework. Souza et al.\ \cite{Souza} used the Saturation (S) channel for calculating cloud coverage. Mantelli-Neto et al. \cite{Sylvio} investigated the locus of cloud pixels in the RGB color model. Li et al.\ \cite{Li2011} proposed cloud detection using an adaptive threshold technique in the normalized blue/red channel. Yuan et al.\ \cite{BOW-cloud} proposed a cloud detection framework using superpixel classification of image features.

In these existing methods of the current literature for cloud segmentation, the selection of color models and channels has not been studied systematically. Many existing approaches~\cite{Calbo2008,Heinle2010,LiuSP2015,Li2011,LiuGC2015} use combinations of red and blue channels, which is a sensible choice, because the sky is predominantly blue due to the Rayleigh scattering of light at shorter wavelengths. However, we are not aware of any experimental analysis presented regarding the efficacy of these color channels in sky/cloud image segmentation. Furthermore, all of the above methods rely on manually-defined parameters and case-based decisions for segmentation. These make the methods somewhat ad-hoc and prone to errors. Finally, most of them assign binary labels by design, which further reduces their flexibility and robustness. We address this limitation in Chapter~\ref{chap:colorchannels}, and propose a probabilistic color-based image segmentation algorithm in Chapter~\ref{chap:segmentation}.

The successful detection of clouds in sky/cloud images is also helpful for its classification into various cloud types. Such cloud-type recognition tasks are generally done manually. However, a few approaches have been recently developed for such tasks---we discuss them in the next Section~\ref{sec:lit-classify} of this chapter.

\section{Image Type Recognition}
\label{sec:lit-classify}

For varied applications viz.\ aviation, weather prediction, and solar energy, clouds are continuously monitored by experts from meteorological institutes. In most cases, cloud observation is done manually by the experts. Cloud experts from the meteorological institutes observe these clouds to better understand the atmospheric phenomenon; and classify the clouds into various categories as identified by World Meteorological Organization (WMO)~\cite{WMO_guide}. They report the different cloud parameters such as cloud type, cloud base height, cloud coverage regularly. These observations are performed manually by cloud experts who have received extensive training in this field. Though accurate, such manual observations are highly expensive and cumbersome. Therefore, it is necessary to employ automatic cloud classification algorithms which are systematic and less expensive as compared to its human counterpart.

Automatic cloud type recognition is done primarily from satellite or ground-based sky cameras. Traditionally, satellite images were mostly used for such tasks. However, these images suffer from low temporal and spatial resolutions, and thus cannot be used in geographically small countries like Singapore. Cloud formation and the weather conditions are highly localized in such countries. Therefore, we use images from WSIs for automatic cloud classification task.

The WMO recommends a genera-based classification~\cite{WMO_guide}, which defines how to classify cloud patches into various categories based on their shape, structure, transparency, arrangement inside the cloud, texture, color, and height of their base. For example, cumulus clouds are puffy in shape and are regularly patterned; stratus clouds are mostly featureless, and are characterized by their transparent, whitish veil appearance; nimbostratus clouds are rain clouds, having thick dark appearance; and so on. Although clouds do not exhibit \emph{strong} image-based features, we can still exploit the color and texture of the cloud to extract discriminatory cues.

In the literature, several features were developed for automatic cloud type recognition. Some of the earlier methods used co-occurrence and auto-correlation matrices~\cite{singh2005}, Fourier transformation in classifying pre-defined sky conditions~\cite{Calbo2008}. Heinle et al.~\cite{Heinle2010} extracts several statistical features from pre-defined sky conditions and uses k-nearest neighbor classifier during the classification step. In order to exploit the textural information of the clouds, classical texture descriptors such as Scale-Invariant Feature Transform (SIFT)~\cite{SIFT} and Local Binary Patterns (LBP)~\cite{cloud_LBP} have been also exploited. Considering simplicity and efficiency, LBP and its variants have been used extensively~\cite{Liu2013,Zhang2016}. However, they cannot be an ideal technique in cloud classification task because of the inherent varying illumination conditions and dependency on camera parameters. Liu et al.\ \cite{Liu2012} has proposed a descriptor called Illumination-invariant Completed Local Ternary Pattern (ICLTP) for cloud classification tasks.

Most of the existing approaches in the literature use a combination of color and texture features, which make sense, as different cloud types can be categorized mainly based on these discriminatory cues. However, there is no rigorous experimental analysis on the efficacy of these features for such multi-class classification framework. We provide a systematic evaluation of different cloud features in Chapter~\ref{chap:classification}, and propose a complete framework for cloud type recognition in Singapore.

In most cases, collocated meteorological sensors are also present with sky cameras. Such scenario provides us ample opportunities to establish the connections between them. Weather sensors are point-devices that collects data for a particular point on the earth's surface. On the other hand, sky cameras equipped with wide-angled lenses provide us more information about the evolution of cloud. This motivates us to identify a few research problems and motivate us to develop techniques for a few intended applications---we will discuss such related works in the next Section~\ref{sec:lit-sensor} of this chapter.

\section{Meteorological Sensors \& Cameras}
\label{sec:lit-sensor}
In addition to ground-based sky cameras, the other meteorological sensors measuring solar radiation, precipitation, wind speed are used in tandem to provide a holistic analysis of various phenomena in earth's atmosphere. Ground-based meteorological sensors are mainly point devices that measures and records the various weather parameters at a particular location on earth's surface. However, collocated sky cameras can provide us more information about the evolution of clouds over a period of time. Therefore, it helps us to use these sky camera images to estimate and/or predict some of the weather parameters. It greatly helps the remote sensing analysts for application areas such as solar energy generation and study of cloud attenuation.

Firstly, meteorological sensors and cameras were extensively used in the field of solar energy generation. These sensors provide useful information about clouds---it is necessary as clouds have a significant impact on solar energy generation. The clouds intermittently block the sun and significantly reduce the solar irradiance reaching solar panels. A short-term forecast of the solar irradiance is needed for the grid operators to mitigate the effects of a power generation ramp-down. The daily variations in temperature, pressure and humidity, coupled with clear-sky model of solar radiation were used in the literature to estimate the instantaneous solar radiation. Several attempts have been done to estimate the solar radiation from general meteorological measurements viz.\ temperature, humidity and precipitation~\cite{HSmodel,DCmodel,BCmodel,Huntmodel}. These existing models aim to provide global solar radiation using different sensors. Recently, with the development of low-cost photogrammetric techniques, sky cameras are being deployed for such purposes. Alonso-Montesinos and Batlles used sky cameras to quantify the total solar radiation~\cite{alonso2015}. However, it could not model the sharp short-term variations of solar radiation.

Secondly, sky cameras can also be used to identify the onset of precipitation. In the literature, rainfall onset is studied mainly using long-term climate data. Rainfall measurements from weather stations are analyzed to detect hidden patterns, and subsequently used to predict the onset of precipitation~\cite{Farahmand2014}. Precipitation radar is also used to measure tropical rainfall with high accuracy~\cite{TRMM2002}. However, these studies are based on long-term rain forecasting. Recently, sky cameras have been used to estimate the clear sky intensity distribution~\cite{Nou2015}. To the best of our knowledge, no prior work have used sky cameras to detect rainfall onset.

And finally, sky cameras are regularly used to detect and predict future location of clouds. Cloud tracking is an essential task in the field of solar energy generation and forecasting. Traditionally, cloud tracking has been performed from satellite images for accurate weather prediction. Pioneer work of tracking involved detecting optical flow patterns in satellite images~\cite{trackingpioneer}. These flow patterns are useful to detect the evolution of several weather patterns. This can be seen in \cite{Sieglaff13}, where Sieglaff et al.\ fused data from satellites images, radar, and numerical models to understand the evolution of convective clouds. Very recently, estimation of cloud motion from sky cameras has been used in solar irradiance forecasting~\cite{Chow15,Chauvin2016}. This seamless cooperation of sensor data from various sources helps in creating robust frameworks and best practices for numerous applications. This is comparatively a new development in remote sensing, as most of the existing works are based on long-term climate statistics. We aim to complement such studies and establish new methodologies using sky cameras---more details are discussed later in Chapter~\ref{chap:solar} of this thesis.

Such application areas of solar energy forecasting also require a fair estimate of base height of cloud mass, along with predicting its future location. Most of the existing works use a pair of (or multiple) sky cameras for reconstructing cloud base. We discuss these existing works in the last Section~\ref{sec:lit-3D} of this chapter.

\section{Stereo Reconstruction}
\label{sec:lit-3D}
Estimating the precise localization of clouds in the atmosphere is required for several applications. The energy production of solar panels greatly depends on solar irradiance. Due to its intermittency, operators need a precise short-term forecast of the cloud coverage above solar panels to take preventive actions before a ramp-down. Similarly, air-to-ground or air-to-air communications through the atmosphere suffer from attenuation due to rain, clouds, atmospheric particles, and water vapor~\cite{site_diversity}. Accurate information about cloud formations along the signal path is key to better understanding these phenomena.

Several works in the literature have tried to address this task. Allmen and Kegelmeyer~\cite{allmen} compute cloud base height from a pair of whole sky imagers using correlation of images rectified by a pseudo-cartesian transformation and optical flow fields along successive images. Seiz et al.\ \cite{seiz} match points extracted  with F\"orstner and Harris operators from two different cameras with fish-eye lenses. They use least-squares matching and introduce a hierarchical pyramid-based approach based. Kassianov et al.\ \cite{kassianov} compute the overlapping area between two images from a pair of ground-based imagers using a merit function. They derive the height of the clouds from the size of this overlapping area, which results in one value per image pair. Peng et al.\ \cite{peng} use three total sky imagers for 3D cloud detection and tracking. They assume clouds have only planar motion vectors and define an objective function to be maximized based on both motion tracking and height estimation.

The concept of 3D scene flow is also widely used for such purposes. It was first introduced by Vedula et al.\ \cite{vedula1999three}. Popular methods for computing scene flow include Huguet and Devernay~\cite{Huguet07}, who couple optical flow and dense stereo matching via partial differential equations; Li and Sclaroff~\cite{Li200875}, who introduce probability distributions for optical flow and disparity; and Cech et al.\ \cite{cech}, who reduce the computational complexity using seed growing.

Reconstructing the base height of a cloud mass using stereo cameras is a challenging task. Conventional stereo reconstruction algorithms do not work well in these cases, as clouds are generally non-rigid and do not exhibit strong features. In our study, we propose a framework based on 3D scene flow technique to estimate cloud base height. In Chapter~\ref{chap:localize} of this thesis, we also analyze the localization performance in a multi-camera setup with finite pixel-width dimension.

\section{Summary}
In this chapter, we have presented an overview of the existing works of cloud imaging for various remote sensing applications. The detection of clouds in the sky/cloud images is one of the fundamental tasks in this field. Furthermore, for the purpose of weather monitoring and other applications, it is also necessary to classify the clouds into various types. Other tasks such as correlating images with weather sensors and reconstructing cloud-base height are necessary to understand the different phenomenon of the earth's atmosphere. In this chapter, we have identified the short-comings in the existing methods for these specific tasks. In the following chapters of this thesis, we will explore the contributions of our work in extensive details.

### 2018-07-16 misc/thesis-hardbound/Chapters/Chapter3.tex
Update 16/7/2018

\chapter{Whole Sky Imager}
\label{chap:wsi}

\lhead{Chapter 3. \emph{Whole Sky Imager}}

\section{Introduction}
Whole sky imagers are becoming popular amongst the research community for a variety of applications and domains, such as aviation, weather prediction, and solar energy. The resulting images are of higher resolution than what can be obtained from satellites. Furthermore, the upwards pointing nature of the camera makes it easy to capture low-altitude clouds. Therefore, they provide a useful complement to satellite images.

Several models of automatic whole sky imagers have been developed at the Scripps Institute of Oceanography, University of California, San Diego, with cloud detection in mind~\cite{WSI-history}. Yankee Environmental Systems commercialize the \emph{TSI-880}, which is used by many institutions~\cite{Long,Souza}. Those imagers provide a good starting point for cloud analysis, but their design and fabrication is controlled by a company, making specialized adaptations hard or impossible. Besides, those devices are expensive (around 30,000-35,000~US\$ for the \emph{TSI-880}) and use very low image resolution ($352\times288$)capturing devices. Those limitations encouraged us to build our own.

In this chapter, we propose three novel designs of a whole sky imager called \textbf{WAHRSIS} (Wide Angle High-Resolution Sky Imaging System). The first version of WAHRSIS consists of a sun-blocker that reduces the sun glare in the captured images. It uses mostly off-the-shelf components which are available on the market for an overall price of around 2,500~US\$. A simple overall design allows a home-made mounting of the various parts. The resulting images are of high resolution and can be used for various applications. In addition to this sun-blocked based design of WAHRSIS, we also propose two additional compact models of WAHRSIS. These compact models uses High-Dynamic-Range-Imaging (HDRI) techniques to reduce sun glare in captured images. The designs of these sky cameras are specifically catered to hot and humid weather conditions of Singapore. The hermetically sealed enclosure needs to operate at permissible temperature and humidity levels for proper functioning of the several electronic items, housed inside the enclosure.

\section{Outline of Our Contribution}

The main novel contributions of this chapter include:

\begin{itemize}
\item Design of low-cost, flexible and high resolution ground-based sky cameras;
\item Framework for spatial-, color- and luminance- calibration of sky cameras;
\end{itemize}

The rest of this chapter is organized as follows. We describe the general design of our imaging infrastructure in Section~\ref{sec:gen-design}. Section~\ref{sec:WSI-design} describes the mechanical designs of its three models: sun-blocker based model, actively-cooled model and passively-cooled model. We describe the various calibration processes in Section~\ref{sec:WSI-calibration}. Finally, the uses of HDRI imaging techniques are introduced in Section~\ref{sec:HDR-WAHRSIS}. Section~\ref{sec:WSI-conclude} concludes the chapter.

\section{General Design of WAHRSIS} 
\label{sec:gen-design}
Our WAHRSIS system essentially consists of a hermetically sealed box, a workstation and an imaging system. The sealed box is necessary to protect its different internal components from the outdoor weather conditions. It consists of a temperature and humidity control module, that helps in maintaining the internal working conditions of WAHRSIS. It also comprises a micro-computer that helps in controlling the various components of the sky imager. Different models of WAHRSIS have various sun-glare control mechanisms. The entire sky imaging system is connected to a remote server, that helps in archiving the captured images. A general system design of WAHRSIS is shown in Fig.~\ref{fig:sysDesign}.

\begin{figure}[htb]
\begin{center}
\includegraphics[clip,trim={0.3cm 2cm 0 0},width=0.8\textwidth]{systemDiagram.pdf}
\caption[General design of WAHRSIS.]{General design of WAHRSIS. The camera, workstation and the sealed mechanical box is used in real-time image acquisition, whereas offline image processing and visualization are performed in the remote server.\label{fig:sysDesign}}
\end{center}
\end{figure}

The WAHRSIS system captures images at regular intervals of time. This creates enormous amount of image data. Therefore, a centralized and an efficient storage system is required. We have thus setup a server for this purpose, as shown in Fig.~\ref{fig:serverclient}. It currently stores the sky images, as well as the weather station, radiosonde, human observation, ceilometer and weather radar measurements. Three WAHRSIS models and three weather stations are located at Nanyang Technological University, which are sending their measurements to this server in real time. The radiosonde data is retrieved twice a day from the website of the \emph{Department of Atmospheric Science (University of Wyoming)}.\footnote{\url{http://weather.uwyo.edu/upperair/sounding.html}.}

\begin{figure}[htb]
\begin{center}
\includegraphics[clip,trim={0.3cm 2.6cm 0 0},width=0.75\textwidth]{serverClient.pdf}
\caption[Server-client setup in WAHRSIS.]{Server and client setup for data storage and visualization.\label{fig:serverclient}}
\end{center}
\end{figure}

\section{WAHRSIS Design} 
\label{sec:WSI-design}
In this section, we describe the mechanical designs of three WAHRSISs. The sun-blocker based WAHRSIS model consists of a sun-tracking blob that tracks the position of sun over the period of the entire day. This helps in reducing the glare of the sun in the captured images. However, most part of the captured images get occluded by the sun-blocker. The other models of WAHRSIS do not use a sun-blocker in its design. Instead, it uses HDRI techniques to reduce sun-glare in the images. More details on the advantages of HDRI can be found in Section~\ref{sec:HDR-WAHRSIS}. The design of the various models of the sky cameras are kept as simple as possible. This is because we use off-the-shelf components to build the sky imagers, and it can be easily replicated by other enthusiasts, as a part of engineering design project~\footnote{The design of our sky camera is recently featured in `H.\ Godrich, Students' Design Project Series: Sharing Experiences [SP Education], IEEE Signal Processing Magazine, Jan 2017' as a part of student project series.}~\footnote{A tutorial to build the WAHRSIS Sky Imager with automated cloud coverage estimation is available online at \url{https://github.com/Soumyabrata/DIY-sky-imager}.}.

\subsection{Sun-blocker based WAHRSIS Model} 
\subsubsection{Components} 
\label{sec:components}

Figure~\ref{fig:MechDesgn} shows a drawing of the sun-blocker based WAHRSIS. Its main components are the following:
\begin{itemize}
\item The \emph{sun-blocker} occludes the light coming directly from the sun and thus reduces the glare in the circumsolar region of the captured image. It is composed of a main arm, which is rotated around the outside of the box by a motor. A polystyrene ball is fixed on top of a stem, which is attached to the main arm via a second motor rotating along the other axis. Details about estimating the position of sun at a particular location on earth are described in Appendix~\ref{append:sunposition}.
\item An \emph{Arduino board} controls the two motors of the sun blocker. The algorithm is briefly explained in the Appendix~\ref{append:motor}.
\item \emph{Outer casing:} A hermetically-sealed box prevents moisture and dirt from affecting the internal components. It contains a transparent dome at the top in which the fish-eye lens of the camera is positioned.
\item The \emph{camera and lens} is discussed in more detail in Section \ref{sec:camera} below.
\end{itemize}

\begin{figure}[htb]
\begin{center}
\includegraphics[width=0.6\textwidth]{SkelDesgn2.pdf}
 \caption{Schematic drawing of WAHRSIS.\label{fig:MechDesgn}}
\end{center}
\end{figure}

The device operates autonomously. However, some periodic manual maintenance interventions may be needed occasionally, for example to prevent the wear and tear of the motor gears. We have currently built and installed this on the roof-top of our university building. Table~\ref{cost} details all the components and their respective prices at the time of purchase.

\begin{table}[htbp]
\centering
\begin{scriptsize}
    \begin{tabular}{ | l | r |}
    \hline
    \textbf{Items} & \textbf{Cost (in US\$)} \\ \hline
    Arduino Mega & 90 \\ \hline
    Arduino Mega 2560-control board	& 60 \\ \hline
    Bipolar 5.18:1 Planetary Gearbox Stepper & 25 \\ \hline
    Bipolar 99.55:1 Planetary Gearbox Stepper & 35 \\ \hline
    Stepper Motor Driver & 20 \\ \hline
    Real Time Clock & 15 \\ \hline
    Big Easy Stepper Motor Driver & 30 \\ \hline
    12 V DC Power Supply & 50 \\ \hline
    Base Hard plastic or Acrylic (Water-proof housing) & 120 \\ \hline
    Plastic Dome & 25 \\ \hline
    Metal Arm & 50 \\ \hline
    Sun Blocker & 5 \\ \hline
    Cables and accessories & 40 \\ \hline
    Sigma 4.5 mm F2.8 EX DC HSM Circular Fisheye Lens & 950\\ \hline
    Canon EOS Rebel T3i (600D) camera body & 360 \\ \hline
    Alteration for near-infrared sensitivity & 300 \\ \hline
    Built-in laptop & 350 \\ \hline
    \textbf{Total Cost} & \textbf{2525} \\ \hline
    \end{tabular}
    \caption{Cost analysis for all the components of WAHRSIS.}
    \label{cost}
\end{scriptsize}
\end{table}

\subsubsection{Imaging System} 
\label{sec:camera}
The imaging system of WAHRSIS consists of a \emph{Canon EOS Rebel T3i} (a.k.a.~\emph{EOS 600D}) camera body and a \emph{Sigma 4.5mm F2.8 EX DC HSM} Circular Fisheye Lens with a field of view of $180$ degrees. It captures images with a resolution of $5184 \times 3456$ pixels. Due to the lens design and sensor size, the entire scene is captured within a circle with a diameter of approximately $2950$ pixels (see Figure \ref{fig:wb}). A custom program running on the built-in laptop uses the \emph{Canon Digital Camera SDK} to control the camera. Images can be automatically captured at regular time intervals, and the camera settings can be adjusted as needed.

The sensor of a typical digital camera absorbs near-infrared light quite effectively, so much that there is an infra-red blocking filter behind the lens. We had this filter physically removed and replaced by a piece of glass, which passes all wavelengths. The reasoning is that near-infrared light is less susceptible to attenuation due to haze~\cite{schaul2009color}, which is a common phenomenon in the atmosphere and especially around large cities. Haze consists of small particles in suspension in the air. Those have a scattering effect on the light whose incidence is modeled by Rayleigh's law, meaning that the intensity of the scattered light $E_s \sim E_0/\Lambda^4$, where $E_0$ is the intensity of the emitted light, and $\Lambda$ the wavelength of the light. We can thus reduce this effect by considering longer wavelengths, such as the ones in near-infrared. This model is however only valid for particles whose size is smaller than $\Lambda/10$. Most cloud consist of larger particles; their resulting scattering effect obeys Mie's law, which is wavelength-independent. For this reason, we expect our modified camera to provide us sharper images of cloud formations.

The sun-blocker-based WAHRSIS model provides us high resolution images of the sky scene. However, a significant portion of the captured image is occluded by the sun-blocker. In the subsequent sections, we present two models of WAHRSIS, that do not use sun-blocker in their designs. Instead, it uses HDRI techniques to reduce sun-glare in the captured images. More details about HDRI can be found later in Section~\ref{sec:HDR-WAHRSIS} of this chapter.

\subsection{Actively-cooled WAHRSIS Model}

\begin{figure}[htbp]
\centering
\begin{tikzpicture}
\begin{scope}[xshift=1.5cm]
    \node[anchor=south west,inner sep=0] (image) at (0,0) {\includegraphics[width=0.7\textwidth]{W3-open}};
    \begin{scope}[x={(image.south east)},y={(image.north west)}]
        \draw[->,black,dashed](0.3,0.9) -- (1.1,0.9) node[anchor=west,black] {(a)};
        \draw[->,black,dashed](0.8,0.77) -- (1.1,0.77) node[anchor=west,black] {(b)};
        \draw[->,black,dashed](0.1,0.6) -- (1.1,0.6) node[anchor=west,black] {(c)};
        \draw[->,black,dashed](0.2,0.3) -- (1.1,0.3) node[anchor=west,black] {(e)};
        \draw[->,black,dashed](0.8,0.45) -- (1.1,0.45) node[anchor=west,black] {(d)};
    \end{scope}
\end{scope}
\end{tikzpicture}%
\caption[Actively-cooled WAHRSIS design along with its different components.]{Actively-cooled WAHRSIS design. (a) DSLR camera, (b) dome, (c) ODROID board, (d) casing, (e) thermoelectric cooler with fans.}
\label{fig:W3-design}
\end{figure}

The actively-cooled WAHRSIS model consists of a hermetically-sealed plastic box with sunlight-reflecting paint on it, as shown in Fig.~\ref{fig:W3-design}. A thermoelectric Peltier cooler is placed at the bottom of the casing. When electricity is provided, the side facing inside the box gets cold while the outside face gets hot. Fans are placed at both sides to dissipate the cold or heat produced. The on-board computer controls the cooler operation using temperature and humidity sensors.

\subsection{Passively-cooled WAHRSIS Model} 
The passively-cooled WAHRSIS model consists of a ventilated casing made of galvanized steel, as shown in Fig.~\ref{fig:version2}. This material reflects the sun light well and prevents rusting and corrosion. Ventilation grids are placed on each side, allowing ambient air to flow inside while preventing rainwater from entering. A metallic sheet is placed a few centimeters on top of the box, along with the transparent dome for the camera lens. The air in between acts as insulator, which protects the case from being heated by direct sunlight. We refer this model as passively-cooled model, as we use only ambient air and ventilation to maintain its internal temperature and humidity, without using any external cooling devices.

\begin{figure}[htb]
\centering
\begin{tikzpicture}
\hspace{0.8cm}
\begin{scope}[xshift=1cm]
    \node[anchor=south west,inner sep=0] (image) at (0,0) {\includegraphics[width=0.7\textwidth]{WSI4}};
    \begin{scope}[x={(image.south east)},y={(image.north west)}]
        \draw[->,black,dashed](0.5,0.85) -- (1.1,0.85) node[anchor=west,black] {(a)};
        \draw[->,black,dashed](0.8,0.77) -- (1.1,0.77) node[anchor=west,black] {(b)};
        \draw[->,black,dashed](0.4,0.25) -- (1.1,0.25) node[anchor=west,black] {(c)};
        \draw[->,black,dashed](0.65,0.1) -- (1.1,0.1) node[anchor=west,black] {(d)};
    \end{scope}
\end{scope}
\end{tikzpicture}
\caption[Passively-cooled WAHRSIS design along with its different components.]{Passively-cooled WAHRSIS design. (a) Dome, (b) shelter, (c) air vent cover, (d) casing. }
\label{fig:version2}
\end{figure}

\section{WAHRSIS Calibration} 
\label{sec:WSI-calibration}
The images captured by WAHRSIS are of high resolution and capture the full sky hemisphere. However, the scene appears distorted by the fish-eye lens, and the colors are not rendered correctly due to the alteration for near-infrared sensitivity. Various calibration stages are thus required~\footnote{The source code of the various calibration processes for our sky camera WAHRSIS is available online at \url{https://github.com/Soumyabrata/WAHRSIS}.}. We discuss geometric calibration, white balancing and vignetting correction for our WAHRSIS models.

\subsection{White Balancing}
\label{sec:white_balancing}
The camera of sun-blocker based WAHRSIS is sensitive to near-infrared light and thus sees beyond the visible spectrum. Color calibration in the traditional sense is less meaningful for our camera, because it is sensitive to both visible and near-infrared light. However, white balancing is still necessary, as we will explain here.

The sensitivity of the various channels depends on the Bayer filter in front of the sensor. It is known that the red pixels show more near-infrared leakage than the blue or green ones. The automatic white balance settings were engineered for a non modified camera. As a result, images captured under an automatic white balance mode appear reddish, as shown in Fig.~\ref{fig:auto}. Fortunately, our camera also provides a custom mode. It relies on a known white patch in the scene, for which the camera computes the incident light intensity quantization parameters to render this patch white in the captured picture. The resulting image after custom white balancing looks visually plausible, as is shown in Fig.~\ref{fig:custom}.

\begin{figure}[htb]
\centering
\subfloat[\emph{Auto}\label{fig:auto}]{\includegraphics[height=0.27\textwidth]{wb1auto.pdf}}
\subfloat[\emph{Custom}\label{fig:custom}]{\includegraphics[height=0.27\textwidth]{wb8custom.pdf}}
\caption{Captured images using automatic and custom white balance settings.}\label{fig:wb}
\end{figure}

Without white balancing, the red channel of our camera is prone to over-saturation and color clipping due to the additional near-infrared light reaching the sensor. The red channel of Fig.~\ref{fig:auto} contains 24.5\% of clipped values (i.e. where $R=255$), whereas the same channel in Fig.~\ref{fig:custom} contains only 0.7\% of them. This shows the importance of the custom white balancing, which manages to compensate quite well for the near-infrared alteration.

The other models of WAHRIS do not use near-infrared sensitive lenses in its design. Therefore, we perform no color calibration on the actively-cooled- and passively-cooled- model of WAHRSIS.

\subsubsection{Chromatic Aberration} 
\label{sec:chromatic_aberration}

The refractive index of lenses is wavelength-dependent. This means that light rays from different parts of the spectrum converge at different points on the sensor. Chromatic aberration refers to the color distortions introduced to the image as a result of this phenomenon. Since the camera of sun-blocker based WAHRSIS is sensitive to near-infrared, a larger part of the light spectrum is captured by the sensor, making the device more prone to this issue. Figure~\ref{fig:example_chrom_aberr} shows chromatic aberration on an image captured by the camera.

\begin{figure}[htb]
\centering
\subfloat[Example of chromatic aberration. Notice the green and magenta artifacts at the edges of the squares.\label{fig:example_chrom_aberr}]{\includegraphics[height=0.35\textwidth]{example_chrom_aberr.pdf}}
\quad 
\subfloat[Difference between the calibration function of each color channel and the grayscale calibration function.\label{fig:difference_RGB}]{\includegraphics[height=0.35\textwidth]{difference_RGB.pdf}}
\caption{Example of chromatic aberration and calibration function}
\end{figure}

The calibration process described in the previous section uses grayscale images. In order to obtain more accurate calibration functions, we apply the same process on each of the red, green, and blue channels individually. As shown in Fig.~\ref{fig:difference_RGB}, we observe small differences in the resulting calibration functions, especially for the red channel. Visually, there is a striking difference in the color of the building for grayscale- and color-channel-specific- based calibration method. We show it in Fig.~\ref{fig:proj}.

\begin{figure}[htb]
\centering
\subfloat[Grayscale calibration.\label{fig:projBw}]{\includegraphics[width=0.35\textwidth]{undistort_result.pdf}}
\quad 
\subfloat[Color-channel-specific calibration.\label{fig:projDiffChannels}]{\includegraphics[width=0.35\textwidth]{undistort_result_chromm.pdf}}
\caption[Illustration to show the advantages of color-channel-specific calibration as compared to grayscale calibration.]{Section of an image taken with WAHRSIS that was rectified using grayscale (left) and color-channel-specific (right) calibration. The chromatic aberration in the right image is much less noticeable.}
\label{fig:proj}
\end{figure}

\subsection{Geometric Calibration} 
\label{sec:geometrical_calib}
A geometric calibration of the capturing device needs to be performed in order to obtain a precise model of the distortion introduced by the imaging system, which in our case includes the fish-eye lens and the dome~\cite{HUOJuan}. This consists of determining the intrinsic parameters of the camera, which relates the pixel coordinates with their 3D correspondences in a camera coordinate system. On the other hand, extrinsic parameters express the translations and rotations required to use other 3D world coordinate systems, such as the ones span by the checkerboard borders. Intrinsic parameters give all the information needed to relate each pixel of a resulting image with the azimuth and elevation angles of the incident light ray and vice-versa, which is essential to be able to measure the physical extent of clouds.

\subsubsection{Fisheye Lens Calibration Background} 
\label{sec:rel_studies}
The modeling of a typical (non-fisheye) camera uses the pinhole model. However, this is not applicable to our case because of the very wide capturing angle. A schematic representation of the refraction of an incident ray in a fisheye lens is shown in Fig.~\ref{fig:Fig6}. Most common approaches relate the incident angle ($\beta$) with the radius on the image plane ($r$) and the focal length ($\bar{f}$), assuming that the process is independent of the azimuth angle.

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=0.6\textwidth]{Fig6_v2.pdf}
\caption{Schematic representation of object space and image plane\label{fig:Fig6}}
\end{center}
\end{figure}

Several theoretical models relating those two values exist:

\begin{itemize}
\item Stereographic projection: $r=2\bar{f}\tan(\beta/2)$
\item Equidistance projection: $r=\bar{f}\beta$
\item Equisolid angle projection: $r=2\bar{f}\sin(\beta/2)$
\item Orthogonal projection: $r=\bar{f}\sin(\beta)$
\item Perspective projection: $r=\bar{f}\tan(\beta)$
\end{itemize}

Fisheye lens manufacturers usually claim to obey one of those, but those equations cannot be exactly matched in practice. However, they can be approximated by a polynomial due to the Taylor series theory. Some of the calibration techniques make use of this, as it easily allows a slight deviation from the projection equation. Two polynomial functions can also be used to cope with possible radial and tangential distortions caused by the lens.

Most calibration techniques use a checker-board with a known pattern. Shah et al.~\cite{shah1996intrinsic} introduce a calibration method where such a polynomial is used. Furthermore, they model radial and tangential distortions. The optical center of the camera has to be found using a low power laser beam, which is cumbersome in practice. Bakstein et al.~\cite{bakstein2002panoramic} use a spherical retina model, but do not provide any extrinsic parameter estimation technique and use cylindrical patterns. Sturm et al.~\cite{sturm2004generic} introduce a very generic model, where a camera is described by the coordinates of a set of rays and a mapping between those and the image pixels. However the authors experienced difficulties with a fish-eye lens, especially on the side view.  Kannala et al.~\cite{Kannala_calib} use polynomials to describe the calibration and the radial and tangential distortions, but they also assume that the positions of the pattern on the checker-board are known.  Finally, Scaramuzza et al.~\cite{scaramuzza2006toolbox} provide an algorithm estimating both intrinsic camera parameters and the extrinsic parameters describing the positions of the checker-board. They provide a full \emph{MATLAB} implementation of their method, making it the easiest to use.  We have chosen to use this method and enhanced it for our needs.

\subsubsection{Calibration Method} 
\label{sec:calibration_method}
The calibration toolbox proposed by Scaramuzza et al.~\cite{scaramuzza2006toolbox} takes as input a number of images containing a known checker-board pattern. The first step is corner detection, which is performed by the toolbox. User interaction is required when the automatic detection algorithm fails. Those points are then used to find the parameters by a least-squares linear minimization, followed by a non-linear refinement with a maximum likelihood criterion. The toolbox uses a polynomial to model the ray refraction as well as a $2 \times 2$ matrix transformation and a translation to cope with small axis misalignment and the digitizing process. The intrinsic parameters thus consist of both the coefficients of the polynomial as well as the values of the matrix and the translation parameters, which describe the position of the center of the image.

Figure~\ref{fig:calibration_images} shows a sample of the images we used for the calibration.

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=0.23\textwidth]{grid1.pdf}
\includegraphics[width=0.23\textwidth]{grid2.pdf}
\includegraphics[width=0.23\textwidth]{grid3.pdf}
\includegraphics[width=0.23\textwidth]{grid4.pdf}
\caption{Sample of the checker-board images used for the calibration\label{fig:calibration_images}}
\end{center}
\end{figure}

The toolbox also outputs the re-projection errors, i.e. the difference between the original point location computed during the corner detection and the one resulting from the estimated parameters. This is done on the same images as the ones used for the parameter estimation. However we noticed that the returned errors do not necessarily relate the quality of the calibration, as the re-projection sometimes looks more accurate than the corner detection or the user input in estimating the coordinates of a grid corner. Furthermore, we would like to estimate a general error which does not only rely on the location of the checker-boards in the images used for the fitting. We also observed that the choice of the input images has a significant influence on the output of the algorithm. We thus modified the calibration process in the following way: we randomly split our captured checker-board images into a training set of $10$ images and a validation set of $6$ images. We compute the parameters using the training set and the re-projection error using the validation set. We repeat this process $50$ times with different randomized splits and finally consider the parameters leading to the smallest error on the validation set as the most accurate one. In this way we can reduce the uncertainty of the whole process.

\begin{figure}[htbp]
\centering
\subfloat[Relationship between the incident angle of a light ray and the corresponding distance from the image center.\label{fig:calibration_results}]{\includegraphics[width=0.47\textwidth]{result_with_projections.pdf}}
\hspace{0.2cm}
\subfloat[Difference between equisolid model and our imaging system.\label{fig:diff_model_calib}]{\includegraphics[width=0.47\textwidth]{calibration_error.pdf}}
\caption{Result of the calibration process compared to the various theoretical projection models.}
\end{figure}

Our fish-eye lens (\emph{Sigma 4.5mm F2.8 EX DC HSM}) was designed by the manufacturer to follow the equisolid projection for visible light, but may be less accurate for the near-infrared spectrum. There is also a transparent dome on top of the camera lens, which may have an additional refracting effect on the incident rays. The toolbox models the calibration function as a polynomial and can thus incorporate these effects when fitting the coefficients.  We have set the maximum degree of the polynomial to $4$, as advised by the authors of the toolbox. We indeed noticed a bigger re-projection error with smaller degrees. However when the maximum degree is set to a higher number, the values of the coefficients of the degrees higher than $4$ are almost zero.

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=0.7\textwidth]{reprojection_error_bw_no_equisolid.pdf}
\caption[Re-projection errors as a function of the distance to the image center.]{Re-projection errors as a function of the distance to the image center (crosses: raw data; line: moving average).\label{fig:reprojection_error_bw}}
\end{center}
\end{figure}

Figure~\ref{fig:calibration_results} shows the result of the resulting calibration compared to the various theoretical projection models. Figure \ref{fig:diff_model_calib} shows the distance in pixels between our estimated calibration parameters and the various projection models. We see that we reach a distance of more than $16$ pixels for angles around $40$ degrees. We also find that the maximum viewing angle of the whole device is $178.7$ degrees, slightly less than hemispheric.

Figure~\ref{fig:reprojection_error_bw} shows the re-projection error for all the points of the grids in the validation set. A moving average with a window of $50$ pixels is also shown. The average re-projection error for our model is $3.87$ pixels. We can see a minor increase of the error with distance from the image center (and thus the elevation angle of the incident ray).

\subsection{Vignetting Correction}
\label{sec:intensity}

Vignetting refers to a darkening toward the corners of the image which is introduced during the capturing process. It has several origins. Natural vignetting is due to the incident light rays reaching the camera sensors with varying angles. It is commonly modeled by the cosine fourth law of the angle at which the light ray strikes the image sensor. The camera of WAHRSIS is particularly prone to this effect due to its wide angle. Optical vignetting describes the shading caused by the lens cylinder itself, blocking part of the off-axis incident light. This is aperture-dependant~\footnote{\url{http://toothwalker.org/optics/vignetting.html}}.

In most cases, it is difficult to model such vignetting function using the cosine forth law. It is however approximated by a higher-order polynomial function with respect to the radial distance of the fish eye image. We denote this radial distance as $r$, as introduced previously in Section~\ref{sec:geometrical_calib}. In a perfectly calibrated imaging system, the image center coincides exactly with vignetting center. However, in practice, there is a mismatch between the two.

Suppose the vignetting luminance of a pixel in a fish-eye lens image is denoted by $L_w$. In \cite{d2007radiometric}, d\`{}Angelo parameterized this luminance $L_w$ with respect to radial distance $r$ using a sixth-order polynomial:

\[L_w = \epsilon_1 r^6 + \epsilon_2 r^4 + \epsilon_3 r^2 + 1\],

where $\epsilon_1, \epsilon_2, \ldots$ are the polynomial fitting coefficients.

\begin{figure}[htb]
\begin{center}
\includegraphics[width=0.5\textwidth]{integrating_sphere.pdf}
\caption{Image captured inside the integrating sphere.\label{fig:sphere}}
\end{center}
\end{figure}

In order to analyze such vignetting phenomenon in our WAHRSIS system, we use an integrating sphere for our experiments. It consists of a large sphere, whose interior surface is made of a diffuse white reflective coating, resulting in a uniform light source over the whole surface. A Light-Emitting Diode (LED) light source as well as the camera are placed inside. Figure~\ref{fig:sphere} shows an image captured inside this sphere. Notice the higher brightness at the center. This image has been taken with the biggest available aperture ($\bar{f}/2.8$) and constitutes the worst case with regards to vignetting. Smaller aperture values will result in less significant distortions.

We plot the luminance value of the pixels in the fish-eye lens ($L_w$) with respect to the radius ($r$) of the image center~\footnote{For the sake of simplicity, we assume that the vignetting center and image center coincides in our system.}. Figure~\ref{fig:pro_distance} shows the luminance of the pixels inside the lens circle as a function of the distance from the image center.

\begin{figure}[htb]
\centering
\includegraphics[width=0.7\textwidth]{vig_distance.pdf}
\caption[Luminance as a function of the distance from the image center.]{Luminance as a function of the distance from the image center. The red line is the fitting equation $ L_w = -1.365 \times 10^{-5} r^2 - 0.004006 r + 235.8 $.}
\label{fig:pro_distance}
\end{figure}

We observe that the luminance of an uniformly-lit scene is perceived differently at different radial distances of the image. The luminance is highest near the center, and it radially drops off with increasing distance. We fit a second-degree polynomial function between the two. We obtain the fitting equation as:

\[L_w = \epsilon_1 r^2 + \epsilon_2 r + \epsilon_3 \],

where $\epsilon_1 = -1.365 \times 10^{-5}$, $\epsilon_2 = -0.004006$ and $\epsilon_3 = 235.8$ are the corresponding polynomial fitting constants.

In order to correct the luminance values, we normalize the obtained luminance values and then take their inverse. We fit a moving average and use this result as a radius dependent correction coefficient, as shown in Fig.~\ref{fig:coefficients}. We repeat this process for each aperture setting.

\begin{figure}[htb]
\centering
\includegraphics[width=0.7\textwidth]{vig_correction.pdf}
\caption{Correction coefficients in red and scatter plot of all the values in blue.}
\label{fig:coefficients}
\end{figure}

In this section, we discussed the various calibration processes that we perform in our WAHRSIS system. In the subsequent section, we will see how HDRI techniques can help in reducing sun-glare in (two of) our sky-camera models, and significantly simplify post-processing techniques.

\section{High Dynamic Range Imaging} 
\label{sec:HDR-WAHRSIS}
The conventional cameras cannot capture and render a wide range of the luminosity of a scene. On a typical sunny and clear day, it is difficult to capture the entire luminance range of the sky scene using a conventional camera. The region around sun has a luminous intensity several orders of magnitude higher than other parts of the scene. The ratio between the largest and the smallest luminance value of a scene is referred to as its Dynamic Range (DR). Typical cameras can only capture a Low Dynamic Range (LDR) image. Therefore, we use the exposure bracketing option of our cameras to capture three pictures at $0$, $-2$ and $-4$ exposure value (EV) in quick succession. The aperture remains fixed across all captured images, while the shutter speed automatically adapts to match the appropriate exposure. Figure~\ref{fig:ldr-input} shows an example of the captured images at varying exposure levels.

\begin{figure}[htb]
\centering
\includegraphics[width=0.3\textwidth]{wahrsis4-high}\hspace{0.5mm}    
\includegraphics[width=0.3\textwidth]{wahrsis4-med}\hspace{0.5mm} 
\includegraphics[width=0.3\textwidth]{wahrsis4-low}\hspace{0.5mm}\\
\makebox[0.3\textwidth][c]{(a)}
\makebox[0.3\textwidth][c]{(b)}
\makebox[0.3\textwidth][c]{(c)}
\caption[Example of three LDR images captured by sky camera.]{Example of three images captured by the camera at varying exposure levels and shutter speeds. (a) 0 EV, 1/400 sec. (b) -2 EV, 1/1600 sec. (c) -4 EV, 1/4000 sec.}
\label{fig:ldr-input}
\end{figure}

These LDR images are then fused together to generate a High-Dynamic-Range (HDR) image. A detailed discussion on the generation of HDR image is found in the subsequent section.

\subsection{HDR Image Generation}
\label{sec:HDR-discuss}

The different LDR images can be fused together into a single, high-dynamic-range radiance map. As their exposure times are known, we can compute the camera response curve of the imaging system using samples obtained from the different LDR images~\footnote{The source code to generate the camera response curve and other HDR imaging techniques are available online at \url{https://github.com/Soumyabrata/HDRCaptures}.}. We use Debevec and Malik's algorithm~\cite{DebevecHDR} to recover HDR radiance map from LDR images. This is shown in Fig.~\ref{fig:response-RGB}. The dynamic range of the resulting HDR radiance map is $15$ bits, which represents a significant improvement over the $8$-bit  LDR images.

\begin{figure}[htb]
\begin{center}
\includegraphics[width=0.55\textwidth]{exp-contri.pdf}
\caption{Response curve of the HDRI system, computed from three LDR images with different exposure settings.
}
\label{fig:response-RGB}
\end{center}
\end{figure}

This generated HDR radiance map cannot be viewed directly on a conventional LDR display. Therefore, we tone-map the HDR radiance map into a conventional $8$-bit LDR image using contrast-limited adaptive histogram equalization (CLAHE)~\cite{CLAHE}. We use CLAHE for this application because it involves a logarithmic transformation of the higher DR radiance map to a lower $8$-bit display. This produces a perceptually recognizable image, because response of human eye to light is also logarithmic. This operation compresses the dynamic range by preserving the details in the image. Figure~\ref{fig:tonemapped} shows an example of a tone-mapped image.

\begin{figure}[htb]
\centering
\includegraphics[width=0.5\textwidth]{wahrsis4-tonemapped}
\caption{Tone-mapped image computed with the pictures shown in Fig. \ref{fig:ldr-input}}
\label{fig:tonemapped}
\end{figure}

\subsection{Introducing HDRI techniques in sky cameras}
The actively-cooled and the passively-cooled WAHRSIS models do not have a physical sun blocking mechanism. Instead, we use HDRI techniques to reduce the over-exposure resulting from sun glare. This avoids occlusions from the sun-blocker and its support structure in the captured images (which significantly complicate subsequent computer vision tasks), while at the same time keeping the number of saturated pixels in the circumsolar region to a minimum.

The imaging system of these WAHRSIS models consists of the same imaging system as compared to our sun-blocker based WAHRSIS model. These imagers use an ODROID-C1 single board computer; with its 1.5 GHz processor and 1 GB RAM, this board is powerful enough to perform on-board image processing tasks.

We perform the HDR fusion and tone-mapping on a server that collects the images from all our WSIs. Since we have three imagers capturing one frame every $2$ minutes, we need algorithms which are computationally efficient. 
In that context, we use the GPU implementation of Aky\"uz \cite{akyuz2012high}. It relies on the OpenGL API to perform the entire HDR pipeline on the GPU. Computing a $18$ megapixels HDR image and its tone-mapped version takes less than 7 seconds, compared to a few minutes with standard CPU algorithms.

For storage efficiency, we use the \emph{JPEG-XT} format~\cite{jpegxt} to compress our HDR images\footnote{We use the reference software source code available at \url{https://jpeg.org/jpegxt/software.html}}. \emph{JPEG-XT} is an extension of \emph{JPEG} currently being developed for HDR images. The tone-mapped version is stored as a standard \emph{JPEG} image, while the inverse tone-mapping operation is added to the file as metadata. This allows for the HDR radiance map to be decoded.  Using \emph{JPEG-XT} at a quality level of $90$\%, we obtain a file size of about $8$~MB. The \emph{JPEG-XT} format is used to store the HDR images. An important advantage of \emph{JPEG-XT} format is that it is backward compatible to the popular \emph{JPEG} compression technique. It consists of a base layer that is compatible with the legacy systems and an extension layer that provides the full dynamic range. This represents a significant improvement compared to the common \emph{RGBE} format, which uses $50$MB per image by storing every pixel with one byte per color channel and one byte as a shared exponent.

We use such HDR imaging techniques instead of using RAW images. There are compelling trade-offs in choosing either HDR or RAW images. HDR images uses a set of Low Dynamic Range (LDR) images to compute the HDR radiance map; and we can access the 0EV LDR image which is needed for subsequent analysis. The size of an LDR image is approximately 2-3MB per image. On the other hand, the entire dynamic range of the sky scene can be captured using a single RAW image. However, the size of a conventional RAW image is approximately 18MB per image. Therefore, because of operational issues, we have chosen to use exposure bracketed LDR images, instead of capturing in RAW mode. In the future designs, we can consider using only RAW mode while capturing the sky/cloud images. In the upcoming Chapter~\ref{chap:segmentation} of this thesis, we discuss how HDRI techniques can improve cloud segmentation algorithms, especially around circumsolar region.

As a final comparison, we compare the images obtained from the different models of our sky camera. 
Figure~\ref{fig:sun-blocking}(c) shows the resulting image, along with those obtained from a sky imager with a mechanical sun blocker and a normal single-exposure image. In order to visualize the efficacy of our proposed approach, we zoom-in on the circumsolar region in each of the three images to look at the amount of detail visible around the sun. Although the sun-blocker is effective at reducing sun glare, the occlusion is significant. Without a sun-blocker, the number of saturated pixels is very high in a normal single-exposure image. Fusing multiple exposures into an HDR image is indeed a good solution for minimizing the effects of over-exposure.

\begin{figure}[htb]
\begin{center}
\subfloat[With sun blocker]{\includegraphics[height=0.32\columnwidth]{IB-rect.pdf}}
\subfloat[Auto exposure]{\includegraphics[height=0.32\columnwidth]{J1-rect.pdf}}
\subfloat[With HDR imaging]{\includegraphics[height=0.32\columnwidth]{TM-rect.pdf}}\\
\vspace{-2.5mm}
\subfloat{\includegraphics[height=0.33\columnwidth]{IB-mask.pdf}}
\subfloat{\includegraphics[height=0.33\columnwidth]{auto-mask.pdf}}
\subfloat{\includegraphics[height=0.33\columnwidth]{HDR-mask.pdf}}
\caption[Effect of sun glare with different strategies for sun occlusion.]{Effect of sun glare with different strategies.  The white rectangle outlines the circumsolar region, which is enlarged in the bottom row. Saturated pixels are shown in pink.
\label{fig:sun-blocking}}
\end{center}
\end{figure}

Unlike our sky imagers, the commercial sky imagers have a low image resolution of $352\times288$. Moreover, the total cost is high too (US\$30-35K). Also, no HDRI techniques are present in the commercial imager. We employ HDRI techniques in our imager, that helps us in building more compact versions of sky cameras.
A more detailed discussion on HDRI techniques, and how they solve cloud segmentation problems in circumsolar region will be discussed later in this thesis in Chapter~\ref{chap:segmentation}. Most of our works are performed in LDR images, unless otherwise stated.

\section{Conclusions} 
\label{sec:WSI-conclude}
In this chapter, we have presented WAHRSIS - a new custom-built whole sky imager. Its advantages are low cost and simple design. We presented three models of WAHRSIS: sun-blocker based model, actively-cooled model and passively-cooled model. We described its components and the calibration of its imaging system. Our imager provides high resolution images of the whole sky hemisphere, which can be useful for many various applications, as indicated in the subsequent chapters.

Unlike our sun-blocker based model, the remaining two models does not use a mechanical sun blocker. Instead, they rely on the fusion of multiple exposures to create a high-dynamic-range image and minimize over-saturation of pixels near the circumsolar region. Table~\ref{tab:diff-WAHRSIS} summarizes the various characteristics of the different models of WAHRSIS.

\begin{table}[htb]
\small
\centering
\begin{tabular}{ |l|p{3cm}|p{3cm}|p{3cm}| }
\hline 
WAHRSIS Properties  & \textbf{Sun-blocker model} &  \textbf{Actively-cooled model} & \textbf{Passively-cooled model} \\
\hline \hline
Glare reduction method & Sun blocker & HDRI & HDRI  \\ \hline
Occlusion severity & Moderate & Nil & Nil \\ \hline 
Weatherability  & Limited & Good & Good \\ \hline
Portability  & Limited & Good  & Good \\ \hline
Image resolution  & High & High  & High \\ \hline 
Total cost (in US\$)& \$2525  & \$1895 & \$1769  \\ \hline
\end{tabular}
\caption{Comparison of the different WAHRSIS models.}
\label{tab:diff-WAHRSIS}
\end{table}

We use the captured images for sky/cloud segmentation and classification into different cloud types. Moreover, we deploy multiple sky cameras in order to estimate cloud base height.

### 2018-07-16 misc/thesis-hardbound/Chapters/Chapter4.tex
Update 16/7/2018

\chapter{Color Space Analysis for Cloud Detection}
\label{chap:colorchannels}

\lhead{Chapter 4. \emph{Color Space Analysis for Cloud Detection}}

\section{Introduction}

The most fundamental problem in cloud imaging is the successful detection of clouds in the captured sky/cloud images. The detection of clouds from sky images is challenging as clouds do not possess any definite structure, contour, shape, or size. As a result, color has been used as the predominant feature for sky/cloud segmentation. Numerous techniques based on different color models and spectral wavelengths have been proposed in the literature to solve this problem. However, the selection of color models and channels in the existing algorithms seem ad-hoc in manner, without systematic analysis or comparison.  This chapter aims to address this issue by providing a structured review and evaluation of color models for the segmentation of sky/cloud images.  For this purpose, we make use of several tools and techniques. Our comprehensive analysis is able to clearly identify the most suitable color models and components for the analysis of cloud/sky images. The analysis in this chapter is limited to Low-Dynamic-Range (LDR) images only.

\section{Outline of Our Contribution}

The main novel contributions of this chapter include:

\begin{itemize}
\item Structured and systematic analysis of various color channels in sky/cloud images using various statistical tools such as color distribution characteristics, principal component analysis (PCA), rough-set based feature selection and clustering methods;
\item Proposal of a rough-set based method that can accurately assess the efficiency of different color channels for cloud segmentation. To the best of our knowledge, our proposed approach is the first that uses rough set theory for color channel selection in visible-light images. 
\end{itemize}

The rest of this chapter is organized as follows. Section~\ref{sec:colorchannels} describes the different color spaces and components that are used for detection of clouds in ground-based sky/cloud images. We introduce the different statistical tools in Section~\ref{sec:approachtools} that are exploited to identify the most discriminatory color channels. In Section~\ref{sec:rset-approach}, we propose a rough-set based color channel selection method. Experimental results are discussed and analyzed in Section~\ref{sec:chap4-exp}. Finally, Section~\ref{sec:chap4-conclude} concludes this chapter.

\section{Color Models for Sky/Cloud Images}
\label{sec:colorchannels}

In the literature, several techniques based on different color models have been proposed for sky/cloud segmentation. Long et al.\  \cite{Long} use the ratio of red and blue channels ($R/B$) to detect clouds using appropriate threshold values. Calb{\'{o}} and Sabburg~\cite{Calbo2008} use the same ($R/B$) ratio to derive statistical features (mean, standard deviation, entropy etc.) of the clouds and subsequently classify the sky/cloud images into different cloud types. Heinle et al.\ \cite{Heinle2010} utilize a k-nearest-neighbor classifier using the difference of red and blue channels ($R-B$) to classify cloud types. Souza-Echer et al.\ \cite{Souza} choose saturation for the estimation of cloud coverage. Mantelli-Neto et al.\ \cite{Sylvio} classify clouds by exploiting the locus of pixels in the RGB color model. Most recently, Li et al.\ use a normalized difference of blue and red channels ($\frac{B-R}{B+R}$~\cite{Li2011} for cloud detection.

The choices of color models employed in existing literature are based on empirical observations about the color distributions of cloud and sky pixels.  However, there exists no systematic analysis to determine the most suitable color channel(s) for this purpose. The purpose of this chapter is to present a unified approach in the analysis of sky/cloud images using different color channels and to identify the color channels with the best results~\footnote{The source code of our color channel analysis on sky/cloud images is available online at \url{https://github.com/Soumyabrata/color-channels}.}.

We consider the following color spaces and components for analysis (see Table~\ref{ps}): $RGB$, $HSV$, $YIQ$, CIE $L^{*}a^{*}b^{*}$, three forms of red-blue combinations ($R/B$, $R-B$, $\frac{B-R}{B+R}$), and chroma $C=\mbox{max}(R,G,B)-\mbox{min}(R,G,B)$. In addition to the color channels $c_{1-9}$ and $c_{13-16}$ used in the existing literature, we also include $c_{10-12}$ and $c_{16}$, as separating chromatic and achromatic information may prove beneficial for sky/cloud image segmentation. All the color channels are normalized.

\begin{table}[htbp]
\normalsize
\centering
\setlength{\tabcolsep}{4pt} % default: 6pt
\begin{tabular}{c|c||c|c||c|c||c|c||c|c||c|c}
  \hline
  $c_{1}$ & R & $c_{4}$ & H & $c_{7}$ & Y & $c_{10}$ & $L^{*}$ & $c_{13}$ & $R/B$ & $c_{16}$ & $C$\\
  $c_{2}$ & G & $c_{5}$ & S & $c_{8}$ & I & $c_{11}$ & $a^{*}$ & $c_{14}$ & $R-B$& $ $ & $ $\\
  $c_{3}$ & B & $c_{6}$ & V & $c_{9}$ & Q & $c_{12}$ & $b^{*}$ & $c_{15}$ & $\frac{B-R}{B+R}$ & $ $ & $ $\\
  \hline
\end{tabular}
\caption{Color spaces and components used for analysis.}
\label{ps}
\end{table}

Figure~\ref{fig:objective} illustrates the $16$ color channels of a sample sky/cloud image.

\begin{figure}[htbp]
\centering
\makebox[0.1\textwidth][c]{\hspace{-1mm}\tiny{Input Image}}
\makebox[0.1\textwidth][c]{$c_1$}
\makebox[0.1\textwidth][c]{$c_2$}
\makebox[0.1\textwidth][c]{$c_3$}
\makebox[0.1\textwidth][c]{$c_4$}
\makebox[0.1\textwidth][c]{$c_5$}
\makebox[0.1\textwidth][c]{$c_6$}
\makebox[0.1\textwidth][c]{$c_7$}
\makebox[0.1\textwidth][c]{$c_8$}\\    
\vspace{0.5mm}
\includegraphics[width=0.1\textwidth]{B1.pdf}
\includegraphics[width=0.1\textwidth]{c1.pdf}
\includegraphics[width=0.1\textwidth]{c2.pdf} 
\includegraphics[width=0.1\textwidth]{c3.pdf}   
\includegraphics[width=0.1\textwidth]{C4-inv.pdf}
\includegraphics[width=0.1\textwidth]{C5-inv.pdf}
\includegraphics[width=0.1\textwidth]{c6.pdf}
\includegraphics[width=0.1\textwidth]{c7.pdf}
\includegraphics[width=0.1\textwidth]{c8.pdf}\\
\vspace{1mm}
\includegraphics[width=0.1\textwidth]{B1_GT.pdf}
\includegraphics[width=0.1\textwidth]{C9-inv.pdf}
\includegraphics[width=0.1\textwidth]{c10.pdf}
\includegraphics[width=0.1\textwidth]{c11.pdf} 
\includegraphics[width=0.1\textwidth]{c12.pdf}
\includegraphics[width=0.1\textwidth]{c13.pdf}
\includegraphics[width=0.1\textwidth]{c14.pdf}
\includegraphics[width=0.1\textwidth]{C15-inv.pdf}
\includegraphics[width=0.1\textwidth]{C16-inv.pdf}\\
\makebox[0.1\textwidth][c]{\hspace{-2mm}\tiny{Ground Truth}}
\makebox[0.1\textwidth][c]{$c_9$}
\makebox[0.1\textwidth][c]{$c_{10}$}
\makebox[0.1\textwidth][c]{$c_{11}$}
\makebox[0.1\textwidth][c]{$c_{12}$}
\makebox[0.1\textwidth][c]{$c_{13}$}
\makebox[0.1\textwidth][c]{$c_{14}$}
\makebox[0.1\textwidth][c]{$c_{15}$}
\makebox[0.1\textwidth][c]{$c_{16}$}
\caption[Visual representation of $16$ color channels for a sample sky/cloud image.]{Sample image and segmentation mask from the HYTA database~\cite{Li2011}, together with the $16$ color channels from Table~\ref{ps} (the color maps for $c_4$, $c_5$, $c_9$, $c_{15}$, and $c_{16}$ are inverted such that cloud pixels always have a lighter shade than sky pixels).}
\label{fig:objective}
\end{figure}

\section{Approach and Tools}
\label{sec:approachtools}
\subsection{Color Distribution}
\label{sec:PBI}
Since we are essentially trying to distinguish between two classes of pixels (sky and clouds), a color model with a bimodal distribution can facilitate this task.  Color components with a high degree of bimodality are not only good candidates for determining the number of clusters in a sample image, but can also be used to decide whether or not the sample image requires segmentation in the first place. Pearson's Bimodality Index (PBI) is a popular statistic to evaluate the bimodal behavior quantitatively~\cite{pearson}. It is defined as:

\begin{equation}
\label{eq:pbi_defn}
\mbox{PBI}= b_2-b_1,
\end{equation}
where $b_{2}$ is the kurtosis and $b_{1}$ is the square of skewness.  A PBI value close to $1$ indicates a highly bimodal distribution.

\subsection{Principal Component Analysis}
\label{sec:PCA}
We use the Principal Component Analysis (PCA) to (a) check the correlation and similarity between different color components, and (b) determine those color components that capture the greatest variance.

The PCA is computed as follows.  Let us assume a sample image $\textbf{X}_{i}$ of dimension $m \times n$ pixels from a set of $N$ images ($i=1,...,N$).  Each color channel of the sample image is reshaped into a straight vector $\textbf{c}_{j}$ of dimensions $mn \times 1$. These column vectors are stacked alongside each other to form a matrix $\hat{\textbf{X}_{i}}$ of dimensions $mn \times 16$:
\begin{equation}
\label{eq:eq1}
\hat{\textbf{X}_{i}}=[\textbf{c}_{1}, \textbf{c}_{2},..,\textbf{c}_{j}..,\textbf{c}_{16}] ; j=1,...,16
\end{equation}

The ranges of these $16$ color channels are different and need to be normalized so that no color channel is under- or over-represented in the PCA analysis. Each of the $16$ color channels is normalized using its mean and standard deviation across all the images in the dataset, thereby generating the new image representation $\ddot{\textbf{X}_{i}}$ with zero mean and unit variance:

\begin{equation}
\label{eq:eq3}
\ddot{\textbf{X}_{i}}= [\frac{\textbf{c}_{1}-\bar{c_{1}}}{\sigma_{c_{1}}}, \frac{\textbf{c}_{2}-\bar{c_{2}}}{\sigma_{c_{2}}},..,\frac{\textbf{c}_{j}-\bar{c_{j}}}{\sigma_{c_{j}}},..,\frac{\textbf{c}_{16}-\bar{c_{16}}}{\sigma_{c_{16}}}],
\end{equation}

where $\bar{c_{j}}$ and $\sigma_{c_{j}}$ are the mean value and standard deviation of the $j$-th color channel.

Subsequently the covariance matrix $\textbf{M}_{i}$ is computed for each of the $\ddot{\textbf{X}_{i}}$. Let the eigenvector $\textbf{e}_{ij}$ and eigenvalue $\lambda_{ij}$ ($j=1,...,16$) be obtained from the eigenvalue decomposition of the matrix $\textbf{M}_{i}$. For the $i^\textrm{th}$ image, the eigenvectors $\textbf{e}_{ij}$ corresponding to the largest eigenvalues $\lambda_{ij}$ encompass an orthonormal vector subspace. The eigenvectors and eigenvalues are calculated to project the multi-dimensional vector space into lower dimensions and to reveal the underlying relationship amongst them.

\subsection{Discrimination Threshold}
\label{sec:bimodality}
In addition to principal component analysis, we also use the Receiver Operating Characteristics (ROC) curve~\cite{ROC_main,microarray-ROC} to identify the important color components in sky/cloud image segmentation. The ROC curve represents the fraction of true positives and false positives samples in the sky/cloud binary classification problem for varying values of discrimination threshold. The area between this ROC curve and the random classifier slope is widely used as a measure for the discriminatory performance in a classification framework.

We consider the set of $16$ color components and compute the area under the ROC curve for each, which is subsequently used to identify the best color components for sky/cloud segmentation.

\subsection{Clustering}
\label{sec:cloudcluster}
For clustering the sky/cloud images, we employ the fuzzy c-means algorithm~\cite{Bezdek,Jawahar} to assign probabilities of cloud detection to the set of pixels of the input image. The algorithm for the effective segmentation of clouds from the sky/cloud images employs the minimization of the following objective function:

\begin{equation}
\label{eq:eq4}
J = \sum\limits_{n_c=1}^{2} \sum\limits_{l=1}^{mn} p(\mathbf{x}_{f})^{\tau}d(\mathbf{x}_{f},\mathbf{v}_{r}),
\end{equation}

where $\tau$ is called the fuzziness index which controls the degree of fuzziness during the clustering process, and $n_c$ is the number of clusters. In our experiments, we set $\tau=2$ and $n_c=2$ clusters (binary segmentation). The term $d(\mathbf{x}_{f},\mathbf{v}_{n_c})$ denotes the 2D Euclidean norm between the input feature vector $\mathbf{x}_{f}$ and the cluster centers $\mathbf{v}_{n_c}$. Both $\mathbf{v}_{1}$ and $\mathbf{v}_{2}$ are vectors of dimension $o$, where $o$ can take any positive integer number.

\subsection{Kullback-Leibler Divergence}
Information-theoretic measures like Kullback-Leibler (KL) distance or divergence are also widely used for band selection purposes, especially in hyperspectral imaging~\cite{InfoTheory_TGRS}. This distance can be interpreted as the amount of dissimilarity of the color channel from the ground truth. In other words, a higher distance indicates an unfavorable color channel for cloud segmentation. Therefore, we also compute the KL-divergence of the color channels from the binary ground truth images.

In this section, we introduced the various statistical tools for a systematic analysis of color channels. However, these techniques had certain shortcomings with regards to ranking color channels according to their relevance for cloud detection. In the subsequent section, we will propose a \emph{rough-set} based approach that provides better results.

\section{Rough Set Based Color Channel Selection}
\label{sec:rset-approach}
Classical rough sets~\cite{Pawlak92} are an approximation of conventional sets in set theory. In a scenario where it is difficult to define the boundaries of a conventional set, rough set theory provides a set of mathematical tools to  define them in a approximate way. It facilitates an objective analysis in a data-driven system which is vague, uncertain and incomplete. Here we first explain the related terminologies of rough sets, and subsequently define the use of rough sets for visible-light images.

\subsection{Rough Set Theory}
In rough sets, information is expressed in the form of a \emph{decision table}. We define a decision table $\mathcal{L}$ such that each row represents an observation, and each column is an attribute from attribute set  $\mathcal{A}$. This non-empty set of observations is usually referred to as the \emph{universe} $\mathcal{U}$.
Formally, for each entry in the decision table, we define the function $f$ that maps attribute $\mathcal{A}$ to value domain $\mathcal{V}$, $f: \mathcal{U} \times \mathcal{A} \rightarrow \mathcal{V}$.

Any reduct $\mathcal{P}$ from the set of attributes $\mathcal{A}$ satisfies the indiscernibility (or  equivalence) relation IND($\mathcal{P}$). For any reduct $\mathcal{P} \in \mathcal{A}$, the $\mathcal{P}$-indiscernibility relation is defined as:

\begin{align}
\label{eq:p-ind}
\mbox{IND}(\mathcal{P}) = \{(x_s,x_t) \in \mathcal{U}^2 | \forall a \in \mathcal{P}, f(x_s,a) = f(x_t,a)\},
\end{align}

where $x_s$ and $x_t$ are two observations from the universe $\mathcal{U}$, and $a$ is an element from set $\mathcal{P}$. This indicates that $x_s$ and $x_t$ are indiscernable based on the attribute $\mathcal{P}$, as the value function $f$ assigns both $x_s$ and $x_t$ to the same value. This partition of $\mathcal{U}$ generated by IND($\mathcal{P}$) is denoted as:

\begin{align}
\label{eq:p-part}
\mathcal{U}/\mbox{IND}(\mathcal{P}) = \{[x_s]_{\mathcal{P}} | x_s \in \mathcal{U}\}.
\end{align}

Let $\mathcal{X}$ be a set of observations from the universe $\mathcal{U}$. Rough set theory asks the question: how can we express this conventional set $\mathcal{X}$, using only the information in attribute set $\mathcal{P}$? In general, there is no precise answer, and therefore approximations are generated. They are defined by their corresponding $\mathcal{P}$-\emph{lower}- and $\mathcal{P}$-\emph{upper}-approximations as:

\begin{subequations}
\label{eq:low-upp}
\begin{equation}
\underline{\mathcal{P}}(\mathcal{X}) = \cup \{[x_s] | [x_s] \subseteq \mathcal{X}\},
\end{equation}    
\begin{equation}
\overline{\mathcal{P}}(\mathcal{X}) = \cup \{[x_s] | [x_s] \cap \mathcal{X} \neq \phi\}.
\end{equation}
\end{subequations}

The observations in the lower approximation set $\underline{\mathcal{P}}(\mathcal{X})$ are the definite members of $\mathcal{X}$, also called the \emph{positive} region $\mbox{POS}(\mathcal{X})$. On the other hand, $\overline{\mathcal{P}}(\mathcal{X})$ represents the upper approximation of the set. It denotes the possible members of $\mathcal{X}$, based on the knowledge in the decision table. 
We illustrate this in Fig.\ref{fig:rs-illus}.

\begin{figure}[htbp]
\centering
\begin{tikzpicture}
\hspace{0.8cm}
\begin{scope}[xshift=1cm]
    \node[anchor=south west,inner sep=0] (image) at (0,0) {\includegraphics[width=0.5\textwidth]{rd-fig.pdf}};
    \begin{scope}[x={(image.south east)},y={(image.north west)}]
        \draw[->,black,dashed](0.6,0.75) -- (1.1,0.75) node[anchor=west,black] {$\overline{\mathcal{P}}(\mathcal{X})$};
        \draw[->,black,dashed](0.63,0.49) -- (1.1,0.49) node[anchor=west,black] {$\mathcal{X}$};
        \draw[->,black,dashed](0.53,0.3) -- (1.1,0.3) node[anchor=west,black] {$\underline{\mathcal{P}}(\mathcal{X})$};
    \end{scope}
\end{scope}
\end{tikzpicture}
\caption[Pictoral illustration of different rough-set terminology.]{Illustration of a typical rough set, which approximates a conventional set (depicted in blue). Each individual grid depicts a partition of the universe generated by an equivalence relation. The union of all such partitions indicated with solid green borders (definite members) represents the \emph{lower approximation}; while the dotted red borders (possible members) represent the \emph{upper approximation}.}
\label{fig:rs-illus}
\end{figure}

Let us assume that the attribute set $\mathcal{A}$ consists of both condition and decision attributes $\mathcal{C}$ and $\mathcal{D}$ respectively, such that $\mathcal{A} = \mathcal{C} \cup \mathcal{D}$. The \emph{relevance} criterion is defined as the dependence between $\mathcal{C}$ and $\mathcal{D}$, and can be expressed as:

\begin{align}
\label{eq:rel-defn}
\gamma_\mathcal{C}(\mathcal{D}) = \frac{|\mbox{POS}_\mathcal{C}(\mathcal{D})|}{|\mathcal{U}|},
\end{align}

where |$\cdot$| denotes the cardinality of the set. This dependence value is an important measure to identify the most discriminate attribute from set $\mathcal{A}$. The value of $\gamma_\mathcal{C}(\mathcal{D})$ ranges between $0$ and $1$, where $0$ indicates independence and $1$ indicates $\mathcal{D}$ fully depends on $\mathcal{C}$.

\subsection{Proposed Rough-Set Based Selection Method}
We now describe the problem of color channel selection using rough set terminology and propose our algorithm for this purpose~\footnote{The source code of our proposed rough-set based algorithm is available online at \url{https://github.com/Soumyabrata/rough-sets}.}. The main benefit of using rough set theory is that it provides a systematic method to approximate the segmentation ground truth, with the highest degree of approximation. Moreover, no prior information about the data is needed for the analysis.

We consider $16$ color channels in our analysis, as shown in Table~\ref{ps} and  illustrated in Fig.~\ref{fig:objective}.  We utilize rough set theory to identify the most \emph{informative} color channel(s) (a.k.a.\ reducts) from these $16$.

Suppose that $\mathcal{U}_i$ is a non-empty finite universe of pixel observations for a single sky/cloud image $\mathbf{X}_i$ from the image dataset $\mathcal{T}=\{\mathbf{X}_1,\mathbf{X}_2, \ldots, \mathbf{X}_N\}$. We assume that $\mathbf{Y}_{i}$ is the binary ground-truth image of the sample image $\mathbf{X}_{i}$. 
We define $\mathcal{A}_i$ as the set of its corresponding vectorized color channels \{$\mathbf{c}_1$, $\mathbf{c}_2$, \ldots, $\mathbf{c}_{16}$\} for a particular image $\mathbf{X}_i$, along with the vectorized decision attribute $\mathbf{y}_i$. These $16$ color channels are called condition attribute sets, and one ground truth vectorized image is the decision attribute set from the family of attributes $\mathcal{A}_i$.

We define a decision table $\mathcal{L}_i$ such that each row represents a pixel, and each column represents an attribute. 
Thus, for a single image $\mathbf{X}_i$, the function $f$ assigns a value $v_i^{kj}$ in the value domain to each variable-attribute pair ($q_k$,$a_j$), where $q_k$ is the $k$-th pixel value of the image and $a_z$ is the $z$-th attribute from the set $\mathcal{A}_i$. For the sake of brevity, we will drop the index $i$ in the subsequent discussions of this chapter.

Our objective is to characterize the ground-truth image $\mathbf{y}$ from the knowledge of the reduct $\mathcal{P}$. We define the reduct $\mathcal{P}$ as the subset of condition attribute sets $\mathcal{C}$.

We are interested in identifying the most discriminative color channel that is strongly dependent on the sky/cloud decision attribute $\mathbf{y}$. This dependence on a particular color channel is measured by the corresponding \emph{relevance} criterion of the color channels. Color channels with a high relevance value are better candidates for sky/cloud segmentation.

In analogy to Eq.~(\ref{eq:rel-defn}), we define the relevance criterion $\gamma_j$ for each color channel $\mathbf{c}_j$, which indicates the dependence between ground truth $\mathbf{y}$ and color channels:

\begin{align}
\label{eq:rel}
\gamma_j = \frac{|\mbox{POS}(\mathbf{y})|}{|\mathcal{U}|}.
\end{align}

For image $\mathbf{X}_i \in {\rm I\!R}^{m \times n}$, we generate the decision table $\mathcal{L}_i \in {\rm I\!R}^{mn \times 17}$. Each row of the decision table $\mathcal{L}_i$ corresponds to a pixel. The first $16$ columns represent the color channels, and the $17^\mathrm{th}$ column corresponds to the ground truth label. We generate $16$ distinct partitions from this decision table using the knowledge of the ground truth labels. Subsequently, the corresponding lower approximations of $16$ color channels are generated using Eq.~(\ref{eq:low-upp}). In fact, this lower-approximation set is the union of all partitions (generated by the equivalence relation) that are possible members of the \emph{cloud} label. Next, we compute the relevance value $\gamma_j$ of all color channels for the image $\mathbf{X}_i$ using Eq.~(\ref{eq:rel}).

We perform this for all images of dataset $\mathcal{T}$. Finally, we compute the average relevance $\overline{\gamma}_j$ of each color channel across all the images. The color channel with the maximum average relevance value $\overline{\gamma}_j$ is the best amongst all color channels under consideration.

\section{Experiments}
\label{sec:chap4-exp}
\subsection{Dataset}
\label{sec:introduceHYTA}
In order to analyze the various statistical approaches and check the efficacy of our proposed color channel selection algorithm, we conduct experiments on a publicly available sky/cloud image database called HYTA~\cite{Li2011}.

It consists of $32$ distinct images with different sky/cloud conditions along with their binary ground-truth segmentation masks. These images are collected from two main sources, namely ground-based sky cameras located at Beijing and Conghua, China. These sky cameras were developed by the Institute of Atmospheric Sounding at the Chinese Academy of Meteorological Sciences. The obtained images are stored in \emph{JPEG} format. No radiometric calibration data are available for this dataset. Additionally, several images found on the Internet from other cameras and locations are included. The ground truth segmentation masks of each of the images are generated using a Voronoi polygonal region generator. The images in HYTA\footnote{In this thesis, the dataset name and its associated algorithm are referred as HYTA interchangeably.} are of various dimensions; the average is $682 \times 512$ pixels. A few sample images of HYTA along with their ground truth are shown in Fig.\ \ref{fig:sample_HYTA}.

\begin{figure}[htbp]
\centering
\includegraphics[height=1in]{B1.pdf}\hspace{0.5mm}
\includegraphics[height=1in]{B8.pdf}\hspace{0.5mm}
\includegraphics[height=1in]{C5.pdf}\hspace{0.5mm}
\includegraphics[height=1in]{U2.pdf}\\\vspace{1mm}
\includegraphics[height=1in]{B1_GT.pdf}\hspace{0.5mm}
\includegraphics[height=1in]{B8_GT.pdf}\hspace{0.5mm}
\includegraphics[height=1in]{C5_GT.pdf}\hspace{0.5mm}
\includegraphics[height=1in]{U2_GT.pdf}
\caption[Sample images from the HYTA database along with corresponding sky/cloud segmentation ground truths.]{Sample images from the HYTA database (top row) along with corresponding sky/cloud segmentation ground truth (bottom row).}
\label{fig:sample_HYTA}
\end{figure}

\subsection{Distribution Bimodality}
The segmentation of input image into two classes (sky and clouds) becomes easier for those color channels which exhibit higher bimodality. The bimodal behavior of a color channel for the concatenated distribution is measured using PBI as described in Section~\ref{sec:PBI}.  The results are summarized in Table~\ref{PBI16}. Out of the 16 color channels, $c_{5}$ (S), $c_{1}$ (R), and $c_{13}$ ($R/B$) have the lowest PBI and thus exhibit the most bimodal distributions, indicating that the segmentation of images into two distinct classes should work well in these color channels.

\begin{table}[H]
\normalsize
\centering
\setlength{\tabcolsep}{3pt} % default: 6pt
\begin{tabular}{c|c||c|c||c|c||c|c||c|c||c|c}
  \hline
  $c_{1}$ & \textbf{2.24} & $c_{4}$ & 3.11 & $c_{7}$ & 2.71 & $c_{10}$ & 2.86 & $c_{13}$ & \textbf{2.27} & $c_{16}$ & 4.27\\
  $c_{2}$ & 2.83 & $c_{5}$ & \textbf{1.94} & $c_{8}$ & 3.98 & $c_{11}$ & 8.85 & $c_{14}$ & 4.43 & $ $ & $ $\\
  $c_{3}$ & 3.25 & $c_{6}$ & 3.26 & $c_{9}$ & 5.96 & $c_{12}$ & 4.59 & $c_{15}$ & 2.92 & $ $ & $ $\\
  \hline
\end{tabular}
\caption[PBI values for all color channels.]{PBI values for all color channels. The most bimodal channels are highlighted in bold.}
\label{PBI16}
\end{table}

\subsection{Principal Component Analysis}
The distribution of the amount of variance captured by the principal components is shown in Fig.~\ref{fig:pca16_stefan}. The combination of first and second principal components capture a large majority ($95.4$\%) of variance in the input data across the individual images, and over $90$\% for the entire database.

\begin{figure}[htbp]
\centering
\includegraphics[width=0.75\columnwidth]{pca_stefan_conc.pdf}
\caption[Distribution of the variance across the principal components for all images of the HYTA database.]{Distribution of the variance across the principal components for all images of the HYTA database. The separate bar on the right shows the variance distribution for the concatenation of all images of the entire database.
\label{fig:pca16_stefan}}
\end{figure}

Table~\ref{table:PCA-table} shows the variance captured by each principal component for the concatenated distributions. We observe that the first two principal components capture a large part of the variance across all the images, namely $85.6\%$ of the total variance.

\begin{table}[htb]
\normalsize
\centering
\setlength{\tabcolsep}{3pt} 
\begin{tabular}{c||c|c|c|c|c|c}
  \hline
  \textbf{Database} & $\mathbf{1^{st}}$ & $\mathbf{2^{nd}}$ & $\mathbf{3^{rd}}$ & $\mathbf{4^{th}}$ & $\mathbf{5^{th}}$ & $\mathbf{6^{th}}$ \\
  \hline
  HYTA & $60.8\%$ & $24.8\%$ & $7.86\%$ & $5.11\%$ & $0.84\%$ & $0.36\%$ \\
  \hline
\end{tabular}
\caption{Percentage of variance captured across different principal components for HYTA database.}
\label{table:PCA-table}
\end{table}

In order to find the most significant vector for the detection of clouds, the contributing effect of the individual variables on the primary principal component axis is analyzed. Every  color channel has different loading factors on the most important principal component axis, and consequently each of them has a different contribution to the common variance captured in the corresponding data matrix $\ddot{\textbf{X}_{i}}$. These individual loading factors are essentially the projections of the input vectors (color channels) on the principal components. The significant color channels in terms of relative contribution to the first principal component axis are $c_{13}$ ($R/B$), $c_{15}$ ($\frac{B-R}{B+R}$, and $c_{5}$ ($S$).

Extending our analysis to finding the most significant pair of color channels, we need to understand a pair's cumulative contribution to the common variance. The sum of the squares of the corresponding loading factors for different color channels in the concatenated distribution represents the cumulative common variance captured by the pair. The pairs that have the highest cumulative loading on the first principal component are $c_{13}$-$c_{15}$, $c_{5}$-$c_{13}$, and $c_{5}$-$c_{15}$.

Another aspect to consider is the orthogonality between the individual color channels. For this purpose, we compute the triangular area enclosed by two given input vectors (color channels) projected on the plane spanned by the first and second principal components. There are ${{16}\choose{2}}=120$ combinations of two color channels. The triangular area for all unique cases is shown in Fig.~\ref{fig:area_grid_v7}, where the brightness of each square represents the area captured by the corresponding pair.  As expected, certain color channel pairs (the dark patches) are highly correlated, for example the green channel ($c_2$) with most luma channels ($c_7$, $c_{10}$), the various $R$-$B$ combinations ($c_{13-15}$) with one another, and so on.

\begin{figure}[htbp]
\centering
\includegraphics[width=0.8\textwidth]{area_combo2}
\caption[Distribution of triangular area enclosed by two given color channels projected on the plane spanned by the first and second principal components.]{Distribution of area \emph{AOB} for all input vector pairs, where \emph{OA} and \emph{OB} are two color channels. The brightness of each square represents the area captured by the corresponding pair.}
\label{fig:area_grid_v7}
\end{figure}

\subsection{Rough-set Based Relevance Scores}

In our proposed rough set based method, we measure the dependency of each color channel and report its corresponding average relevance value $\overline{\gamma}$ across all images of HYTA. Table~\ref{tab:rel-val} summarizes the results. We observe that certain color channels viz.\ $c_{15}$ ($\frac{B-R}{B+R}$), $c_{13}$ ($\frac{R}{B}$), $c_5$ ($S$) have higher relevance scores as compared to others, making these color channels  favorable candidates for sky/cloud image segmentation.
On the other hand, color channels $c_{11}$ ($a^{*}$) and $c_4$ ($H$) have low relevance scores, indicating that these color channels contribute less to the decision attribute for (non-) cloud pixels. Therefore, the latter color channels are not conducive for sky/cloud segmentation.

\begin{table}[htbp]
\normalsize
\centering
\begin{tabular}{ r | c || c | c || c | c || c | c|| c | c ||c | l }
\hline
$c_{1}$ & 0.70 & $c_{4}$ & 0.46 & $c_{7}$ & 0.72 & $c_{10}$ & 0.66 & $c_{13}$ & \textbf{0.84} & $c_{16}$ & 0.66\\
$c_{2}$ & 0.66 & $c_{5}$ & \textbf{0.82} & $c_{8}$ & 0.78 & $c_{11}$ & 0.33 & $c_{14}$ & 0.69 & $ $ & $ $\\
$c_{3}$ & 0.58 & $c_{6}$ & 0.58 & $c_{9}$ & 0.69 & $c_{12}$ & 0.61 & $c_{15}$ & \textbf{0.84} & $ $ & $ $\\
\hline
\end{tabular}
\caption[Average relevance value across all images of the HYTA database.]{Average relevance value across all images of the HYTA database. The most relevant color channels are highlighted in bold.}
\label{tab:rel-val}
\end{table}

\subsection{Cloud Classification Performance}
In this section, we evaluate the discriminative power of each of the $16$ color channels with respect to the cloud classification task. The performance results of the $16$ color channels will help us to benchmark our proposed rough-set based method and other statistical benchmarking measures.

We follow a supervised learning approach and train a Support Vector Machine (SVM) to validate our findings. We use each of the $16$ color channels separately as candidate feature vectors and train $16$ different SVMs. The trained SVMs are then used for sky/cloud pixel classification in order to check the efficacy of respective color channels in the classification task. We randomly  segregate the HYTA dataset into $15$ training images and $17$ test images.

For an objective evaluation of our algorithm, we report the F-score and Accuracy. Suppose $TP$, $FP$, $TN$, and $FN$ denote the True Positives, False Positives, True Negatives, and False Negatives, respectively, in this binary classification task. Accuracy is defined as the ratio of pixels that are correctly classified, $(TP + TN)/(TP + TN + FP + FN)$. The F-score, a popular metric in a binary classification problems, is defined as the harmonic mean of Precision $= TP/(TP + FP)$ and Recall $= TP/(TP + FN)$.

Figure~\ref{fig:boxplots} shows the binary classification results for each of the $16$ color channels, computed over $50$ different random selections of training and test sets.

\begin{figure}[htbp]
\centering
\subfloat[Accuracy]{\includegraphics[height=0.36\textwidth]{accuracy_HYTA.pdf}}
\hspace{0.1in}
\subfloat[F-score]{\includegraphics[height=0.36\textwidth]{fs_HYTA.pdf}}
\caption[Average accuracy and F-score values for $16$ color channels across all image of HYTA database.]{(a) Accuracy and (b) F-scores for $16$ color channels for all images in the HYTA database. For each box, the central red line indicates the median, the top and bottom edges correspond to $25^\textrm{th}$ and $75^\textrm{th}$ percentiles, and the whiskers represent the extreme data points.}
\label{fig:boxplots}
\end{figure}

We observe from Fig.~\ref{fig:boxplots} that color channels $c_{15}$ ($\frac{B-R}{B+R}$) and $c_5$ ($S$) have relatively higher accuracy and smaller variation as compared to the other color channels. Conversely, color channels $c_{11}$ ($a^*$) and $c_4$ ($H$) score poorly in terms of accuracy. Therefore, each color channel has different discriminative power to classify sky and cloud pixels from ground-based images. This ranking of color channels in terms of their classification performance serves as the ground-truth to verify the efficacy of different color channel selection algorithms.

\subsection{Benchmarking}
In this section, we will benchmark our proposed rough-set based method and other color channel selection methods with the accuracy measures of the color channels.

We check the correlation of the average accuracy scores for all the color channels with the normalized scores obtained from different approaches. Table~\ref{tab:RS_corr_results} shows the correlation coefficients of these approaches with the average classification accuracy of the color channels. Our proposed method using rough sets achieves the highest correlation.

\begin{table}[htbp]
\normalsize
\centering
\begin{tabular}{lc}
\hline
\textbf{Methods} & \textbf{Correlation} ($r$) \\
\hline 
Proposed approach & $0.84$ ($\uparrow$)\\
Bimodality & $-0.58$ ($\downarrow$)\\
Loading factors & $0.57$ ($\uparrow$)\\
ROC curve & $0.78$ ($\uparrow$) \\
Kullback-Leibler divergence & $0.12$ ($\downarrow$) \\
\hline
\end{tabular}
\caption[Correlation of cloud classification accuracy with ranking scores obtained using different methods.]{Correlation of cloud classification accuracy with ranking scores obtained using different methods. The \mbox{$\uparrow$ (or $\downarrow$)} indicates if \mbox{higher (or lower)} magnitude signifies better performance.}
\label{tab:RS_corr_results}
\end{table}

Figure~\ref{fig:corr} shows the respective scatter plots. The correlation coefficient is highest ($r=0.84$) for our proposed algorithm. From Fig.~\ref{fig:corr}(a), we can clearly see that color channels $c_5$ ($S$) and $c_{15}$ ($\frac{B-R}{B+R}$) are better candidates for sky/cloud classification. Similarly, color channels $c_{11}$  and $c_4$ with lower relevance scores are poor candidates. Figure~\ref{fig:corr}(b) also reveals that $c_5$ and $c_{15}$ are conducive color channels as their PBI values are closer to $1$. Similar results can be drawn from Fig.~\ref{fig:corr}(c), where favorable color channels $c_5$ and $c_{15}$ have comparatively lower KL-divergence values, and color channel $c_4$ has the highest KL-distance. However, the order of ranking for the other color channels is poor, leading to a low correlation value ($r=0.12$).

\begin{figure}[htbp]
\centering
\subfloat[Relevance]{\includegraphics[height=4.2cm]{FigA.pdf}}
\subfloat[Bimodality]{\includegraphics[height=4.2cm]{FigB.pdf}}
\subfloat[Kullback-Leibler distance]{\includegraphics[height=4.2cm]{FigC.pdf}}
\caption[Scatter plot between average accuracy and different benchmarking measures, while ranking the different color channels.]{Scatter plot between average accuracy and (a) relevance ($r=0.84$), (b) bimodality ($r=-0.57$), and (c) Kullback-Leibler distance ($r=0.12$) for all $16$ color channels (cf.\ Table~\ref{tab:corr_results}). Our proposed approach using relevance scores  achieves the highest correlation when ranking the color channels with respect to their segmentation performance.} 
\label{fig:corr}
\end{figure}

From these results, we observe that the relevance criterion has the highest correlation with the cloud segmentation accuracy among all methods. Therefore we conclude that our proposed rough set based color channel selection algorithm is useful to rank  color channels and identify suitable ones for image segmentation. We also note that certain color channels viz.\ $c_5$ and $c_{15}$ always perform best in all three benchmarking methods. Conversely, color channels $c_4$ and $c_{11}$ rank lower than others. Visual inspection of these color channels confirms these findings (cf.\ Fig.~\ref{fig:objective}).

\section{Discussion}
We discussed the performance of the different statistical tools and our proposed rough-set based selection method; and identified the most appropriate color channels for cloud detection. However, we used a \emph{single} color channel in our analysis - and identified the color channels that are conducive for detection. In this section, we explore the possibilities of using multiple channels for this purpose.

\begin{figure}[htbp]
\centering
\includegraphics[width=0.75\textwidth]{fscore_grid_CR2.pdf}
\caption[F-score values of $16$ color channels for 1D and 2D clustering cases.]{F-Scores for all unique cases of 1D (along the diagonal) and 2D clustering, represented on a brightness scale.  The highest F-Scores for 1D (dotted frames) and 2D cases (bold frames) are indicated numerically.
\label{fig:2d_result}}
\end{figure}

As described in Section~\ref{sec:cloudcluster}, we perform fuzzy c-means clustering using the varied existing color channels. There are $16$ color channels for $1$D clustering.  In a similar manner, there are ${{16}\choose{2}}$ unique color channel combinations for $2$D-clustering. Their performance is illustrated in Fig.~\ref{fig:2d_result} in an upper-triangular grid, where the intensity of a particular grid denotes the F-score of that particular color channel pair. Similarly, the diagonal elements represent the F-scores of the corresponding $1$D color channels. Since the ground truth provided by the HYTA database are binary images consisting of two classes, namely sky and cloud, we convert the probabilistic distribution of cloud pixels $p(\textbf{x}_{f})$ (cf.\ Section~\ref{sec:cloudcluster}) to a binary image by thresholding, i.e.\ a pixel having a probability of cloud $>50\%$ is assigned to a cloud pixel and others to sky pixels.

The most promising color channels for $1$D-clustering are $c_{13}$ ($R/B$), $c_{15}$ ($\frac{B-R}{B+R}$), and $c_{5}$ ($S$) with high precision, recall, and F-scores.  For $2$D, the best combinations include $c_5$-$c_8$, $c_8$-$c_{13}$, and $c_8$-$c_{15}$ ($c_8$ is the in-phase component of the \emph{YIQ} color model and it represents essentially another variety of red-blue difference), with several other close contenders. However, there is hardly any performance gain from using two color components rather than just one. Therefore, for the task of cloud detection, a single color channel (if chosen carefully) can have optimal performance, in comparison to computationally-expensive multiple color channels.

\section{Conclusions}
\label{sec:chap4-conclude}
In this chapter, we have presented a systematic analysis of color spaces and components for detection of clouds in sky/cloud images. We analyzed using a variety of statistical tools and methods: distribution bimodality, PCA, clustering and KL divergence.  Experimental evaluation with a cloud segmentation database yields consistent results across analysis methods. Additionally, we proposed a rough-set based method that provides the best correlation results with the performance measures of the color channels. Also, we observed that clustering results obtained using the best $1$D color channels or $2$D color channel pairs (including red-blue combinations $R/B$ and $\frac{B-R}{B+R}$, saturation $S$, or in-phase component $I$) are on par with each other. Future works involve the use of these identified color channels for several tasks.

### 2018-07-16 misc/thesis-hardbound/Chapters/Chapter5.tex
Update 16/7/2018

\chapter{Color-based Image Segmentation}
\label{chap:segmentation}
\setlength{\fboxsep}{0pt}
\setlength{\fboxrule}{0.2pt}

\lhead{Chapter 5. \emph{Color-based Image Segmentation}}

\section{Introduction}

Segmentation is one of the first steps in sky/cloud image analysis. It remains a challenging task because of the non-rigid, feature-less, and poorly-defined structure of clouds, whose shape also changes continuously over time. Thus, classical image segmentation approaches based on shape priors~\cite{wrapper_Jain} are not suitable. Furthermore, the wide range of lighting conditions (direct sunlight to completely covered skies) adds to the difficulty. Therefore, in most cases, color is used as the most discriminatory cue. In the previous Chapter~\ref{chap:colorchannels}, we have provided a systematic analysis of the various color spaces and components. 
In one of our earlier works~\cite{ICIP2015a}, we learnt the semantics of sky/cloud images for an automatic annotation of pixels with three class labels---sky, thin clouds and thick clouds. However, the segmentation results were not promising for thin clouds. Therefore, based on the findings of the previous chapter, we propose a probabilistic color-based image segmentation algorithm in this chapter.

\section{Outline of Our Contribution}
The motivation of this chapter is to propose a robust framework for color-based cloud segmentation under any illumination conditions, including a systematic analysis of color channels. The framework is based on partial least squares (PLS) regression and provides a straightforward, parameter-free supervised segmentation method. We show that our approach is robust and offers a superior performance across two different databases as compared to current state-of-the-art algorithms. Furthermore, it allows annotating each pixel with a degree of \emph{belongingness} to the sky or cloud category, instead of the usual binary labeling.

The main novel contributions of this chapter compared to earlier works include:

\begin{itemize}
\item Introduction of a large public sky/cloud image database with segmentation masks;
\item Extensive evaluation of color components and selection of appropriate color channels on two different sky/cloud image databases;
\item Robust learning-based framework for sky/cloud segmentation that outperforms existing methods.
\end{itemize}

The rest of this chapter is organized as follows. Section~\ref{sec:prob-segment} discusses our proposed supervised probabilistic segmentation framework. The sky/cloud databases used for evaluation, including our newly introduced database, are presented in Section~\ref{sec:database}. Section~\ref{sec:result-segment} presents the experimental evaluation of the segmentation framework. We extend our discussion to High Dynamic Range (HDR) images in Section~\ref{sec:HDRI-segment}. Section~\ref{sec:conc} concludes this chapter.

\section{Probabilistic Segmentation}
\label{sec:prob-segment}
Using statistical tools, we identify the most discriminative color channels for cloud segmentation. Out of $16$ color channels, the best performing color channels may be subsequently used as discriminatory feature $\mathbf{X}^{f}_{i}$ in the segmentation framework.

Our objective is to predict the label of a pixel as either sky or cloud, given a set of training images with manually annotated ground truths. We formulate this task of sky/cloud image segmentation in a probabilistic manner using PLS regression. Both Principal Component Analysis (PCA) and PLS are based on the same underlying motivation, namely to extract components that accounts for maximum variation in input data. Unlike alpha matting, we do not assume that a particular pixel is a linear combination of two classes -- \emph{sky} and \emph{cloud}.

We start with the assumption that the sky/cloud segmentation problem is dependent on a large number of explanatory independent variables (color channels in this case). Using dimensionality reduction techniques like PCA, we observe the degree of correlation amongst the variables and the amount of variance captured. PCA provides this information based only on the independent input color channels and project the data into new sets of orthogonal axes. In PLS however, both the input color channels and the output labels (sky/cloud) are considered. Using a set of manually defined ground truth images, we model the relationship between the input features and the output label. In the testing stage, we use this estimated model to predict the output labels of the pixels of a given test image.

Suppose, for a sample $\mathbf{X}_{i} \in {\rm I\!R}^{m \times n}$, the feature vector is denoted by $\mathbf{X}^{f}_{i} \in {\rm I\!R}^{mn \times k}$ and the corresponding binary ground-truth image as $\mathbf{Y}_{i} \in {\rm I\!R}^{mn \times 1}$.  The feature vector $\mathbf{X}^{f}_{i}$ consists of $k$ color channels from the set of $16$ color channels. We decompose the feature vector $\mathbf{X}^{f}_{i}$ and labels $\mathbf{Y}_{i}$ as 
\begin{align}
\mathbf{X}^{f}_{i} = \mathbf{T}_{i}\mathbf{P}_{i}^{T} + \mathbf{E}_{i},\\
\mathbf{Y}_{i} = \mathbf{U}_{i}\mathbf{Q}_{i}^{T} + \mathbf{F}_{i},
\label{eq:pls1}
\end{align}
where $\mathbf{T}_{i} \in {\rm I\!R}^{mn \times p}$ and $\mathbf{U}_{i} \in {\rm I\!R}^{mn \times p}$ are $p$ extracted latent matrices.  $\mathbf{P}_{i} \in {\rm I\!R}^{k \times p}$ and $\mathbf{Q}_{i} \in {\rm I\!R}^{1 \times p}$ are the loading matrices, and $\mathbf{E}_{i} \in {\rm I\!R}^{mn \times k}$ and $\mathbf{F}_{i} \in {\rm I\!R}^{mn \times 1}$ are the residual matrices. Henceforth, for the sake of brevity and without loss of generality we drop the suffix $i$ in the notations.

In the generalized partial least squares regression sense, we decompose $\mathbf{X}^{f}$ and $\mathbf{Y}$ so as to maximize the covariance between $\mathbf{T}$ and $\mathbf{U}$~\cite{SIMPLS}.
Under the assumption that the input matrix $\mathbf{X}^{f}$ can be expressed as a linear combination of a few latent variables, we can assume the existence of a linear relationship between $\mathbf{T}$ and $\mathbf{U}$ such that \begin{align}
\label{eq:pls2}
\mathbf{U} = \mathbf{T}\mathbf{D}+\mathbf{H},
\end{align}
where $\mathbf{D} \in {\rm I\!R}^{p \times p}$ is a diagonal matrix and $\mathbf{H}$ is the residual matrix. Combining Eqs.\ (\ref{eq:pls1}) and (\ref{eq:pls2}), we get
\begin{gather}
\label{eq:pls3}
\mathbf{Y}=\mathbf{T}\mathbf{D}{\mathbf{Q}}^{T} + (\mathbf{H}\mathbf{Q}^{T} + \mathbf{F}),\\
\mathbf{Y}=\mathbf{T}\mathbf{C}^{T} + \mathbf{F}^{*},
\end{gather}
where $\mathbf{C}^{T}$ is the matrix of regression coefficients and $\mathbf{F}^{*}$ is the residual matrix. We extract score vectors $\mathbf{t}$ and $\mathbf{u}$ from predictors and response variables respectively, and express as: 
\begin{gather}
\mathbf{t}=\mathbf{Xw},\\
\mathbf{u}=\mathbf{Yc},
\end{gather}
where $\mathbf{w}$ and $\mathbf{c}$ are the corresponding weight vectors of $\mathbf{X}$ and $\mathbf{Y}$. These score vectors are necessary to define the response and predictor variables in the PLS setting. $\mathbf{W}$ represents a set of orthogonal basis vectors, such that $\mathbf{W}=(\mathbf{w}_1, \mathbf{w}_2, \ldots, \mathbf{w}_p)$. From~\cite{Manne1987}, we can express the regression coefficient matrix as 
\begin{align}
\label{eq:pls4}
\mathbf{T} = \mathbf{X}\mathbf{W}(\mathbf{P}^{T}\mathbf{W})^{-1}.
\end{align}

Using Eqs.~(\ref{eq:pls3}) and (\ref{eq:pls4}), we get
\begin{gather}
\label{eq:pls5}
\mathbf{Y}=\mathbf{X}\mathbf{W}(\mathbf{P}^{T}\mathbf{W})^{-1}\mathbf{C}^{T} + \mathbf{F}^{*}, \\
\label{eq:pls6}
\mathbf{Y}=\mathbf{XB} + \mathbf{F}^{*},
\end{gather}
where $\mathbf{B}=\mathbf{W}(\mathbf{P}^{T}\mathbf{W})^{-1}\mathbf{C}^{T}$ represents the matrix of regression coefficients.

In our proposed approach, we select a set of training images from the database and obtain the regression coefficient matrix $\mathbf{B}$ as per Eq.\ (\ref{eq:pls6}). In the testing stage, we obtain the corresponding segmentation result as
\begin{align}
\label{eq:testing_eqn}
\mathbf{Y}_{\mathrm{\mathrm{test}}}=\mathbf{X}_{\mathrm{\mathrm{test}}}\mathbf{B}
\end{align}
by using the obtained regression coefficient matrix $\mathbf{B}$. However, because of the residual matrices and the inherent imperfections in modeling, the values of $\mathbf{Y}_{\mathrm{\mathrm{test}}}$ are not discrete in nature. We do not employ any thresholding at this stage, but rather normalize these values to the range $[0,1]$ ($0=\mbox{sky}, \mbox{ }1=\mbox{cloud}$). 
These normalized values provide a probabilistic  indication of the \emph{belongingness} of a particular pixel to a specific class (i.e.\ cloud or sky) instead of a binary decision.

One of the most important pre-requisites for rigorous evaluation of any segmentation algorithm is an annotated dataset of suitable images. Most research groups working on sky/cloud segmentation use their own proprietary images that are not publicly available. In the subsequent section, we will introduce a new segmentation database that is released to the research community for future benchmarking purposes.

\section{Sky/Cloud Image Databases}
\label{sec:database}
In this section, we briefly mention the currently available database containing ground truth images and describe the need for a more comprehensive and consistent database.

\subsection{HYTA Database}
Till date, the only publicly available sky/cloud image dataset annotated with segmentation masks was the Hybrid Thresholding Algorithm (HYTA) database\footnote{Thanks to Prof. Qingyong Li, Professor of Beijing Jiaotong University for providing the dataset.} by Li et al.\ \cite{Li2011}. More details of HYTA dataset were already provided in our earlier Chapter~\ref{chap:colorchannels}.

\subsection{SWIMSEG Database}
Because of the dearth of public databases for sky/cloud images, we created SWIMSEG, the \textbf{S}ingapore \textbf{W}hole Sky \textbf{IM}aging \textbf{SEG}mentation Database.\footnote{~The SWIMSEG database can be downloaded from \url{http://vintage.winklerbros.net/swimseg.html}.} It consists of $1013$ images that were captured by a custom-designed ground-based sky imager called Wide Angle High Resolution Sky Imaging System (WAHRSIS), developed and deployed at Nanyang Technological University in Singapore~\cite{WAHRSIS}. 
The imaging system of our ground-based sky camera consists of a Canon EOS Rebel T3i (a.k.a. EOS 600D) camera body and a Sigma 4.5mm F2.8 EX DC HSM Circular Fish-eye Lens with a field of view of 180 degrees. We discussed the various models of our sky cameras earlier in Chapter~\ref{chap:wsi}.

The images captured by this system suffer from distortions in illumination and color, which need to be corrected.  An example is shown in Fig.~\ref{fig:pre-process}. First, because of a phenomenon called vignetting, the images are comparatively darker at the edges as compared to the center. Vignetting occurs because the incident light rays reach the camera sensor with varying angles and is particularly noticeable for fish-eye lenses. We analyze vignetting in our imaging system using an integrating sphere \cite{WAHRSIS}  and perform the necessary correction in the image, the result of which is shown in Fig.~\ref{fig:pre-process}(b).

Second, the colors in the captured images vary due to the different weather conditions and capturing hours of the images  and often do not correspond to the actual colors in the scene. We use a color checkerboard with $18$ different color patches as a reference, whose exact $L^{*}a^{*}b^{*}$ values are specified by the manufacturer. Using the mapping between captured and actual color, we thereby obtain the color-corrected image, which is shown in Fig.~\ref{fig:pre-process}(c).

\begin{figure}[htb]
\centering
   \subfloat[Original image]{\includegraphics[height=0.3\textwidth]{org-image.pdf}}
   \subfloat[Vignetting correction]{\includegraphics[height=0.3\textwidth]{illum-image.pdf}}
   \subfloat[Color correction]{\includegraphics[height=0.3\textwidth]{illum-color-image.pdf}}
\caption[Illustration to show vignetting- and color-correction.]{Image correction w.r.t.\ illumination and color.}\label{fig:pre-process}
\end{figure}

Finally, the images from the database are undistorted using the geometric calibration function, which models the effect of the lens. This function relates each pixel of the captured image to the azimuth and elevation angle of the corresponding incident light ray. Using that information, we can project the image onto a hemisphere whose center is the focal point. This is shown in Fig.~\ref{fig:undistortion-results}(a). We generate undistorted pictures using a ray tracing approach by considering an imaginary camera (with a standard lens) at center of the hemisphere, which points towards a user defined direction with a given azimuth and an elevation angle. In order to simulate this camera, we consider an output image with dimension $600 \times 600$. Each output image corresponds to a viewing angle of $62^{\circ}$. The rays passing through each pixel will intersect the hemisphere and then converge towards the center. The value of a pixel is then equal to the color of the hemisphere at its intersection point. We perform this process at varying azimuth angles for a particular angle of elevation to generate several undistorted images. Figure~\ref{fig:undistortion-results} shows the output image as well as the lines corresponding to its borders and diagonals on the original image.

\begin{figure}[htbp]
\centering
   \subfloat[]{\includegraphics[width=0.45\textwidth]{undistortion-3d.pdf}}
   \subfloat[]{\includegraphics[width=0.25\textwidth]{undistortion-original-mask.pdf}}
   \subfloat[]{\includegraphics[width=0.25\textwidth]{undistortion-result.pdf}}
\caption[Generation of undistorted images using ray-tracing.]{Generation of undistorted images using ray-tracing. (a) Projection of the image on a hemisphere; (b) Input image with borders and diagonals of the output image; (c) Undistorted output image. }\label{fig:undistortion-results}
\end{figure}

The corresponding sky/cloud segmentation masks of the images were created in consultation with cloud experts from the Singapore Meteorological Services. A few representative sample images from this database are shown in Fig.\ \ref{fig:WAHRSISdb600}.

\begin{table}[htbp]
\centering
\begin{tabular}{ccccc}
\includegraphics[width=0.2\textwidth]{img1.pdf} & 
\includegraphics[width=0.2\textwidth]{img2.pdf} &  
\includegraphics[width=0.2\textwidth]{img3.pdf} &
\includegraphics[width=0.2\textwidth]{img4.pdf}\\
\fbox{\includegraphics[width=0.2\textwidth]{img1_2GT.pdf}} &
\fbox{\includegraphics[width=0.2\textwidth]{img2_2GT.pdf}} &
\fbox{\includegraphics[width=0.2\textwidth]{img3_2GT.pdf}} & 
\fbox{\includegraphics[width=0.2\textwidth]{img4_2GT.pdf}} \\
{\fontsize{0.4cm}{2em}\selectfont $6.2\%$} & 
{\fontsize{0.4cm}{2em}\selectfont $48.7\%$} & 
{\fontsize{0.4cm}{2em}\selectfont $72.5\%$} & 
{\fontsize{0.4cm}{2em}\selectfont $95.0\%$} \\
\end{tabular}
\captionof{figure}[Sample images from the SWIMSEG database along with its corresponding ground truths.]{Sample images from the SWIMSEG database (top row), along with corresponding sky/cloud segmentation ground truth (bottom row) and percentage of cloud coverage.}
\label{fig:WAHRSISdb600}
\end{table}

SWIMSEG consists of $1013$ patches that were handpicked carefully from images taken over the period from October 2013 till July 2015 in Singapore. In the selection process, different parameters (viz.\ azimuth and elevation angle of sun, time of day, cloud coverage percentage, camera parameters) were considered. 
The camera elevation angle is set to three distinct angles ($36^{\circ}$, $45^{\circ}$, and $60^{\circ}$), whereas the azimuth angle is sampled at various angles around the unit hemisphere. The camera is set to auto mode while capturing pictures, and we observe that the settings tend to remain similar across all images. This is primarily because weather conditions in Singapore remain fairly similar throughout the year.

Figure~\ref{fig:image-stats} characterizes the images in the dataset according to the time of day they were taken, cloud coverage, and distance from the sun. The sun rises and sets at around the same time throughout the year in Singapore, namely at 7am and 7pm local time.  The number of clear sky patches is relatively low as compared to moderately-cloudy or overcast conditions. This is because Singapore experiences a tropical climate in which clear-sky conditions are rare. Although most of the image patches are sampled at a certain distance from the sun to avoid saturation effects, we still include  a substantial number of images  close to sun.

\begin{figure}[htbp]
\centering
\subfloat[Time of day]{\includegraphics[height=0.36\textwidth]{dist_hours-Mar16.pdf}}
\subfloat[Cloud coverage]{\includegraphics[height=0.36\textwidth]{dist_CC.pdf}}\\
\vspace{-0.1in}
\subfloat[Distance from the sun]{\includegraphics[height=0.36\textwidth]{dist_solarangle_Mar17.pdf}}
\caption{Distribution of images in SWIMSEG according to various characteristics.}\label{fig:image-stats}
\end{figure}

\section{Segmentation Results}
\label{sec:result-segment}
In the previous Section, we identified suitable candidate color components for segmentation, such as $c_{5}$ (saturation) and various blue-red ratios ($c_{13}$, $c_{14}$, $c_{15}$). These color channels are expected to perform better than others. We now evaluate the segmentation results for all $16$ color channels, by individually considering them as the discriminatory feature vector $\mathbf{X}^{f} \in {\rm I\!R}^{mn \times 1}$ for segmentation. We showed previously \cite{ICIP1_2014} that there is hardly any performance improvement when using more than $1$ color channel in the feature matrix $\mathbf{X}_f$.

We perform extensive experiments of our proposed approach on the HYTA and SWIMSEG databases. Each of the images in the two datasets are expressed in the form of $\hat{\mathbf{X}_{i}}$, as shown in Eq.\ (\ref{eq:eq1}). The corresponding feature vector $\mathbf{X}_i^{f}$ is computed for both training and testing stages.  The training images are used to calculate the matrix of regression coefficients $\mathbf{B}$ as per Eq.\ (\ref{eq:pls6}). In our experiments, we use \texttt{plsregress}, the MATLAB implementation of the SIMPLS algorithm \cite{SIMPLS} for this. 
We set $p=k=1$, as we use a single color channel for evaluation.
During the testing phase, $\mathbf{X}_{\mathrm{test}}$ of the testing image is computed. Using the matrix of regression coefficients $\mathbf{B}$, the corresponding $\mathbf{Y}_{\mathrm{test}}$ is computed.

In the ideal scenario, the value of $\mathbf{Y}_{\mathrm{test}}$ is either $0$ or $1$. However, in the actual implementation, the values are continuous in nature. Suppose we denote the obtained values of $\mathbf{Y}_{\mathrm{test}}$ as $\{v_1, v_2, \ldots, v_{mn} \}$. Let $\theta$ be the function that normalizes the obtained values of $\mathbf{Y}_{\mathrm{test}}$ to the interval $[0,1]$:
$$\theta(v_i)=\frac{v_i - \min v_i}{\max v_i-\min v_i}.$$ 
We perform \emph{soft} thresholding by normalizing these values in the range [0,1]. Therefore, this normalized value indicates the belongingness of a pixel to belong to the cloud (or sky) category.

The objective evaluation is based on the true positive (\emph{TP}), true negative (\emph{TN}), false positive (\emph{FP}), and false negative (\emph{FN}) samples in a binary image. We report Precision, Recall, F-score, and Misclassification rate for the different benchmarking algorithms, which are defined as follows:

\begin{gather*}
\mbox{Precision}=TP/(TP+FP),\\
\mbox{Recall}=TP/(TP+FN),\\
\mbox{F-score}=\frac{2\times\mbox{Precision}\times\mbox{Recall}}{{\mbox{Precision}+\mbox{Recall}}},\\
\mbox{Misclassification rate}=\frac{FP+FN}{TP+TN+FP+FN}.
\end{gather*}

\subsection{Choice of Color Channels}
As described earlier, the segmentation performance is dependent on the choice of color channels. In order to understand the effect of color channels, we use the individual color channels to constitute the feature vector $\mathbf{X}^{f}$ in this experiment. We choose training and test set sizes as per Table~\ref{table:train-test}.

\begin{table}[htbp]
\normalsize
\centering
\begin{tabular}{r||c|c|c}
  \hline
  \textbf{Database}  & \textbf{Training Set} & \textbf{Test Set} & \textbf{Total}  \\
  \hline
  HYTA & 17 & 15 & 32 \\
  SWIMSEG & 500 & 513 & 1013 \\
  \hline
\end{tabular}
\caption{Number of training and test images for HYTA and SWIMSEG databases.}
\label{table:train-test}
\end{table}

We compute F-scores (the harmonic mean of precision and recall) to characterize the segmentation performance of each color channel. We perform a $5$-fold and $10$-fold cross validation in HYTA and SWIMSEG datasets, respectively. In each of these experiments, $1$ fold is used for testing and the remaining folds are used in the training stage. Figure~\ref{fig:CV-result} shows the results for HYTA and SWIMSEG datasets.

\begin{figure}[H]
\centering
\subfloat[HYTA]{\includegraphics[width=0.7\textwidth]{HYTA-CV-Apr20.pdf}}\vspace{-0.4cm}\\
\subfloat[SWIMSEG]{\includegraphics[width=0.7\textwidth]{SWIM-CV-Apr20.pdf}}
\caption{Binary classification performance for different color channels.}\label{fig:CV-result}
\end{figure}

The classification performance for individual color channels follows the same trend in both HYTA and SWIMSEG dataset. Color channels $c_5$ and the red-blue ratio channels $c_{13,15}$ perform best, which is consistent with what we found in the earlier Chapter~\ref{chap:colorchannels}. Based on these results, we conduct the subsequent evaluations with $c_{15}$ as the feature vector $\mathbf{X}^{f}$.

\subsection{Effect of Database Characteristics}
We study the effect of the different characteristics of the database on the obtained F-score values of our proposed segmentation algorithm by checking whether the obtained segmentation results are biased towards a particular set of image parameters, specifically time of day, cloud coverage, and distance from the sun. We present the distribution of F-score values across these parameters in Fig.~\ref{fig:fscore-distribution}.

The average F-score is slightly high in the morning and late afternoon, while it drops during mid-day. This is because the images captured during mid-day have a higher tendency to get over-exposed because of the presence of direct sun. On the other hand, the images captured at the morning and evening hours of the day receive slant sun-rays, and contain more clouds. The variation of the F-score values w.r.t. the percentage of cloud in an image is shown in Fig.~\ref{fig:fscore-distribution}(b). We observe that the performance is marginally better for higher percentage of cloud coverage in an image. Finally, we note that there is no clear relationship of the distance of the image patch from the sun on the obtained F-score values, which is illustrated in Fig.~\ref{fig:fscore-distribution}(c).

\begin{figure}[H]
\centering
\subfloat[Time of day]{\includegraphics[height=0.4\textwidth]{FS-time-Mar16.pdf}}
\subfloat[Cloud coverage]{\includegraphics[height=0.4\textwidth]{FS-CC.pdf}}\\
\subfloat[Distance from the sun]{\includegraphics[height=0.45\textwidth]{FS-sun-thesis.pdf}}
\caption{Distribution of average F-score value as a function of various characteristics of the images in SWIMSEG.}\label{fig:fscore-distribution}
\end{figure}

\subsection{Benchmarking}
We benchmark our proposed approach with current state-of-the-art cloud detection algorithms: Li et al.\ \cite{Li2011}, Souza et al.\ \cite{Souza}, Long et al.\ \cite{Long}, and Mantelli-Neto et al.\ \cite{Sylvio}. We also compare against another popular image segmentation algorithm viz. SLIC superpixels \cite{SLIC}.

Li et al.\ \cite{Li2011} use HYTA that combines both adaptive and fixed threshold approach. Souza et al.\ \cite{Souza} use the saturation component of the intensity, hue, and saturation ($IHS$) color model in defining appropriate thresholds to obtain the final segmentation mask. Long et al.\ \cite{Long} use the ratio of red and blue channels to model the molecular scattering in the atmosphere. Mantelli-Neto et al.\ \cite{Sylvio} use multi-dimensional Euclidean geometric distance and Bayesian approaches to identify sky and cloud pixels.

The popular superpixel segmentation Simple Linear Iterative Clustering (SLIC) divides the input image into a number of superpixels. We combine it with the DBSCAN algorithm~\cite{DBSCAN} to cluster the superpixels and subsequently categorize them into sky/cloud based on the average ratio of red and blue of a particular superpixel.

In addition to these state-of-the-art cloud segmentation algorithms, we also compare our proposed algorithm with other typical machine-learning based methods. We extract discriminative features from image, and use them in a classifier model. In our case, we employ Support Vector Machine (SVM) classifier along with various image features.

We use several feature descriptors viz. Local Binary Patterns (LBP)~\cite{LBP_PAMI}, Color Histogram (colorHIST)~\cite{colorhist-CVPR}, and Dense Scale Invariant Feature Transform (dSIFT)~\cite{SIFT} for extracting discriminatory features from sky/cloud images. Quite recently, Yuan et al.\ \cite{BOW-cloud} used Bag-Of-Words (BOW) model to model cloud- and non-cloud- satellite images from dSIFT local features. Yuan et al.\ \cite{BOW-cloud} over segments a satellite image into sub-images using SLIC superpixel generation method. Image descriptors are thereby extracted from these sub-patches using dense SIFT extractor. Subsequently, the BOW model is used to model the cloud- and non-cloud images and the corresponding codebook is generated. A Support Vector Machine (SVM) classifier is finally used for the super-pixel classification into cloud- and non-cloud- parts \cite{BOW-cloud}.
In addition to these features, we also use texture descriptors (using Schmid filter~\cite{Schmid_CVPR}) along with BOW and SVM as a benchmarking cloud segmentation algorithm.
Furthermore, we also use the raw gray-scale (GRAY) color channel values as discriminatory feature in feature extraction stage. These features are used in training a SVM classifier. In the testing stage, these descriptors are again computed for the test images, and the trained SVM classifier classifies them to either sky or cloud pixels. Therefore, these different image features together with SVM classifier form a collection of machine-learning based sky/cloud classification algorithms.

In our proposed approach, we assign a membership value for the cloud category to each pixel. However, as the available ground-truth masks are binary, we convert our probabilistic map into a binary map by simple thresholding in order to perform the objective evaluations.
The threshold value can be any value in the closed interval [0,1]; a lower value indicates a higher tendency for a pixel to classify as \emph{cloud} and a higher value indicates a higher tendency to classify as \emph{cloud} pixel. Figure~\ref{fig:ROC-prop} shows the ROC curve for our proposed algorithm by changing the threshold value in the closed interval [0,1] for both HYTA and SWIMSEG databases.  $20$ trials were performed for each threshold value, with training and testing sets of images chosen randomly for each trial. The subsequent results were obtained with a threshold of $0.5$.

\begin{figure}[H]
\centering
\subfloat[HYTA]{\includegraphics[width=3.5in]{ROC_HYTA-Apr20.pdf}}\\
\subfloat[SWIMSEG]{\includegraphics[width=3.5in]{ROC_SWIMSEG_Apr20.pdf}}
\caption[ROC curves of our proposed segmentation approach for HYTA and SWIMSEG databases.]{ROC curves of our proposed algorithm, including error bars in X- and Y-directions for (a) HYTA and (b) SWIMSEG datasets.}
\label{fig:ROC-prop}
\end{figure}

Figure~\ref{fig:sample-results} shows a few sample images from the HYTA and SWIMSEG databases together with the segmentation ground truth and the corresponding output images obtained by our proposed approach and other existing methods.  Most of the approaches work quite well when there is a clear contrast between sky and cloud regions, as is often the case for the HYTA database. The method of Mantelli-Neto et al.\ \cite{Sylvio} fails on images that contain non-uniform illumination of cloud mass from sunlight. The detection of thin clouds is  the most problematic: Long et al.\ \cite{Long} and SLIC+DBSCAN methods classify the entire image patch as cloud in such cases. The method of Li et al.\ \cite{Li2011} fails in cases where the boundary between sky and cloud is ill-defined. We observe from the last two examples in Fig.~\ref{fig:sample-results} that Li et al.\ over-segments the corresponding input images. Except for Souza et al. \cite{Souza}, most of the approaches fail for images of the SWIMSEG dataset with generally less well-defined sky/cloud separation. 
Similarly, the other machine-learning based methods viz. GRAY+SVM and dSIFT+BOW+SVM ~\cite{BOW-cloud} perform poorly for the wide range of images. This is because the Bag-of-words model obtained for cloud- and non-cloud- superpixels fails to discriminate between the superpixels in the test images.
The results obtained by our PLS-based approach show that it works well across diverse illumination conditions and for both databases.

\begin{table}[htbp]
\begin{tabular}{m{2cm}ccccccc}
{\fontsize{0.4cm}{1em}\selectfont Input Image} \vspace{1.5cm}& 
\includegraphics[height=0.08\textheight]{B1.pdf} &
\includegraphics[height=0.08\textheight]{B4.pdf} &
\includegraphics[height=0.08\textheight]{C1.pdf} &
\includegraphics[height=0.08\textheight]{482img.pdf} &
\includegraphics[height=0.08\textheight]{583img.pdf} &
\includegraphics[height=0.08\textheight]{im2.pdf}& \vspace{-0.39in}\\

{\fontsize{0.4cm}{1em}\selectfont Ground Truth} \vspace{1.5cm}& 
\includegraphics[height=0.08\textheight]{B1_GT.pdf} &
\includegraphics[height=0.08\textheight]{B4_GT.pdf} &
\includegraphics[height=0.08\textheight]{C1_GT.pdf} &
\fbox{\includegraphics[height=0.08\textheight]{482img_2GT.pdf}} &
\fbox{\includegraphics[height=0.08\textheight]{583img_2GT.pdf}} &
\fbox{\includegraphics[height=0.08\textheight]{im2-GT.pdf}}& \vspace{-0.39in}\\

{\fontsize{0.4cm}{1em}\selectfont Our \mbox{approach}} \vspace{1.5cm}& 
\includegraphics[height=0.08\textheight]{B1-map.pdf} &
\includegraphics[height=0.08\textheight]{B4-map.pdf} &
\includegraphics[height=0.08\textheight]{C1-map.pdf} &
\includegraphics[height=0.08\textheight]{482img-map.pdf} &
\includegraphics[height=0.08\textheight]{583img-map.pdf} &
\includegraphics[height=0.08\textheight]{im2-prob.pdf}&
\hspace{-0.18in}\includegraphics[height=0.08\textheight]{redblue-map.pdf}\vspace{-0.39in}\\

{\fontsize{0.4cm}{1em}\selectfont Our \mbox{approach} (binary)} \vspace{1.5cm}& 
\includegraphics[height=0.08\textheight]{B1-thr.pdf} &
\includegraphics[height=0.08\textheight]{B4-thr.pdf} &
\includegraphics[height=0.08\textheight]{C1-thr.pdf} &
\fbox{\includegraphics[height=0.08\textheight]{482img-thr.pdf}} &
\fbox{\includegraphics[height=0.08\textheight]{583img-thr.pdf}} &
\fbox{\includegraphics[height=0.08\textheight]{im2-prop.pdf}}& \vspace{-0.39in}\\

{\fontsize{0.4cm}{1em}\selectfont Li et al.} \vspace{1.5cm}& 
\includegraphics[height=0.08\textheight]{B1-HYTA.pdf} &
\includegraphics[height=0.08\textheight]{B4-HYTA.pdf} &
\includegraphics[height=0.08\textheight]{C1-HYTA.pdf} &
\fbox{\includegraphics[height=0.08\textheight]{482img-HYTA.pdf}} &
\fbox{\includegraphics[height=0.08\textheight]{583img-HYTA.pdf}} &
\fbox{\includegraphics[height=0.08\textheight]{im2_li.pdf}}& \vspace{-0.33in}\\

{\fontsize{0.4cm}{1em}\selectfont Souza et al.} \vspace{1.5cm}& 
\includegraphics[height=0.08\textheight]{B1-Souza.pdf} &
\includegraphics[height=0.08\textheight]{B4-Souza.pdf} &
\includegraphics[height=0.08\textheight]{C1-Souza.pdf} &
\fbox{\includegraphics[height=0.08\textheight]{482img-Souza.pdf}} &
\fbox{\includegraphics[height=0.08\textheight]{583img-Souza.pdf}} &
\fbox{\includegraphics[height=0.08\textheight]{im2-Souza.pdf}}& \vspace{-0.37in}\\

{\fontsize{0.4cm}{1em}\selectfont Long et al.} \vspace{1.5cm}& 
\fbox{\includegraphics[height=0.08\textheight]{B1-Long.pdf}} &
\fbox{\includegraphics[height=0.08\textheight]{B4-Long.pdf}} &
\fbox{\includegraphics[height=0.08\textheight]{C1-Long.pdf}} &
\fbox{\includegraphics[height=0.08\textheight]{482img-Long.pdf}} &
\fbox{\includegraphics[height=0.08\textheight]{583img-Long.pdf}} &
\fbox{\includegraphics[height=0.08\textheight]{im2-long.pdf}}& \vspace{-0.39in}\\

{\fontsize{0.4cm}{1em}\selectfont Mantelli-Neto et al.} \vspace{1.5cm}& 
\fbox{\includegraphics[height=0.08\textheight]{B1-Syl.pdf}} &
\fbox{\includegraphics[height=0.08\textheight]{B4-Syl.pdf}} &
\includegraphics[height=0.08\textheight]{C1-Syl.pdf} &
\fbox{\includegraphics[height=0.08\textheight]{482img-Syl.pdf}} &
\fbox{\includegraphics[height=0.08\textheight]{583img-Syl.pdf}} &
\fbox{\includegraphics[height=0.08\textheight]{im2-sylvio.pdf}}& \vspace{-0.33in}\\

{\fontsize{0.4cm}{1em}\selectfont SLIC + \mbox{DBSCAN}} \vspace{1.5cm}& 
\includegraphics[height=0.08\textheight]{B1-SLIC.pdf} &
\includegraphics[height=0.08\textheight]{B4-SLIC.pdf} &
\fbox{\includegraphics[height=0.08\textheight]{C1-SLIC.pdf}} &
\fbox{\includegraphics[height=0.08\textheight]{482img-SLIC.pdf}} &
\fbox{\includegraphics[height=0.08\textheight]{583img-SLIC.pdf}} &
\fbox{\includegraphics[height=0.08\textheight]{im2-slic.pdf}}& \vspace{-0.36in}\\

{\fontsize{0.4cm}{1em}\selectfont GRAY + SVM} \vspace{1.2cm}& 
\fbox{\includegraphics[height=0.08\textheight]{B1-graySVM.pdf}} &
\includegraphics[height=0.08\textheight]{B4-graySVM.pdf} &
\fbox{\includegraphics[height=0.08\textheight]{C1-graySVM.pdf}} &
\fbox{\includegraphics[height=0.08\textheight]{482img-graySVM.pdf}} &
\fbox{\includegraphics[height=0.08\textheight]{583img-graySVM.pdf}} &
\fbox{\includegraphics[height=0.08\textheight]{im2-gray-svm.pdf}}& \vspace{-0.39in}\\

{\fontsize{0.4cm}{1em}\selectfont dSIFT + BOW + SVM} \vspace{1.5cm}& 
\fbox{\includegraphics[height=0.08\textheight]{B1-dSIFT.pdf}} &
\includegraphics[height=0.08\textheight]{B4-dSIFT.pdf} &
\fbox{\includegraphics[height=0.08\textheight]{C1-dSIFT.pdf}} &
\fbox{\includegraphics[height=0.08\textheight]{482img-dSIFT.pdf}} &
\fbox{\includegraphics[height=0.08\textheight]{583img-dSIFT.pdf}} &
\fbox{\includegraphics[height=0.08\textheight]{im2-dSIFT.pdf}}& \vspace{-0.39in}\\

\end{tabular}
\captionof{figure}[Segmentation results of sample images from HYTA and SWIMSEG databases for different benchmarking algorithms.]{Sample images from HYTA (left 3 columns) and SWIMSEG (right 3 columns) databases, along with the corresponding ground truth and the sky/cloud segmentation obtained using various methods. The \emph{blue} and \emph{red} in the colormap indicate \emph{sky} and \emph{cloud} respectively.}
\label{fig:sample-results}
\end{table}

The simulations were conducted in Matlab on a 64-bit Ubuntu 14.04 LTS workstation, Intel i5 CPU $@$2.67GHz.  In terms of computation time, our proposed method takes an average of  $1.31$s and $1.89$s for a single image from the HYTA and SWIMSEG databases, respectively. In the training stage, HYTA requires $21.5$s and SWIMSEG required $1018.6$s for computing the regression coefficient matrix $\mathbf{B}$. The computation times of other benchmarking algorithm are provided in Table~\ref{scoretable}.

Table~\ref{scoretable} provides an objective evaluation of our proposed approach with other state-of-the-art algorithms for all images in the testing set of the two databases.  Existing algorithms require extensive tuning using various manually-defined thresholds, and achieve either high precision or high recall in our evaluation, but not both. Long et al.\ and Mantelli-Neto et al.\ have high recall values. However, they fare poorly in the corresponding precision values. Souza et al.\ on the other hand has a high precision value, but low recall. These existing methods often suffer from under- or over-identification of cloud pixels as they are threshold-based, and a single threshold may not work well for all types of sky/cloud images. Our proposed approach performs best for both HYTA and SWIMSEG databases on the basis of F-scores, highlighting the effectiveness of PLS-based learning method.

\begin{table}[htbp]
\footnotesize
\centering
\begin{tabular}{ |lr||r|r|r|c|c| }
\hline
& Methods & Precision & Recall & F-score & Misclassification rate & Time [s] \\ 
\hline\hline
\parbox[t]{3mm}{\multirow{12}{*}{\rotatebox[origin=c]{90}{\small \textbf{HYTA}}}} 
& Li et al.\ & 0.89 & 0.82 & 0.81 & 0.12 & 1.34 \\ 
& Souza et al.\ & 0.88 &  0.67 &  0.65 & 0.15 & 1.33 \\ 
& Long et al.\ & 0.64 & \textbf{0.97} & 0.71  & 0.26 & 1.22 \\ 
& Mantelli-Neto et al.\ & 0.54 & \textbf{0.97} & 0.63 & 0.44 & 1.43 \\ 
& SLIC + DBSCAN & 0.65 & 0.83 & 0.60 & 0.32 & 5.10 \\ 
& GRAY + SVM & 0.89 & 0.58 & 0.67 & 0.31 & 2.44  \\
& LBP + SVM & 0.80 & 0.65 & 0.72 & 0.22 & 4.29 \\
& ColorHIST + SVM & 0.75 & 0.74 & 0.75 & 0.21 & 2.47  \\
& dSIFT + BOW + SVM & 0.61 & 0.66 & 0.62 & 0.38 & 4.91 \\
& Texture + BOW + SVM & 0.82 & 0.62 & 0.69 & 0.25 & 2.60  \\
& Proposed Method & \textbf{0.94} & 0.80 & \textbf{0.85} & \textbf{0.10} & 1.31  \\ 
\hline\hline
\parbox[t]{3mm}{\multirow{12}{*}{\rotatebox[origin=c]{90}{\small \textbf{SWIMSEG}}}} 
& Li et al.\ & 0.90 & 0.86 & 0.88 & 0.11 & 2.06  \\ 
& Souza et al.\ & 0.95 &  0.76 &  0.81 & 0.14 & 2.04 \\ 
& Long et al.\ & 0.71 & \textbf{0.98} & 0.80 & 0.23 & 1.83  \\ 
& Mantelli-Neto et al.\ & 0.70 & 0.97 & 0.79 & 0.24 & 2.16 \\ 
& SLIC + DBSCAN & 0.72 & 0.79 & 0.65 & 0.33 & 5.39 \\ 
& GRAY + SVM & 0.87 & 0.56 & 0.64 & 0.33 & 2.61 \\
& LBP + SVM & 0.62 & 0.65 &  0.63 & 0.36 & 4.73 \\
& ColorHIST + SVM & 0.81 & 0.64 & 0.66 & 0.31 & 2.63  \\
& dSIFT + BOW + SVM & 0.65 & 0.88 & 0.72 & 0.28 & 5.04 \\
& Texture + BOW + SVM & 0.82 & 0.71 & 0.70 & 0.31 & 2.74  \\
& Proposed Method  & \textbf{0.92} & 0.90 & \textbf{0.90} & \textbf{0.09} & 1.89 \\ 
\hline
\end{tabular}
\caption[Performance evaluation of different benchmarking algorithms.]{Performance evaluation using binary ground truth of HYTA and SWIMSEG databases. The best performance according to each criterion is indicated in bold. All experiments are evaluated on the same set of testing images from the HYTA and SWIMSEG databases. We also list the computation time for a single image for all algorithms.}
\label{scoretable}
\end{table}

\section{High-Dynamic-Range Imaging for Cloud Segmentation}
\label{sec:HDRI-segment}
While there have been several studies analyzing clouds and their features from WSI images~\cite{Long,Souza,Li2011,LiuSP2015,ICIP1_2014}, most of them avoid the circumsolar region, because capturing the details in this area is a non-trivial task. In this section, we show how to improve segmentation results by capturing a larger dynamic range of the sky using High-Dynamic-Range Imaging (HDRI) techniques. We then introduce HDRSeg, a graph-cut based segmentation algorithm that uses the HDR radiance map for accurate segmentation of sky/cloud images. Figure~\ref{fig:story-HDRSeg} briefly summarizes our proposed approach.

\begin{figure}[htb]
\centering
\includegraphics[width=0.18\textwidth]{LDR1-E}\hspace{0.5mm}    
\includegraphics[width=0.18\textwidth]{LDR2-E}\hspace{0.5mm} 
\includegraphics[width=0.18\textwidth]{LDR3-E}\hspace{0.5mm}
\includegraphics[width=0.18\textwidth]{tonemapped-E}\hspace{0.5mm}
\includegraphics[width=0.18\textwidth]{binary-E}\hspace{0.5mm}\\
\makebox[0.18\textwidth][c]{(a)}
\makebox[0.18\textwidth][c]{(b)}
\makebox[0.18\textwidth][c]{(c)}
\makebox[0.18\textwidth][c]{(d)}
\makebox[0.18\textwidth][c]{(e)}
\caption[Proposed HDRSeg cloud segmentation approach.]{Proposed HDRSeg cloud segmentation approach. (a) High- (b) Mid- (c) Low-exposure Low-Dynamic-Range (LDR) images; (d) Tonemapped High-Dynamic-Range (HDR) image; (e) Binary output using HDRSeg. Saturated pixels in all images are shown in pink. The number of saturated pixels is significantly reduced in the tonemapped HDR image, without compromising on the fine cloud details.}
\label{fig:story-HDRSeg}
\end{figure}

The motivation is to propose the use of HDR imaging for cloud segmentation in ground-based sky cameras. We have already detailed the process of image capture and storage in our sky camera system an earlier Chapter~\ref{chap:wsi} of this thesis. We showed that using HDR images for cloud imaging significantly reduces the amount of saturated pixels in an image, and is therefore an efficient manner to capture the circumsolar region. Furthermore, HDR imaging generally provides better segmentation results, as compared to LDR images, regardless of the segmentation method used.

\subsection{Cloud Segmentation Using HDRI}
We propose a graph-based segmentation algorithm called HDRSeg, that formulates the sky/cloud segmentation task as a graph-partitioning problem. Graph-cut for cloud segmentation was proposed earlier by Liu et al.~\cite{Liu_AGC}. However, Liu et al.\ used conventional LDR images in their segmentation framework and generated seeds using Otsu threshold~\cite{Otsu79}. Also, they did not consider the circumsolar regions in their evaluation.

\subsubsection{Notations}
Suppose that the low-, mid- and high-exposure LDR sky/cloud images are represented by $\mathbf{Z}_i^{L}$, $\mathbf{Z}_i^{M}$ and $\mathbf{Z}_i^{H}$ respectively, $i=1,\ldots,N_h$, where $N_h$ is the total number of HDR sets in the dataset. Without any loss of generality, $\mathbf{Z}_i$ denotes either low-, mid- or high-exposure LDR image in the subsequent sections. Each of these LDR images are \emph{RGB} color images, $\mathbf{Z}_i \in {\rm I\!\mathbf{R}}^{m \times n \times 3}$, having a dimension $m \times n$ for each \emph{R}, \emph{G} and \emph{B} channels. We generate the HDR radiance map $\mathcal{H}_i \in {\rm I\!\mathbf{R}}^{m \times n \times 3}$ from the set of three LDR images $\mathbf{Z}_i^{L}$, $\mathbf{Z}_i^{M}$ and $\mathbf{Z}_i^{H}$, as described in Section~\ref{sec:HDR-discuss}.

Let $\tilde{p}$ be a sample pixel in the image $\mathbf{Z}_i$. We aim to assign labels to each of the pixels $\tilde{p}$, as either \emph{cloud} or \emph{sky}. We denote the label as $L_{\tilde{p}}$, where $L_{\tilde{p}} = 1 \mbox{ or } 0$ if $\tilde{p}$ is a \emph{cloud} or \emph{sky} pixel, respectively. We model this task as a graph-based discrete labeling problem, wherein we represent $\mathbf{Z}_i$ as a graph, comprising a set of nodes and edges.

\subsubsection{Generating Seeds}
Graph-cut based segmentation algorithms~\cite{Boykov_ICCV} require the user to initially label a few pixels as 'foreground' and 'background'.   We refer to these prior labeled pixels as \emph{seeds}. The process of generating seeds is generally done manually before partitioning the graph into two sub-graphs. In HDRSeg, we automatically generate these initial seeds by assigning a few pixels in the sky/cloud image with \emph{sky} and \emph{cloud} labels.

In our previous Chapter~\ref{chap:colorchannels}, we have performed a systematic analysis of the existing color spaces and components, and observed that $(B-R)/(B+R)$ is one of the most discriminating color channels for cloud segmentation ($B$ and $R$ indicate the blue and red channels of the image). Furthermore, in this current chapter, we have proposed a probabilistic approach for sky/cloud image segmentation, instead of the conventional binary approach. In this probabilistic approach, each pixel is assigned a \emph{soft} membership to belong to \emph{cloud} category, instead of a \emph{hard} membership.

To illustrate these concepts, consider the example shown in Fig.~\ref{fig:see-seeds}. Figure~\ref{fig:see-seeds}(a) shows a sample LDR sky/cloud image $\mathbf{Z}_i$. We extract the $(B-R)/(B+R)$ color channel from this LDR image and show it in Fig.~\ref{fig:see-seeds}(b). A fuzzy c-means clustering on this extracted color channel yields the probabilistic output image, shown in Fig.~\ref{fig:see-seeds}(c). It denotes the confidence level of each pixel to belong to the cloud category. We assume that for a given pixel, the sum of membership values for sky and cloud category is unity.

\begin{figure}[htb]
\centering
\includegraphics[height=0.28\textwidth]{mid-expo}\hspace{0.5mm}    
\includegraphics[height=0.28\textwidth]{BR}\hspace{0.5mm} 
\includegraphics[height=0.28\textwidth]{BR_block_v2}\hspace{0.5mm}\\
\makebox[0.3\textwidth][c]{(a)}
\makebox[0.3\textwidth][c]{(b)}
\makebox[0.3\textwidth][c]{(c)}
\caption[Illustrative example to show the ratio image and probabilistic segmented image.]{Illustrative example to demonstrate the probability of a pixel belonging to the `cloud' category. (a) Sample sky/cloud image; (b) $(B-R)/(B+R)$ color channel image; (c) Probabilistic output image using the method described in Section~\ref{sec:prob-segment}.}
\label{fig:see-seeds}
\end{figure}

In HDRSeg, we apply fuzzy c-means clustering to the $(B-R)/(B+R)$ ratio channel of the HDR radiance map $\mathcal{H}_i$ to estimate the probability of a pixel belonging to the cloud category. We denote the ratio channel as $\tilde{\mathcal{R}}_i$. The membership values obtained by clustering provide us a mechanism in assigning the seeds with a degree of confidence. We assign these initial seeds for HDRSeg as follows: pixels having membership \textgreater $\tilde{\alpha}$ and \textless $(1-{\tilde{\alpha}})$ are labeled as cloud and sky respectively. The value of $\tilde{\alpha}$ is a constant and is set experimentally (more on this below).

\subsubsection{Partitioning the HDR Graph}
The segmentation framework of HDRSeg employs a graph-based image segmentation approach, wherein we represent the ratio-image $\tilde{\mathcal{R}}_i \in {\rm I\!\mathbf{R}}^{m \times n}$ as a set of nodes and edges. Each edge of the graph is given a corresponding weight that measures the dissimilarity between two pixels. We follow the work of Boykov and Jolly~\cite{Boykov_ICCV} and try to minimize the segmentation score $E$:
\begin{equation}\label{eq:agc}
\begin{aligned}
E=\sum_{\tilde{p}}^{}  A_{\tilde{p}} +\mu \sum_{(\tilde{p},\tilde{q}) \in \tilde{\mathcal{N}} ; A_{\tilde{p}} \neq A_{\tilde{q}}}^{}B_{\tilde{p},\tilde{q}},
\end{aligned}
\end{equation}
where $A_{\tilde{p}}$ denotes the data cost for an individual pixel $\tilde{p}$, $B_{\tilde{p},\tilde{q}}$ denotes the interaction cost between two neighboring pixels $\tilde{p}$ and $\tilde{q}$ in a small neighborhood $\tilde{\mathcal{N}}$, and $\mu$ is the weighting parameter.

The complete proposed HDR segmentation algorithm can be summarized as follows:

\begin{algorithm}[htb]
\caption{HDRSeg}
\label{alg:HDRSegalgo} 
\begin{algorithmic}[1]
\Require LDR sky/cloud images with varying EVs.
\Ensure Segmented image.
\State Create HDR radiance map $\mathcal{H}_i$ from bracketted set of LDR images;
\State Extract $(B-R)/(B+R)$ ratio channel $\tilde{\mathcal{R}}_i$ from HDR radiance map $\mathcal{H}_i$;
\State Generate initial seeds from extracted ratio channel for image segmentation;
\State Partition the ratio channel $\tilde{\mathcal{R}}_i$ into two subgraphs using the generated seeds;
\State \textbf{return} Binary segmented image.
\end{algorithmic}
\end{algorithm}

We illustrate the complete HDRSeg segmentation framework in Fig.~\ref{fig:HDRcut}. Figure~\ref{fig:HDRcut}(a) represent the three sample LDR images $\mathbf{Z}_i^{L}$, $\mathbf{Z}_i^{M}$ and $\mathbf{Z}_i^{H}$ respectively captured at $\{-4,-2,0\}$ EV settings. We generate the corresponding HDR radiance map $\mathcal{H}_i$ from these LDR images. A tone-mapped version of $\mathcal{H}_i$ is shown in Fig.~\ref{fig:HDRcut}(b), for visualization purposes. We extract the $(B-R)/(B+R)$ ratio channel from $\mathcal{H}_i$, and generate the initial cloud and sky seeds marked in \emph{green} and \emph{red} color respectively, as shown in Fig.~\ref{fig:HDRcut}(c). The binary output image after graph cut is shown in Fig.~\ref{fig:HDRcut}(d).

\begin{figure}[htb]
\centering
\includegraphics[width=0.15\textwidth]{low-expo}\hspace{0.5mm}    
\includegraphics[width=0.15\textwidth]{mid-expo}\hspace{0.5mm} 
\includegraphics[width=0.15\textwidth]{high-expo}\hspace{0.5mm}
\includegraphics[width=0.15\textwidth]{HDR-tonemap}\hspace{0.5mm}
\includegraphics[width=0.15\textwidth]{seeded-image_v2}\hspace{0.5mm}
\includegraphics[width=0.15\textwidth]{binary-mask}\hspace{0.5mm}\\
\makebox[0.15\textwidth][c]{(a-i)}
\makebox[0.15\textwidth][c]{(a-ii)}
\makebox[0.15\textwidth][c]{(a-iii)}
\makebox[0.15\textwidth][c]{(b)}
\makebox[0.15\textwidth][c]{(c)}
\makebox[0.15\textwidth][c]{(d)}
\caption[Illustrating explaining the proposed HDRSeg framework.]{Proposed HDRSeg framework for sky/cloud segmentation. (a) Exposure bracketed $\{-4,-2,0\}$ Exposure Value (EV) LDR images; (b) High Dynamic Range (HDR) image tone-mapped for visualization purpose; (c) Image with initial seeds, where \emph{cloud} seeds and \emph{sky} seeds are represented in \emph{green} and \emph{red} respectively, and undecided pixels are represented in \emph{yellow}; (d) Binary sky/cloud segmentation result. The saturated pixels in (b), (c) and (d) are masked in pink.}
\label{fig:HDRcut}
\end{figure}

\subsection{Experimental Evaluation}

\subsubsection{HDR Sky/Cloud Image Database}
Currently there are no available HDR image datasets for sky/cloud images. We therefore consider $26$ sets of HDR captures, which comprise a total of $78$ LDR images. Each HDR capture is based on three LDR images (low- ,mid- and high-) which were captured in Automatic Exposure Bracketing (AEB) mode of our camera. These high-quality HDR images are captured with our sky imagers, which we cropped to remove the occlusions by buildings or antennas near the horizon line. The average dimension of the captured LDR images is of $1800 \times 1600$ pixels. They were captured at various times of the day, under different weather conditions. The corresponding ground truth images were manually generated in consultation with experts from the Meteorological Service Singapore (MSS). We perform a detailed evaluation of several cloud segmentation algorithms on this newly created dataset.

\subsubsection{Results}
HDR imaging is an effective technique for cloud observation. It helps us better image the circumsolar region, without saturating the neighboring pixels. To illustrate this fact, we calculate the number of saturated pixels in the low-, med- and high- LDR images. We also calculate the number of saturated pixels (if any) in tonemapped images, in the dataset. Using our HDR techniques, we observe that the tonemapped images have $87.2$ times fewer saturated pixels, as compared to the high-exposure LDR images. Similarly, it has $9.5$ times and $2.0$ times fewer saturated pixels with respect to mid- and low-exposure LDR images.

In addition to containing fewer saturated pixels, HDR imaging also helps in improved cloud segmentation performance, regardless of the techniques used, as we demonstrate in the following. 
Cloud segmentation is essentially a binary classification problem, wherein we classify each pixel as either sky or cloud labels. We report the Precision, Recall and Error values for the different cloud segmentation methods. A detailed definition of these metrics are already provided earlier in Section~\ref{sec:result-segment}.

For evaluation purposes, we benchmark HDRSeg with existing cloud segmentation algorithms. We consider Li et al.~\cite{Li2011}, Long et al.~\cite{Long}, Souza et al.~\cite{Souza} and Mantelli-Neto et al.~\cite{Sylvio}. All these existing algorithms, which were briefly described in Chapter~\ref{chap:litreview}, are designed for conventional LDR images.

We designed our proposed HDRSeg segmentation algorithm on the HDR radiance maps. We extract the $(B-R)/(B+R)$ channel from these high-dynamic radiance maps, and assign the initial seeds for \emph{cloud} and \emph{sky} pixels. The value of $\tilde{\alpha}$ determines the amount of initial seeds in HDRSeg. We empirically set the value of $\tilde{\alpha}$ to $0.98$. We set a high value of $\tilde{\alpha}$, because it corresponds to higher confidence in assigning the correct labels.

Since existing cloud segmentation algorithms are designed for conventional LDR images, we evaluate these current cloud segmentation algorithms on the mid-exposure LDR images as well as the tonemapped images. Our proposed HDRSeg algorithm is the only one designed to make use of the full HDR radiance maps. However, for the sake of comparison, we also evaluate for mid-exposure LDR and tonemapped images. The detailed evaluation results of HDRSeg, along with the other cloud segmentation algorithms, are shown in Table~\ref{tab:scores}.

\begin{table}[htb] % start table environment
\footnotesize
\begin{center} % center the table and caption
% build the table
\begin{tabular}{p{2.2cm}|p{1cm}p{1cm}p{1cm}|p{1cm}p{1cm}p{1.5cm}|p{1cm}p{1cm}p{1.5cm}}
& \multicolumn{3}{c}{Using LDR image} & \multicolumn{3}{c}{Using Tonemapped image} 
			& \multicolumn{3}{c}{Using HDR Luminance map} \\
Methods & \scriptsize{Precision} & \scriptsize{Recall} & \scriptsize{Error [\%]} & \scriptsize{Precision} & \scriptsize{Recall} & \scriptsize{Error [\%]} & \scriptsize{Precision} & \scriptsize{Recall} & \scriptsize{Error [\%]}\\
\hline
Long et al.\ & 0.68 & 0.99 & 31.77 & 0.72 & 0.99 & 27.31 ($\uparrow$) & - & - & -\\
Souza et al.\ & 0.76 & 0.99 & 21.80 & 0.79 & 0.95 & 20.98 ($\uparrow$) & - & - & -\\
Mantelli-Neto et al.\ & 0.69 & \textbf{1.0} & 31.33 & 0.84 & \textbf{1.0} & 15.41 ($\uparrow$) & - & - & -\\
Li et al.\ & 0.90 & 0.90 & 11.93 & 0.79 & 0.92 & 24.45 ($\downarrow$) & - & - & -\\
HDRSeg & 0.77 & 0.98 & 21.12 & 0.81 & 0.95 & 18.93 ($\uparrow$) & \textbf{0.95} & 0.88 & \textbf{10.44} ($\uparrow$) \\
\hline
\end{tabular}
\caption[Comparison of HDRSeg segmentation algorithms with other benchmarking algorithms.]{The average scores across all the images are reported for the various benchmark methods. The \emph{arrow} inside the parenthesis indicates the error performance of the algorithm as compared to its corresponding LDR version. We indicate increase (and decrease) in performance with $\uparrow$ (and $\downarrow$) respectively, when compared with LDR image. The best performance according to each criterion is indicated in bold.} % caption for the table (gives it a number)
\label{tab:scores}
\end{center}
\end{table}

From Table~\ref{tab:scores}, we observe that HDR imaging improves the cloud segmentation performance, irrespective of the methods used. We observe that most of the benchmark algorithms (except for Li et al.) have a better performance with tonemapped images, as compared to mid-exposure LDR image. This is because a tonemapped version exhibits fewer saturated pixels and clearer contrast between sky and cloud, as compared to the corresponding LDR image. However, HDRSeg using the entire HDR luminance map achieves the best error performance of $10.44 \%$ across all the methods.

Most of the other algorithms are biased towards a higher recall value (tendency to over-estimate cloud cover), as compared to precision. These existing algorithms are based on a set of thresholds, either fixed or adaptive, and are therefore more prone to high error percentage. However, HDRSeg uses the entire dynamic range of sky/cloud scenes to make a more informed decision in classifying a pixel as cloud or sky.

\section{Conclusions}
\label{sec:conc}
There are three primary advantages of our proposed segmentation approach compared to other cloud detection algorithms.

First, our cloud segmentation framework is not based on any pre-defined assumptions about color spaces and does not place any restrictions on the type of input images.  We systematically compare different color channels and identify the most suitable ones. We also explain the reason for their better performance based on rigorous statistical evaluations in two datasets.

Second, many existing cloud segmentation algorithms rely on a set of thresholds, conditions, and/or parameters that are manually defined for a particular sky/cloud image database. Our proposed cloud segmentation approach is entirely learning-based and thus provides a systematic solution to training for a given database.

Third, conventional algorithms provide a binary output image from the input sky/cloud image. Although these binary images are informative in most cases, they lack flexibility and robustness. We have no indication of the effectiveness of the thresholding of the input image. In reality, because of the nature of clouds and cloud images, it is undoubtedly better to employ a \emph{soft} thresholding approach. Our proposed approach achieves a probabilistic classification of cloud pixels. This is very informative as it provides a general sense of \emph{belongingness} of pixels to the cloud class. However, as only binary ground-truth images are available, we convert these probability maps into binary images for performing a quantitative evaluation of our algorithm. In our future work, we plan to extend this analysis by creating \emph{probabilistic ground truth} images, where the ground truth of the input images is generated by aggregating  annotations from multiple experts.

Finally, from the extensive experiments on the two datasets (cf.\ Table~\ref{scoretable}), we observe that the performance with images from the SWIMSEG database is generally better than for HYTA, even though the behavior of color channels is similar in both (i.e.\ the same color channels do well for both SWIMSEG and HYTA).  We believe this is because the images in SWIMSEG were captured with a camera that has been calibrated for color, illumination, and geometry~\cite{WAHRSIS}.

Naturally, many challenges remain, for example: How do different weather conditions affect the classification performance?  The weather in Singapore is relatively constant in terms of temperature and humidity, with little variation throughout the year.  Usually it is either partly cloudy, or rainy (in which case the sky will be completely overcast, making segmentation unnecessary). As a result, our database is not suitable for investigating this question. Completely overcast conditions can be dealt with by simple pre-processing of the image before segmentation, e.g.\ by calculating the number of clusters, as we have done in our previous work~\cite{ICIP2015a}.

In this chapter, we have proposed a probabilistic approach using PLS-based regression for the segmentation of ground-based sky/cloud images. Our approach is entirely learning-based and does not require any manually-defined thresholds, conditions, or parameters at any stage of the algorithm. We also release an extensive sky/cloud image database captured with a calibrated ground-based camera that has been annotated with ground-truth segmentation masks. The conventional segmentation techniques are not catered for the circumsolar region, as those particular images are completely saturated. In the later part of this chapter, we solved the cloud segmentation problem for images around the sun using HDRI techniques.

Our future work will include the annotation of a database with probabilistic ground-truth segmentation maps. In the following chapters, we will go beyond segmentation, and devise algorithms to classify clouds into different types~\cite{ICIP2015a}. Also, we will provide theoretical studies in estimating cloud base height for multi-camera setups.

### 2018-07-16 misc/thesis-hardbound/Chapters/Chapter6.tex
Update 16/7/2018

\chapter{Texture-based Image Classification}
\label{chap:classification}

\lhead{Chapter 6. \emph{Texture-based Image Classification}}

In this chapter, we discuss our work on multi-class image classification that is based on an efficient integration of \emph{color} and \emph{texture} cues. We present our proposed classification method to efficiently recognize cloud types from Low Dynamic Range (LDR) sky/cloud image patches. 
Multi-class classification of cloud types from images obtained by ground-based sky cameras is a challenging task. This is because clouds are generally featureless, and conventional machine learning techniques cannot be directly applied on them. Several feature descriptors are therefore developed to extract the most discriminatory cloud features. In this chapter, we systematically study the several features that were developed for cloud classification task. Also, we propose a new filter-bank based classification algorithm that efficiently extracts color and texture information from sky/cloud images, and surpasses the performance of these existing approaches.

\section{Cloud Classification}

The classification of clouds into various types is an important step because individual cloud types have different properties. The most common scheme is the genera-based cloud classification proposed by the World Meteorological Organization (WMO)~\cite{WMO_guide}. It consists of $10$ categories. They can be sorted in $3$ basic groups based on their shapes:
\begin{itemize}
\item Cumulus: heap clouds (cumulus, stratocumulus, altocumulus, cirrocumulus and cumulonimbus)
\item Stratus: layer clouds (stratus, nimbostratus, altostratus and cirrostratus)
\item Cirrus: hair-like/feathery clouds (cirrus, cirrocumulus and cirrostratus)
\end{itemize}
Each genus can be further subdivided into several species and varieties, according to their shape and structure, or their transparency and arrangement inside the cloud. In our specific application of analyzing cloud attenuation in satellite path links~\cite{cloud_model_compare}, we however do not assume such precise categorization. This is because, occurrence of the all types of cloud is not significant in our tropical climate. In tropical countries like Singapore, we do not witness all the various kinds of cloud types. Furthermore, it is not possible to classify into various cloud categories, based on visual inspection only. Moreover, they are too precise for our measurement techniques and our objectives. Therefore, we contrive the $10$ different cloud types into $5$ categories. More details about the $5$ categories will be discussed later in Section~\ref{sec:chap6-exps} of this chapter.

Cloud classification is challenging because clouds are non-rigid in nature and do not have definite structure, color, texture or contour. The inherent difficulty in such problems is that the appearance of an object is heavily dependent on the illumination conditions, camera settings and the other ambient conditions. In the literature, several approaches based on the concept of filter responses and filter banks have been widely used. Gabor filters, Laplacian-of-Gaussian and other wavelet form filters are used in such applications. Moreover, several statistical features viz.\ mean, standard deviation and entropy of color channels are successfully used for cloud type recognition. In this chapter, we attempt to analyze these features from a machine-learning framework. We explore: which features have higher inter-class separability in the feature space, and are thus good candidates for classification?

Conventional feature extraction techniques fail in cloud type recognition task, as clouds are generally \emph{fuzzy} in nature, and do not exhibit any strong features. Therefore, in most cases, color and texture plays the role of dominant cue features. However, a seamless integration of color into a texture classification framework is still an open question. In this chapter, we attempt to solve the question: how can \emph{color} and \emph{texture} cues be combined for an efficient cloud type recognition task?

\section{Outline of Our Contribution}
In this chapter, we discuss our proposed methodology to efficiently integrate \emph{texture} and \emph{color} cues for robust image classification. We evaluate the efficacy of several cloud features that were specifically designed for cloud type recognition. A systematic selection of color channel and texture parameters of cloud images is an important step for better classification results. We propose a filter-bank based cloud classification framework, that is competitive with respect to the state-of-the-art algorithms. We release the first large-scale cloud categorization database called SWIMCAT to the research community. SWIMCAT stands for Singapore Whole sky IMaging CATegories Database, containing $784$ images categorized in $5$ distinct categories: clear sky, patterned clouds, thick dark clouds, thick white clouds, and veil clouds. In this chapter, we will present a thorough analysis of the proposed classification algorithm for the task of cloud type recognition.

The main contributions of this chapter include: 
\begin{itemize}
\item A novel cloud classification framework which is extensively studied and tested in cloud images obtained in a tropical region like Singapore.
\item Extensive evaluation of different cloud features in a large-scale cloud category database.
\item Introduction of the first publicly-available, large-scale cloud category database called SWIMCAT, for further benchmark analysis.
\end{itemize}

The rest of this chapter is organized as follows. In Section~\ref{sec:chap6-features}, we analyze the different existing features that were developed for the task of cloud classification. We visualize these features, and identify the shortcomings of the existing methods. In this chapter, we perform a systematic analysis of the \emph{color} and \emph{texture} cues of sky/cloud images, and propose a complete framework in Section~\ref{sec:chap6-proposed} for cloud type recognition. Evaluation metrics and the first publicly available cloud categorization database are introduced in Section~\ref{sec:chap6-exps}. We discuss our classification results in Section~\ref{sec:chap6-results}. Finally, Section~\ref{sec:chap6-conclude} concludes the chapter.

\section{Cloud Features}
\label{sec:chap6-features}
In this section, we will briefly go through the several features that were designed for effective cloud type classification. Suppose that a sample sky/cloud image is represented by $\mathbf{Z}_i \in {\rm I\!\mathbf{R}}^{m \times n \times 3}$,$i=1,2,\ldots,N$ which is an \emph{RGB} image in a dataset consisting of $N$ images. We assume that there are a total of $\overline{p}$ classes, and each category consists of $\overline{q}$ sky/cloud images. The corresponding $R$,$G$, $B$ images of $\mathbf{X}_i$ are represented by $\mathbf{Z}_i^{R}$, $\mathbf{Z}_i^{G}$ and $\mathbf{Z}_i^{B}$ respectively. Heinle et al.\ \cite{Heinle2010} uses a combination of these channels to design discriminatory features. Most of the other features were designed on the corresponding gray-scale image $\overline{\mathbf{Z}}_i$. For the sake of brevity and without the loss of generality, we will drop the index $i$ in our subsequent discussions of this chapter.

\subsection{Statistical Features (SF)}
Statistical Features (SF) were widely used by ~\cite{cloud_LBP,satellite03}. It consists of calculating several statistical measures from an image such as mean, median, standard deviation, skewness and kurtosis. These features provide a overall sense of the color of the image and its variation. For example, the gray-scale version of a thick dark cloud will be \emph{darker} than a corresponding clear sky patch. The vectorized form of the gray-scale image $\overline{\mathbf{Z}}$ is represented as $\overline{\mathbf{z}}$. We derive the statistical features on the vectorized image. We calculate the mean, median, standard deviation, skewness and kurtosis on the vectorized image and represent it as $\overline{\mathbf{z}}_m$, $\overline{\mathbf{z}}_d$, $\overline{\mathbf{z}}_v$, $\overline{\mathbf{z}}_w$ and $\overline{\mathbf{z}}_k$ respectively. The SF feature is formed by concatenation all these measures together to form a $5$-dimensional feature vector [$\overline{\mathbf{z}}_m$, $\overline{\mathbf{z}}_d$, $\overline{\mathbf{z}}_v$, $\overline{\mathbf{z}}_w$, $\overline{\mathbf{z}}_k$] from a single gray-scale image $\overline{\mathbf{Z}}$. The SF do not take into account the spatial dependencies of the pixel values.

\subsection{Spatial Gray Level Dependence Matrices (SGLDM)}
Haralick et al.\ in ~\cite{Haralick73} proposed a texture feature that takes into account the spatial dependency of the gray-scale pixel values in an image. This feature indicates the probability that two pixels have the same gray-level values for a specific distance in a given orientation. We represent this in the form of a matrix called Gray-Level Co-occurrence Matrix (GLCM). We calculate the corresponding $8$-level quantized image of the gray-scale cloud image $\overline{\mathbf{Z}}$, and measure the spatial dependencies of two pixels with the same quantized value. For a particular pixel-of-interest in $\overline{\mathbf{Z}}$, we check the corresponding pixels which are oriented at angles of $0^{\circ}$, $45^{\circ}$, $90^{\circ}$ and $135^{\circ}$. This helps in distinguishing clouds having a regular pattern, as compared to other cloud types. Once GLCMs are calculated for the four different orientations, we calculate $13$ statistical measures for each of these orientations. We compute the angular second moment, contrast, correlation, sum of squares, inverse difference moment, sum average, sum variance, sum entropy, entropy, difference variance, difference entropy, and two information measures of correlation. The corresponding means and ranges of these $13$ statistical measures are computed across the $4$ directions. We concatenate the mean values of these $13$ measures and represent it as $\mbox{SGLDM}_m$. The corresponding feature with range values is called $\mbox{SGLDM}_r$.

\subsection{Gray Level Difference Statistics (GLDS)}
Gray Level Difference Statistics (GLDS) is a subset feature from SGLDM. It is developed by Weszka et al.\ ~\cite{Weszka76} and has been originally used for terrain classification. It is now used for the task of cloud classification as well. We compute the gray-level co-occurrence matrix for the four orientations of $0^{\circ}$, $45^{\circ}$, $90^{\circ}$ and $135^{\circ}$. The means of these four matrices are calculated, and we denote the $4$-dimensional feature vector as GLDS.

\subsection{Fractal Feature (FF)}
Wu et al.\ in ~\cite{Wu92} developed a multi-resolution feature descriptor that provides good classification accuracy for ultrasonic liver images, as compared to other textural features. This feature describes the overall \emph{roughness} in an image, which is based on fractal geometry in an image. This fractal dimension is represented using the Hurst exponent. We use the gray-scale cloud image $\overline{\mathbf{Z}}$, and compute three multi-resolution versions at ratios $1$, $1/2$ and $1/3$. The Hurst exponents are calculated for these $3$ versions, and we generate a $3$-dimensional fractal feature vector.

\subsection{Fourier Magnitude (FM)}
The fourier transform is one of the conventional techniques to study the patterns in an image. In this case, we first generate the Fast Fourier Transform (FFT) of gray-scale cloud image $\overline{\mathbf{Z}}$. The FFT output contains both the magnitude and phase component. We use the magnitude component as the Fourier Magnitude (FM) feature vector for the image.

\subsection{Heinle Feature (HF)}
Heinle in ~\cite{Heinle2010} proposed a $12$-dimensional feature for the task of cloud type recognition. It uses all the red, green and blue color channels, $\mathbf{Z}^R$, $\mathbf{Z}^G$ and $\mathbf{Z}^B$. Heinle Feature (HF) computes the following: the average of red and blue channel, standard deviation and skewness of blue channel, the average difference between red and green, red and blue, and green and blue. It also generates the GLCM matrix from the blue channel, and extracts the energy, contrast, homogeneity and entropy from it. The last dimension of the $12$-dimensional feature vector is the cloud cover, which is generated from the blue channel.

\subsection{Local Binary Pattern (LBP)}
Local Binary Pattern (LBP) is a popular feature descriptor technique that is widely used in the computer vision community. It captures the distribution of gray-scale pixels in $8$-point neighborhood of a pixel value. LBP is a popular technique for feature extraction as it is invariant to illumination changes. Liu and Zhang in ~\cite{Liu16} used LBP in ground-based cloud classification. We use the LBP pattern of gray-scale cloud image $\overline{\mathbf{Z}}$ for our evaluation.

\subsection{Scale Invariant Feature Transform (SIFT)}

Scale Invariant Feature Transform (SIFT) is another popular technique developed in computer vision community~\cite{SIFT}. It generates a collection of descriptors from an image that are invariant to an affine rotation, translation and scaling. It is also robust to illumination changes. SIFT has been used in numerous applications. Wu et al.\ in ~\cite{Wu15SIFT} has extracted SIFT features from ground-based images to identify $4$ distinct cloud conditions. For our analysis, we compute the SIFT descriptor on the gray-scale cloud image $\overline{\mathbf{Z}}$. Each descriptor is a $128$-dimensional vector, and subsequently all descriptors are concatenated together to form a single feature vector.

These features have been used extensively for cloud type recognition at several occasions. However, there is no unified study on all these $9$ cloud features. In a conventional classification framework, these feature descriptors are generated and used as an input in a classifier model (SVM, KNN etc.). In this chapter, we ask this question: does these \emph{designed} cloud features help in increasing the inter-class separability, leading to an increased classification accuracy?

\section{Proposed Classification Approach}
\label{sec:chap6-proposed}
The existing cloud features are useful in identifying the color spaces and textural features for cloud type recognition. However, the classification results using these features are low. In this section, we propose a cloud classification framework that integrates color and texture cues efficiently to provide higher classification accuracy. Our approach is based on the original Varma and Zisserman's texton approach~\cite{varma_ziss2005}.

In the original texton approach~\cite{varma_ziss2005}, the gray-scale input images are first convolved with a set of filters from a filter bank. These responses are clustered using k-means clustering to generate a set of cluster centers, which are called \emph{textons}. The process is repeated separately for all the classes. The generated textons from each classes are combined together to form a \emph{texton dictionary}. The individual classes are finally modeled using a histogram distribution of the individual textons from the dictionary. In our proposed cloud  classification methodology, we modify the original texton-based method primarily in two distinct ways.

\begin{enumerate}
\item We generate the texton dictionary by exploiting the inherent information across categories. 
\item Instead of a gray-scale image, we incorporate color into the classification framework in a systematic manner.
\end{enumerate}

Firstly, in the original approach, the set of textons are generated individually for each categories. In most cases, the differences between images across several categories are faint. This results in the generation of \emph{similar} textons in the dictionary, leading to a higher mismatch in the model creation stage. The motivation of any classification algorithm is to generate appropriate discriminative models for each categories. In our proposed approach, we aggregate the filter responses of the training images across all the categories. We use conventional k-means clustering on this concatenated filter response instead of individual classes' filter responses. The generated cluster centers are the modified textons. Subsequently, discriminative histogram for each category is generated. Our method uses the minimum number of textons and help in a compact and relevant representation of the input data space.

Secondly, the original texton-based approach works on gray-scale image. Several methods have been introduced in the literature that exploits both color and texture in a single framework. One of the popular extensions to gray-scale texton-based classification is to apply the methodology separately to different color channels and components. The responses are then integrated into representative histograms of different categories. However, no clear analysis has been carried out which color channels are the most representative candidates in this approach? Usually, an educated guess is taken on what color spaces seem to appropriately represent the different features ably. In ~\cite{Sun2009}, Sun and He generate the composite feature vector by combining both filter response and RGB color vector. Burghouts and Geusebroek in ~\cite{bur2006} have treated color as a separate entity and added it as a post-processing step. In our proposed approach for cloud categorization task, we systematically choose the color channel that is best suited for this task.

\subsection{Feature Descriptor}

In our earlier Chapter~\ref{chap:colorchannels}, we identified the color channels that are optimum for cloud type recognition. 
For the sample image $\mathbf{Z}_i \in {\rm I\!\mathbf{R}}^{m \times n \times 3}$, we extract the particular channel and refer as $\mathcal{R} \in {\rm I\!\mathbf{R}}^{m \times n}$. More details on this ratio channel can be found later in this chapter in Section~\ref{sec:chap6-optimalparams}. We convolve this color channel with the set of filters $\mathcal{F}_1, \mathcal{F}_2,\ldots,\mathcal{F}_{n_f}$ from the filter bank.

\begin{equation*}
\label{eq:conv}
\mathbf{Y}=(\mathcal{F}_1 * \mathcal{R}(x,y),...,\mathcal{F}_{n_f} * \mathcal{R}(x,y)); \forall (x,y) \epsilon {\rm I\!\mathbf{R}} 
\end{equation*}

This convolution operation is executed for all $\bar{q}$ images in the category. Also, the same is replicated across all the $\overline{p}$ categories. We obtain the concatenated matrix by aggregating the filter responses of the images across all categories. This aggregated matrix is the combined filter response; and we denote it by $\mathbf{Z}_{\Delta} \in {\rm I\!\mathbf{R}}^{m \times n \times {n_f} \times \bar{q} \times \overline{p}}$.

\subsection{Discriminative Model}
The filter responses for $mn$ pixels in the stacked filter response $\mathbf{Z}_{\Delta} \in {\rm I\!\mathbf{R}}^{m \times n \times {n_f} \times \overline{q} \times \overline{p}}$ are highly correlated with each other. We perform a general k-means clustering process in this stacked filter response matrix in order to find its subspace representation. The $n_t$ generated cluster centers are referred as the modified-textons in our classification framework. We illustrate this process in Fig.~\ref{fig:frmwrk}.

\begin{figure}[htbp]
\centering
\includegraphics[width=0.9\textwidth]{flow_chart.pdf}
\caption[Proposed texton-based framework for cloud type recognition.]{Texton generation in our proposed cloud classification approach. Sky/cloud images from individual categories are convolved with filter bank. The generated filter responses are aggregated across the categories. The textons are generated from the k-means cluster of the concatenated filter response.}
\label{fig:frmwrk}
\end{figure}

The frequency of occurrence of textons is a distinguishing feature for each category. For an individual image in each category, we compare the filter response at each pixel with every textons from the texton dictionary. Out of the $n_t$ textons, the one having the least $2$D Euclidean norm is mapped to the particular pixel. Thereby, we generate a texton map from each of the individual images of a category. The histogram generated from the texton map give us an indication of the frequency distribution of the textons in a single image. We average the $\overline{q}$ images in a category to determine the histogram $h_{\hat{j}}^{\mbox{class}}, \hat{j}=1,2,..,\overline{p}$.

\subsection{Classification Metric}
The testing stage of our classification framework involves the assignment of a category to each of the testing image. We generate the test histogram $h_{\hat{j}}^{\mbox{test}}$ using the textons in the texton dictionary. The generated histogram $h_{\hat{j}}^{\mbox{test}}$ is compared with each of the $\hat{j}$ model histograms one-by-one using $\chi^2$ statistic. This distance metric is shown in Eq.~\ref{eq:chi_metric}.

\begin{equation}
\label{eq:chi_metric}
\chi^2=\frac{1}{2}\sum_{ }^{ }\frac{(h_{\hat{j}}^{\mbox{class}}-h_{\hat{j}}^{\mbox{test}})^2}{(h_{\hat{j}}^{\mbox{class}}+h_{\hat{j}}^{\mbox{test}})^2}
\end{equation}

This distance metric describes how unlikely a particular distribution is drawn from a given distribution. The category having the least $\chi^2$ distance is the assigned category for the test image. In our case, the number of bins is fixed for training and test histograms. Therefore, we do not suffer from any disadvantages in using this bin-by-bin dissimilarity metric.

\section{Experimental Evaluations}
\label{sec:chap6-exps}
\subsection{Evaluation Metric}
Let $TP$, $TN$, $FP$, $FN$ denote true positive, true negative, false positive and false negative respectively in a binary classification task. The performance of a general binary classification task is measured using precision and recall. They are described as $\mbox{Precision}=\frac{TP}{TP+FP}$ and $\mbox{Recall}=\frac{TP}{TP+FN}$ respectively.

However, in our task of cloud type recognition, we need an evaluation metric that is applicable for multi-class classification problem. Therefore, we report the following metrics to evaluate the performance: a) Average accuracy, b) Macro- precision and recall, c) Micro- precision and recall.

\subsubsection{Average accuracy}
One of the most common metrics is accuracy, that represents the ratio of correctly matched classification results. We report the average accuracy value across the $\overline{p}$ categories. It is defined as: $\mbox{Accuracy}=\frac{1}{\overline{p}}\sum_{\hat{j}=1}^{\overline{p}}\frac{TP_{\hat{j}}+TN_{\hat{j}}}{TP_{\hat{j}}+FP_{\hat{j}}+TN_{\hat{j}}+FN_{\hat{j}}}$.

\subsubsection{Macro- averaged values}
Macro- averaged values provide an indication of the general performance of the classification framework. It provides equal weight to each categories. Macro- precision and recall for our multi-class classification task are described as $P_{macro}=\frac{1}{\overline{p}}\sum_{{\hat{j}}=1}^{\overline{p}}\frac{TP_{\hat{j}}}{TP_{\hat{j}}+FP_{\hat{j}}}$ and $R_{macro}=\frac{1}{\overline{p}}\sum_{{\hat{j}}=1}^{\overline{p}}\frac{TP_{\hat{j}}}{TP_{\hat{j}}+FN_{\hat{j}}}$ respectively.

\subsubsection{Micro- averaged values}
Micro- average values, on the other hand, provide equal weights to per-image classification performance. Micro- precision and recall for our multi-class classification task are described as $P_{micro}=\frac{\sum_{\hat{j}=1}^{\overline{p}}TP_{\hat{j}}}{\sum_{\hat{j}=1}^{\overline{p}}TP_{\hat{j}}+\sum_{\hat{j}=1}^{\overline{p}}FP_{\hat{j}}}$ and $R_{micro}=\frac{\sum_{\hat{j}=1}^{\overline{p}}TP_{\hat{j}}}{\sum_{\hat{j}=1}^{\overline{p}}TP_{\hat{j}}+\sum_{\hat{j}=1}^{\overline{p}}FN_{\hat{j}}}$ respectively.

These evaluation metrics should be evaluated on a multi-class categorization database, along with the other state-of-the-art algorithms. Unfortunately, most of the existing works in the literature use proprietary images that are not publicly available. In the next section, we will discuss more on this drawback.

\subsection{SWIMCAT Database}
While there has been extensive work on sky/cloud images image analysis captured by ground-based cameras by a number of research groups around the world, public benchmarking databases in this domain are rare. We therefore created our own database for this purpose, which we call \textbf{SWIMCAT} (\textbf{S}ingapore \textbf{W}hole-sky \textbf{IM}aging \textbf{CAT}egories database)~\footnote{The SWIMCAT database is available for download from \url{http://vintage.winklerbros.net/swimcat.html}.}. This is the first of its kind in the application of automatic cloud classification.

\subsubsection{Image acquisition}
SWIMCAT contains images captured using WAHRSIS, a calibrated ground-based whole sky imager, which was designed by us~\cite{WAHRSIS}. We selected a total of $784$ patches comprising $5$ cloud categories from images that were captured in Singapore over the period January $2013$ to May $2014$.  The $5$ categories of clear sky, patterned clouds, thick dark clouds, thick white clouds, and veil clouds are defined based on visual features of sky/cloud conditions, in consultation with experts from the Singapore Meteorological Services. All image patches are of dimension $125 \times 125$ pixels. A representative image from each category is shown in Fig.~\ref{fig:cloud_classes}.

\begin{figure}[htbp]
\centering
\includegraphics[width=0.17\textwidth]{clear_sky.pdf}
\includegraphics[width=0.17\textwidth]{pattern_cloud.pdf}
\includegraphics[width=0.17\textwidth]{thick_dark_cloud.pdf}
\includegraphics[width=0.17\textwidth]{thick_white_cloud.pdf}
\includegraphics[width=0.17\textwidth]{veil_cloud.pdf}
\caption[Various cloud classes of SWIMCAT database.]{(a) Clear sky (b) Patterned clouds (c) Thick dark clouds (d) Thick white clouds (e) Veil clouds}
\label{fig:cloud_classes}
\end{figure}

\subsubsection{Patch generation}
The images captured by WAHRSIS are distorted owing to the fish eye lens of its imaging system. We model its fish eye lens using the geometric calibration function. By virtue of this calibration function, we can successfully relate every pixel of the captured image to the corresponding azimuth and elevation angle of the incident ray. We use ray tracing approach to generate undistorted cropped images. The camera is assumed to lie in the center of an hemisphere. We use a constant view angle of $15^{\circ}$ to generate output images having a fixed dimension $125 \times 125$, as illustrated in Fig.~\ref{fig:chap6-undistortion-results}. This process is continued for varying sets of azimuth and elevation angles.

\begin{figure}[htbp]
\centering   
\subfloat[Input image with the representation of the borders and diagonals of the output image]{\includegraphics[width=0.35\textwidth]{undistortion-original-mask}}\hspace{1em}
\subfloat[Output image]{\includegraphics[width=0.35\textwidth]{undistortion-result}}
\caption{Process to generate image patches of fixed dimension $125 \times 125$.}
\label{fig:chap6-undistortion-results}
\end{figure}

This process of generating image patches is performed for several input images. Out of the generated image patches, a few images contain occlusion because of the neighboring buildings and surroundings. These patches are discarded from the database.

\section{Classification Results}
\label{sec:chap6-results}
In this section, we will provide a detailed analysis of the existing cloud features on SWIMCAT dataset. Our proposed approach based on texton-based classification is also evaluated on this dataset. We identify the most discriminatory cloud features in this task. However, the multi-class accuracy results using existing features is not high. We, thereby, provide the results of our proposed approach.

\subsection{Cloud Features}
The objectives of extracting features from sky/cloud images is to represent the various classes in the most discriminatory manner. A higher inter-class separation in the feature space representation indicate good candidates for classification.

We extract the features on all the $784$ images of the dataset. The features SF, $\mbox{SGLDM}_m$, $\mbox{SGLDM}_r$, GLDS, FF, FM, LBP and SIFT are extracted from the gray-scale versions of the SWIMCAT dataset. The HF features are generated from a combination of red and blue channels of the image. These existing features are of different dimensions, and encode the discriminatory cues in the feature space. The dimensions of these feature vectors are high, and it is not possible to visualize them in their original feature space.

Dimensionality reduction techniques are therefore, extensively used to project the higher dimension vectors into a lower dimension subspace. We use the Principal Component Analysis (PCA) to perform the dimensionality reduction of our feature vectors. PCA aims to transform the original feature space into distinct orthogonal axes, such that these new axes capture the maximum variance of the input data.

\begin{figure}[htb]
\centering
\includegraphics[height=3.2cm]{separate_f1n}
\includegraphics[height=3.2cm]{separate_f2n}
\includegraphics[height=3.2cm]{separate_f3n}\\
\makebox[0.31\textwidth][c]{\hspace{3cm} \small(a) SF}
\makebox[0.31\textwidth][c]{\small (b) $\mbox{SGLDM}_m$}
\makebox[0.31\textwidth][c]{\hspace{-2.5cm} \small (c) $\mbox{SGLDM}_r$}\\
\includegraphics[height=3.2cm]{separate_f4n}
\includegraphics[height=3.2cm]{separate_f5n}
\includegraphics[height=3.3cm]{separate_f6n}\\
\makebox[0.31\textwidth][c]{\hspace{3cm} \small (d) GLDS}
\makebox[0.31\textwidth][c]{\small (e) FF}
\makebox[0.31\textwidth][c]{\hspace{-2.5cm} \small (f) FM}\\
\includegraphics[height=3cm]{separate_f7n}
\includegraphics[height=3cm]{separate_f8n}
\includegraphics[height=3cm]{separate_f9n}\\
\makebox[0.31\textwidth][c]{\hspace{3cm} \small (d) HF}
\makebox[0.31\textwidth][c]{\small (e) LBP}
\makebox[0.31\textwidth][c]{\hspace{-2.5cm} \small (f) SIFT}\\
\caption[Visual representation of various cloud features in lower dimensional subspace.]{Each data point represents an image in the SWIMCAT dataset, and each color represents individual classes. The five categories: clear sky, patterned clouds, thick dark clouds, thick white clouds and veil clouds are represented in red, green, blue, cyan and magenta markers.}
\label{fig:separation}
\end{figure}

Figure~\ref{fig:cloud_classes} shows the dimensionality reduction results for the different features. The SF feature separates the various classes comparatively well. This is because the variations in color between sky, dark clouds and white clouds are quite distinct. However, there is an overlap between patterned clouds and white clouds, as their average color of the two classes are quite similar. The $\mbox{SGLDM}_m$, $\mbox{SGLDM}_r$ features are based on GLCM matrices, and we observe that there is a high correlation between the features of different classes. The patterned clouds stand out in $\mbox{SGLDM}_r$, as they have a distinctive texture pattern. The GLDS feature is based on GLCM matrix, and we observe the same observation in its representation. The patterned clouds (represented in green) have clear separation with respect to the other cloud classes. The FF perform poorly, as the roughness is not a discriminatory feature cue between the $5$ cloud classes. We also observe that, in FM, the variation is observed mainly along the first principal axis. On the other hand, the HF uses a combination of red and blue channels' statistics, and cloud coverage measure to discriminate between the individual classes. The conventional computer vision techniques of LBP and SIFT fail to separate the different cloud classes.

\subsection{Optimal Parameter Selection}
\label{sec:chap6-optimalparams}
Our proposed texton-based approach is dependent on a number of parameters viz.\ color channel, set of filters in the filter bank, dimensions of the filters, and the number of textons needed in the clustering process. In this section, we will provide a detailed evaluation of these parameters for our proposed approach.

\subsubsection{Color Channel}
Based on the results of an earlier analysis of color channels we conducted in Chapter~\ref{chap:colorchannels}, we check the performance of Saturation ($S$) channel of the HSV color space, various common red-blue combinations ($R/B$, $R-B$, $\frac{B-R}{B+R}$), and chroma $C=\mbox{max}(R,G,B)-\mbox{min}(R,G,B)$. All other parameters are kept fixed (Filter set $3$, dimension $49 \times 49$, $30$ textons). From Table~\ref{tab:perform-eval}, it is observed that most of the color channels work well for sky, patterned clouds and thick white clouds because of their distinctive texture and color. Thick dark clouds have a low saturation component and are therefore correctly classified by color channel $S$ and $R/B$. The best performing color channel $R/B$ is selected for our final classification task.

\definecolor{Gray}{gray}{0.8}
\begin{table}[htb]
\scriptsize
\centering
%\begin{tabular}{ |rr||c|c|c|c|c|c|c|c|c|c| }
\begin{tabular}{ |rr||L|L|L|L|L|L|L|L|L|L| }
%\begin{tabularx}{0.5\textwidth}{ |XX||X|X|X|X|X|X|X|X|X|X|X|X| }
\hline
%& & \multicolumn{10}{c|}{\textbf{Performance Evaluation of different cloud types}}\\
& & Sky & Pattern Clouds & Thick Dark Clouds & Thick White Clouds & Veil Clouds & Average & $P_{macro}$ & $R_{macro}$ & $P_{micro}$ & $R_{micro}$ \\ 
%& &  & Clouds & Dark & White & Clouds &  &  &  &  &  \\ 
\hline\hline
\parbox[t]{3mm}{\multirow{5}{*}{\rotatebox[origin=c]{90}{Channels}}} & S & 0.96 & 1.00 & 0.82 & 0.93 & 0.82 & 0.91 & 0.91 & 0.91 & 0.87 & 0.84 \\ %\cline{2-12}\cline{2-5}
& \cellcolor{Gray} $R/B$ & \cellcolor{Gray}1.00 & \cellcolor{Gray}1.00 & \cellcolor{Gray}0.98 & \cellcolor{Gray}1.00 & \cellcolor{Gray}0.69 & \cellcolor{Gray}0.93 & \cellcolor{Gray}0.94 & \cellcolor{Gray}0.93 & \cellcolor{Gray}1.00 & \cellcolor{Gray}0.75\\ %\cline{2-12}
& $R-B$ & 0.93 & 1.00 & 0.09 & 1.00 & 0.91 & 0.79 & 0.79 & 0.79 & 0.92 & 0.89 \\ %\cline{2-12}
& $\frac{B-R}{B+R}$ & 0.76 & 0.98 & 0.38 & 1.00 & 0.60 & 0.74 & 0.78 & 0.74 & 0.97 & 0.65 \\ %\cline{2-12}
& $C$ & 0.91 & 1.00 & 0.38 & 1.00 & 0.91 & 0.84 & 0.87 & 0.84 & 0.95 & 0.90 \\ %\cline{2-12}\hline
\hline\hline
\parbox[t]{3mm}{\multirow{5}{*}{\rotatebox[origin=c]{90}{Filter sets}}} & Set 1 & 1.00& 1.00& 0.49 & 0.78 & 0.89 & 0.83 & 0.86 & 0.83 & 0.86 & 0.88 \\ %\cline{2-12}
& Set 2 & 0.98 & 1.00& 0.60 & 0.78 & 0.89 & 0.85 & 0.87 &	0.85 & 0.88 & 0.88\\ %\cline{2-12}
& \cellcolor{Gray}Set 3 & \cellcolor{Gray}1.00 & \cellcolor{Gray}1.00 & \cellcolor{Gray}0.93 & \cellcolor{Gray}1.00 & \cellcolor{Gray}0.70 & \cellcolor{Gray}0.92 & \cellcolor{Gray}0.93 &	\cellcolor{Gray}0.92 & \cellcolor{Gray}0.96 & \cellcolor{Gray}0.76\\ %\cline{2-12}
& Set 4 & 1.00& 1.00& 0.53 & 0.78 & 0.89 & 0.84 &	0.86 & 0.84 & 0.88 & 0.88 \\ %\cline{2-12}
& Set 5 & 0.98 & 1.00& 0.47 & 0.78 & 0.89 & 0.82 & 0.85 &	0.82 & 0.86 & 0.88 \\ %\cline{2-12}
\hline\hline
\parbox[t]{3mm}{\multirow{9}{*}{\rotatebox[origin=c]{90}{Filter dimension}}} & 19 $\times$  19 & 0.98 & 0.93 & 0.47 & 0.78 & 0.91 & 0.81 & 0.85 & 0.81 &	0.95 & 0.90 \\ %\cline{2-12}
& 29 $\times$  29 & 1.00& 0.78 & 0.51 & 0.78 & 0.67 & 0.75 & 0.78 &	0.75 & 0.79 & 0.69 \\ %\cline{2-12}
& 39 $\times$  39 & 1.00& 0.98 & 0.38 & 0.76 & 0.82 & 0.79 & 0.83 &	0.79 & 0.97 & 0.82 \\ %\cline{2-12}
& \cellcolor{Gray}49 $\times$  49 & \cellcolor{Gray}1.00 & \cellcolor{Gray}1.00 & \cellcolor{Gray}0.97 & \cellcolor{Gray}1.00 & \cellcolor{Gray}0.68 &	\cellcolor{Gray}0.93 & \cellcolor{Gray}0.94 & \cellcolor{Gray}0.93 & \cellcolor{Gray}0.97 & \cellcolor{Gray}0.75 \\ %\cline{2-12}
& 59 $\times$  59 & 0.98 & 1.00& 0.64 & 0.76 & 0.89 & 0.85 & 0.87 &	0.85 & 0.91 & 0.89 \\ %\cline{2-12}
& 69 $\times$  69 & 0.98 & 0.84 & 0.64 & 0.58 & 0.87 & 0.78 & 0.79 & 0.78 & 0.69 & 0.85 \\ %\cline{2-12}
& 79 $\times$  79 & 0.98 & 0.71 & 0.58 & 0.51 & 0.84 & 0.72 & 0.75 & 0.72 &	0.59 & 0.82\\ %\cline{2-12}
& 89 $\times$  89 & 0.98 & 0.71 & 0.69 & 0.47 & 0.87 & 0.74 & 0.76 & 0.74 & 0.57 & 0.85 \\ %\cline{2-12}
& 99 $\times$  99 & 1.00& 0.69 & 0.58 & 0.24 & 0.87 & 0.68 & 0.68 &	0.68 & 0.52 & 0.84 \\ %\cline{2-12}
\hline\hline
\parbox[t]{3mm}{\multirow{10}{*}{\rotatebox[origin=c]{90}{Number of textons \mbox{ }}}} & 10 & 1.00& 0.44 & 0.78 & 0.76 & 0.47 & 0.69 & 0.69 &	0.69 & 0.53 & 0.56\\ %\cline{2-12}
& 20 & 0.98 &	0.98	& 0.42 & 0.8 &	0.82 &	0.80 & 0.84 &	0.80 &	0.95 &	0.82\\ %\cline{2-12}
& \cellcolor{Gray}30 & \cellcolor{Gray}1.00 &	\cellcolor{Gray}1.00 & \cellcolor{Gray}0.97 & \cellcolor{Gray}1.00 & \cellcolor{Gray}0.68 & \cellcolor{Gray}0.93 & \cellcolor{Gray}0.94 & \cellcolor{Gray}0.93 &	\cellcolor{Gray}1.00 & \cellcolor{Gray}0.75\\ %\cline{2-12}
& 40 & 1.00&	1.00 &	0.62 &	0.78 &	0.91 &	0.86 &	0.87 &	0.86 &	0.91 & 0.91\\ %\cline{2-12}
& 50 & 1.00& 1.00& 0.56 & 0.80 & 0.91 & 0.85 &	0.87 & 0.85 & 0.93 & 0.91 \\ %\cline{2-12}
& 60 & 0.98 & 1.00& 0.58 & 0.82 & 0.89 & 0.85 & 0.88 &	0.85 & 0.91 & 0.89 \\ %\cline{2-12}
& 70 & 0.98 & 1.00& 0.56 & 0.82 & 0.89 & 0.85 & 0.87 &	0.85 & 0.91 & 0.88 \\ %\cline{2-12}
& 80 & 0.98 & 	1.00 &	0.60 &	0.80 &	0.89 &	0.85 &	0.87 &	0.85 &	0.93 &	0.89 \\ %\cline{2-12}
& 90 & 0.98 & 1.00& 0.58 & 0.82 & 0.89 & 0.85 & 0.87 &	0.85 & 0.93 & 0.89 \\ %\cline{2-12}
& 100 & 0.98 & 1.00& 0.60 & 0.82 & 0.91 & 0.86 & 0.88 &	0.86 & 0.93 & 0.91 \\ %\cline{2-12}\hline
\hline
\end{tabular}
\caption[Extensive evaluation of different parameters in our proposed cloud classification approach.]{Performance evaluation of sky/cloud recognition rates for different color channels, filter sets, filter dimensions, and number of textons. The best performing parameters are highlighted.}
\label{tab:perform-eval}
\end{table}

\subsubsection{Filter Set}
For our experiments, we use different sets of S-filters that aim to capture the majority of frequency components, and subsequently choose the most suitable filter set. Table~\ref{filter_table} shows the ($\hat{\sigma}$,$\hat{\tau}$) pairs for various scenarios, where $\hat{\sigma}$ denotes the scale of the filter in the filter set and $\hat{\tau}$ represents the number of cycles inside the gaussian envelope of the filter set. The individual filters are $L_1$-normalized before convolution with the input images.

\begin{table}[htb]
\footnotesize 
\centering
\definecolor{Gray}{gray}{0.92}
\begin{tabular}{r|ccccc}%{0.5\textwidth}{|X||X |X |X|X|X |X|}
\hline 
\scriptsize 
($\hat{\sigma}$,$\hat{\tau}$) & Set 1 & Set 2 & Set 3 & Set 4 & Set 5\\ \hline
(0.5,0) & \  & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ \\ 
%\rowcolor{Gray}
(2,1) & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$  \\ 
%\rowcolor{Gray}
(4,1) & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$  \\
%\rowcolor{Gray}
(4,2) & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$  \\ 
%\rowcolor{Gray}
(6,1) & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$  \\
%\rowcolor{Gray}
(6,2) & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$  \\
%\rowcolor{Gray}
(6,3) & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$  \\ 
%\rowcolor{Gray}
(8,1) & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$  \\
%\rowcolor{Gray}
(8,2) & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$  \\
%\rowcolor{Gray}
(8,3) & $\checkmark$ & $\checkmark$ & $\checkmark$ & \  & $\checkmark$  \\ 
%\rowcolor{Gray}
(10,1) & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & \   \\
%\rowcolor{Gray}
(10,2) & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & \   \\
%\rowcolor{Gray}
(10,3) & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & \   \\
%\rowcolor{Gray}
(10,4) & $\checkmark$ & $\checkmark$ & $\checkmark$ & \  & \   \\ 
(12,1) & \  & \  & $\checkmark$ & \  & \   \\
(12,2) & \  & \  & $\checkmark$ & \  & \   \\
(12,3) & \  & \  & $\checkmark$ & \  & \   \\
(12,4) & \  & \  & $\checkmark$ & \  & \   \\ 
\hline
%\end{tabular}
\end{tabular}
\caption[Various sets of filters in the filter bank of our proposed cloud classification approach.]{The ($\hat{\sigma}$,$\hat{\tau}$) values for different sets. Set 1 represents the original S-Filter set.}
\label{filter_table}
\end{table}

Table~\ref{tab:perform-eval} shows the effect of different filter sets ($\sigma$,$\tau$) on the final results. The other parameters are kept constant (Color channel $R/B$, Filter dimension $49 \times 49$, $30$  textons). The DC component in the filter set is required to capture the low frequencies of the image. An absence of the DC component particularly affects the performance for thick dark clouds, as such images contain pre-dominantly low frequency components. The optimal filter Set $3$ corresponds to a scenario that contains DC component and higher values of both $\sigma$ and $\tau$.

\subsubsection{Filter Dimension}
As the SWIMCAT database consists of images with fixed dimension $125 \times 125$, the optimum filter size needs to be tuned accordingly. As before, we keep the other parameters fixed (Color channel  $R/B$, Filter set $3$, $30$ textons). From Table~\ref{tab:perform-eval}, we see that the average classification accuracy across different categories is poor for small filter sizes, as they fail to capture the predominant essence of the cloud textures. Also, at large filter size, the boundary effects reduce accuracy. The best performance is achieved with an intermediate filter size of $49 \times 49$ pixels, which is thus a good choice for the final classification task.

\subsubsection{Number of Textons}
Table~\ref{tab:perform-eval} shows the effect of the number of textons on the classification performance. The other parameters are kept fixed (Color channel $R/B$, Filter Set $3$, dimension $49 \times 49$). The results are poor when the number of textons is small. However, beyond 30 textons, there is no significant performance gain in the classification accuracy. Thus, we select the number of textons as $30$ to avoid overfitting.

\subsection{Benchmarking Methods}
In order to understand the efficacy of these features, we provide an objective evaluation of these benchmarking features. We use these individual features to train a Support Vector Machine (SVM) classifier. The trained model is used in the evaluation of the remaining testing images.

The entire SWIMCAT dataset is divided into two distinct sets - training and testing sets. We choose $40$ distinct images from each category in a random fashion, to create the training set. The remaining images from each category are considered as the testing set.

We train individual SVM models for each of the features. The generated multi-class SVM is used to classify the images in the testing set. As described in Section~\ref{sec:chap6-exps}, we evaluate the accuracy, $P_{macro}$, $R_{macro}$, $P_{micro}$ and $R_{micro}$ of the images. The averaged value across all the testing images is reported in Table~\ref{tab:class_results}.

\begin{table}[htb]
\normalsize
\centering
%\setlength{\tabcolsep}{4pt} % default: 6pt
\begin{tabular}{|p{6cm}|c|c|c|c|c|}
\hline
\textbf{Methods} & \textbf{Accuracy} & \textbf{$P_{macro}$}& \textbf{$R_{macro}$}& \textbf{$P_{micro}$}& \textbf{$R_{micro}$}\\
\hline

SF+SVM & 0.53 & 0.63 & 0.53 & 0.85 & 0.41 \\

$\mbox{SGLDM}_{m}$+SVM & 0.65 & 0.67 & 0.83 & 0.56 & 0.67 \\

$\mbox{SGLDM}_{r}$+SVM & 0.57 & 0.57 & 0.57 & 0.45 & 0.45 \\

GLDS+SVM & 0.50 & 0.54 & 0.50 & 0.63 & 0.36 \\

FF+SVM & 0.31 & 0.40 & 0.31 & \textbf{1.00} & 0.24 \\

MI+SVM & 0.64 & 0.65 & 0.64 & 0.53 & \textbf{0.94} \\

HF+SVM & 0.83 & 0.83 & 0.83 & 0.85 & 0.64 \\

LBP+SVM & 0.27 & 0.41 & 0.27 & 0.07 & 0.93 \\

SIFT+SVM & 0.31 & 0.40 & 0.31 & \textbf{1.00} & 0.24 \\

Original texton approach & 0.78 & 0.78 & 0.78 & 0.70 & 0.85 \\

Proposed approach (using GRAY color channel) & 0.75 & 0.73 & 0.75 & 0.77 & 0.71 \\

Proposed approach (using $R/B$ ratio channel) & \textbf{0.95} & \textbf{0.95} & \textbf{0.95} & \textbf{1.00} & 0.79 \\
\hline
\end{tabular}
\caption[Benchmarking of various cloud classification algorithms.]{Cloud type classification results of our proposed approach along with other benchmarking algorithms. We use Support Vector Machine (SVM) classifier, along with several feature descriptors. The best performances according to each criterion are depicted in bold.}
\label{tab:class_results}
\end{table}

As expected, the conventional image-based feature extractor viz.\ LBP and SIFT have a poor classification accuracy. The HF+SVM performs comparatively well with an accuracy of $0.83$, as compared to other feature-based techniques. These observations are also evident from the various scatter plots in Fig.~\ref{fig:separation}. The confusion matrix generated using HF+SVM is shown in Fig.~\ref{fig:cmatrix}(a). The clear sky and patterned clouds are classified quite accurately. However, the thick white and veil clouds are mis-classified with each other. This is also confirmed from Fig.~\ref{fig:separation}, that \emph{cyan} and \emph{magenta} overlap with each other. We also benchmark our proposed texton-based approach on these images. We obtain the best accuracy of $0.95$, amongst all the methods. We use the $R/B$ color channel, because this channel is most appropriate amongst various color spaces and components~\cite{ICIP2015b}. The corresponding confusion matrix is shown in Fig.~\ref{fig:cmatrix}(b). All classes except veil clouds are classified accurately. Our proposed approach has a limitation that it obtains a low accuracy of $0.76$ for veil clouds. This is primarily, because veil clouds are very difficult to detect, and are often mis-interpreted as clear sky.

\begin{figure}[htb]
\centering
\includegraphics[height=4.4cm]{cm-HF}
\includegraphics[height=4.4cm]{cm-proposed}\\
\hspace{1cm}
\makebox[0.4\textwidth][c]{(a) \small HF+SVM}\hspace{1cm}
\makebox[0.4\textwidth][c]{(b) \small Proposed approach}\\
\caption[Confusion matrix of cloud classification results.]{Confusion matrix across $5$ categories generated from (a) HF+SVM and (b) Proposed approach.}
\label{fig:cmatrix}
\end{figure}

\section{Conclusion}
\label{sec:chap6-conclude}
In this chapter, we have provided a systematic analysis of the various features that were developed for the task of cloud type recognition. We observed that conventional machine-learning based feature extraction techniques do not generalize well in this task. Amongst the various features, Heinle features perform the best as it exploits the discriminatory cues of red and blue color channels, and also considers the cloud coverage as one of the parameters. However, the best performance is obtained from our proposed texton-based approach that uses optimized filter bank and color channel for optimal performance. We have presented an effective way to combine both color and texture features for accurate cloud classification results. Future works include the extension of this proposed texton-based approach to other remote sensing applications.

### 2018-07-16 misc/thesis-hardbound/Chapters/Chapter7.tex
Update 16/7/2018

\chapter{Weather Parameters Estimation from Images}
\label{chap:solar}

\lhead{Chapter 7. \emph{Weather Parameters Estimation from Images}}
In the previous chapters, we have described our proposed frameworks for cloud segmentation and cloud-type recognition. In this chapter, we extend our analysis of sky/cloud images to the field of solar and renewable energy. Here, we describe how clouds impact the generation of solar energy; and we propose a model to estimate the solar irradiance using whole sky imagers. We derive a model for estimating the solar irradiance using pictures taken by those imagers. Unlike pyranometers, these sky images contain information about the cloud coverage and can be used to derive cloud movement. An accurate estimation of the solar irradiance using solely those images is thus a first step towards short-term solar energy generation forecasting, as cloud movement can also be derived from them. We derive and validate our model using pyranometers co-located with our whole sky imagers. Our method shows a significant improvement in estimating strong short-term variations. As intended applications, we also discuss our current ongoing works on cloud tracking and detecting rainfall onset from sky images.

\section{Introduction}
Localized and short-term forecasting of cloud movements is an on-going research topic. Optical flow techniques can be used to generate forecasted images using two anterior frames. Our proposed method is thus a first step towards solar irradiance forecasting, as the input data used to estimate the irradiance is the same as the one used to forecast the sky condition.

The accurate estimation of solar energy is a challenging task, as clouds greatly impact the total irradiance received on the earth's surface in an intermittent fashion. In the event of clouds covering the sun for a short time, there is a sharp decline of the produced solar energy. Therefore, it is of utmost importance to model the incoming solar radiation accurately. In this chapter, we ask this fundamental question: in what ways can the rapid fluctuations of the solar irradiance be best captured? We use ground-based sky cameras to estimate the solar irradiance.

The analysis of clouds and several other atmospheric phenomenon is traditionally done using satellite images. The most widely used satellite data is from Moderate-resolution Imaging Spectroradiometer (MODIS), which is on board the Terra and Aqua satellites. They provide a large-scale view of the cloud dynamics and various atmospheric phenomenons. The data from this satellite on-board instruments are usually available only twice in a day. This is useful for a macro-analysis of cloud formation at a particular location on the earth's surface. One of the illustrative examples of such satellite data is the HelioClim-1 database from Global
Earth Observation System of Systems (GEOSS). It provides hourly and daily average of surface solar radiation received at ground level~\cite{HelioClim2014}. Ouarda et al.\ in~\cite{SEVIRI2016} assessed the solar irradiance from six thermal channels obtained from SEVIRI instrument. However these information are temporal and spatial averages. Solar energy applications requires knowledge of the solar irradiance at specific locations and at every time through the day. Therefore, images obtained from satellite are not conducive for such analysis, especially in geographical small countries like Singapore where the cloud formation is highly localized. We discussed the advantages of using sky cameras in detail earlier in Chapter~\ref{chap:wsi} of this thesis.

\section{Outline of Our Contribution}
In this chapter, we use images obtained from Whole Sky Imagers (WSIs) to accurately model the fluctuations of the solar radiation~\footnote{The source code of our proposed methodology to estimate solar irradiance from circumsolar region of the sky/cloud images is available online at \url{https://github.com/Soumyabrata/solar-irradiance-estimation}.}. There are several advantages of using a WSI to estimate solar irradiance, instead of using a pyranometer. Common weather stations generally use a solar sensor that measures the total solar irradiance. It is a point-source device providing information for a particular location. We do not have access to the cloud macrophysical properties, and its evolution over time. On the other hand, the wide-angle view of ground-based sky camera provide us extensive information of the sky. We can track a cloud mass over successive image frames, and also predict its future location. In this chapter, we attempt to solve the fundamental problem of modeling solar irradiance from sky images. This will also help in solar energy forecasting, which is useful in photovoltaic (PV) systems~\cite{solar_PV}.

The main contributions of this chapter compared to existing works in the literature include:

\begin{itemize}
\item A robust framework to accurately estimate and track the rapid fluctuations of solar irradiance; 
\item A proposal of a solar irradiance model using ground-based sky camera images, with an extensive benchmarking of our proposed model with other solar irradiance estimation models;
\item A methodology to use whole sky images to detect the onset of precipitation; and
\item A proposed approach to perform short-term prediction of localized cloud motion using ground-based sky images.
\end{itemize}

The rest of the chapter is organized as follows. In Section~\ref{sec:data}, we briefly discuss our experimental setup comprising whole sky imagers and weather stations. Our proposed model of estimating the solar radiations along with its rapid fluctuations are described in detail in Section~\ref{sec:model-solar}. In Section~\ref{sec:comparemodels}, we benchmark our proposed methodology with other existing solar estimation models. However, our proposed method suffers from a few disadvantages. We identify those drawbacks and suggest solutions to address them; these are discussed in detail in Section~\ref{sec:solar-discuss}. In this chapter, we also identify two intended applications of using whole sky images in the field of solar energy generation. In Section~\ref{sec:rainfallonset}, we discuss how the luminance of whole sky images can be used to indicate the onset of precipitation. Finally, in Section~\ref{sec:trackclouds}, we discuss our methodology of using optical flow techniques to perform short-term cloud forecasting. Section~\ref{sec:chap7-conclude} concludes this chapter.

\section{Data Collection}
\label{sec:data}
Our experimental setup consists of weather stations and ground-based WSIs. These devices are collocated at the rooftop of our university building ($1.34^{\circ}$N, $103.68^{\circ}$E). These devices continuously capture the various meteorological data, and archive them for subsequent analysis.

The pyranometer reads the instantaneous solar irradiance reaching the sensor at any instant of time. This constitutes both the direct and diffuse components of solar radiation. On a typical day, the solar radiation can fluctuate significantly in a short span of time, which is quite different from the ideal cosine response. If we examine the solar radiation readings on the $7$th of December $2015$ (cf.\ Fig.~\ref{fig:fluctuation_example}), we observe that the recorded solar radiation falls drastically from $758$ Watt/$\mbox{m}^2$ at $10$:$30$, to $283$ Watt/$\mbox{m}^2$ at $10$:$32$, and then rises again to $714$ Watt/$\mbox{m}^2$ at $10$:$34$. We observe two rapid fluctuations within a span of a few minutes.

\begin{figure}[htb]
\begin{center}
\includegraphics[height=0.28\textwidth]{sun1.png}\hspace{-1mm}
\includegraphics[height=0.28\textwidth]{sun2.png}\hspace{-1mm}
\includegraphics[height=0.28\textwidth]{sun3.png}\\
\makebox[0.3\textwidth][c]{\small 10:30 (758 W/$\mbox{m}^2$)}
\makebox[0.3\textwidth][c]{\small 10:32 (283 W/$\mbox{m}^2$)}
\makebox[0.3\textwidth][c]{\small 10:34 (714 W/$\mbox{m}^2$)}
\caption[Impact of clouds on direct solar irradiance.]{Consecutive images captured over an interval of $4$ minutes on $7$ December, $2015$. The amount of total solar radiation recorded by the weather station is shown in parentheses. The sun is obscured by clouds at $10$:$32$, resulting in a sudden dip in solar radiation.
\label{fig:fluctuation_example}}
\end{center}
\end{figure}

The images captured using Wide Angle High Resolution Sky Imaging System (WAHRSIS) at the corresponding time instants are shown in Fig.~\ref{fig:fluctuation_example}. It becomes clear that the fluctuation in solar radiation is due to clouds obscuring the sun from view. Assuming the diffuse component of solar radiation to be almost constant at these three instants of the day, the fluctuations in solar radiation recording are primarily because of the direct irradiance component. Therefore, the clouds in the vicinity of sun have the highest impact on recorded solar radiation.

In ~\cite{ursi2017}, we study the impact of clouds on total solar irradiance reaching the earth's surface. We define the difference between measured solar irradiance and clear-sky irradiance as the Cloud Radiative Effect (CRE). We analyze the relationship between measured solar irradiance and computed cloud coverage value. Extensive  results on a set of $6365$ images show that  higher cloud coverage leads to larger cloud radiative effect~\footnote{The source code of our study on cloud radiative effect using sky cameras is available online at \url{https://github.com/Soumyabrata/cloud-radiative-effect}.}.

\subsection{Whole Sky Imager (WSI)}
Commercial WSIs are available in the market. However, those imagers have high cost, low image resolution, and less flexibility in operation. In Chapter~\ref{chap:wsi}, we have discussed the design of our custom-built, low-cost, and high-resolution sky imagers. We refer these imagers as WAHRSIS, that stands for Wide Angle High Resolution Sky Imaging System~\cite{WAHRSIS}. Over the years, we have built several versions of WAHRSIS~\cite{WAHRSIS,IGARSS2015a}. They are now deployed at several rooftops of our university campus, capturing images of the sky at intervals of $2$ minutes. We use these images to estimate the total solar radiation.

\subsection{Weather Station}
In addition to the sky imagers, we have also installed collocated weather stations. We use \emph{Davis Instruments 7440 Weather Vantage Pro} for our recordings. It measures rainfall, total solar radiation, temperature and pressure at intervals of $1$ minute. The resolution of the tipping-bucket rain gauge is $0.2$ mm/tip.

It also includes a solar pyranometer measuring the total solar irradiance flux density in Watt/$\mbox{m}^2$. This consists of both direct and diffused solar irradiance component. The solar sensor integrates the solar irradiance across all angles, and provide the net solar irradiance. On a clear day with no occluding clouds, the solar sensor ideally follows a typical cosine response. The solar sensor reading is highest during noon when the incident angle of sun rays is at the minimum, whilst the reading is low during morning and evening hours.

The solar radiation on a clear sky can be modeled using the solar zenith angle, and earth's eccentricity. Several clear sky models have been developed for various regions. The best clear-sky model for Singapore is provided by Yang et al.\ \cite{dazhi2012estimation}. The clear-sky Global Horizontal Irradiance (GHI) $G_c$ is modeled as:

\begin{align}
G_c = 0.8277E_{k}I_{sc}(\cos\psi)^{1.3644}e^{-0.0013\times(90-\psi)},
\end{align}

where $E_k$ is the eccentricity correction factor for earth, $I_{sc}$ is the solar irradiance constant ($1366.1$Watt/$\mbox{m}^2$), and $\psi$ is the solar zenith angle (measured in degrees). The factor $E_k$ is calculated as:

\begin{equation*}
\begin{aligned}
\label{eq:E0value}
E_k = 1.00011 + 0.034221\cos(\Gamma) + 0.001280\sin(\Gamma) + \\0.000719\cos(2\Gamma) + 0.000077\sin(2\Gamma),
\end{aligned}
\end{equation*}

where $\Gamma = 2\pi(d_n-1)/365$ is the day angle (measured in radians) and $d_n$ is the day number of the year.

As an illustration, we show the clear-sky radiation for the 1st of September 2016 in Fig.~\ref{fig:Cos_response}. The actual solar radiance measured by our weather station is also plotted. We also show the deviation of the measured solar radiation from the clear-sky model. We observe that there are extremely rapid fluctuations in the measured readings. These rapid fluctuations are caused by the incoming clouds that obstruct the sun from direct view. Such information about the cloud profile and its formation cannot be obtained from a point-source solar recording. Therefore, we aim to model these rapid fluctuations in the measured solar radiation from wide-angle images captured by our sky cameras.

\begin{figure}[htb]
\centering
\subfloat[Measured solar radiation along with clear-sky model.]{\includegraphics[width=0.85\textwidth]{2016WS.pdf}\label{fig:2016WS}}\\ 
\subfloat[Percentage deviation of solar radiation from clear sky data.]{\includegraphics[width=0.85\textwidth]{2016_diff.pdf}\label{fig:2016diff}}
\caption[Measured solar radiation, and its deviation from the clear-sky model over a day.]{Solar radiation measurements on the 1st of September 2016. Note the rapid fluctuations of high magnitude in the measured solar radiation recording.}
\label{fig:Cos_response}
\end{figure}

\section{Modeling Solar Irradiance}
\label{sec:model-solar}
This section details our model for computing the solar irradiance from images captured by a whole sky imager. We sample pixels using a cosine weighted hemispheric sampling to simulate the behavior of a pyranometer based on the fisheye camera lens. We then compute the relative luminance using the image capturing parameters, after gamma correction. We finally derive a linear regressor to scale the computed luminance to match measured irradiance values.

\subsection{Cosine-weighted hemispheric sampling}
The behavior of our fisheye lens with focal length $\bar{f}$ is modeled by the equisolid equation $r=2\bar{f} \sin(\beta/2)$, relating the distance ($r$) of any pixel from the center of the image to its incident light ray elevation angle ($\beta$). This allows to project a captured image on a unit hemisphere, as shown in Fig.~\ref{fig:sampling3D}.

\begin{figure}[htb]
\centering
\subfloat[Projection on a hemisphere of the original image]{\includegraphics[width = 1.8in]{JSTARS-sampled-empty-noborder}\label{fig:sampling3D}}\ 
\subfloat[Cosine hemispheric sampling of the hemisphere with origin on the top]{\includegraphics[width = 1.8in]{JSTARS-sampled-noborder}\label{fig:sampling3Dsam}}\ 
\subfloat[Applying a rotation matrix to center at the sun location]{\includegraphics[width = 1.8in]{JSTARS-sampled-sun-noborder}\label{fig:sampling3Drot}}\\
\subfloat[Original image with detected sun location in red]{\includegraphics[width = 1.8in]{JSTARS-sun-noborder}}\ 
\subfloat[Projection on the image of the sampled points]{\includegraphics[width = 1.8in]{JSTARS-sampled-image-noborder}}\ 
\subfloat[Projection on the image of the rotated sampled points]{\includegraphics[width = 1.8in]{JSTARS-rotated-noborder}}\ 
\caption{Cosine weighted hemispheric sampling process used to select the pixels used for solar irradiance estimation.}
\label{fig:sampling}
\end{figure}

The solar irradiance is composed of a direct component relating the sun light reaching the earth without interference, as well as diffuse and reflected components. Given the high resolution of our images, we consider randomly sampled pixel locations on the hemisphere as input to the luminance computation. We follow a cosine weighted hemispheric distribution function, the center of which is at the location of the sun. This is because clouds in the circumsolar region have the highest impact on the total solar irradiance received on the earth's surface. We provide more emphasis to the clouds around the sun, as compared to those near the horizon.

The first step is to compute the sampled locations from the top of the unit hemispheric dome. Each of the locations are computed as follows, using two random floating points $R_1$ and $R_2$ as input, where $(0 \leq R_1, R_2 \leq 1)$: %between 0 and 1 
\[\phi = 2\pi R_1,\ \beta = \arccos(\sqrt{R_2})\]
\begin{equation}
     \begin{bmatrix}
         x \\
         y \\
         z
        \end{bmatrix}=\begin{bmatrix}
         \sin(\beta)\cdot \cos(\phi) \\
         \sin(\beta)\cdot \sin(\phi) \\
         \cos(\beta)
        \end{bmatrix}
  \end{equation}

This is represented in Fig.~\ref{fig:sampling3Dsam}.

The second step is to detect the location of the sun using a thresholding method. This is needed to align the center of the previously computed distribution (i.e.\ top of the hemispheric dome) to the actual sun location in the unit sphere. We choose a threshold of $240$ in the red channel $R$ of the $RGB$ captured image, and compute the centroid of the largest area above the threshold~\footnote{We experimentally calculated this threshold and the process is described in ~\cite{IGARSS16_calib}}. We then compute the rotation matrix transforming the z-axis unit vector to the unit vector pointing towards the sky. We apply this rotation to all the sampled points, resulting in Fig.~\ref{fig:sampling3Drot}.

This means that the amount of sampled points in a region of the hemisphere is proportional to the cosine of the angle between the sun direction and the direction to that region. We experimentally concluded that this achieves a good balance between all irradiance components. We thus consider the pixel values of $5000$ points sampled using this method as input for the irradiance estimation.

\subsection{Relative Luminance Calculation}

For each of the $\bar{s}$ sampled pixels in the $RGB$ image, we compute its brightness value using the following formula~\footnote{following SMPTE Recommended Practice 177}:
\[Y_{\bar{s}} = 0.2126\cdot R_{\bar{s}}  + 0.7152\cdot G_{\bar{s}} + 0.0722\cdot B_{\bar{s}}\]

The JPEG compression format encodes images after applying a gamma correction. This non-linearity mimics the behavior of the human eye. This needs to be reversed in order to compute the luminance. In our case, we use a non-linear correction factor of $2.2$, which is most commonly used in imaging systems~\cite{Poynton03}. We thus apply the following formula, assuming pixel values normalized between $0$ and $255$:
\[Y_{\bar{s}}' = 255{(Y_{\bar{s}}/255)}^{2.2}\]

Unlike the conventional approach, we perform this non-linear correction stage directly on the brightness values, instead of employing to the individual red-, green- and blue- channels. We then average the pixel values across all the $\bar{s}$ sampled points in the image, and denote it by $\mathcal{N}$. This pixel value given by $\mathcal{N} = (1/{t_s})\sum_{i=1}^{t_s} Y_{\bar{s}}'$, denotes the average luminance value of the sampled points from the image, where $t_s$ is the total number of sampled points in the hemispheric sampling process.

However, each image of the sky camera is captured with varying camera parameters viz.\ ISO, F-number and shutter speed. These camera parameters can be read from the image metadata, and are useful to estimate the scene luminance. The amount of brightness of the sampled points $\mathcal{N}$, is proportional to the number of photons hitting the camera sensor. This relationship between scene luminance and pixel brightness~\cite{hiscocks2011measuring} can be modeled using the camera parameters as:

\[\mathcal{N} = K_c \left( \frac{e_t\cdot {I_s}}{f_s^2}\right) \mathcal{L}_s\]

where $\mathcal{N}$ is the pixel value, $K_c$ is a calibration constant, $e_t$ the exposure time in seconds, $f_s$ the aperture number, $I_s$ the ISO sensitivity and $\mathcal{L}_s$ the luminance of the scene.

We can thus compute the relative luminance $\mathcal{L}_r$ using the following:
\[\mathcal{L}_r = \mathcal{N} \left( \frac{f_s^2}{e_t\cdot {I_s}}\right)\]

\subsection{Modeling Irradiance from Luminance Values}
Using our hemispheric sampling and relative luminance computation, we therefore have one relative luminance value $\mathcal{L}_r$ per image. We propose our model using this relative luminance value to estimate the solar radiation. The usual sunrise time in Singapore is between $6$:$40$ am and $7$:$05$ am, and sunset time is approximately between $6$:$50$ pm and $7$:$10$ pm\footnote{\url{http://www.nea.gov.sg/weather-climate/forecasts}}. Therefore, we consider images captured in the time interval of $7$:$00$ am till $7$:$00$ pm. We use our ground-based whole sky images captured during the time period from January $2016$ till August $2016$ to model the solar radiation. The solar irradiance is computed as the flux of radiant energy per unit area normal to the direction of flow. The first step in estimating irradiance from the luminance is thus to cosine weight it according to its direction of flow. We weight our measurements according to the solar zenith angle $\psi$.

The modeled luminance $\mathcal{L}_m$ is expressed as:

\begin{equation*}
\mathcal{L}_m = \mathcal{L}_r(\cos\psi)
\end{equation*}

Let us assume that the actual solar radiation recorded by the weather station be $\mathcal{S}$. We check the nearest weather station measurement, for all the images captured by WAHRSIS between April $2016$ till December $2016$. Figure~\ref{fig:solar_model} shows the scatter plot between the image luminance and solar radiation. The majority of the data follows a linear relationship between the two. However, it deviates from linearity for higher values of luminance. This is mainly because of the fact that the mapping between scene luminance and obtained pixel value in the camera sensor becomes non-linear for large luminances. A more detailed discussion on this is provided in Section~\ref{sec:solar-discuss}.

\begin{figure}[htb]
\begin{center}
\includegraphics[width=0.7\textwidth]{proposedmodel2.png}
\caption[Proposed linear regressor model to estimate solar irradiance from sky images.]{Model of the solar radiation using the image luminance computed with our proposed framework. We observe that it deviates from linearity at higher luminance values. \label{fig:solar_model}}
\end{center}
\end{figure}

We use a linear regressor to model the measured solar radiation $\mathcal{S}$ from the image luminance $\mathcal{L}_m$. This is based on our assumption that the mapping from scene luminance to pixel values in the captured image is linear. Thus, we model solar radiation as: $\mathcal{S} = a\times{\mathcal{L}}_m + b$. The values of $a$ and $b$ are derived as $0.0138$ and $-39.896$ respectively for our data. Therefore, our proposed model for estimating solar irradiance is:

\begin{align}
\label{eq:propmodel}
\mathcal{S} = 0.0138\times{\mathcal{L}}_m - 39.896.
\end{align}

This model is derived specifically for equatorial region like Singapore, and the regression constants are based on our WAHRSIS sky imaging system. However, these values need to be fine-tuned while applying our methodology for other regions and different imaging system.

\subsection{Performance Comparison and Validation}
\label{sec:comparemodels}
In this section, we evaluate the accuracy of our proposed model. The model is derived based on WAHRSIS images captured 
from January to August $2016$. We also use these images to evaluate the accuracy of our proposed model. Furthermore, we benchmark our algorithm with other existing solar radiation estimation models.

\subsubsection{Evaluation}

One of the main advantages of our approach is that all rapid fluctuations of solar radiation can be accurately tracked from the image luminance. We illustrate this by providing the measured solar readings of 01-Sep-2016 in Fig.~\ref{fig:tracksun}. The clear-sky model follows a cosine response and is shown in black; whereas the measured solar recordings is shown in red. We normalize our computed luminance in a manner that matches the measured solar readings. We multiply each data points of the luminance with a conversion factor, such that the distance between corresponding inter-samples of luminance and weather station is minimized (cf.\ Appendix~\ref{append:solarestimation} for details). We observe that our computed luminance from the whole-sky image and the measured solar radiation closely follows each other. We emphasize here that it is an important contribution to successfully track the rapid solar fluctuations. Unlike other solar estimation models based on meteorological sensor data, our proposed model can successfully estimate the \emph{peaks} and \emph{troughs} of solar readings accurately.

\begin{figure}[htb]
\centering
\includegraphics[width=0.95\textwidth]{example-proposeddash.pdf}
\caption[Solar radiation and image luminance follows each other closely over the entire period of the day.]{We show the measured weather station data (in red), and the clear sky radiation (in black) as on 01-Sep-2016. We observe that the image luminance normalized w.r.t. the measured solar radiation, follows the measured readings closely. The sampling interval between two measurements is $2$ minutes.
\label{fig:tracksun}}
\end{figure}

Using our proposed methodology, we compute the luminance of all the captured images. We use Eq.~\ref{eq:propmodel}, and estimate the corresponding solar radiation values. The actual ones are recorded in the collocated weather station. These recordings serve as the ground-truth measurements. Figure~\ref{fig:HOD} shows the histogram of difference between the estimated and actual solar radiation. We observe that the estimated solar radiation do not deviate much from the actual solar radiation. It is clear that $47.9\%$ of data points are concentrated in the range [$-100$,$+100$] Watt/$\mbox{m}^2$.

\begin{figure}[htb]
\begin{center}
\includegraphics[width=0.6\textwidth]{diff_hist2.pdf}
\caption{Histogram of difference between estimated and actual solar radiation. We observe that most of the data are concentrated in the $0$-bin. 
\label{fig:HOD}}
\end{center}
\end{figure}

\subsubsection{Benchmarking Techniques}
We benchmark our proposed approach with other existing solar estimation models. To the best of our knowledge, currently, there are no proposed models to estimate short-term fluctuations of solar irradiance from ground-based images. However, most remote sensing analysts have been using other meteorological sensor data eg.\ daily temperature, humidity, rainfall and dew point temperature to estimate daily solar irradiance. One of the pioneer work was done by Hargreaves and Samani~\cite{HSmodel}, who proposed a model based on daily temperature variations. Donatelli and Campbell~\cite{DCmodel} improved the model by including clear sky transitivity as one of the factors. On the other hand, Bristow and Campbell~\cite{BCmodel} also proposed a new model of solar radiation estimation, by including the atmospheric transmission coefficient. Subsequently, Hunt et al.~\cite{Huntmodel} showed that the solar estimation model can be further improved by incorporating the daily precipitation data in the model. We benchmark our proposed approach with these different existing models.

We calculate the Root Mean Square Error (RMSE) of the estimated solar radiation and Spearman's rank correlation coefficient as the evaluation metrics. The RMSE of an estimation algorithm represents the standard deviation of the actual and estimated solar radiation values. Table~\ref{tab:corr_results} shows the RMSE values of our proposed algorithm with the other existing benchmarking algorithms. Our proposed approach performs the best. We also evaluate the spearman correlation coefficients of the different benchmarking algorithms, since this is a non-parametric measure to find the relationship between measured and estimated solar radiation. This does not assume that the underlying dataset are derived from a normal distribution. We report the correlation values in Table~\ref{tab:corr_results}. Our proposed approach has also the highest correlation amongst all methods.

\begin{table}[htb]
\normalsize
\centering
\begin{tabular}{l|c|c}
\hline
\textbf{Methods} & \textbf{RMSE} (Watt/$\mbox{m}^2$) & \textbf{Correlation}\\
\hline 
Proposed approach & 178.27 & 0.86\\
Hargreaves and Samani & 982.35 & 0.67\\
Bristow and Campbell & 318.07 & 0.68\\
Donatelli and Campbell & 324.48 & 0.67\\
Hunt et al.\ & 922.66  & 0.65\\
\hline
\end{tabular}
\caption[Benchmarking of our proposed approach with other solar radiation estimation models.]{Benchmarking of our proposed approach with other solar radiation estimation models. All correlation values have p-value equal to $0$.}
\label{tab:corr_results}
\end{table}

Table~\ref{tab:corr_results} explains the results where the training and testing set of images are identical, and all images are considered for evaluation. We are also interested to check if our proposed model can generalize well with random samples of our captured sky camera images. We choose a random selection of images as the training set, and fit our linear regressor on these selected training images. The RMSE values are then calculated on these training images. We perform this analysis for varying percentage of training images. Each experiment is performed $100$ times to remove any selection bias. Figure~\ref{fig:train_test}(a) shows the results on training images. We observe that the variation of the RMSE values gradually decreases, as we increase the number of training images. Moreover, we also check the variation of RMSE values when the testing images are not identical as training images. Once we choose a random selection of images as training set, the remaining images are considered as the testing set. We show the RMSE results on such images in Fig~\ref{fig:train_test}(b). As expected, the variation of RMSE values increases with higher percentage of training images. The linear regressor model overfits the data, and provides higher variation in the error when tested on a fewer testing images. However, the average RMSE does not vary much in all cases. Therefore, our proposed model is free from selection bias, and generalizes well with random selection of training and testing images.

\begin{figure}[htb]
\begin{center}
\includegraphics[width=0.48\textwidth]{training}
\includegraphics[width=0.48\textwidth]{testing}\\
\makebox[0.4\textwidth][c]{(a) Training images}
\makebox[0.4\textwidth][c]{(b) Testing images}
\caption[Effect of the percentage of training and testing images on the RMSE of proposed model.]{Effect of the percentage of training images on RMSE values. The lower and upper end of each box represents the $25^{th}$ and $75^{th}$ percentile of the data, and the red line represents the median value. Each experiment is conducted $100$ times with a random choice of training and testing sets. \label{fig:train_test}}
\end{center}
\end{figure}

\begin{figure}[htb]
\centering
\includegraphics[width=0.95\textwidth]{diffmodelsdash.pdf}
\caption[Comparison of several solar estimation models amongst each other.]{Comparison amongst different benchmarking solar estimation models, along with clear sky model and measured solar radiation on 01-Sep-2016. We observe most of the existing algorithms fail to capture the rapid fluctuations of the measured solar radiation. 
\label{fig:othermodels}}
\end{figure}

As a final comparison, we illustrate the various benchmarking models in Fig.~\ref{fig:othermodels}. Unfortunately, most of these algorithms fail to capture the short-term variations of the actual solar radiation.

We represent the scatter plot between the measured solar radiation and estimated solar radiation for the different benchmarking algorithms in Fig.~\ref{fig:scatter-other}. We observe that there is no strong correlation for most of these existing algorithms. This is because meteorological sensor data alone, with no cloud information cannot determine the sharp fluctuations of the solar radiation. 
This is an important limitation of these models, which we attempt to address in this chapter. Our model based on sky images have additional information about cloud movement and its evolution, which is the fundamental reason behind rapid solar radiation fluctuations. In our proposed model, most of these short-term variations are captured properly as shown in Fig.~\ref{fig:tracksun}.

\begin{figure}[htb]
\centering
\includegraphics[width=0.4\textwidth]{scatterHS.png}
\includegraphics[width=0.4\textwidth]{scatterBC.png}\\
\makebox[0.4\textwidth][c]{\small{(a) Hargreaves and Samani}}
\makebox[0.4\textwidth][c]{\small{(b) Bristow and Campbell}}\\
\includegraphics[width=0.4\textwidth]{scatterDC.png}
\includegraphics[width=0.4\textwidth]{scatterHunt.png}\\
\makebox[0.4\textwidth][c]{\small{(c) Donatelli and Campbell}}
\makebox[0.4\textwidth][c]{\small{(d) Hunt et al.}}
\caption{Scatter plot between measured solar radiation and estimated solar radiation for the benchmarking algorithms. 
\label{fig:scatter-other}}
\end{figure}

\subsection{Discussion}
\label{sec:solar-discuss}
Our proposed approach can estimate the solar radiation accurately with the least root mean square error, as compared to other models. The main advantage of our approach is that it can be used on predicted images as well, opening the potential for short term solar irradiance forecasting, which is needed in the solar energy field.

However, it suffers from a few drawbacks. In this section, we highlight them and suggest techniques to address them. Firstly, we use \emph{JPEG} images instead of uncompressed \emph{RAW} images for the computation of scene luminance. The \emph{JPEG} compression algorithm introduces non-linearities in the pixel values and our proposed model thus deviates from a linear relationship. In Fig.~\ref{fig:solar_model}, we have demonstrated the obtained relationship between actual solar radiation and the estimated image luminance from our sky camera images. We observe that the relationship is linear for low luminance values (or low solar radiation). However, it deviates from non-linearity at higher luminance values (or higher solar radiation). We can generate more consistent results by using only \emph{RAW} format images. Nevertheless, we still use \emph{JPEG} images, as \emph{JPEG} images have a significantly smaller size and less perceptible distortion in image quality, as compared to other lossy compression techniques. We capture images at an interval of $2$ minutes -- this amounts to an incredibly huge dataset of RAW images. Therefore, we stick to capture images in JPEG mode because of operational use. This assumption is practical from an operational point of view. On the other hand, uncompressed \emph{RAW} images have large file size and it is impossible to capture and store \emph{RAW} images at short capturing intervals due to the induced latency.

Secondly, our captured images have a wide range of camera settings with varying shutter speed, ISO and aperture values. This is disadvantageous because the relationship between pixel value and camera aperture value becomes non-linear for larger F-numbers. The relationship deviates from linearity above F $4.0$~\cite{hiscocks2011measuring}.  Figure~\ref{fig:fn_dist} depicts the wide range of F-numbers in the captured images used in deriving our proposed model. We observe that a significant percentage of images have large F-numbers, where the non-linearity sets in. In our future work, we intend to use an integrating sphere to calibrate our camera to varying levels of scene brightness.

\begin{figure}[htb]
\begin{center}
\includegraphics[width=0.6\textwidth]{dist_fnumber2.pdf}
\caption{Distribution of F-number of the WAHRSIS images that are used to derive the proposed model.
\label{fig:fn_dist}}
\end{center}
\end{figure}

Hence, we are able to estimate the sharp short-term variations of solar radiation, which significantly improves the state-of-the-art. This approach is of interest in the solar energy field, because these variations cause a sudden decrease in the electricity generation from solar panels. Short-term predictions of such ramp-downs are needed to maintain the stability of the power grid. Combining our solar irradiance estimation approach with cloud movement tracking in the input images could ultimately lead to better irradiance predictions. This approach of using whole sky imagers in the field of solar radiation has other applications as well.

A correct estimation of solar radiation from sky images can also assist us in devising an alternative manner to detect the onset of precipitation. This is because, \emph{dark clouds} (clouds with low luminance value) generally occur before a rainfall event, and is a good indication of rainfall onset. We discuss this in detail in the subsequent Section~\ref{sec:rainfallonset}.

\section{Detecting Rainfall Onset from Sky Cameras}
\label{sec:rainfallonset}
In this section, we discuss how sky images can be used effectively for the detection of rainfall onset. These images contain additional information about cloud coverage and movement and are therefore useful for accurate rainfall nowcast. We validate our results using rain gauge measurement recordings and achieve an accuracy of $89$\% for correct detection of rainfall onset.

\subsection{Impact of Precipitation}
We observed that the luminance of the image in the circumsolar region (region around the sun) and the measured solar radiation from the weather station are correlated. Therefore, we can define the empirical luminance of the clear sky from the theoretical clear-sky model (cf.\ Eq.~\ref{eq:propmodel}), based on the relationship between solar irradiance and image luminance. We define this estimated luminance of a cropped image around the sun as the \emph{clear-sky luminance}, denoted by $\mathcal{L}_c$. In other words, it measures the luminous intensity per second around the sun observed by our camera sensor, in the event of a clear sky.

In addition to clear-sky luminance, we also calculate the luminance of the whole sky image denoted by $\mathcal{L}_m$. We crop a square of dimension $2000 \times 2000$ pixels from the image to exclude the occlusions and neighboring buildings. The average luminance of the cropped image is $\mathcal{L}_m$.

Figure~\ref{fig:example} shows the luminance value of the images captured across different times of the day for a typical day in December. We also calculate the clear-sky luminance and plot it in Fig.~\ref{fig:example}.

\begin{figure}[htb]
\centering
\includegraphics[width=0.8\textwidth]{image_solar2.pdf}
\caption[Effect of the onset of rainfall on the measured luminance from sky camera.]{We illustrate the measured luminance and clear-sky luminance for the $11^\mathrm{th}$ of December 2015. The primary y-axis shows the normalized luminance value, and the secondary y-axis measures the rainfall rate (measured in mm/hour). We also show the corresponding sky images captured by our sky camera at three distinct times -- before, during and after the rain event.} 
\label{fig:example}
\end{figure}

We observe that the measured luminance value sharply decreases with the onset of rainfall. The luminance continues to remain low during the entire duration of the rainfall. It gradually increases after the precipitation event. We verify this by referring to the corresponding sky images captured by our WSI at different time instants. The sun is visible in the first image captured at 12:54 (before the rain event), when we record a normalized luminance of $0.7$. The second image captured at 14:07 (during the rain event) has dark clouds, with a much lower normalized luminance of $0.02$. Finally, the third image captured at 16:00 (after the rain event) shows a clearer sky condition, and the normalized luminance is $0.58$. Therefore, we observe that the onset of precipitation reduces the luminance measured in the sky images compared to the clear-sky luminance.

\subsection{Methodology \& Results}
In this section, we describe our methodology to detect precipitation from sky camera images. The measured luminance value deviates from the ideal luminance value (corresponding to clear sky) during a rainfall event. We use this deviation from clear sky luminance as a measure to indicate rainfall onset.

We define Clearness Luminance Index ($I$) as the ratio of measured luminance ($\mathcal{L}_m$) value to the clear-sky luminance ($\mathcal{L}_c$) value, $I = \mathcal{L}_m/\mathcal{L}_c$.

In case of overcast condition, the obtained Clearness Luminance Index $I$ is low. On the other hand, $I$ equals unity during ideal clear-sky cases. We evaluate the values of $I$ for a longer period of time, namely the entire month of December 2015. Figure~\ref{fig:CLIvalues} shows the relationship between index $I$ of the captured images and its corresponding distance from the nearest rain event (measured in minutes).

\begin{figure}[htb]
\centering
\includegraphics[width=0.8\textwidth]{ratioluminance2.pdf}
\caption[Trend of Clearness Luminance Index ($I$) w.r.t. proximity of rainfall onset.]{Trend of Clearness Luminance Index ($I$) before and after precipitation measured for all days in December $2015$. The value of $I$ gradually decreases as it approaches rainfall onset, and then gradually increases again. } 
\label{fig:CLIvalues}
\end{figure}

From Fig.~\ref{fig:CLIvalues}, we observe that the index value gradually decreases as it approaches a rain event, and reaches a minimum during rainfall. Post rain event, the clearness luminance index gradually increases with the passage of time. The trend roughly follows a V-shaped curve.

\subsubsection{Critical Clearness Luminance Index}
In this section, we define a threshold in $I$ to detect the onset of rainfall as the Critical Clearness Luminance Index ($I_c$). The criterion for rainfall detection proposed here is as follows: if the measured index $I$ decreases below the critical $I_c$, there is an indication of precipitation.

We consider all the images captured in December $2015$. We use rainfall recorded by the collocated weather station as ground truth measurements. We classify each of the weather station measurements into \emph{rain} and \emph{non-rain} events, based on the rain gauge measurements. We also check the corresponding WSI images captured at the same time, and calculate their index $I$. The entire set of images in our dataset are segregated into two categories. The first category comprises those images that are within $\pm 15$ minutes of a rain event, including the images captured during the rain event. The rest of the images are considered in the second category.

Figure~\ref{fig:cdf} plots the Cumulative Distribution Plot (CDF) of clearness luminance index of images within and outside the time window of $\pm 15$ minutes.

\begin{figure}[htb]
\centering
\includegraphics[width=0.8\textwidth]{cdfcombined.pdf}
\caption[CDF plots of Clearness Luminance Index of images within and outside $\pm 15$ minutes of rain event.]{CDF plots of Clearness Luminance Index of images within and outside $\pm 15$ minutes of rain event. Each point in the graph denotes the percentage of time the clearness index $I$ is less than its corresponding value.} 
\label{fig:cdf}
\end{figure}

The motivation of classifying the images into two categories (within and outside $\pm 15$ minutes interval) is to analyze the impact of precipitation on the image luminance $\mathcal{L}_m$.
From Fig.~\ref{fig:cdf}, we observe that images within $\pm 15$ minutes interval of rain event have a much lower luminance index than those images further from a rain event. This is intuitive as dark cumulus clouds appear before a rainfall, and they often persist for a brief period after the rainfall event. Furthermore, dark clouds are generally not present on non-rainy days.

\subsubsection{Operating Characteristics (OC) Curve}
In this section, we are interested in determining the critical clearness luminance index ($I_c$). For this purpose, we calculate the operating characteristics (OC), which shows the percentage of time for images within $\pm 15$ minutes of rain event against those  outside $\pm 15$ minutes of rain event. We vary the value of $I_c$ from $0.01$ to $0.2$, in steps of $0.01$. The resulting OC curve is shown in Fig.~\ref{fig:roc}.

\begin{figure}[htb]
\centering
\includegraphics[width=0.8\textwidth]{roc.pdf}
\caption[Operating Characteristics (OC) curve generated by varying the critical clearness luminance index ($I_c$).]{Operating Characteristics (OC) curve generated by varying the critical clearness luminance index ($I_c$). The \emph{elbow} in the plot (shown in red) is our chosen $I_c$.} 
\label{fig:roc}
\end{figure}

We observe a sharp transition at $I_c = 0.08$. This is generally referred as the \emph{elbow} of the OC curve, and is chosen as the operating point as it has the best performance. 
We check the corresponding percentage of time for this critical threshold ($I_c$) of $0.08$. We observe that the images within $\pm 15$ minutes of rain events have a clearness index below the critical threshold for $89.41\%$ of time. On the other hand, only $13.13\%$ of time images outside the time window have a clearness index below the critical threshold. 
Therefore, $I_c=0.08$ can be used as the threshold for the clearness index for estimating the onset of rainfall. However, this threshold is derived for a tropical region like Singapore. This value may need to be adjusted when applying this model to other regions or using different sky imagers.

\subsection{Summary}
In this section, we have discussed how ground-based sky cameras can be effectively used to detect rainfall onset. We defined a Clearness Luminance Index that measures the deviation of estimated luminance from the clear-sky luminance. We have proposed a critical clearness luminance index that indicates the onset of precipitation. Extensive results on a month of sky images and weather station recordings show the efficacy of our proposed approach. In the future, we plan to verify these results over longer periods.

\section{Short-term Cloud Tracking Using Sky Images}
\label{sec:trackclouds}
In addition to detecting rainfall onset, we also use sky images to perform short-term forecasting of cloud images. This is useful for solar energy forecasting. We use two successive frames to compute optical flow and predict the future location of clouds. We achieve good prediction accuracy for a lead time of up to $5$ minutes.

\subsection{Methodology}
In this section, we first give a general formulation of the optical flow technique and then describe how it is applied to our problem.

\subsubsection{Optical Flow Formulation}
Optical flow is based on the brightness constancy constraint, which states that pixels of an image sequence do not change value, but only shift position over time. Let's define a pixel intensity at image coordinates $(x,y)$ and time $t_m$ by $\mathbf{X}(x,y,t_m)$. Under this condition, this intensity would have moved by $(\Delta x, \Delta y)$ after a time $\Delta t_m$:
\[\mathbf{X}(x,y,t_m) = \mathbf{X}(x + \Delta x, y + \Delta y, t_m + \Delta t_m).\]

Using a first order Taylor series expansion, the optical flow equations can be derived \cite{fleet2006optical}:
\[\frac{\partial \mathbf{X}}{\partial x}u_x + \frac{\partial \mathbf{X}}{\partial y}u_y + \frac{\partial \mathbf{X}}{\partial t_m} = 0,\]
where $(u_x, u_y)$ is the optical flow (or velocity), and $\frac{\partial \mathbf{X}}{\partial x}$, $\frac{\partial \mathbf{X}}{\partial y}$ and $\frac{\partial \mathbf{X}}{\partial t_m}$ are the derivatives of the image in the $x$, $y$, and $t_m$ dimensions.

This equation cannot be solved analytically, as it has two unknowns. This is known as the \emph{aperture problem}. In order to solve it, two main approaches exists:

\begin{itemize}
\item Local methods state that the optical flow vectors are constant within some neighborhood and thus increase the number of equations to solve for the same optical flow vector. A typical example is the Lucas-Kanade method \cite{lucas1981iterative}.
\item Global methods assume that the optical flow vector distribution should be smooth across the spatial and temporal axes. They mimimize a global energy function in order to reduce large optical flow gradients. A famous algorithm is the Horn-Schunck method \cite{horn1981determining}.
\end{itemize}

We use the implementation~\footnote{Available at \url{https://people.csail.mit.edu/celiu/OpticalFlow/}} from~\cite{liu2009beyond}, which is based on a combination of both local and global approaches, following the method proposed in~\cite{bruhn2005lucas}.

\subsubsection{Cloud Tracking}
We use two image frames taken at times $t_m-2$ minutes and $t_m$, and compute the translational vectors in both $x$ and $y$ direction of the images, using the method mentioned above. We rely on the assumption that clouds do not significantly change between image frames. The optical flow vectors estimate the direction and orientation of the moving clouds, assuming an affine transformation between two frames. The algorithm provides a dense result, i.e.\ a velocity vector is associated to every pixel coordinate in the input image.

\begin{figure}[htb]
\centering
\subfloat[Frame at time $t_m-2$ minutes]{\includegraphics[height=0.33\textwidth]{Picture1.png}}
\hspace{2mm}
\subfloat[Frame at time $t_m$]{\includegraphics[height=0.33\textwidth]{Picture2.png}}
\caption{Ratio channels of two successive image frames.}\label{fig:ratioimage}
\end{figure}

Since we are interested in tracking the detailed cloud shape, it is important to use a color space which provide a good separation of clouds and sky. We use a variant of the ratio of red and blue color channels of the image. In an earlier chapter, we have analyzed various color channels and concluded that $(B-R)/(B+R)$ is the most discriminatory color channel, where $B$ and $R$ indicate the blue and red color channels respectively.

As an illustration, we show the ratio channel of two successive image frames in Fig.~\ref{fig:ratioimage}. We observe that there is a clear contrast in this channel. These ratio channels are used to estimate the flow field of clouds.

Using the images in Fig.~\ref{fig:ratioimage}, we obtain the horizontal and vertical translations of each of the pixels, which can be combined into a vector field. We show them in Fig.~\ref{fig:vectorflow}, plotted in terms of pixels/minute. This provides an idea about the relative speed and direction of each of the pixels between the two frames.

\begin{figure}[htb]
\begin{center}
\stackunder[5pt]{\includegraphics[height=0.3\textwidth]{Picture3.png}}{\small (a) Horizontal translation}
\includegraphics[width=0.08\textwidth]{Picture4.png}
\stackunder[5pt]{\includegraphics[height=0.3\textwidth]{Picture5.png}}{\small (b) Vertical translation}
\caption[Horizontal and vertical translation of pixels between two successive sky/cloud image frames.]{Horizontal and vertical translation of pixels between Frame 1 and Frame 2. The color map represents the speed in pixels/minute units.
\label{fig:vectorflow}}
\end{center}
\end{figure}

\begin{figure}[htb]
\begin{center}
\subfloat[Frame at time $t_m-2$ minutes]{\includegraphics[trim={4cm 1cm 4cm 1cm}, clip, height=0.15\textwidth]{tm2-img}}\,
\subfloat[Frame at time $t_m$]{\includegraphics[trim={4cm 1cm 4cm 1cm}, clip, height=0.15\textwidth]{t0-img}}\\
\vspace{-4mm}
\subfloat[Actual Frame at time $t_m+2$ minutes]{\includegraphics[trim={4cm 1cm 4cm 1cm}, clip, height=0.15\textwidth]{act-tp2-img.pdf}}\,
\subfloat[Binary of (c)]{\includegraphics[trim={4cm 1cm 4cm 1cm}, clip, height=0.15\textwidth]{act-tp2-map.pdf}}\,
\subfloat[Predicted Frame at time $t_m+2$ minutes]{\includegraphics[trim={4cm 1cm 4cm 1cm}, clip, height=0.15\textwidth]{pre-tp2-img.pdf}}\,
\subfloat[Binary of (e)]{\includegraphics[trim={4cm 1cm 4cm 1cm}, clip, height=0.15\textwidth]{pre-tp2-map.pdf}}\\
\vspace{-4mm}
\subfloat[Actual Frame at time $t_m+4$ minutes]{\includegraphics[trim={4cm 1cm 4cm 1cm}, clip, height=0.15\textwidth]{act-tp4-img.pdf}}\,
\subfloat[Binary of (g)]{\includegraphics[trim={4cm 1cm 4cm 1cm}, clip, height=0.15\textwidth]{act-tp4-map.pdf}}\,
\subfloat[Predicted Frame at time $t_m+4$ minutes]{\includegraphics[trim={4cm 1cm 4cm 1cm}, clip, height=0.15\textwidth]{pre-tp4-img.pdf}}\,
\subfloat[Binary of (i)]{\includegraphics[trim={4cm 1cm 4cm 1cm}, clip, height=0.15\textwidth]{pre-tp4-map.pdf}}
\caption[Prediction of sky/cloud image for a sample day with a lead time of $2$ and $4$ minutes. ]{Prediction of sky/cloud image on 16 April 2015 with a lead time of $2$ and $4$ minutes. The prediction accuracy is $83.44\%$ for a lead time of $2$ minutes, and $72.37\%$ for a lead time of $4$ minutes. The binary images are generated using our sky/cloud segmentation algorithm described in Chapter~\ref{chap:segmentation}.
\label{fig:example1}}
\end{center}
\end{figure}

\subsubsection{Cloud Motion Prediction}

We can now use the above information to predict future frames. The vector fields are applied individually to each of the red, green, and blue channels of the image.

Clouds have an ill-defined shape, and can change their shape and size very quickly. However, even though the underlying assumptions do not exactly match this reality, they work well to track clouds for short lead times, as is the case in many other optical flow problems.

For higher lead times, we use the actual frame at time $t_m$ and predicted frame at time $t_m+2$ minutes to predict the frame at time $t_m+4$ minutes. Similarly, we use the  predicted frame at time $t_m+2$ minutes and the predicted frame at $t_m+4$ minutes, to predict the frame at time $t_m+6$ minutes, and so on. At every stage, we use the previous two frames (actual or predicted), to compute the subsequent frame. This works well under the assumption that the clouds do not \emph{significantly} change their shape and location for the given lead time.

\subsection{Results \& Discussions}

We now evaluate the forecasting accuracy of our methodology. For this purpose, we compute the binary sky/cloud image of the forecasted image using our cloud detection algorithm as described in Chapter~\ref{chap:segmentation}. We then compare it with the binary image computed from the original image. The accuracy is then calculated as the percentage of correctly classified pixels (sky or cloud) in the predicted binary image, as compared to the actual binary image.

We compute the prediction accuracy of our cloud tracking algorithm for a typical day in April 2015 and present our results for different lead times. Figure~\ref{fig:LT} shows the performance of our cloud tracking algorithm for different lead times.  We observe that prediction accuracy is good for short lead times, but gradually decreases as lead times become larger. This makes sense as clouds generally move quite fast, and can change shape between image frames.  Furthermore, the error obtained in the intermediate forecast image is cascaded to future images.

\begin{figure}[htb]
\begin{center}
\includegraphics[width=0.6\textwidth]{leadtime_cut2}
\caption{Comparison of prediction accuracy percentage with different lead times.}
\label{fig:LT}
\end{center}
\end{figure}

We provide a few illustrative examples of our prediction accuracy upto $4$ minutes. Figure~\ref{fig:example1} shows the output of our algorithm with a lead time of upto $4$ minutes, in intervals of $2$ minutes. We use the frame at time $t_m-2$ minutes and the frame at time $t$ as the input images of our proposed approach to predict the frame at time $t_m+2$ minutes. We show the actual and predicted images along with their corresponding binary images. The accuracy achieved with our algorithm is $83.44\%$. We then use the frame at $t_m$ minutes along with the predicted image at $t_m+2$ minutes to predict the frame at $t_m+4$ minutes. The accuracy is still good (around $72.37\%$) given the higher lead time. However, we observe for higher lead times, the predicted image gets progressively more distorted as compared to its actual image, and artifacts appear. This happens because the error incurred in the previous lead times gets cascaded to future frames, as clouds significantly changes in shape over a relatively short period of time. After 10 minutes, the clouds have moved significantly, and there is little correlation between frames. These predictions are only based on images capturing a small area of the sky, and better long-term predictions would only possible at a larger scale and a lower level of detail.

\subsection{Summary}
In this section, we have discussed about our methodology to track cloud movement across successive image frames from sky cameras. It is based on optical flow and performs well for lead times of a few minutes. The accuracy gradually decreases for larger lead times. Our proposed approach is intended mainly for the short-term prediction of cloud movements, as we perform a localized analysis of cloud motion. We also show how the luminance of images captured by our sky camera can be used to detect the onset of precipitation. In our future work, we plan to use other meteorological data, such as wind sensors, to further increase the prediction accuracy.

\section{Conclusion}
\label{sec:chap7-conclude}
In this chapter, we presented a method for estimating solar irradiance using the luminance of images taken by a whole sky imager. We are able to estimate the sharp short-term variations, which significantly improves the state-of-the-art. This approach is of interest in the solar energy field, because these variations cause a sudden decrease in the electricity generation from solar panels. Short-term predictions of such ramp-downs are needed to maintain the stability of the power grid. Combining our solar irradiance estimation approach with cloud movement tracking in the input images could ultimately lead to better irradiance predictions.

### 2018-07-16 misc/thesis-hardbound/Chapters/Chapter8.tex
Update 16/7/2018

\chapter{3D Scene Analysis Using Multiple Cameras}
\label{chap:localize}

\lhead{Chapter 8. \emph{3D Scene Analysis Using Multiple Cameras}}
In the earlier chapters, we used a single ground-based sky camera for an extensive analysis of the earth's atmosphere. We used our custom-built sky cameras to perform segmentation, classification, estimation and prediction of meteorological parameters etc. In this chapter, we analyze the localization error of \emph{cloud mass} in a setup consisting of multiple whole sky imagers. To better understand the localization error in a more general imaging context, we use simulated camera models in our study. We assume our cameras have a finite pixel resolution, which are kept in a multi-camera setup. Using concepts drawn from computational geometry, we provide bounds on the localization of a point in a multi-camera setup. In the later part of this chapter, we show how multi cameras (i.e.\ several whole sky imagers) can help in accurate estimation of cloud base height.

Point localization in multi-camera setups~\footnote{A part of the work presented in this chapter was done during my doctoral internship in Audiovisual Communications (LCAV) Laboratory, \'{E}cole Polytechnique F\'{e}d\'{e}rale de Lausanne, in collaboration with Prof.\ Martin Vetterli, Dr.\ Adam Scholefield and Alireza Ghasemi.} has been widely studied in computer vision. In the first part of this chapter, we explain our work on consistent and optimal point localization algorithm, for a multi-camera setup. 
We formulate this point localization task as a gradient-ascent optimization function, for maximizing the objective function under computational geometric constraints. Experimental results verify the efficacy of our approach as compared to the current state-of-the-art localization algorithms. In the later part of this chapter, we show how point localization of cloud mass is performed in a network of sky cameras.

\section{Outline of Our Contribution}

The main contributions of this chapter compared to existing works in the literature include:

\begin{itemize}
\item We propose a new localization algorithm in a multi-camera setup, where the camera poses are noisy and feature matching are noiseless; and
\item We describe a method to localize a cloud mass using a pair of sky cameras.
\end{itemize}

The rest of the chapter is organized as follows. In Section~\ref{sec:chap8-locproblem}, we introduce the problem of localization in multi-camera setup. Section~\ref{sec:chap8-setup} discusses the setup and introduces the various notations that will be used throughout this chapter. We describe a recently introduced point localization algorithm for noiseless camera poses in Section~\ref{sec:SHARP}. We propose a modified algorithm for noisy camera poses in Section~\ref{sec:chap8-noisySHARP}. The detailed computation of our proposed algorithm is described in Section~\ref{sec:prop-alg} and its experimental results are presented in Section~\ref{sec:chap8-exps}. The remaining part of this chapter illustrates an application of point localization in the context of cloud imaging. Section~\ref{sec:chap8-cloudheight} discusses this. Finally, Section~\ref{sec:chap8-conclude} concludes this chapter.

\section{Introduction of Localization Problem}
\label{sec:chap8-locproblem}
The classical \emph{Art Gallery Problem} is a widely known problem in the computer vision community. We illustrate this problem in Fig.~\ref{fig:empty-room}. The objective of this problem is to \emph{guard} an art gallery room (either convex or non-convex type) from an intruder, denoted by $\mathbf{p}$. Every point (\emph{intruder}) $\mathbf{p}$ inside polygon is guarded by set of cameras (\emph{guards}) $\mathbf{S}$ iff $\forall q \in \mathbf{S}$ s.t. $\mathbf{pq} \ni$ polygon. This problem has been widely studied in the literature for different room types.

\begin{figure}[htb]
\centering
\hspace{-1.5cm}
{\includegraphics[width=0.75\textwidth]{empty-room.pdf}}
\vspace{-1.5cm}
\caption{Guarding a non-convex shape art gallery from an intruder $\mathbf{P}$.}
\label{fig:empty-room}
\end{figure}

An interesting extension of this art gallery problem is the \emph{Point Localization Problem}. This involves localizing the \emph{intruder}, in addition to guarding the \emph{art gallery} from various intruders. Considering cameras with infinite resolution, we need \emph{at least} two cameras to localize the intruder. We illustrate this in Fig.~\ref{fig:room}. The intruder $\mathbf{P}$ can be localized by the two cameras, as shown in the figure if the intruder do not lie in the line joining the two cameras. If the intruder is \emph{seen} by the two cameras, the exact position and orientation of the intruder can be estimated via triangulation. However, in practice, we do not have infinite resolution cameras. Therefore, the intruder can no longer be localized via triangulation in the line of sight of the camera with the highest accuracy.

\begin{figure}[htb]
\centering
{\includegraphics[width=0.7\textwidth]{room.pdf}}
\vspace{-1.5cm}
\caption{Localizing an intruder $\mathbf{P}$ in \emph{any} room type using infinite resolution cameras.}
\label{fig:room}
\end{figure}

In the case of finite-resolution cameras, the intruder can therefore be localized in a \emph{region of interest}, instead of a particular point. This region of interest is generated by the intersecting half-planes of the activated pixels~\footnote{Activated pixel denotes the corresponding pixel in the finite-resolution camera that contains the corresponding feature-point of the localized object.} in the two cameras. We illustrate this scenario in Fig.~\ref{fig:room2}.

\begin{figure}[htb]
\centering
{\includegraphics[width=0.45\textwidth]{roi-room.pdf}}
\caption{Region of interest is an \emph{area} instead of a particular point, when we deal with finite resolution pixel camera.}
\label{fig:room2}
\end{figure}

From Fig.~\ref{fig:room2}, we also observe that the consistent region for localizing the intruder progressively reduces with the addition of new cameras, assuming that the intruder can be captured in the new cameras as well. The new consistent region is estimated by the progressive intersection of the half-spaces.

\section{Problem Set-up}
\label{sec:chap8-setup}
In this section, we will formally introduce the problem setup and also explain the various notations. These notations will be used throughout this chapter and will be consistent throughout this chapter, unless specified otherwise.

For the sake of simplicity, we consider the case of localizing a point $\mathcal{I}$ in a 2-dimensional search space, $\hat{\mathcal{S}} \in {\rm I\!R}^{2}$. The analysis can be easily extended to 3-dimensional search space as well. Let us consider that we are interested to localize the point $\mathcal{I}$, as shown in Fig.~\ref{fig:setup-one}. The figure describes the acquisition system with one finite-resolution camera. The camera location is denoted by ($\hat{x}^1$,$\hat{y}^1$), and its view angle as $\Theta^1$. Therefore, the camera pose is referred as ($\hat{x}^1$,$\hat{y}^1$,$\Theta^1$), which collectively defines the camera location and the view angle. All these measurements are denoted with respect to any global co-ordinate system. In the illustration, we denote the finite-resolution camera to have $4$ equal-width pixels, with $5$ corresponding light rays\footnote{We consider a pin-hole camera model}. All these rays have viewing angles of $\theta_1$, $\theta_2$, \ldots , $\theta_5$, with respect to the X-axis. Without any loss of generality, we consider the corresponding feature point of point $\mathcal{I}$ is observed in the fourth pixel of the camera. This pixel is referred as the \emph{active pixel}, throughout this chapter. The half-spaces corresponding to the active pixel make angles $\theta_4$ and $\theta_5$ respectively with the X-axis.

\begin{figure}[htb]
\centering
{\includegraphics[width=0.5\textwidth]{setup-one_2_ver2.pdf}}
\caption{Acquisition system with one camera, mentioning the various camera pose notations.}
\label{fig:setup-one}
\end{figure}

This problem set-up can also be extended to that with multiple cameras. We illustrate this in Fig.~\ref{fig:setup-many}. The illustration shows a set-up consisting of two cameras. Following a similar naming convention, the second camera has the pose ($\hat{x}^2$,$\hat{y}^2$,$\Theta^2$). Also, the corresponding feature of the point $\mathcal{I}$ is observed in the first pixel of the camera.

\begin{figure}[htb]
\centering
{\includegraphics[width=0.7\textwidth]{setup-many_2_ver2.pdf}}
\caption{Acquisition system with multiple cameras, mentioning the various camera pose notations.}
\label{fig:setup-many}
\end{figure}

This set-up can be therefore generalized for $\tilde{n}$ cameras, with random camera poses. The pose of the $\tilde{n}$-th camera is denoted by ($\hat{x}^{\tilde{n}}$,$\hat{y}^{\tilde{n}}$,$\Theta^{\tilde{n}}$).

For subsequent calculations, we also define \emph{offset angle} of all the rays with respect to its corresponding view angles. These offset angles are the difference of angles between the light rays and the camera view angle~\footnote{Camera View Angle can also be defined as the angle made by the central pixel with the global X-axis.}. Mathematically speaking, it can defined as follows:

\begin{equation*}
\centering
\begin{aligned}
\theta_1 = \delta_1 + \Theta \\
\theta_2 = \delta_2 + \Theta \\
\ldots \\
\theta_5 = \delta_5 + \Theta \\
\end{aligned}
\end{equation*}

For the sake of brevity, we will drop the index $\hat{i}$ for the $\hat{i}$-th camera in most of our discussions.

\section{SHARP: A Consistent and Optimal Localization Algorithm}
\label{sec:SHARP}
For cameras having noiseless camera poses and noiseless feature matching, a recent point localization algorithm called \textbf{SHARP} was proposed by Ghasemi et al.\ ~\cite{SHARP}. \textbf{SHARP} stands for \textbf{S}equential \textbf{H}alf space \textbf{A}ggregation for \textbf{R}econstructing a \textbf{P}oint. It consists in the generation of half spaces from the light rays corresponding to the active pixel. Subsequently, the convex polygon is generated with these intersection of half spaces. This process is continued till all the cameras in the set-up are added in the system. These half-space intersections generate a closed convex polygon. Assuming that the point is equally likely to be present inside the polygon, SHARP returns the centroid of the polygon as the optimal estimate. We have illustrated this concept in Fig.~\ref{fig:sharp-fig}.

\begin{figure}[htb]
\centering
{\includegraphics[width=0.5\textwidth]{SHARP-illustrate.pdf}}
\caption{Illustration of half-space intersections to generate a closed convex polygon in a multiple-camera setup.}
\label{fig:sharp-fig}
\end{figure}

The current state-of-the-art localization algorithms consists in minimizing the re-projection error of the point to the center of the active pixel, under different constraints. We explain this by illustrating the simplest case of point reconstruction with single camera, as shown in Fig.~\ref{fig:setup-one}.

The estimate $\mathbf{p}^{*}$, for the actual point $\mathbf{p}$ is calculated as an error minimization problem. Let us suppose the pixel center is denoted by $\mathbf{q}$, and the re-projection function to the image plane is defined as ${\Phi}(\boldsymbol{p'})$. The estimate is calculated as shown in Eq.~\ref{eq:norm_min}, under different norm constraints (viz.\ $\ell_1, \ell_2, \ell_\infty$).

\begin{equation}
\centering
		\mathbf{p}^{*} = \arg \min_{\boldsymbol{p'}} \left\|\boldsymbol{q} - {\Phi}(\boldsymbol{p'})\right\|_{\ell_1, \ell_2, \ell_\infty}
\label{eq:norm_min}		
\end{equation}

\section{SHARP with Noisy Camera Poses}
\label{sec:chap8-noisySHARP}
In the case of noiseless camera poses, half spaces corresponding to the active pixels of the different cameras form a consistent region. We show this in Fig.\ref{fig:nless-example}. Three cameras having finite-resolution pixels are stationed in ${\rm I\!R}^{2}$ with random camera poses. With noiseless camera poses, the probability of localizing the point is unity anywhere inside the consistent region (cf.\ Fig.~\ref{fig:nless-example}(b)). SHARP returns the centroid of this region as the optimal estimate.

\begin{figure}[htb]
\centering
\includegraphics[height=0.4\textwidth]{NLess.pdf} 
\hspace{1mm}
\includegraphics[height=0.4\textwidth]{NlessReg.pdf}\\
\makebox[0.45\textwidth][c]{(a)}
\makebox[0.45\textwidth][c]{(b)}
\caption[Illustration of a consistent region when the camera poses are noiseless.]{A consistent region is formed when the camera poses are noiseless.}
\label{fig:nless-example}
\end{figure}

However, in the event of noisy camera poses, a consistent region can no longer be computed. We illustrate this in Fig.~\ref{fig:nmore-example}. In this chapter, we propose a modified SHARP algorithm that localizes the point with high accuracy in the event of noisy camera poses.

\begin{figure}[htb]
\centering
\includegraphics[width=0.4\textwidth]{Nmore} 
\makebox[0.45\textwidth][c]{\centering No Consistent Region}
\caption[Illustration of a non-consistent region when the camera poses are noisy.]{Consistent region can no longer be formed with noisy camera poses.}
\label{fig:nmore-example}
\end{figure}

\subsection{Motivation \& Insights}
We explain the insights behind our proposed approach with a simple example. Consider a single camera (CAM 1) with $4$ equal-width pixels in ${\rm I\!R}^{2}$, as shown in Fig.~\ref{fig:one-examp}. We are interested to localize the point $P$, shown in \emph{red}. The fourth pixel of the camera is the corresponding active pixel.

\begin{figure}[htb]
\centering
\includegraphics[width=0.5\textwidth]{theta-example2.pdf} 
\caption{Illustration of a single camera with finite pixel resolutions.}
\label{fig:one-examp}
\end{figure}

Considering that the feature-point matching is correct, the point $P$ can lie anywhere between the two half spaces defined by the active pixels. Therefore, we obtain a uniform probability of unity for the distribution of active region, as shown in Fig.~\ref{fig:act-reg}(b). This holds true for noiseless camera poses.

\begin{figure}[htb]
\centering
\includegraphics[width=0.45\textwidth]{theta-example3.pdf} 
\includegraphics[width=0.45\textwidth]{theta-ex-nless}\\
\makebox[0.45\textwidth][c]{(a)}
\makebox[0.45\textwidth][c]{(b)}	
\caption{Distribution of active region with noiseless camera view angle.}
\label{fig:act-reg}
\end{figure}

However, it no longer holds for noisy camera poses. As an example, we consider noise only in view angle of the camera. We illustrate this in Fig.~\ref{fig:nois-act}, where the view angle of the camera CAM 1 is noisy. In this case, the probability of point $P$ (which is outside the region enclosed between two half-spaces) to lie in active region is \emph{non-zero}. Assuming a gaussian noise model, we are interested to compute the distribution of active region in ${\rm I\!R}^{2}$ for this illustration.

\begin{figure}[htb]
\centering
\includegraphics[width=0.5\textwidth]{theta-6.pdf} 
\caption[Illustration of a single camera with noisy view angle.]{Single camera with noisy view angle. There exists a finite non-zero probability for the point $P$ to lie in active region.}
\label{fig:nois-act}
\end{figure}

We assume the view angle follows a gaussian distribution with mean value $\bar{\Theta}$ and variance $\sigma_\Theta^2$.

\begin{equation}
\centering
\begin{aligned}
\Theta \sim \mathcal{N}(\bar{\Theta} , \sigma_\Theta^2)
\end{aligned}
\end{equation}

We are interested to compute the two limits for which point $\mathbf{p}$ (which makes an angle $\theta$ with X-axis) fall in the active region. We illustrate the case of upper limit in Fig.~\ref{fig:upp-bnd}. Point $\mathbf{p}$ can be inside active region when CAM 1 is rotated in the clock-wise direction by a specific amount as shown in Fig.~\ref{fig:upp-bnd}.

\begin{figure}[htb]
\centering
\includegraphics[width=0.75\textwidth]{theta-6a.pdf} 
\caption{Computation of upper bound on the view angle.}
\label{fig:upp-bnd}
\end{figure}

We calculate this angle as:

\begin{equation}
\centering
\begin{aligned}
\theta_4^{'} = \theta_4 - (\theta_4 - \theta)\\
\implies \theta_4^{'} = \theta \\
\implies \Theta + \delta_4 = \theta \\
\implies \Theta  = \theta - \delta_4
\end{aligned}
\end{equation}

Therefore, camera view angle ($=\Theta$) equal to $\theta - \delta_4$ corresponds to the upper limit of the view angle for which the point $\mathbf{p}$ lie inside the active region.

Similarly, we compute the lower bound. We illustrate it in Fig.~\ref{fig:low-bnd}. In this case, CAM 1 needs to be rotated further such that the new position of $\theta_5$ coincides with $\theta$.

\begin{figure}[htb]
\centering
\includegraphics[width=0.75\textwidth]{theta-6b.pdf} 
\caption{Computation of lower bound on the view angle.}
\label{fig:low-bnd}
\end{figure}

We calculate this angle as:

\begin{equation}
\centering
\begin{aligned}
\theta_4^{'} = \theta_4 - (\theta_5 - \theta)\\
\implies \theta_4^{'} = \theta_4 - \theta_5 + \theta\\
\implies \Theta + \delta_4 = \theta_4 - \theta_5 + \theta\\
\implies \Theta  = \theta_4 - \theta_5 + \theta - \delta_4\\
\end{aligned}
\end{equation}

Therefore, camera view angle ($=\Theta$) equal to $\theta_4 - \theta_5 + \theta - \delta_4$ corresponds to the lower limit of the view angle for which the point $P$ lie inside the active region.

For a particular noise level in camera view angle (fixed variance $\sigma_\Theta^2$), we can thus calculate the probability of each point in ${\rm I\!R}^{2}$ to fall in active region. We show the distribution of active region in Fig.~\ref{fig:dist-actr}.

\begin{figure}[htb]
\centering
\includegraphics[height=0.4\textwidth]{theta-ex-noisy} 
\includegraphics[height=0.4\textwidth]{colorbar.pdf}
\caption{Distribution of active region with noise only in view angle.}
\label{fig:dist-actr}
\end{figure}

Assuming gaussian noise, this distribution is generated by calculating the normal cumulative probability defined over appropriate \emph{lower} and \emph{upper} bounds. We will formally define our proposed algorithm in Section~\ref{sec:prop-alg}.

\subsection{Geometric Constraints}
In the illustration in Fig.~\ref{fig:nois-act}, we explain the scenario where noise is present only in view angle. However, noise can also be present in the camera positions (x- and y- coordinate in ${\rm I\!R}^{2}$ plane). In this section, we will compute the geometrical limits for three distinct cases: noise in view angle, X- and Y- coordinate of the camera.

It should be noted here that the geometrical limits depend on the position of point $P$ in ${\rm I\!R}^{2}$. We divide this search space into $6$ distinct scenarios, as depicted in Fig.~\ref{fig:scene}.

\begin{figure}[htb]
\centering
\includegraphics[width=0.65\textwidth]{scenario.pdf} 
\caption{Depicting $6$ distinct scenarios in ${\rm I\!R}^{2}$, when the noise is present in camera locations.}
\label{fig:scene}
\end{figure}

\subsubsection{Noise in view angle}
We calculate the bounds in the view angle, assuming that the camera locations are noiseless.

\subsubsection{Upper Bound}
We show the computation for Scenario I. 
\begin{figure}[htb]
\centering
\includegraphics[width=0.85\textwidth]{theta-1a.pdf} 
\caption[Determination of upper bound of view angle for the rotation of camera.]{Determination of upper bound of view angle for the rotation of camera (Scenario I).}
\end{figure}

\begin{equation}
\centering
\begin{aligned}
\theta_5^{'} = \theta_5 + (\theta - \theta_4)\\
\Theta + \delta_5 = \theta_5 + (\theta - \theta_4)\\
\implies \Theta = \theta_5 + (\theta - \theta_4) - \delta_5
\end{aligned}
\end{equation}

\subsubsection{Lower Bound}

\begin{figure}[htb]
\centering
\includegraphics[width=0.6\textwidth]{theta-1b.pdf} 
\caption[Determination of lower bound of view angle for the rotation of camera.]{Determination of lower bound of view angle for the rotation of camera (Scenario I).}
\end{figure}

\begin{equation}
\centering
\begin{aligned}
\theta_4^{'} = \theta_4 - (\theta_5 - \theta)\\
\Theta + \delta_4 = \theta_4 - (\theta_5 - \theta)\\
\implies \Theta = \theta_4 - \theta_5 + \theta - \delta_4
\end{aligned}
\end{equation}

Therefore, the lower and upper geometrical limits are $+(\theta_4 - \theta_5 + \theta - \delta_4)$ and $+(\theta_5 + (\theta - \theta_4) - \delta_5)$ \footnote{Please note the positive and negative conventions. Rotations in the clockwise direction are positive, while the counter-clockwise rotations are referred as negative.}. Also note that these bounds are restricted to all points lying in Scenario I \footnote{Calculation related to Scenario II-VI are provided in Appendix~\ref{append:multicamera}.}.

\section{Proposed Algorithm}  % Article style
\label{sec:prop-alg}

In this section, we will define our proposed localization algorithm.

\subsection{Noise Model}
We assume that the poses for the different cameras in the multi-camera system assume a gaussian distribution. Let us assume that $\Theta^{\hat{i}}$ is the view angle of $\hat{i}$-th camera. And $\Delta \hat{x_c}^{\hat{i}}$ and $\Delta \hat{y_c}^{\hat{i}}$ are the translations of the $\hat{i}$-th camera in X- and Y- directions respectively. Without any loss of generality, we will drop the suffix $\hat{i}$ in our discussions.

We assume that the view angle $\Theta$ follows a normal distribution with mean $\bar{\Theta}$ and variance $\sigma_\Theta^2$.

\begin{equation}
\centering
\begin{aligned}
\Theta \sim \mathcal{N}(\bar{\Theta} , \sigma_\Theta^2)
\end{aligned}
\end{equation}

Similarly, $\Delta \hat{x_c}$ and $\Delta \hat{y_c}$ follow a gaussian distribution with mean $0$ and variance $\sigma_{\Delta \hat{x_c}}^2$ and $\sigma_{\Delta \hat{y_c}}^2$ respectively.

\begin{equation}
\centering
\begin{aligned}
\Delta \hat{x_c} \sim \mathcal{N}(0, \sigma_{\Delta \hat{x_c}}^2)\\
\Delta \hat{y_c} \sim \mathcal{N}(0, \sigma_{\Delta \hat{y_c}}^2)
\end{aligned}
\end{equation}

Considering independent and identically distributed random variables, noise in each of the three components: view angle, X- and Y- coordinate can be treated separately.

However, we combine them in a single model by defining a multivariate gaussian distribution. We define this distribution for any position ($\hat{x}$,$\hat{y}$) in ${\rm I\!R}^{2}$ as:

\begin{equation}
\centering
\Psi(\hat{x},\hat{y}) = \mathcal{N}(\boldsymbol{\mu},\mathbf{\Sigma})
\end{equation}

, where $\boldsymbol{\mu}$ is the mean vector and $\mathbf{\Sigma}$ is the covariance matrix. They are given by:

\begin{equation}
\centering
\boldsymbol{\mu}=[\mu_\Theta, \mu_{\Delta \hat{x}}, \mu_{\Delta \hat{y}}]
\label{eq:mean-vector}
\end{equation}

and

\begin{equation}
\mathbf{\Sigma} = 
\begin{pmatrix} 
\sigma_\Theta^2 & \sigma_\Theta \sigma_{\Delta \hat{x_c}} & \sigma_\Theta \sigma_{\Delta \hat{y_c}}\\ 
\sigma_{\Delta \hat{x_c}} \sigma_\Theta  & \sigma_{\Delta \hat{x_c}}^2 & \sigma_{\Delta \hat{x_c}} \sigma_{\Delta \hat{y_c}}\\
\sigma_{\Delta \hat{y_c}} \sigma_\Theta & \sigma_{\Delta \hat{y_c}} \sigma_{\Delta \hat{x_c}}& \sigma_{\Delta \hat{y_c}}^2
\end{pmatrix}
\end{equation}

\subsection{Proposed Approach}

Our proposed approach returns the point in the search space ${\rm I\!R}^{2}$ having the highest value. We observe the noisy view angle, and set it to $\mu_\Theta$ as shown in Eq.~\ref{eq:mean-vector}. The other parameters $\mu_{\Delta \hat{x}}$ and $\mu_{\Delta \hat{y}}$ are set to $0$. We compute the \textbf{multivariate normal cumulative probability} evaluated over the \emph{4-dimensional hypercube} defined with \emph{appropriate} lower and upper limits, for all the cameras in the system. We compute the product of these values for all the cameras, and return the point having the highest measure.

We outline our algorithm in Algorithm~\ref{alg:mod_sharp}.

\begin{algorithm}[htb]
\caption{Point localization algorithm with noisy camera poses}
\label{alg:mod_sharp} 
\begin{algorithmic}[1]
\Require Set of parameters for noise in view angle, X- and Y- component i.e.\ $\boldsymbol{\mu}$ and $\mathbf{\Sigma}$.
\Ensure Estimated point position in ${\rm I\!R}^{2}$.
\Loop { For all points in search space ${\rm I\!R}^{2}$}
\Loop { For all $\hat{i}$ cameras in multi-camera system}
	\State Observe a noisy realization for a camera in multi-camera system.
	\State Set $\mu_\Theta$ as the noisy view angle for the camera.
	\State Rotate the half-spaces such that these half-spaces lie in $1$st quadrant, as shown in Fig.~\ref{fig:scene}.
	\State Compute the \textbf{multivariate normal cumulative probability} evaluated over the \emph{4-dimensional hypercube} defined with \emph{appropriate} lower and upper limits, denoted by $p^{\hat{i}}$. 
\EndLoop
\EndLoop
\State Compute the product of all the multivariate normal cumulative probability values, i.e.\ $p$ =$p^1*p^2*\ldots*p^{\hat{i}}$.
\State \textbf{return} point in ${\rm I\!R}^{2}$ with maximum value, i.e.\ $(\hat{x},\hat{y})$= $\underset{\hat{x},\hat{y}}{\operatorname{argmax}}\mbox{ }p$.
	\end{algorithmic}
\end{algorithm}

\subsection{Computation of Proposed Approach}
In this section, we will describe the process of computing the multivariate normal cumulative probability values. We define the geometrical bounds $\forall$ ($\hat{x}$,$\hat{y}$) $\in {\rm I\!R}^{2}$ as $\hat{a}(\hat{x},\hat{y})$ and $\hat{b}(\hat{x},\hat{y})$. Let us assume that the multivariate normal distribution for view angle, X- and Y- component be $f(\Theta)$, $f(\Delta \hat{x})$ and $f(\Delta \hat{y})$. We define the multivariate normal cumulative probability for a single camera as $F(\hat{x},\hat{y})$.

For a single camera, we define as,

\begin{equation*}
\centering
F(\hat{x},\hat{y}) = \int_{\hat{a}(\hat{x},\hat{y})}^{\hat{b}(\hat{x},\hat{y})} f(\Theta , \Delta \hat{x} , \Delta \hat{y})d\Theta d\Delta \hat{x} d\Delta \hat{y}\forall \hat{x},\hat{y} \in \hat{\mathcal{S}},
\end{equation*}

where it is integrated over the geometrical bounds $\hat{a}(\hat{x},\hat{y})$ and $\hat{b}(\hat{x},\hat{y})$ for all the components.

Assuming that noises are i.i.d. over these three components, we can re-define $F(\hat{x},\hat{y})$ as follows:

\begin{equation*}
\centering
F(\hat{x},\hat{y}) = \int_{\hat{a}(\hat{x},\hat{y})}^{\hat{b}(\hat{x},\hat{y})} f(\Theta)d\Theta * \int_{\hat{a}(\hat{x},\hat{y})}^{\hat{b}(\hat{x},\hat{y})} f(\Delta \hat{x})d\Delta \hat{x} * \int_{\hat{a}(\hat{x},\hat{y})}^{\hat{b}(\hat{x},\hat{y})} f(\Delta \hat{y})d\Delta \hat{y}
\end{equation*}

\begin{equation*}
\centering
F(\hat{x},\hat{y}) = F_{\Theta}(\hat{x},\hat{y})*F_{\Delta \hat{x}}(\hat{x},\hat{y})*F_{\Delta \hat{y}}(\hat{x},\hat{y})
\end{equation*}

We are interested to compute ${\operatorname{argmax}}F(\hat{x},\hat{y})$, and localize the point $(\hat{x},\hat{y})$ in ${\rm I\!R}^{2}$. We employ a simple gradient ascent algorithm for the same; we state it in Algorithm~\ref{alg:grad_asc}. We define a learning rate $\eta$, and compute the gradient $F'(\mathbf{t})$ \footnote{$F'(\mathbf{t})$ has different forms depending on the location of point $\mathbf{t}$ in search space $\hat{\mathcal{S}}$.}. Thus, each point $\mathbf{t} \in {\rm I\!R}^{2}$ is updated accordingly.

\begin{algorithm}[htb]
\caption{Gradient ascent algorithm for the computation of $F(\hat{x},\hat{y})$.}
\label{alg:grad_asc} 
\begin{algorithmic}[1]
\Require Noisy camera parameters for all the $\hat{i}$ cameras.
\Ensure Estimated point location $\mathcal{I}, (\hat{x},\hat{y}) \in {\rm I\!R}^{2}$
\State Choose an initial point $\mathbf{t} \in {\rm I\!R}^{2}$, in search space $\hat{\mathcal{S}}$, and learning rate $\eta$
\Loop { Until \emph{convergence} is achieved.}
\State Compute $F'(\mathbf{t})$ at point $\mathbf{t}$.
\State Update new location, $$\mathbf{t}^u \coloneqq \mathbf{t} + \eta F'(\mathbf{t})$$
\EndLoop
\State Converged optimal point, $\mathbf{t}^{*}$ = $\mathbf{t}^u$.
\State \textbf{return} point location $\mathcal{I}$, as indicated by $\mathbf{t}^{*}$.
\end{algorithmic}
\end{algorithm}

Our objective function $F(\hat{x},\hat{y})$ has no closed form expression; however an exact expression exists for $F'(\hat{x},\hat{y})$.

Let us now show the computation of gradient for view angle. We know,

\begin{equation*}
\centering
F_{\Theta}(\hat{x},\hat{y}) = \int_{\hat{a}(\hat{x},\hat{y})}^{\hat{b}(\hat{x},\hat{y})} f_{\Theta}(\hat{x},\hat{y})d\hat{x} d\hat{y}, \forall \hat{x},\hat{y} \in \hat{\mathcal{S}},
\end{equation*}

We define the gradient $F'_{\Theta}(\hat{x},\hat{y})$ over $\hat{x}$ and $\hat{y}$ as

\begin{equation*}
\centering
F'_{\Theta}(\hat{x},\hat{y}) =  [\frac{\partial F_{\Theta}(\hat{x},\hat{y})}{\partial \hat{x}} \mbox{   }\frac{\partial F_{\Theta}(\hat{x},\hat{y})}{\partial \hat{y}}]
\end{equation*}

The partial derivatives are computed using Leibniz integral rule.

\begin{equation*}
\frac{\partial F_{\Theta}(\hat{x},\hat{y})}{\partial \hat{x}} = f_{\Theta}(\hat{b}(\hat{x},\hat{y}))\frac{\partial f_{\Theta}(\hat{b}(\hat{x},\hat{y}))}{\partial \hat{x}} - f_{\Theta}(\hat{a}(\hat{x},\hat{y}))\frac{\partial f_{\Theta}(\hat{a}(\hat{x},\hat{y}))}{\partial \hat{x}}
\end{equation*}

\begin{equation*}
\frac{\partial F_{\Theta}(\hat{x},\hat{y})}{\partial \hat{y}} = f_{\Theta}(\hat{b}(\hat{x},\hat{y}))\frac{\partial f_{\Theta}(\hat{b}(\hat{x},\hat{y}))}{\partial \hat{y}} - f_{\Theta}(\hat{a}(\hat{x},\hat{y}))\frac{\partial f_{\Theta}(\hat{a}(\hat{x},\hat{y}))}{\partial \hat{y}}
\end{equation*}

We compute these partial derivatives separately for all $6$ different scenarios. Let us check for Scenario $1$.

For scenario $1$, the lower- and upper- bounds are given by $\hat{a}(\hat{x},\hat{y})=+(\theta_4 - \theta_5 + \theta - \delta_4)$ and $\hat{b}(\hat{x},\hat{y})=+(\theta_5 + (\theta - \theta_4) - \delta_5)$ respectively. All quantities except $\theta$ are constant, and then their corresponding derivatives are zero. The quantity $\theta$ can be expressed in terms of $\hat{x}$ and $\hat{y}$, as follows:

\begin{equation*}
\theta = \tan ^{-1}\frac{(\hat{y}-\hat{y}_c)}{(\hat{x}-\hat{x}_c)}
\end{equation*}

Therefore, $\frac{\partial f_{\Theta}}{\partial \hat{x}}$ and $\frac{\partial f_{\Theta}}{\partial \hat{y}}$ are given by

\begin{equation*}
\frac{\partial f_{\Theta}}{\partial \hat{x}} = \frac{\hat{y}_c - \hat{y}}{(\hat{x} - \hat{x}_c)^2 + (\hat{y} - \hat{y}_c)^2}
\end{equation*}

\begin{equation*}
\frac{\partial f_{\Theta}}{\partial \hat{y}} = \frac{(\hat{x} - \hat{x}_c)^2}{(\hat{x} - \hat{x}_c)^2 + (\hat{y} - \hat{y}_c)^2}
\end{equation*}

Similarly, the gradient over the remaining two X- and Y- components $F'_{\Delta \hat{x}}(\hat{x},\hat{y})$ and $F'_{\Delta \hat{y}}(\hat{x},\hat{y})$ can be defined accordingly.

In a general setting having multiple cameras in the setup, our objective function takes the form as,

\begin{equation*}
G(\hat{x},\hat{y}) = F_1(\hat{x},\hat{y})F_2(\hat{x},\hat{y}) \ldots F_{\tilde{n}}(\hat{x},\hat{y})
\end{equation*}

Similarly, the gradient $F'(\hat{x},\hat{y})$ can be generalized to $\tilde{n}$ cameras as follows:

\begin{equation*}
\centering
\begin{aligned}
G'(\hat{x},\hat{y}) = F_1'(\hat{x},\hat{y})F_2(\hat{x},y) \ldots F_{\tilde{n}}(\hat{x},\hat{y}) \\
+ F_1(\hat{x},\hat{y})F_2'(\hat{x},\hat{y}) \ldots F_{\tilde{n}}(\hat{x},\hat{y}) \\
+ \ldots \\
+ F_1(\hat{x},\hat{y})F_2(\hat{x},\hat{y}) \ldots F_{\tilde{n}}'(\hat{x},\hat{y})
\end{aligned}
\end{equation*}

\section{Experimental Evaluations}
\label{sec:chap8-exps}
In order to assess the accuracy of the modified SHARP algorithm, we conduct extensive experiments. We compare the re-projection error of the proposed algorithm with the other state-of-the-art algorithms. We have briefly described the various benchmarking algorithms in Section~\ref{sec:SHARP}.

We consider a three-camera setup for our experimental evaluations. The scenario is depicted in Fig.~\ref{fig:eval3}. Each camera has a random position and view-angle in the $2$-dimensional search space, $\hat{\mathcal{S}} \in {\rm I\!R}^{2}$. Suppose that the actual position of the localized point is denoted by \emph{red} dot. We are interested to localize this point with highest accuracy in case of noisy camera poses.

\begin{figure}[htb]
\centering
\includegraphics[width=0.5\textwidth]{NLess}
\caption[Experimental set-up with three cameras having random camera poses.]{Experimental set-up with three cameras having random camera poses. The three cameras are represented as CAM 1, CAM 2 and CAM 3 respectively. The actual location of the localized point is denoted in \emph{red} dot.}
\label{fig:eval3}	
\end{figure}

In case of noiseless scenario, a consistent and convex polygon is generated by the intersection of corresponding half-spaces. Considering a uniform distribution in the probability of localizing the point, the centroid of the convex polygon provides the optimal estimate. However, a consistent region can no longer be computed in case of noisy camera poses.

In order to understand the effect of noise in the re-projection error, we experiment for various scenarios.

\subsection{Effect of Noise in View Angle}
We vary the noise in the view angle, by keeping the noise in camera locations fixed. We set the camera location noise as $\sigma_{\Delta \hat{x}}$ = $0.1$ and $\sigma_{\Delta \hat{y}}$ = $0.1$. We should note that noise is present in all the three cameras. Using the modified SHARP algorithm, we compute the location having the highest probability in ${\rm I\!R}^{2}$. We perform this experiment for $100$ different trials, and report the average re-projection error. We show the results in Fig.~\ref{fig:noise-angle}. Clearly, the proposed algorithm works best as compared to $\ell_1$-, $\ell_2$- and $\ell_{\mbox{inf}}$- norm minimization techniques. Moreover, with increasing noise, the performance of the other algorithms continues to degrade. Our proposed approach has a stable performance at higher noise levels too.

\begin{figure}[htb]
\centering
\includegraphics[width=0.7\textwidth]{noise-theta}
\caption{Effect on re-projection error with varying noise in view angle.}
\label{fig:noise-angle}	
\end{figure}

\subsection{Effect of Noise in X-component of Camera Positions}

We also analyze the effect of noise in X- component of camera position on the average re-projection error. We vary this noise, by keeping the noise in the other components fixed. We set the noise in view angle as $\sigma_{\Theta}$ = $1$ and in the Y-component as $\sigma_{\Delta \hat{y}}$ = $0.1$. We calculate the average re-projection error for varying amount of noise in X- component. Each score is averaged over $100$ different experiment trials. Figure~\ref{fig:noise-X} reports the results. It is clear that our proposed approach works best as compared to other algorithms.
\begin{figure}[htb]
\centering
\includegraphics[width=0.7\textwidth]{noise-X}
\caption{Effect on re-projection error with varying noise in X co-ordinate of the camera positions.}
\label{fig:noise-X}	
\end{figure}

\subsection{Effect of Noise in Y-component of Camera Positions}

We perform similar experiments for varying amount of noise in Y-component of camera positions for the $3$ cameras. We set the noise in other components fixed: $\sigma_{\Theta}$ = $1$ and $\sigma_{\Delta \hat{x}}$ = $0.1$, and vary the noise in Y-component of camera locations. We perform $100$ experiments for a single noise setting. Figure~\ref{fig:noise-Y} shows the results for varying amount of noise. It is clear that our proposed approach works best as compared to the benchmark methods.

\begin{figure}[htb]
\centering
\includegraphics[width=0.7\textwidth]{noise-Y}
\caption{Effect on re-projection error with varying noise in Y co-ordinate of the camera positions.}
\label{fig:noise-Y}		
\end{figure}

In this section, we have proposed a point localization algorithm with noisy camera poses. This has been done in $2$-D under arbitrary camera poses with finite resolutions and perfect feature matching. We formalize this as a gradient ascent algorithm, and derive closed-form expressions for the objective function. Extensive experimental results prove the efficacy of our proposed approach as compared to other state-of-the-art point localization algorithms. In the subsequent section, we will discuss such localization task in the context of cloud imaging. We present our current work on localizing a cloud mass using a stereo-setup of sky cameras.

\section{Application to Ground-based Sky Cameras} 
\label{sec:chap8-cloudheight}
In this section, we present an illustration of localization algorithm in a network of multiple ground-based sky cameras. We present a framework for cloud base height estimation using two such imagers. Our method is based on stereoscopic scene flow. We demonstrate the feasibility of our approach and use computer-generated images with controlled cloud height to validate the accuracy of our method.

Localizing clouds in 3D space is a challenging task. Clouds usually do not exhibit precise boundaries and may not have distinctive textures, which makes matching two images difficult. However, clouds evolve slowly, and successive frames look similar. We present a method to estimate the cloud base height from a succession of images captured by ground-based imagers with a hemispherical view of the sky. We use stereoscopic scene flow, which is defined as the three-dimensional motion field of points in the world~\cite{vedula1999three}. This allows us to retrieve the 3D location as well as the motion of the clouds, by incorporating past frames in the computation. Although we focus on the 3D location (i.e.\ cloud base height) in this work, the motion information can be used as input for cloud movement prediction.

\subsection{Workflow}
This section describes the workflow of our proposed approach. It takes as input a sequence of images taken simultaneously by two sky imagers, such as those shown in Fig.~\ref{fig:wahrsis-pictures}. They were taken by a pair of our custom-designed whole sky imagers~\cite{WAHRSIS,IGARSS2015a}, which we call Wide-Angle High-Resolution Sky Imaging System (WAHRSIS). More details of these imaging system were already discussed earlier in Chapter~\ref{chap:wsi} of the thesis. The two imagers are placed approximately 95 meters apart on rooftops of the Nanyang Technological University in Singapore.

\begin{figure}[htb]
\centering
\includegraphics[height=3cm]{wahrsis1.jpg}
\includegraphics[height=3cm]{wahrsis3.jpg}
\caption{Images captured by the pair of sky imagers.}\label{fig:wahrsis-pictures}
\end{figure}

\subsubsection{Undistortion}
The first step consists of removing the distortion due to the fish-eye lens in the images. The projection behavior of the lens used in our imagers follows the equisolid angle mapping function, $r=2\bar{f}\sin(\beta/2)$, where $r$ is the distance from the image center, $\beta$ is the elevation angle of the incident light ray, and $\bar{f}$ is the focal length. More details about different projection functions are described in Chapter~\ref{chap:wsi}. We thus can retrieve the incident light ray of every pixel in the image. The position along that ray is the value which needs to be computed by triangulation to find the position of the cloud in 3D. Fig.~\ref{fig:undistortion} shows the original image and the pixel values projected on a hemisphere.

\begin{figure}[htb]
\centering
\includegraphics[height=6cm]{undistortion.png}
\caption[Illustration of the undistortion process of an image taken with our fish-eye lens of WAHRSIS.]{Illustration of the undistortion process of an image taken with our fish-eye lens (bottom). The color value of each incident light ray is projected on a hemisphere (middle). The image plane (top) is computed as the value of each light ray going through the pixel at its location (as indicated at the corners of the image).}\label{fig:undistortion}
\end{figure}

We use a ray-tracing approach to generate undistorted images. Considering the camera at the origin, we place a virtual plane at a user-defined height. We then compute the pixel values of the image by looking for the incident light ray that intersects the plane at the pixel location, as shown in Fig.~\ref{fig:undistortion}. There is usually no ray going through an exact pixel location, so we interpolate using the nearest rays.

In order to map this image to real world coordinates, we give each pixel a width of one meter. We then define the height of the plane to be at $400$ meters, which translates to a viewing angle of $103$ degrees.

\subsubsection{Rectification}
We use the real world units defined above to place the image plane of the second imager with respect to the first one. In practice, the positions of the imagers can be retrieved by Global Positioning System (GPS). Stereo vision algorithms typically compute the disparity between the left and right images along one axis only in order to reduce the complexity. For this, the input images need to lie on a common image plane. The process of computing such images is known as rectification.

We incorporate this step into the undistortion process described above. We apply 3D rotations on the virtual image plane before computing the pixel values, as shown in Fig.~\ref{fig:rectification}. Two rotations are needed. The first one is applied around the $z$ axis and relates the difference of longitude and latitude between the imagers, quantified with the azimuth angle $\omega_1$. The second rotation is applied around the rotated $y$ axis and relates the difference in altitude between the imagers, which is quantified with the elevation angle $\omega_2$.

\begin{figure}[htb]
\centering
\subfloat[Before rectification]{\includegraphics[height=5cm]{rect1.pdf}}
\subfloat[After rectification]{\includegraphics[height=5cm]{rect2.pdf}}
\caption[Illustration of the rectification process of the fish-eye effect.]{Illustration of the rectification process. The two coloured dots represent the two imagers with their respective image planes. The disparity between the images only appears along one axis after rectification.}\label{fig:rectification}
\end{figure}

Figure~\ref{fig:rectification-result} shows both pairs of undistorted images before and after rectification. Notice how the disparity between the images is only present along the horizontal axis in Fig.~\ref{fig:rectification-result}(b).

\begin{figure}[htb]
\centering
\subfloat[Before rectification]{
\begin{tikzpicture}
\node[inner sep=0pt] (wahrsis) at (-2.1,0)
{\includegraphics[height=3cm]{w1udNoRect}};
\node[inner sep=0pt] (wahrsis2) at (1.05,0)
{\includegraphics[height=3cm]{w3udNoRect}};
\draw[blue] (-3.6,-0.15) -- (2.6,-0.15);
\draw[blue] (-3.6,-0.40) -- (2.6,-0.40);
\end{tikzpicture}}
\hspace{2mm}
\subfloat[After rectification]{\begin{tikzpicture}
\node[inner sep=0pt] (wahrsis) at (-2.1,0)
{\includegraphics[height=3cm]{w1ud}};
\node[inner sep=0pt] (wahrsis2) at (1.05,0)
{\includegraphics[height=3cm]{w3ud}};
\draw[blue] (-3.6,-0.09) -- (2.6,-0.09);
\draw[blue] (-3.6,0.45) -- (2.6,0.45);
\end{tikzpicture}}
\caption{Image pair before and after rectification.}\label{fig:rectification-result}
\end{figure}

\subsubsection{Disparity Map}
The next step is to compute the disparity map between the sequence of pairs of undistorted, rectified images. We use the three-dimensional scene flow algorithm proposed by Cech et al.\ \cite{cech}, which jointly estimates a disparity map and optical flows between stereo image frames.

The strength of the scene flow approach is the inclusion of past frames into the computation of the disparity map. While clouds do not have many distinct features to track, they evolve slowly. Successive frames taken at appropriate intervals indeed do not exhibit large differences, and past frames can thus complement the information provided in the current frame.

Figure~\ref{fig:disparity} shows the disparity map computed from the pair of images shown in Fig.~\ref{fig:rectification-result}(b). Each pixel value of the disparity map indicates the shift to add to the horizontal image coordinate to obtain the position of the pixel capturing the same physical point in the other image. Note that the algorithm does not define values over the whole image, as some parts do not exhibit sufficient texture or do not look similar in the two images due to the different viewpoints.

\begin{figure}[htb]
\centering
\includegraphics[clip,trim=1cm 0cm 0cm 0cm,height=5cm]{disparity}
\caption[Illustration of the computed disparity map.]{Disparity map for the image pair in Fig.~\ref{fig:rectification-result}(b).}
\label{fig:disparity}
\end{figure}

\subsubsection{3D Point Cloud}
The last step consists of mapping the disparity map to real world 3D coordinates. For every defined value of the disparity map, we compute the position of that point on both rectified images in the image plane, as shown by the red and blue dots in Fig.~\ref{fig:3dpoints}. We then consider the two rays going through those points and the device position. Those two rays intersect at the real world location of the captured point, shown in green in Fig.~\ref{fig:3dpoints}.

\begin{figure}[htb]
\centering
\includegraphics[clip,trim=9cm 7.7cm 8cm 9cm,height=5cm]{3dpoints}
\caption{Illustration of the computation of a point in 3D.}
\label{fig:3dpoints}
\end{figure}

Figure~\ref{fig:result-real-image} shows the resulting point cloud for an image pair from the  sequence. We distinguish two different clusters: the first is at an altitude of about $700$ meters and corresponds to the cumulus cloud at the bottom right of the input image, while the second represents the higher cloud layer appearing at around $3000$ meters.

\begin{figure}[htb]
\centering
\includegraphics[height=5.5cm]{result-3D}
\caption{3D point cloud computed for a pair of images from the sequence.}
\label{fig:result-real-image}
\end{figure}

\subsection{Validation}
Since it is very difficult to measure the actual 3D location and shape of clouds, we use computer-generated images with a user-defined cloud bottom altitude for validating our approach. We use \emph{Blender},\footnote{~\url{http://www.blender.org/}} an open-source 3D computer graphics program, for creating images using a procedural cloud shader and a model of the fish-eye lens of WAHRSIS. While being simpler than the reality, these images do have the advantage that the positions of the imagers and clouds can be user-defined.

For this experiment, we created a sequence of $21$ frames with a cloud moving over the two cameras. The average cloud bottom altitude is $500$ meters, and the distance between the cameras is $400$ meters. Fig.~\ref{fig:blender-generated} shows an example of such an image pair.

\begin{figure}[htb]
\centering
\includegraphics[height=4cm]{blender1}
\includegraphics[height=4cm]{blender2}
\caption{Image pair from the computer-generated sequence.}
\label{fig:blender-generated}
\end{figure}

\begin{figure}[htb]
\centering
\subfloat[3D view]{\includegraphics[height=3.6cm]{3D-generate}}
\subfloat[2D projection]{\includegraphics[height=3.6cm]{projection}}
\subfloat[Ground truth for (b)]{\includegraphics[height=3.6cm]{ground_truth}}
\caption[Illustration of 3D point cloud for an image pair computer from the computer-generated sequence.]{3D point cloud for an image pair computer from the computer-generated sequence.  The bounding boxes in which Blender generates the cloud are shown in green. The two black dots indicate the position of the imagers.}\label{fig:results-blender}
\end{figure}

Figure~\ref{fig:results-blender} shows the resulting 3D point cloud for an image pair from the computer-generated sequence. It matches with the ground truth created by Blender. Averaging over the entire sequence, 82.4\% of the reconstructed 3D points lie inside the bounding box in which the cloud is generated.

In this section, we have discussed how 3D scene flow techniques can be used to estimate cloud base height in a multiple-camera setting. We have introduced a workflow to a common scene flow algorithm in this context, which we validated with computer generated images.

\section{Conclusion}
\label{sec:chap8-conclude}
In this chapter, we have proposed a point localization algorithm in a multiple-camera setting, under the assumption of error-free feature matching and noisy camera poses. Our modified SHARP algorithm has the best performance as compared to the other benchmarking algorithms. In the later part of this chapter, we demonstrate a practical example of point localization task---localizing cloud mass in the 3D space using a pair of ground-based sky cameras. Our theoretical analysis on point localization in multi-camera setup serves us an attempt to understand the accuracy of the cloud base height estimation. In practice, point localization in the 3D space is a challenging task, as it depends on a number of important factors: error-free feature matching and tracking, accurate estimation of camera poses and dense feature correspondence between stereo images. The task gets more challenging in cloud base height estimation, as clouds are generally featureless and feature matching between two images gets more challenging.

### 2018-07-16 misc/thesis-hardbound/Chapters/Chapter9.tex
Update 16/7/2018

\chapter{Conclusion \& Future Work}
\label{chap:conclusion}

\lhead{Chapter 9. \emph{Conclusion \& Future Work}}

\section{Conclusion}
In this thesis, we have discussed the wide range of our contributions in remote sensing for varied applications. We mainly focused our attention on the analysis of clouds in satellite communication links. As Singapore is a geographically small land region, conventional techniques using satellite images are not conducive for study. The images obtained from satellites suffer from poor spatial and temporal resolutions. Therefore, we have presented a new paradigm in understanding the earth's atmosphere---using ground-based sky cameras to better analyze clouds for different applications. These cameras, popularly known as Whole Sky Imagers (WSIs) offer a compelling alternative. In this thesis, we have presented several models of our custom-built sky cameras. Our designed sky camera models have lower cost, better image resolution, and higher flexibility as compared to the commercially available sky cameras.

The sky cameras capture the sky/cloud scene at regular intervals of time, and archives the captured images for further analysis. One of the fundamental problems in cloud imaging is the \emph{successful} detection of cloud pixels in these images. This is a non-trivial task, as clouds are non-rigid in shape, and do not conform to any particular shape or size. The \emph{color} of clouds is generally used as the most discriminatory feature. In this thesis, we have provided a systematic analysis of the different color channels that are frequently used for cloud recognition. We have identified the \emph{best} color channels that can be used for subsequent analysis. Furthermore, the conventional sky/cloud image segmentation algorithms are generally binary in nature, i.e.\ each pixel is assigned either \emph{sky} or \emph{cloud} label. In this thesis, we have proposed a probabilistic cloud segmentation approach, wherein each pixel is assigned a probability to be categorized in cloud category.

For the purpose of regular weather monitoring, the various meteorological institutes around the world regularly report cloud types in its meteorological reports. Such classifications are generally done manually, which is of course, cumbersome and time-consuming. In this thesis, we attempt to provide a complete framework for a multi-class classification of cloud types. Our framework has the best classification performance as compared to the other benchmarking algorithms. We systematically integrate the \emph{color} and \emph{texture} cues of cloud for better performance.

In addition to ground-based sky cameras, different meteorological sensors continually record the various weather parameters of the earth's atmosphere. However, these devices are point-measurement devices, i.e.\ these devices only record measurements for a particular point location of the earth's atmosphere. Sky cameras equipped with wide-angle lenses, on the other hand, provide remote sensing analysts better insights on the evolution of clouds over a period of time. In this thesis, we have analyzed the information from sky cameras and other sensors to provide deeper insights in solar energy generation. We have also used sky cameras to predict future location of clouds and to detect the onset of precipitation. These applications greatly help in the field of solar and renewable energy forecasting.

Finally, we discussed our work on estimating the base height of a cloud mass, using a pair of (or multiple) sky cameras. We used stereoscopic scene flow techniques to estimate cloud-base height, and verified its accuracy using computer-generated images. We have also provided deeper insights in the localization performance of an \emph{intruder}~\footnote{This is in reference to the famous art-gallery problem as described in Chapter~\ref{chap:localize}.} in a multi-camera setup with noisy camera poses.

\section{Future Work}
This thesis explored varied aspects of cloud imaging using ground-based sky cameras. While it solved most of the fundamental problems, it also helped us in generating future research proposals. In this section, we will briefly mention some of the intended future works.

In this thesis, we described the design of three models of ground-based sky cameras. These imagers consists of a Digital Single-Lens Reflex (DSLR) camera equipped with a fish-eye lens. We are now interested to design a miniature model using a regular smart-phone. With the rapid development in the imaging system of hand-phones, it seems a plausible alternative to perform our task of cloud imaging using smart-phones. The smart-phone application will be involved in capturing images at regular intervals of time, and will be sent to the server for archival and further processing.

The conventional approach consists in segmenting the cloud image into binary labels---sky and cloud. In this thesis, we have provided a probabilistic segmentation approach wherein we employ a \emph{soft} thresholding approach. In the future work, we aim to generate the ground-truth database with probabilistic labels. We will perform the manual labeling via crowd-sourcing experiments, wherein several cloud experts will manually label the pixels. This will help us to assign a probability ground-truth map for the sky/cloud images.

In this thesis, we deal primarily with daytime images captured by our sky camera. However, nighttime cloud imaging is also essential in certain applications, such as continuous weather analysis and satellite communication. Nighttime sky/cloud images are darker and noisier, and thus harder to analyze. Currently, we use a superpixel-based segmentation technique~\footnote{The source code of our nighttime cloud segmentation is available online at \url{https://github.com/Soumyabrata/nighttime-imaging}.} to detect cloud in nighttime images. In the future, we plan to extend our cloud categorization and cloud localization for nighttime images as well.

In addition to these visible-light imaging techniques, we are also interested to explore further in Near-Infra-Red (NIR) techniques. Such imaging techniques are very important in our current application and has immense potential in capturing sharper and clearer images of sky/cloud hemisphere. Our current work on cloud detection and its classification can be extended to these near-infrared cloud images for better results. Fredembach and S{\"u}sstrunk demonstrated in their recent work~\cite{near_infrared} that the haze disappears in near-infrared capture of an outdoor scene as compared to an image captured by a conventional RGB image. This is because of a physical phenomenon called Rayleigh scattering. Small atmospheric particles present in the air scatter incident light with varying degree. Because of Rayleigh scattering, the component of light having the least wavelength gets scattered the most; and thus provides a bluish color to the sky. However, near-infrared is less scattered as compared to its visible counterparts and renders the sky darker. Clouds however do not change its behavior of light scattering because of its bigger particle size which is referred as Mie scattering.

\begin{figure}[htb]
\begin{center}
\includegraphics[width=0.8\textwidth]{haze_disappear}
\caption[Illustration to show the benefits of near-IR capture in cloud imaging.]{On the left, a conventional RGB image. On the right, a near-IR capture of the same scene. The haze has disappeared, revealing a sharper, cleaner, picture~\cite{near_infrared}.\label{fig:haze_disappear}}
\end{center}
\end{figure}

On top of ground-based imaging, satellite images also provide us interesting perspectives of the upper layer of cloud. In this thesis, our focus was not intended on satellite images as its spatial and temporal resolution were not conducive for our application of cloud attenuation and solar energy forecasting. These high resolution requirements are very strong in satellite imaging. No mission is generally designed for monitoring of small areas, during airborne sensing. However, satellite such as MODIS can offer us interesting insights on the cloud top phenomenon, at the expense of lower resolutions. MODIS stands for Moderate-Resolution Imaging Spectroradiometer. It is a 36 spectral band imaging instrument embedded in two satellites: Terra and Aqua. Its medium resolution ($250$ to $1000$m) allows a large swath, and thus a high revisit time. For the region of Singapore, the two satellites acquire images twice a day. It is a good compromise for our applications, and a good choice for this comparison. The National Aeronautics and Space Administration (NASA) organizes the MODIS data in levels, collections and products. The product is most interesting, as it represents the information stored in a dataset. We plan to use four products, that are frequently used by remote sensing analysts:

\begin{description} 
\item[MOD02] \emph{Level-1B Calibrated Geolocation Data Set} Stores the calibrated radiance for the $36$ bands of data, in $W/(m^{2}\cdot um \cdot sr)$, the reflectance and some quality indicators.
\item[MOD05] \emph{Total Precipitable Water} Contains daytime column water-vapor amount using the near-infrared and infrared channel. It is not used in the image part, but provides information on radio-wave attenuation for another part of this project.
\item[MOD06] \emph{Cloud Product} Only available for the 1km resolution. It uses the visible, NIR, and Thermal Infra-Red (IR) bands. Contains cloud temperature, cloud pressure, particle phase and radius for the top of the cloud.
\item[MOD35] \emph{Cloud Mask} stores two bits that indicate the status of a pixel: \texttt{Confident} \texttt{Clear}, \texttt{Probably Clear}, \texttt{Uncertain}, \texttt{Cloudy}. It uses $19$ bands to decide, and the decision tree for each pixel is included for the $250$m and $1$km resolution.
\end{description}

In our future work, we intend to compare such cloud mask of MODIS data with ground-based sky cameras. It may not be possible to match individual clouds as sky camera is an upward-looking device, whereas MODIS is a downward-looking device. However, it will provide us additional information about cloud top height and other related phenomenon.

Finally, we also intend to explore solar energy harvesting, with the aid of ground-based sky cameras. The prospect of solar energy generation is good in a tropical country like Singapore. But this generation is intermittent and variable because of the presence of clouds that blocks direct solar radiation. The effect of clouds on solar energy generation have been described in detail in Chapter~\ref{chap:solar} of this thesis. In our future work, we plan to develop a Photovoltaic (PV) energy forecast system based on automatic cloud coverage and cloud tracking.

\textbf{Closing note:} This thesis ends here---we believe that our work on imaging the earth's atmosphere can assist the research community in a myriad range of applications.

### 2018-07-16 misc/thesis-hardbound/Misc/abbreviations.tex
Update 16/7/2018

\chapter*{\centering Abbreviations}
\begin{longtable}[l]{p{100pt}p{400pt}}
\textbf{AEB} & Automatic Exposure Bracketing  \\
\textbf{BOW} & Bag-Of-Words \\
\textbf{CDF} & Cumulative Distribution Plot \\
\textbf{CLAHE} & Contrast-Limited Adaptive Histogram Equalization \\
\textbf{colorHIST} & Color Histogram \\
\textbf{CRE} & Cloud Radiative Effect \\
\textbf{DBSCAN} & Density-Based Spatial Clustering of Applications with Noise \\
\textbf{DR} & Dynamic Range\\
\textbf{dSIFT} & Dense Scale Invariant Feature Transform \\
\textbf{EV} & Exposure Value \\
\textbf{FF} & Fractal Feature \\
\textbf{FFT} & Fast Fourier Transform \\
\textbf{FM} & Fourier Magnitude \\
\textbf{FN} & False Negative \\
\textbf{FP} & False Positive \\
\textbf{GEOSS} & Global
Earth Observation System of Systems \\
\textbf{GHI} & Global Horizontal Irradiance \\
\textbf{GLCM} & Gray-Level Co-occurrence Matrix \\
\textbf{GLDS} & Gray Level Difference Statistics \\
\textbf{GPS} & Global Positioning System \\
\textbf{HDR} & High Dynamic Range \\
\textbf{HDRI} & High Dynamic Range Imaging\\
\textbf{HF} & Heinle Feature \\
\textbf{HYTA} & Hybrid Thresholding Algorithm \\
\textbf{ICESat} & Ice, Cloud, and land Elevation Satellite \\
\textbf{ICLTP} & Illumination-invariant Completed Local Ternary Pattern \\
\textbf{IR} & Infra-Red \\
\textbf{KL} & Kullback-Leibler \\
\textbf{LBP} & Local Binary Patterns \\
\textbf{LCAV} & Audiovisual Communications Laboratory \\
\textbf{LDR} & Low Dynamic Range \\
\textbf{LED} & Light-Emitting Diode \\
\textbf{LiDAR} & Light Detection And Ranging \\
\textbf{MODIS} & Moderate-Resolution Imaging Spectroradiometer \\
\textbf{MSS} & Meteorological Service Singapore \\
\textbf{NASA} & National Aeronautics and Space Administration \\
\textbf{NIR} & Near-Infra-Red \\
\textbf{OC} & Operating Characteristics \\
\textbf{PBI} & Pearson's Bimodality Index \\
\textbf{PCA} & Principal Component Analysis \\
\textbf{PLS} & Partial Least Squares \\
\textbf{PV} & Photo Voltaic \\
\textbf{RMSE} & Root Mean Square Error \\
\textbf{ROC} & Receiver Operating Characteristic \\
\textbf{SDK} & Software Development Kit \\
\textbf{SGLDM} & Spatial Gray Level Dependence Matrices \\
\textbf{SHARP} & Sequential Half space Aggregation for Reconstructing a Point \\
\textbf{SIFT} & Scale Invariant Feature Transform \\
\textbf{SLIC} & Simple Linear Iterative Clustering \\
\textbf{SVM} & Support Vector Machine \\
\textbf{SWIMCAT} & Singapore Whole sky IMaging CATegories database \\
\textbf{SWIMSEG} & Singapore Whole sky IMaging SEGmentation database \\
\textbf{TN} & True Negative \\
\textbf{TP} & True Positive \\
\textbf{USB} & Universal Serial Bus \\
\textbf{WAHRSIS} & Wide Angle High Resolution Sky Imaging System \\
\textbf{WMO} & World Meteorological Organization \\
\textbf{WSI} & Whole Sky Imager \\
\textbf{YES} & Yankee Environmental Systems\\
\end{longtable}

### 2018-07-16 misc/thesis-hardbound/Misc/abstract.tex
Update 16/7/2018

\chapter*{\centering Abstract}

With the ubiquity of powerful digital cameras, there has been a paradigm shift in understanding and analyzing any scene. The central theme of this thesis is to use conventional cameras to capture images of a scene and derive essential information about its content. In particular, we focus our attention on images captured by ground-based sky cameras. Ground-based sky cameras, popularly known as Whole Sky Imagers (WSIs), are now extensively used by remote sensing analysts. They are useful in variety of applications: signal attenuation analysis, local weather prediction, or solar and renewable energy forecasting. They complement conventional weather satellite images with higher temporal and spatial resolutions. The WSIs capture images of the earth's atmosphere in regular intervals of time. In this thesis, we analyze this huge amount of captured image data, and propose several algorithms and methodologies for various applications.

We designed and built three different versions of ground-based sky cameras, which are efficient, low-cost, and highly flexible. Our custom-built WSIs are equipped with a high resolution fish-eye lens that captures the images of the sky scene at user defined intervals of time. Our imagers are modular with easily configurable hardware and software, offer a high image resolution ($5184\times3456$ pixels), and cost less than US\$3K to build.\footnote{In comparison, the popular commercial TSI-880 model sold by Yankee Environmental Systems costs around US\$30-35K, and has a far inferior image resolution of only $352\times288$ pixels.} Furthermore, they give us the flexibility to explore the use of High Dynamic Range Imaging (HDRI) techniques to capture the wide range of luminosity of the sky scene.

With the vast image data collected from these ground-based sky cameras, extracting valuable information viz.\ cloud coverage can be challenging. Cloud segmentation of the images into cloud vs.\ sky regions is one of the fundamental problems, as clouds are non-rigid, and have a wide variety of shapes, sizes, colors or textures. In this thesis, we present a supervised segmentation framework for ground-based sky/cloud images based on a systematic analysis of different color spaces and components. Unlike other state-of-the-art cloud segmentation methods, our proposed approach is entirely learning-based and does not require any manually defined parameters. As part of this effort, we released a large segmentation database of annotated sky/cloud images to the research community. In addition to cloud segmentation, we also propose a framework for automatic cloud type recognition that classifies sky/cloud image patches efficiently into various cloud types. Our proposed algorithm systematically integrates both \emph{color} and \emph{texture} cues of cloud, and has a good multi-class classification accuracy. We also released a large-scale cloud categories database for further benchmarking purposes.

In most cases of atmospheric study, collocated weather stations are present alongside these sky cameras. Unlike solar pyranometers and other regular meteorological sensors, ground-based sky images have additional information about the continuous evolution of cloud over time. We use our cloud/sky images to propose a solar radiation estimation model, that can accurately capture the short-term fluctuations of solar irradiance. We also use these sequence of images to estimate cloud motion fields, and thereby predict future locations of cloud with a lead time of a few minutes. These solar estimation and cloud forecasting techniques can be applied in the field of solar energy generation and forecasting.

Finally, we use our ground-based sky cameras in a stereo-setup for accurate reconstruction of cloud-base height. We propose a consistent and optimal point localization algorithm for noisy camera poses and error-free matching between image frames. A rigorous analysis of such localization problems provides better insights in cloud-base height reconstruction.

Ground-based whole sky cameras have opened up new opportunities for monitoring the earth's atmosphere for a range of applications. In this thesis, we have identified a few research gaps and addressed some important problems in the field of cloud imaging. We believe that the techniques and algorithms developed in this thesis will assist the remote sensing community with a better understanding of clouds and associated phenomena.

### 2018-07-16 misc/thesis-hardbound/Misc/ack.tex
Update 16/7/2018

\chapter*{\centering Acknowledgment}

I would like to offer sincere gratitude to my two wonderful supervisors---Prof.\ Lee Yee Hui \& Dr.\ Stefan Winkler. Thanks Prof.\ Lee for admitting me into your research group, and for introducing me into the wonderful world of research and academics. You are a passionate professor, a dedicated researcher and a wonderful friend---sincere thanks for believing in me always, especially during the formative years of my PhD and course work. A huge thanks to Stefan for all your support and guidance throughout my PhD---this thesis is in its current form because of the numerous discussions and regular meetings with you. Thank you for introducing me into the world of \emph{computer vision}, for meticulous reading and editing the papers, and for guiding me throughout this journey.

I have been extremely fortunate to be a visiting Doctoral Assistant at Audiovisual Communication Laboratory (LCAV), at \'{E}cole Polytechnique F\'{e}d\'{e}rale de Lausanne, Switzerland, under the supervision of Prof.\ Martin Vetterli and Dr.\ Adam Scholefield, during my PhD. Thank you Martin for this wonderful opportunity---it was my honor to be a part of LCAV and interact with the brilliant minds. I sincerely appreciate your guidance throughout the period, and always inspiring me to be a better researcher. A special shout-out to Adam for your time and continuous support, for all the white-board discussions at \emph{BC 366}, and for providing me all the confidence.

Friends have been an integral part of this PhD journey, and I am truly indebted to them for their love and support. I would like to thank---Prof.\ J.\ T.\ Ong, Dr.\ Meng Yusong, Dr.\ Lakshmi Sutha, Ma Ting, Mao Xiao Hong, Yeo Jun Xiang, Ian Bajaj, Mi Siya, Shilpa Manandhar (thanks for the warm friendship and companionship) and Yuan Feng (thanks for the wonderful times). A warm thanks to Ong Kee Wang, Darko Jokic \& Charles Wong for assisting to build the mechanical models of our sky cameras. And of course, Florian Savoy---a true engineer and a wonderful friend; thanks for all the co-authorships, \emph{nuits blanches} before the conference deadlines and for all our technical discussions. \emph{Merci Florian!}

I would also like to thank all my friends I met during my internship at Lausanne. Thanks to Alireza Ghasemi, Mitra Fatemi, Runwei Zhang for being a wonderful office-mate, Niranjan Thanikachalam for all the guidance and friendship, Gilles Baechler for the friendship (and running sessions by the lake), Marta Martinez, and of course, Julien Reichel for being an amazing host. Special thanks to Robin Scheibler for introducing me to \emph{python}, for the numerous discussions over coffee, and for being a wonderful friend. A huge thanks to Radmila Popovic for all the love and support. And finally, special thanks to my dearest friend Miranda Krekovi{\'c} for all the good times spent at Lausanne and beyond---I sincerely appreciate and respect it. \emph{Puno hvala Miranda!}

Thank you Subhrajit, Sumanta, Zishan, Binit, Sana, Ankush, Deval, Sushant and my wonderful flatmates---Jithin, Dhirendra, Pravesh \& Raunaq (who were no less than my brothers) for all the love and support throughout this journey. I'm sure I have missed mentioning the names of many who were beside me at all the happy and sad times. Singapore is beautiful because of your presence!

I would also like to thank my thesis advisory committee members Prof.\ Wang Gang and Prof.\ Cai Jianfei for advising this thesis work. Also, thanks to my PhD oral examination panel members, Prof.\ Bi Guoan, Prof.\ Mohammed Yakoob Siyal and Prof.\ Anamitra Makur for taking their respective time in reading this thesis, and providing valuable feedback on the same. Sincere thanks to the anonymous internal and external PhD thesis examiners, who were amongst the first to closely examine the thesis and provide useful feedback.

I would also like to acknowledge the financial support from Nanyang Technological University Singapore and Ministry of Defence (MINDEF) Singapore; and administrative support from Graduate Programme Office, School of Electrical and Electronic Engineering. Thanks Christina Wong for your continuous help and support, and your infectious laughter definitely made the experience more enjoyable. Special thanks to Tay TingFang for assisting me throughout the process of my thesis examination (and for acceding to all my technical and logistical requests for my thesis examination).

Thanks to Dr.\ John Hammersley, Shelly Miller \& Dr.\ Lim Lian Tze from Overleaf for sharing the vision of open science with the community. This entire thesis was written in \emph{Overleaf}; and it was my pleasure to spread the \emph{Overleaf} joy amongst the NTU community, as an advisor.

Finally, I would like to offer my sincere thanks and gratitude to my parents Ashoka Dev \& Bidhu Bhusan Dev, my brother Bedabrata Dev and my sister-in-law Rupsa Banerjee. Thank you for your unconditional love and support and for the innumerable sacrifices. Special thanks to my mother who inspired me to pursue a doctoral degree at the very outset!

### 2018-07-16 misc/thesis-hardbound/Misc/notations.tex
Update 16/7/2018

\chapter*{\centering Notations}

\lhead{Notations}

\begin{longtable}[l]{p{80pt}p{320pt}}

% Greek symbols
$\alpha$ & Stem angle of sun-blocker based WAHRSIS measured from the east direction. \\
$\tilde{\alpha}$ & Membership constant used in assigning seeds of HDR radiance map. \\
$\beta$ & Angle of incidence of light in a fish-eye lens system. \\
$\gamma(.)$ & Relevance criterion of an attribute set in rough-set terminology.\\
$\bar{\gamma}(.)$ & Average relevance value of an attribute set across all images of the dataset.\\
$(\delta_1^{\hat{i}},\delta_2^{\hat{i}},\ldots,\delta_{\hat{n}}^{\hat{i}})$ & Offset angles (w.r.t. view angle $\Theta^{\hat{i}}$) contained by $\hat{n}$-pixels to the camera center for the $\hat{i}$-th camera.\\
$\Delta t_m$ & Time shift.\\
$\Delta x$, $\Delta y$ & Spatial shift in x- and y- coordinates in an image plane.\\
$\Delta \hat{x_c}$ and $\Delta \hat{y_c}$ & Translation of camera along X- and Y- axes of a multi-camera setup.\\
$\sigma_{\Delta \hat{x_c}}^2$ and $\sigma_{\Delta \hat{y_c}}^2$ & Variance of translation of camera along X- and Y- axes of a multi-camera setup.\\
$\epsilon_1, \epsilon_2,\ldots$ & Coefficients in a higher-order polynomial fitting function. \\
$\eta$ & Learning rate for gradient ascent algorithm. \\
$\Gamma$ & Day angle (measured in radians).\\
$\lambda$ & Eigen value. \\
$\Lambda$ & Wavelength of light. \\
$\mu$ & Weighting parameter in the graph-cut framework. \\
$\boldsymbol{\mu}$ & Mean vector of the multivariate gaussian distribution of noisy camera poses in multi-camera setup. \\
$\omega_1$ & Angle of rotation around the $z$ axis to align two imagers.\\
$\omega_2$ & Angle of rotation around the $y$ axis to align two imagers.\\
$\Phi(\mathbf{p}')$ & Re-projection function. \\
$\psi$ & Solar zenith angle (measured in degrees). \\
$\Psi$ & Multivariate gaussian distribution involving the camera poses to model the noisy camera poses in the multi-camera setup. \\
$\sigma_{c_{j}}$ & Standard deviation of $j$-th color channel. \\
$\hat{\sigma}$ & Scale of the filter in the filter set. \\
$\sigma_\Theta^2$ & Variance of view angle in the multi-camera setup.\\
$\sigma_{\Delta \hat{x_c}}$ & Variance of camera position in the X-direction in the multi-camera setup.\\
$\sigma_{\Delta \hat{y_c}}$ & Variance of camera position in the Y-direction in the multi-camera setup.\\
$\mathbf{\Sigma}$ & Covariance matrix of the multivariate gaussian distribution of noisy camera poses in multi-camera setup. \\
$\tau$ & Fuzziness index in clustering process. \\
$\hat{\tau}$ & Number of cycles inside the gaussian envelope of the filter set. \\
$\theta$ & Angle made by the \emph{intruder} $\mathbf{p}$ with the global x-axis in the multi-camera setup.\\
$(\theta_1^{\hat{i}},\theta_2^{\hat{i}},\ldots,\theta_{\hat{n}}^{\hat{i}})$ & Angles contained by $\hat{n}$-pixels to the camera center for the $\hat{i}$-th camera.\\ 
$\tilde{\theta}$ & Arm angle of sun-blocker based WAHRSIS measured from the horizon.\\
$\Theta^{\hat{i}}$ & View angle of $\hat{i}$-th camera w.r.t. global X-axis.\\ 
$\bar{\Theta}$ & Mean value of view angle of the camera in the multi-camera setup.\\
$\varepsilon$ & Elevation angle of the ray from sun to WAHRSIS camera.\\
$\xi$ & Azimuth angle of the ray from sun to WAHRSIS camera.\\

% Smaller case letters
$a$ & Element from set $\mathcal{P}$.\\
$\hat{a}(\cdot)$ & Geometrical lower bound in multivariate distribution for the multi-camera setup.\\
$a_z$ & Represents the $z$-th attribute from the set $\mathcal{A}$.\\
$a_1, a_2,\ldots$ & Individual weather station data points. \\
$\hat{b}(\cdot)$ & Geometrical upper bound in multivariate distribution for the multi-camera setup.\\
$b_{1}$ & Measure of square of skewness.\\
$b_{2}$ & Measure of kurtosis. \\
$\mathbf{c}$ & Weight vectors of $\mathbf{Y}$. \\
$c_1, c_2,\ldots,c_{16}$ & Set of $16$ color channels for analysis of ground-based images.\\
$\textbf{c}_{1}, \textbf{c}_{2}, \ldots, \textbf{c}_{16}$ & Vectorised set of the $16$ color channels $c_1, c_2,\ldots,c_{16}$ with dimensions $mn \times 1$.\\
$\bar{c_{j}}$ & Mean value of $j$-th color channel. \\
$d_n$ & Day number of the year. \\
$\mathbf{e}$ & Eigen vector. \\
$e_t$ & Exposure time of the camera measured in seconds. \\
$f(\cdot)$ & Mapping function. \\
$\bar{f}$ & Focal length of the lens in the imaging system.\\
$f_s$ & Aperture number of the lens in the imaging system.\\
$h_{\hat{j}}^{\mbox{class}}$ & Histogram of textons for a cloud category of training images. \\
$h_{\hat{j}}^{\mbox{test}}$ & Histogram of textons for a cloud category of testing images. \\
$i$ & Index of the set of images. \\
$\hat{i}$ & Index of the set of cameras in a multi-camera setup. \\
$j$ & Index of the set of color channels. \\
$\hat{j}$ & Index of the set of cloud categories. \\
$k$ & Number of color channels in a subset of color channels. \\
$l$ & Index of the vectorised form of an image.\\
$l_1, l_2,\ldots$ & Individual luminance data points for corresponding weather station points. \\
$m$ & Row size of a sample image. \\
$n$ & Column size of a sample image. \\
$\tilde{n}$ & Number of cameras in the multi-camera setup.\\
$\hat{n}$ & Total number of pixels in the finite-dimensional camera.\\
$n_c$ & Number of clusters used in fuzzy clustering process. \\
$n_f$ & Number of filters in the filter bank.\\
$n_t$ & Number of textons generated from k-means clustering.\\
$o$ & Dimension of cluster center vectors $\mathbf{v}_{1}$ and $\mathbf{v}_{2}$. \\
$p$ & Joint multivariate normal cumulative probability values for all the $\hat{i}$ cameras. \\
$p^1, p^2,\ldots$ & Individual multivariate normal cumulative probability values for all the $\hat{i}$ cameras. \\
$\mathbf{p}$ & Reconstruction point in multi-camera setup (also referred as \emph{intruder} in the art-gallery problem). \\
$\mathbf{p}^{*}$ & Optimal reconstruction point. \\
$\bar{p}$ & Total number of cloud categories. \\
$\tilde{p}$ & Sample pixel in the image $\mathbf{Z}_i$. \\
$\tilde{q}$ & Neighboring pixel of $\tilde{p}$ in the image $\mathbf{Z}_i$. \\
$\mathbf{q}$ & Center of the \emph{active pixel} in the multi-camera setup. \\
$\bar{q}$ & Total number of images in each cloud category. \\
$q_k$ & Represents the $k$-th pixel value of the image. \\
$r$ & Radius on the image plane in a fish-eye lens system. \\
$\hat{r}$ & 2D Euclidean distance between the camera location and any sample point ($\hat{x}$,$\hat{y}$) in the XY-plane (=$\lVert (\hat{x},\hat{y}) , (\hat{x}_c^{\hat{i}},\hat{y}_c^{\hat{i}}) \rVert$).\\
$\bar{s}$ & Index of the sampled pixel in an $RGB$ image. \\
$s$,$t$ & Sample indexes of observations from the universe set $\mathcal{U}$. \\
$\mathbf{t}$ & Random initialization point in ${\rm I\!R}^{2}$ used in the gradient ascent algorithm for computation of $F(\cdot)$.\\
$t_m$ & Current observation time. \\
$t_s$ & Total number of sampled points in the hemispheric sampling process. \\
$u_x, u_y$ & Optical flow vectors in x- and y- direction. \\
$\mathbf{w}$ & Weight vectors of $\mathbf{X}$. \\
$\mathbf{v}_{n_c}$ & The $n_c$ cluster centers.\\
$x$, $y$ & Sample x- and y- image coordinate. \\
$\hat{x}^{\hat{i}}_c$,$\hat{y}^{\hat{i}}_c$	& Location of $\hat{i}$-th camera in the XY-plane of a multi-camera setup.\\
$x_m$, $x_n$ & Two sample observations from universe $\mathcal{U}$ in rough set terminology. \\
$\mathbf{x}^{f}$ & Vectorised form of feature matrix $\mathbf{X}^{f}$. \\
$z$ & Index of the set of attributes in attribute set $\mathcal{A}$. \\
$\bar{\mathbf{z}}$ & Vectorized form of the gray-scale image $\bar{\mathbf{Z}}$. \\
$\bar{\mathbf{z}}_m$ & Mean value of the vectorized image $\bar{\mathbf{z}}$.\\
$\bar{\mathbf{z}}_d$ & Median value of the vectorized image $\bar{\mathbf{z}}$.\\
$\bar{\mathbf{z}}_v$ & Standard deviation value of the vectorized image $\bar{\mathbf{z}}$.\\
$\bar{\mathbf{z}}_w$ & Skewness value of the vectorized image $\bar{\mathbf{z}}$.\\
$\bar{\mathbf{z}}_k$ & Kurtosis value of the vectorized image $\bar{\mathbf{z}}$.\\

% Upper case letters
$\mathcal{A}$ & Set of attributes in rough-set terminology. \\
$A_{\tilde{p}}$ & Data cost for an individual pixel $\tilde{p}$ in a graph-cut framework. \\
$\mathbf{B}$ & Regression coefficient matrix. \\
$B_{\tilde{p},\tilde{q}}$ & Interaction cost between two neighboring pixels $\tilde{p}$ and $\tilde{q}$ in a small neighborhood. \\
$\mathcal{C}$ & Set of condition attributes in rough-set terminology. \\
$\mathbf{C}^{T}$ & A matrix of regression coefficients. \\
$\mathcal{D}$ & Set of decision attributes in rough-set terminology. \\
$E$ & Segmentation score for graph-cut algorithm. \\
$E_0$ & Intensity of the emitted light. \\
$\mathbf{E}_{i}$ & Residual matrix corresponding to feature matrix $\mathbf{X}^{f}_{i}$. \\
$E_k$ & Eccentricity correction factor for earth. \\
$E_s$ & Intensity of the scattered light. \\
$F(\cdot)$ & multivariate normal cumulative probability for a single camera in the multi-camera setup.\\
$\mathbf{F}_{i}$ & Residual matrix corresponding to binary image $\mathbf{Y}_{i}$. \\
$\mathcal{F}_1, \mathcal{F}_2,\ldots,\mathcal{F}_{n_f}$ & Set of filters in the filter bank.\\
$G(\cdot)$ & Objective function to optimize the multi-variate distribution in the multi-camera setup.\\
$G_c$ & Global Horizontal Irradiance of the sun at the earth's surface. \\
$\mathbf{H}_{i}$ & Residual matrix corresponding to latent matrix $\mathbf{U}_{i}$. \\
$\mathcal{H}_i$ & HDR radiance map generated from the set of low-, mid- and high-LDR images. \\
$HSV$ & Hue, Saturation and Value color channel model comprising hue ($H$), saturation ($S$) and value ($V$) color channels. \\
$I$ & Clearness Luminance Index. \\
$I_c$ & Critical Clearness Luminance Index. \\
$I_{s}$ & ISO sensitivity of the camera. \\
$I_{sc}$ & Solar irradiance constant ($1366.1$ Watt/$\mbox{m}^2$). \\
$\mathcal{I}$ & Intruder in a 2D search space in a multi-camera setup.\\ 
$IHS$ & Intensity, Hue, and Saturation color model. \\
$J$ & Objective function used during fuzzy-clustering process. \\
$K_c$ & Calibration constant to map scene luminance and pixel brightness.\\
$L_w$ & Calculated luminance of a pixel in a fish-eye lens during vignetting modeling. \\
$\mathcal{L}$ & Decision table in rough-set terminology. \\
$\mathcal{L}_c$ & Clear-sky luminance. \\
$\mathcal{L}_m$ & Measured luminance from sky/cloud image. \\
$\mathcal{L}_r$ & Relative luminance. \\
$\mathcal{L}_s$ & Scene luminance. \\
$L_{\tilde{p}}$ & Binary label of the pixel $\tilde{p}$. \\
$L_{1}$, $L_{2}$, $L_{3}$, $L_{4}$  & Measurement lengths of the different parts of sun-blocker based WAHRSIS model. \\
$L^{*}a^{*}b^{*}$ & Color space comprising lightness ($L$) and color-opponent dimensions ($a^{*}$ and $b^{*}$). \\
$\mathbf{M}_i$  & Covariance matrix of the normalized matrix $\ddot{\mathbf{X}_{i}}$. \\
$N$ & Total number of images in a dataset. \\
$\mathcal{N}$ & Average luminance value of sampled pixels during hemispheric sampling. \\
$\tilde{\mathcal{N}}$ & Small neighborhood region. \\
$\mathcal{P}$ & Subset of attributes from attribute set $\mathcal{A}$.\\
$\underline{\mathcal{P}}(.)$ & Lower approximation of a conventional set.\\
$\overline{\mathcal{P}}(.)$ & Upper approximation of a conventional set.\\
$\mathbf{P}_{i}$ & Loading matrix corresponding to feature matrix $\mathbf{X}^{f}_{i}$. \\
$\mathbf{Q}_{i}$ & Loading matrix corresponding to binary image $\mathbf{Y}_{i}$. \\
$R_1$, $R_2$ & Two random floating points used during cosine weighted hemispheric sampling.\\
$\mathcal{R}$ & Red--blue ratio channel $R/B$ extracted from $\mathbf{Z}$, where $\mathcal{R} \in {\rm I\!\mathbf{R}}^{m \times n}$.\\
$\tilde{\mathcal{R}}$ & Red--blue ratio channel $(B-R)/(B+R)$ extracted from $\mathbf{Z}$, where $\tilde{\mathcal{R}} \in {\rm I\!\mathbf{R}}^{m \times n}$.\\
$RGB$ & Red, Green and Blue color channel model comprising red ($R$), green ($G$) and blue ($B$) color channels. \\
$\mathbf{S}$ & Set of cameras in the multi-camera setup (also referred as \emph{guards} in the art gallery problem). \\
$\mathcal{S}$ & Solar radiation measured by the weather station. \\
$\hat{\mathcal{S}}$ & Search space in point localization task of a multi-camera setup.\\ 
$\mathcal{T}$ & Dataset consisting of a set of images. \\
$\mathbf{T}_{i}$ & Extracted latent matrix corresponding to binary image $\mathbf{Y}_{i}$. \\
$\mathcal{U}$ & Universe with set of observations in rough-set terminology. \\
$\mathbf{U}_{i}$ & Extracted latent matrix corresponding to feature matrix $\mathbf{X}^{f}_{i}$. \\
$\mathcal{V}$ & Value domain in rough set terminology. \\
$\mathcal{X}$ & Set of observations from the universe $\mathcal{U}$. \\
$\mathbf{X}_{i}$ & Sample image of dimension $m \times n$ from a dataset consisting of \emph{N} images ($i=1,2,...,N$), where $\mathbf{X}_{i} \in {\rm I\!R}^{m \times n}$. \\
$\mathbf{X}^{f}_{i}$ & Feature matrix obtained from the sample image $\mathbf{X}_{i}$, where $\mathbf{X}^{f} \in {\rm I\!R}^{m \times n}$. \\
$\hat{\textbf{X}_{i}}$ & Fat matrix obtained from the sample image $\mathbf{X}_{i}$ using all $16$ color channels. \\
$\ddot{\mathbf{X}_{i}}$ & Normalized form of $\hat{\textbf{X}_{i}}$ with its corresponding mean and standard deviation. \\
$Y_{\bar{s}}$ & Mean brightness value of the $\bar{s}$ pixel in an $RGB$ image. \\
$Y_{\bar{s}}'$ & Non-linearly corrected mean brightness value of the $\bar{s}$ pixel in an $RGB$ image. \\
$\mathbf{Y}_{i}$ & Binary ground-truth image of the sample image $\mathbf{X}_{i}$, where $\mathbf{Y}_{i} \in {\rm I\!R}^{m \times n}$.\\
$YIQ$ & Luma and chrominance color channel, where $Y$ is luminance and $I$ and $Q$ represents in- and quadrature-phase of chrominance information.\\
$\mathbf{Z}_{i}$ & Sample image of dimension $m \times n \times 3$ from a dataset consisting of \emph{N} images ($i=1,2,...,N$), where $\mathbf{Z}_{i} \in {\rm I\!R}^{m \times n \times 3}$. \\
$\bar{\mathbf{Z}}_i$ & Gray-scale channel image of the sample image $\mathbf{Z}_{i}$, where $\overline{\mathbf{Z}}_i \in {\rm I\!R}^{m \times n}$.\\
$\mathbf{Z}_i^{R}$ & Red channel image of the sample image $\mathbf{Z}_{i}$, where $\mathbf{Z}_i^{R} \in {\rm I\!R}^{m \times n}$.\\
$\mathbf{Z}_i^{G}$ & Green channel image of the sample image $\mathbf{Z}_{i}$, where $\mathbf{Z}_i^{G} \in {\rm I\!R}^{m \times n}$.\\
$\mathbf{Z}_i^{B}$ & Blue channel image of the sample image $\mathbf{Z}_{i}$, where $\mathbf{Z}_i^{B} \in {\rm I\!R}^{m \times n}$.\\
$\mathbf{Z}_i^{L}$ & Low-exposure LDR image, where $\mathbf{Z}_i^{L} \in {\rm I\!R}^{m \times n \times 3}$.\\
$\mathbf{Z}_i^{M}$ & Mid-exposure LDR image, where $\mathbf{Z}_i^{M} \in {\rm I\!R}^{m \times n \times 3}$.\\
$\mathbf{Z}_i^{H}$ & High-exposure LDR image, where $\mathbf{Z}_i^{H} \in {\rm I\!R}^{m \times n \times 3}$.\\

\end{longtable}

### 2018-07-16 misc/thesis-hardbound/Misc/pubs.tex
Update 16/7/2018

\chapter*{\centering Author's Publications}

\lhead{Author's Publications}

\textbf{Journals}
\begin{itemize}[leftmargin=*]
\item S. Dev, F. M. Savoy, Y. H. Lee, S. Winkler, Rough-set Based Visible Color Channel Selection, \emph{IEEE Geoscience and Remote Sensing Letters}, vol. 14, no. 1, pp. 52--56, Jan 2017. 
\item S. Dev, Y. H. Lee, S. Winkler, Color-based segmentation of sky/cloud images from ground-based cameras, \emph{IEEE Journal of Selected Topics in Applied Earth Observations and Remote Sensing}, vol. 10, no. 1, pp. 231--242, Jan 2017. 
\item S. Dev, B. Wen, Y. H. Lee, S. Winkler, Machine Learning Techniques and Applications For Ground-based Image Analysis, \emph{IEEE Geoscience and Remote Sensing Magazine, Special Issue on Advances in Machine Learning for Remote Sensing and Geosciences}, vol. 4, no. 2, pp. 79--93, Jun 2016. 
\end{itemize}

\noindent 
\textbf{Conferences}
\begin{itemize}[leftmargin=*]
\item S. Dev, F. M. Savoy, Y. H. Lee and S. Winkler, Nighttime sky/cloud image segmentation, \emph{IEEE International Conference on Image Processing (ICIP)}, 2017.
\item F. Savoy, S. Dev, Y. H. Lee and S. Winkler, Stereoscopic Cloud Base Reconstruction Using High-Resolution Whole Sky Imagers, \emph{IEEE International Conference on Image Processing (ICIP)}, 2017. 
\item S. Dev, S. Manandhar, F. Yuan, Y. H. Lee and S. Winkler, Cloud Radiative Effect Study Using Sky Camera, \emph{Proc. IEEE AP-S Symposium on Antennas and Propagation and USNC-URSI Radio Science Meeting}, 2017.
\item  S. Dev, S. Manandhar, Y. H. Lee and S. Winkler,  Detecting rainfall onset using sky images, \emph{TENCON 2016 - 2016 IEEE Region 10 Conference}, 2016.
\item  S. Dev, F. M. Savoy, Y. H. Lee and S. Winkler, Short-term prediction of localized cloud motion using ground-based sky imagers, \emph{TENCON 2016 - 2016 IEEE Region 10 Conference}, 2016.
\item  S. Manandhar, F. Yuan, S. Dev, Y. H. Lee and Y. S. Meng, Weather radar to detect cloud occurence level, \emph{TENCON 2016 - 2016 IEEE Region 10 Conference}, 2016.
\item  S. Dev, F. M. Savoy, Y. H. Lee, S. Winkler, Estimation of solar irradiance using ground-based whole sky imagers, \emph{IEEE International Geoscience and Remote Sensing Symposium (IGARSS)}, 2016.
\item F. M. Savoy, S. Dev, Y. H. Lee, S. Winkler, Geo-referencing and stereo calibration of ground-based whole sky imagers using the sun trajectory, \emph{IEEE International Geoscience and Remote Sensing Symposium (IGARSS)}, 2016.
\item S. Manandhar, Y. H. Lee, S. Dev, GPS Derived PWV for rainfall monitoring, \emph{IEEE International Geoscience and Remote Sensing Symposium (IGARSS)}, 2016.
\item S. Dev, Y. H. Lee, S. Winkler, Categorization of Cloud Image Patches Using an Improved Texton-based Approach, \emph{IEEE International Conference on Image Processing (ICIP)}, 2015. 
\item S. Dev, Y. H. Lee, S. Winkler, Multi-level Semantic Labeling of sky/cloud images, \emph{IEEE International Conference on Image Processing (ICIP)}, 2015. 
\item S. Dev, F. M. Savoy, Y. H. Lee, S. Winkler, Design of low-cost, compact and weather-proof whole sky imagers for high-dynamic-range captures, \emph{IEEE International Geoscience and Remote Sensing Symposium (IGARSS)}, 2015.
\item F. M. Savoy, S. Dev, Y. H. Lee, S. Winkler, Cloud base height estimation using high-resolution whole sky imagers, \emph{IEEE International Geoscience and Remote Sensing Symposium (IGARSS)}, 2015.
\item S. Dev, Y. H. Lee, S. Winkler, Systematic Study of Color Spaces and Components for the segmentation of sky/cloud images, \emph{IEEE International Conference on Image Processing (ICIP)}, 2014. 
\item S. Dev, F. M. Savoy, Y. H. Lee, S. Winkler, WAHRSIS: A low-cost, high-resolution whole sky imager with near-infrared capabilities, \emph{Proc. IS\&T/SPIE Infrared Imaging Systems: Design, Analysis, Modeling, and Testing}, 2014.
\end{itemize}

\noindent
\textbf{Technical Reports}
\begin{itemize}[leftmargin=*]
\item S. Dev, F. M. Savoy, Y. H. Lee and S. Winkler, DIY Sky Imager For Weather Observation: A complete guide to build a ground-based sky imager using off-the-shelf components with automatic cloud coverage computation, SPM Student Design Project Series Documents, \emph{IEEE Signal Processing Society}, 2016.\\
(Featured in H. Godrich, Students' Design Project Series: Sharing Experiences [SP Education], IEEE Signal Processing Magazine, Jan 2017.)
\end{itemize}

### 2018-07-16 misc/thesis-hardbound/thesis.tex
Update 16/7/2018

\documentclass[reqno,12pt,oneside]{book} % For e-report
%\documentclass[reqno,12pt,twoside]{book} % For printing

\newtheorem{theorem}{Theorem}
\usepackage{longtable}
\usepackage[english]{babel}
\usepackage{fancyhdr}
\usepackage{float} \restylefloat{figure} %defines H option for floats
\usepackage{color}   %May be necessary if you want to color links
\usepackage{setspace}
\usepackage{hyperref}
\hypersetup{
    colorlinks=true, %set true if you want colored links
    linktoc=all,     %set to all if you want both sections and subsections linked
    linkcolor=black,  %choose some color if you want links to stand out
    citecolor=blue,
    urlcolor=blue,
}
\usepackage[nameinlink,noabbrev]{cleveref}
\renewcommand\floatpagefraction{.99}
\renewcommand\dblfloatpagefraction{.95}
\usepackage{graphicx}
\graphicspath{{Figures/}}
\usepackage{multirow}
\usepackage{colortbl}
\usepackage{setspace} %\singlespacing 
\onehalfspacing
\usepackage{fixltx2e}
\usepackage{epstopdf}
\usepackage{rotating}
\usepackage{resizegather}
\usepackage{lscape}
\setlength{\textfloatsep}{1mm}
\setlength{\floatsep}{1mm}
\usepackage{bm} %defines \bm for bold greek letters, i.e. $\bm{\alpha}$
\usepackage{cite}
\usepackage{url}
\usepackage[small]{caption}
\usepackage{subfig} %should come after caption package if given, can't be used with caption2, defines subfloat
\usepackage{array} %More formatting options for array and tabular environments
\usepackage{mathtools}
\DeclarePairedDelimiter{\ceil}{\lceil}{\rceil}
\usepackage{amsmath}   % From the American Mathematical Society
% A popular package that provides many helpful commands
% for dealing with mathematics. Note that the AMSmath
% package sets \interdisplaylinepenalty to 10000 thus
% preventing page breaks from occurring within multiline
% equations. Use:
\interdisplaylinepenalty=2500
% after loading amsmath to restore such page breaks
% as IEEEtran.cls normally does. amsmath.sty is already
% installed on most LaTeX systems. The latest version
% and documentation can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/required/amslatex/math/
\usepackage{amsfonts}
\usepackage[T1]{fontenc} % For less than and greater than sign
\usepackage{subfloat}
\usepackage{tikz}
\usepackage{afterpage}
\usepackage{lipsum}
\long\def\symbolfootnote[#1]#2{\begingroup\def\thefootnote{\fnsymbol{footnote}}
\footnote[#1]{#2}\endgroup}

\hyphenation{op-tical net-works semi-conduc-tor}

\usepackage{geometry}
\usepackage{enumitem}
\usepackage{stackengine}
\usepackage{wrapfig} % For wrapping figure with text.
\usepackage{algpseudocode} % For algorithm 
\usepackage{algorithm,algpseudocode}

% To hide the references section.
%\usepackage[hide=true]{nobibprint}

\newcolumntype{L}{>{\centering\arraybackslash}m{8mm}} % Used for Table in cloud classification chapter

\definecolor{orange}{rgb}{0.96, 0.52, 0.08}

\newcommand{\forceindent}{\leavevmode{\parindent=1.5em\indent}}

% Addition ends here----------------------

\usepackage{nomencl}

\begin{document}

\frontmatter
\pagestyle{plain}

\begin{titlepage}

\newcommand{\HRule}{\rule{\linewidth}{0.5mm}} % Defines a new command for the horizontal lines, change thickness here

\begin{center}

\textsc{{\Large \bfseries 2D and 3D Image Analysis and Its Application to Sky/Cloud Imaging}}\vspace{0.4cm} % Thesis title

\vspace{4cm}

\textsc{\Large \bfseries Soumyabrata Dev}\\[0.5cm]

\vspace{5cm}

\vfill

\large {School of Electrical \& Electronic Engineering}\\[0.5cm]

\vspace{1cm}

\normalsize{A thesis submitted to the Nanyang Technological University\\ in partial fulfillment of the requirement for the degree of\\ 
Doctor of Philosophy}\\[0.3cm] % University requirement text

{\large \textbf{2017}}\\[4cm] % Date

\end{center}
\end{titlepage}

\cleardoublepage
\input{Misc/ack}
\addcontentsline{toc}{chapter}{Acknowledgment}

\input{Misc/abstract}
\addcontentsline{toc}{chapter}{Abstract}

\clearpage

\pagestyle{fancy}
\fancyhf{}
\afterpage{\cfoot{\thepage}}    %Forces page number in every line

\cleardoublepage
\lhead{\emph{Contents}}
\tableofcontents
\addcontentsline{toc}{chapter}{Contents}

\cleardoublepage
\lhead{\emph{List of Figures}}
\listoffigures
\addcontentsline{toc}{chapter}{\listfigurename}

\cleardoublepage
\lhead{\emph{List of Tables}}
\listoftables
\addcontentsline{toc}{chapter}{List of Tables}

\clearpage

\cleardoublepage

\input{Misc/abbreviations}
\addcontentsline{toc}{chapter}{Abbreviations}
\clearpage

\mainmatter %[This indicates page number will start now]

%INCLUDE THE CHAPTERS HERE
\input{Chapters/Chapter1}
\clearpage

\input{Chapters/Chapter2}
\clearpage

\input{Chapters/Chapter3}
\clearpage

\input{Chapters/Chapter4}
\clearpage

\input{Chapters/Chapter5}
\clearpage

\input{Chapters/Chapter6}
\clearpage

\input{Chapters/Chapter7}
\clearpage

\input{Chapters/Chapter8}
\clearpage

\input{Chapters/Chapter9}
\clearpage

%----------------------------------------------------------------------------------------
%	THESIS CONTENT - APPENDICES
%----------------------------------------------------------------------------------------

\addtocontents{toc}{\vspace{2em}} % Add a gap in the Contents, for aesthetics

\appendix % Cue to tell LaTeX that the following 'chapters' are Appendices
% Suppressing the counter to not show sections and sub-sections.

\addtocontents{toc}{\protect\setcounter{tocdepth}{0}}

% Include the appendices of the thesis as separate files from the Appendices folder
% Uncomment the lines as you write the Appendices

\input{Appendices/AppendixA}
\input{Appendices/AppendixB}
\input{Appendices/AppendixC}
\input{Appendices/AppendixD}

% Setting the counter back on track!
\addtocontents{toc}{\protect\setcounter{tocdepth}{2}}

\backmatter

\cleardoublepage

\input{Misc/notations}
\addcontentsline{toc}{chapter}{Notations}
\clearpage

\input{Misc/pubs}
\addcontentsline{toc}{chapter}{Author's Publications}

%----------------------------------------------------------------------------------------
%	BIBLIOGRAPHY
%----------------------------------------------------------------------------------------

\label{Bibliography}
\small
\begin{singlespace}
\lhead{\emph{Bibliography}}
\bibliographystyle{IEEEbib}
\bibliography{./References/longforms,./References/references}	
\end{singlespace}

\end{document}

### 2018-07-16 thesis/1_foreword/abstract.tex
Update 16/7/2018

\addcontentsline{toc}{chapter}{Abstract}
\begin{center}
	\textbf{\large Abstract}
\end{center}

\begin{center}
	\textbf{Implementation of An Autonomous Star Recognition Algorithm using Hardware-Software Co-Processing Approach} \\
	\emph{By Dang Le Dang Khoa}
\end{center}

\noindent There are various types of Attitude Determination sensors such as sun sensors, magnetometer, RF beacon but only Star Trackers can achieve the accuracy to arc seconds. A Star Tracker is an embedded system mounted on a spacecraft comprised by an Image sensor and a Computer. It helps determine the attitude of the satellite based on an Autonomous Star Recognition Algorithm. The Star Sensor would take an image of stars at its current position, and then the star pattern recognition algorithms would extract features to construct a pattern from the images. This pattern then is compared with a prebuilt Star Pattern Database (SPD) to return the Star Identity of a star in the Image. This star identity is an important part to determine the attitude of the satellite. \\

\noindent To implement the Algorithm on a specific hardware, the computing system must be appropriately chosen. Programmable System-on-chip (PSoC) is a technology that replaces the traditional ASIC (Application Specific Integrated Circuit) by an FPGA (known as Programmable Logics) combined with an Embedded Processor (known as the Processing system), integrated memories, a variety of peripherals to form an embedded computing system. The Programmable Logic is ideal for implementing high-speed logic, arithmetic and accelerating subsystems while the Processing System supports software routines and Operating systems. Based on this property, an algorithm can be partitioned into submodules to be co-processed by the hardware-software combination. \\

\noindent The goal of this research is to partition and profile a Star Recognition Algorithm then implement these modules on both the Processing System (Software) and the Programmable Logics (Hardware) to analyze the Algorithm implementation regarding Performance, Area of Implementation, Power Consumption. \\

\noindent \textbf{Keywords}: Star tracker, Star pattern recognition, Star recognition, Algorithms, Attitude determination, Embedded System, Programmable System on Chip (PSoC).

### 2018-07-16 thesis/1_foreword/ack.tex
Update 16/7/2018

\addcontentsline{toc}{chapter}{Acknowledgements}
\begin{center}
\textbf{\large Acknowledgements}
\end{center}

\noindent There are many people I want to thank for helping me in completing this work. Foremost, I would express my sincerest gratitude to my supervisor, Asst. Prof. Chen Shoushun for supporting and guiding me through my work and study with his knowledge and patience. I am very grateful for his insights and instructions in the hardware design for FPGA. \\

\noindent Many thanks to all my labmates of Satellite Research Center II, especially MEHTA Deval Samirbhai and Chin Shi Tong for the first steps of my research and the help whenever I am in troubles and doubt. \\

\noindent I would also like to thank Mrs. Janet Tan and Mrs. Pamela Ng, the technicians of Satellite Research Center II for helping me with all the lab facilities instructions also, setting up the equipment and providing resources whenever I need. \\

\noindent Finally, I sincerely thankful to my parents, my brother and all of my friends for their love and support throughout my study.

\vspace{1cm}

\hfill

### 2018-07-16 thesis/2_chapters/chap1.tex
Update 16/7/2018

% Chapter 1
\chapter{Introduction}
\label{chap:intro}

% Section 1.1
\section{Overview and Motivations}

Artificial satellites orbiting the earth are a critical component of modern society. They are used in areas such as communication, positioning, imaging and weather forecasting. Besides the ordinary purposes of satellites like Earth observation, communication, weather forecasting\cite{How_satellites_rule_our_world}, we also use satellites for research purposes. An example of this is the International Space Station (ISS) and the Hubble telescope. \\

\noindent Satellites operate in different orbits. Some popular orbit classes are Low Earth Orbit (LEO), Medium Earth Orbit (MEO) and High Earth Orbit (HEO)\cite{sat_wiki}. Low Earth Orbit is the area below 2000km, High Earth Orbit is the orbit above 35,500 km, and Medium Earth Orbit is the area between Low Earth Orbit and High Earth Orbit. Satellites are launched to their orbit by a self-propelled rocket as a piggyback payload. \\

\noindent Nanosatellite is a small artificial satellite with a wet mass between 1 – 10 kg. Nanosatellites are cheap but capable of performing commercial missions and has lead researchers and scientist to explore the new way to use the Nanosatellites in LEO\cite{network}. Their designs are only comprised of low-cost components. Due to their cost-effective, fast development cycle and size convenience, Nanosatellites are becoming popular in educational and scientific development. Nanosatellites can be quickly built in a small university project. \\

\noindent A satellite needs an attitude determination system for navigation and acknowledging orientations. Its attitude needed to be calculated and predicted continuously during its operation on the orbit. By implying the celestial objects and properties around the satellite, the satellite can autonomously estimate the orientations. Some of the favorite reference objects are the Sun, the Earth magnetic field, the celestial sphere, and the stars. For Nanosatellites, the attitude determination system must be concise but operate effectively.

% SubSection 1.1.1
\subsection{Overview and Motivations}

Based on the celestial reference objects, many attitude determination sensors have been developed. Some of the sensors are the sun sensor, magnetometer, gyroscope, Earth horizon sensor\cite{MDP}. The sun sensor is the most common sensor to be mounted on Nanosatellites due to its low cost, low power consumption, and lightweight. The sun sensor is also integrated with an Inertial Measurement Unit (IMU) which is capable of measuring the magnetic field, rotational speed and acceleration or a GPS to provide satellite’s position and velocity vector. The only disadvantage of the sun sensor is that its accuracy can only reach 1 arcminute resolution while the attitude determination system need a higher efficiency up to arc seconds resolution\cite{edselc.2-52.0-001938469619810101}.

% SubSection 1.1.2
\subsection{Star Tracker for attitude determination approach}

Another way of attitude determination approach is using star trackers. Star Tracker is an optical-electronics subsystem comprised of a CCD or CMOS Image sensor attached to an optical lens and a computing system, usually a microprocessor integrated into an ASIC board. The image sensor will firstly take an image of multiple star clusters at a specific fixed orientation. After that, the image is processed through the computing system to extract a particular feature of the model depending on a predefined algorithm. Then, the specific feature is compared which a prebuilt pattern or feature database stored in the memory. The output of the algorithm is often a star ID, which has a specific attitude, this attitude is again used to determine the attitude(orientation) of the spacecraft. \\

% Figure 1.1 and 1.2
\ntumultiepsfig[width=\textwidth]{1_1}{Star tracker hardwares}{1_2}{Commercial star trackers}

\noindent The star tracker is a preferred attitude determination approach because of its high accuracy compared to other sensors\cite{ntu.19915319780101}. However, the star tracker approach is less low cost and more power consumption than traditional approach by sun sensor and IMU. To achieve the best accuracy, the star tracker depends on the many factors such as the quality of the image sensor, the quality of the optical lens, most importantly the processing time of the computing subsystem, the runtime of the star tracking Algorithm. \\

% Table 1.1
\noindent Table~\ref{tab:AD_accuracy} depicts the accuracy comparison between star reference object and other celestial objects for attitude determination\cite{edseee.38797119950101}.
\begin{ntutab}{|c|c|}{AD_accuracy}{Attitude determination accuracy comparison}
	\hline
	Reference Object & Potential Accuracy \\
	\hline
	Stars & 1 arcsecond \\
	Sun & 1 arcminute \\
	Earth(Horizon) & 6 arcminutes \\
	RF beacon & 1 arcminute \\
	Magnetometer & 30 arcminutes \\
	\hline
\end{ntutab}

\pagebreak

% Section 1.2
\section{Objectives}
The essential goals of this research project are followed.
\begin{itemize}
	\item To analyze several star tracking algorithms especially in Lost in space (LIS) mode.
	\item To implement and evaluate the performance of a star tracking algorithm on specific hardware using hardware and software co-processing approach.
	\item To benchmark and optimize the algorithm on the terms of power consumption, the area of transistor implementation.
\end{itemize}

% Section 1.3
\section{Major contributions}
The following are the significant contributions of this research project.
\begin{itemize}
	\item Investigates and Analyses the star tracking algorithms on the advantages and weaknesses of traditional methods.
	\item Reviews and examines in details the proposed algorithm by precedent research.
	\item Implements the proposed method in term of hardware and software co-processing approach on an embedded system for star tracker.
\end{itemize}

% Section 1.4
\section{Organization of the thesis}
The rest of the thesis is organized as followed:
\begin{itemize}
	\item Chapter 2: Introduces the basis of star tracking operation, reviews some of the state of the art star tracking algorithms and the chosen algorithm to be implemented by the software-hardware co-processing approach.
	\item Chapter 3: Introduces and analyze a proposed algorithm going to be implemented on the hardware.
	\item Chapter 4: Discuss the result of the implementation regarding runtime performance, hardware resources.
\end{itemize}

### 2018-07-16 thesis/2_chapters/chap2.tex
Update 16/7/2018

% Chapter 2
\chapter{Literature preview}
\label{chap:lit_review}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Section 2.1
\section{Star Tracker Operations}

The star tracking algorithm operates mainly in 2 different modes: the Lost in Space (LIS) and Tracking modes:
\begin{itemize}
	\item LIS mode: the initial attitude is unknown, the star tracker must determine it which is the most critical part of the star tracking operation. LIS mode is operated at the time when the power system on or resets after an attitude determination attempt from tracking mode failed\cite{edselc.2-52.0-8487677997120120101}.
	\item Tracking mode: after the initial attitude is recognized. The star tracker is switched to the Tracking mode. With the initial is acknowledged, the computing can easily predict and track the attitude based on the previous information.
\end{itemize}

\noindent On this research topic, we will only focus on the LIS mode operation. The LIS mode operation of a star tracker is generalize in Figure~\ref{fig:2_1} included in 3 main algorithms:
\begin{itemize}
	\item Centroiding Algorithm: Perform an image preprocessing, the input is a star image captured from the image sensor processed to an output which are the coordinates of all star clusters presented in the image.
	\item Star Recognition Algorithm: The main part of LIS mode. The coordinates of the stars will be used to calculate a feature vector depending on a specific Star Algorithm. A Star Pattern Database (SPD) is also prebuilt from the SAO catalog (Smithsonian Astrophysical Observatory Star Catalog) based on the specific pattern of the Star Algorithm and stored into the memory of the processing system for comparison and pattern recognition\cite{edseee.655799920130101}. Then, the feature vector will be looked up and matched to an entry in the SPD. The entry will return a star ID which is an identification of a star presenting in the star image.
	\item Attitude Determination stage: The final stage of star tracking algorithm operated in LIS mode. The Star ID will be looked up again in the SAO catalog to extract the information about its attitude. Then a group of star attitude is still used to calculate the attitude of the satellite. Some of the well-known Attitude Determination methods are the QUEST and TRIAD.
\end{itemize}

% Figure 2.1
\ntuepsfig[width=\textwidth]{2_1}{Stages of star tracking algorithm}

\noindent This research topic will focus on the Centroiding and Star Identification Algorithm to be implemented on a computing system.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Section 2.2
\section{Centroiding Algorithm}

The first step is to acquire the image which is accomplished by the image sensor. The image acquired has to be processed for estimating the coordinate of the stars in the image plane. This is completed by applying the centroiding process on the image. The input of this step is a star image with multiple star clusters, the output is the coordinates of every stars presenting. Due to distributed energy surface, a star projection is spread over a 3x3 to 11x11 square area\cite{ntu.54658220060101}, the star projection is a group of connected pixels. Therefore, the best way to identify the star clusters is to apply the ‘connected component’ algorithm.

% Figure 2.2
\ntuepsfig[width=\textwidth]{2_2}{Stars projection onto a 2D image plane}

% Figure 2.4
\ntuepsfig[width=\textwidth]{2_4}{Centroid of stars in an image}

% Table 2.1
\noindent Table~\ref{tab:starList}. \\

\begin{ntutab}{|c|c|}{starList}{A list of star centroids in an image}
	\hline
	\textbf{Star} & \textbf{Coordinates(X,Y)} \\
	\hline
	Star 1 & $(X_1, Y_1)$ \\
	\hline
	Star 2 & $(X_1, Y_1)$ \\
	\hline
	... & ... \\
	\hline
	Star N & $(X_N, Y_N)$ \\
	\hline
\end{ntutab}

\noindent A star pattern is spread over an area so we can calculate its centroid by applying the weighted pixel intensity technique. Assume that (i, j) is the horizontal and vertical centroid coordinate of a star, $I_{ij}$ is each pixel intensity of the star pattern, i and j are the horizontal and vertical coordinates of each pixel of the star pattern.

% Figure 2.3
\ntuepsfig[width=\textwidth]{2_3}{Star clusters represented in a 2D image plane}

% Equation 2.1
\noindent Equation~\ref{eq:2_1}

\begin{equation} % Equation
	x = \frac{\displaystyle\sum_{i=1}^{n} \displaystyle\sum_{j=1}^{m} (i * I_{ij})} {\displaystyle\sum_{i=1}^{n} \displaystyle\sum_{j=1}^{m} I_{ij}}, y = \frac{\displaystyle\sum_{i=1}^{n} \displaystyle\sum_{j=1}^{m} (j * I_{ij})} {\displaystyle\sum_{i=1}^{n} \displaystyle\sum_{j=1}^{m} I_{ij}}
	\label{eq:2_1}
\end{equation}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Section 2.3
\section{Liebe Star Recognition algorithm}

The star pattern recognition algorithm based on the angular features formed by a star triplet was reported in\cite{edseee.38797119950101,edseee.18038319930101,000176062300018n.d.,edseee.103539620020101,edseee.79314719990101}. The idea of Liebe Algorithm is to utilize 3 nearest-to-the centre stars. The closest-to-the-centre star is chosen as the reference star which will then return the star ID for Attitude Determination stage. Then the next 2 stars are chosen from the neighboring stars of the reference star which have the minimum and the second minimum distance to it. \\

% Equation 2.2
\noindent The star triplet will form 2 angular distance $\theta_1, \theta_2$ and 1 angular angle $\theta$ which are defined by Equation~\ref{eq:2_2}
\begin{equation}
	\begin{aligned}
		\theta_1 = \cos(V_A, V_B) \\
		\theta_2 = \cos(V_A, V_C) \\
		\theta = \cos(V_{AB}, V_{AC})
	\end{aligned}
	\label{eq:2_2}
\end{equation}

\noindent In which A is the reference star. B and C are the 2 stars which are closest to A. \\

% Figure 2.5
\ntuepsfig[scale=0.5]{2_5}{Liebe star pattern}

% Equation 2.3
\noindent The feature vector of the Liebe star recognition algorithm is defined as Equation~\ref{eq:2_3}. \\

\noindent The star triplet will form 2 angular distance $\theta_1, \theta_2$ and 1 angular angle $\theta$ which are defined by Equation~\ref{eq:2_3}
\begin{equation}
	f = \{\theta, \theta_1, \theta_2\}
	\label{eq:2_3}
\end{equation}

% Table 2.2
\noindent Table~\ref{tab:Liebe_SPD}.

\begin{ntutab}{|c|c|c|}{Liebe_SPD}{An example of Liebe star pattern database}
	\hline
	$\theta_1$ & $\theta_2$ & $\theta$ \\
	\hline
	54 & 80 & 32 \\
	54 & 80 & 33 \\
	54 & 81 & 32 \\
	54 & 81 & 33 \\
	54 & 82 & 32 \\
	54 & 82 & 33 \\
	55 & 80 & 32 \\
	55 & 80 & 33 \\
	55 & 81 & 32 \\
	55 & 81 & 33 \\
	55 & 82 & 32 \\
	55 & 82 & 33 \\
	56 & 80 & 32 \\
	56 & 80 & 33 \\
	56 & 81 & 32 \\
	56 & 81 & 33 \\
	56 & 82 & 32 \\
	56 & 82 & 33 \\
	\hline
\end{ntutab}

\noindent The most advantage of Liebe star recognition algorithm is that it is straightforward in implementation. It requires very few computations in the process. \\

\noindent The weakness of this algorithm is the weak robustness due to the limitation of star utilizing. It only employs the three nearest stars to the centre and discards other stars which will then lead to a mismatch if the 2 predefined nearest neighboring star does not appear in the star image. Besides, if the reference star appears in the final entry of the Star Pattern Database.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Section 2.4
\section{Pyramid star recognition algorithm}

To overcome the mismatches caused by lack of information employed by Liebe algorithm, the pyramid star recognition algorithm is proposed in\cite{S100702140670232220060101,citation-254199748,citation-241677739,citation-228999366,citation-26584290}. Its searching pattern is a combination of angular distances of 4 stars in the star image. In Figure~\ref{fig:2_6}, the 4 stars: A,B,C,D is chosen to build the pattern. The reference star which is star A in the example is the closest star to the centre of the image. Next, the 3 neighboring stars around star A are selected to form a feature vector from the 4-star angular distances.

% Figure 2.6
\ntuepsfig[scale=0.5]{2_6}{Pyramid star pattern}

% Equation 2.4
\begin{equation}
	f = \{p_1, p_2, p_3, p_4, p_5, p_6\}
	\label{eq:2_4}
\end{equation}

% Table 2.3
\noindent Table~\ref{tab:Pyramid_pattern}.

\begin{ntutab}{|c|c|c|}{Pyramid_pattern}{A Pyramid star pattern example}
	\hline
	Angular distances & Star 1 & Star 2 \\
	\hline
	$p_1$ & A & B \\
	$p_2$ & A & C \\
	$p_3$ & A & D \\
	$p_4$ & B & C \\
	$p_5$ & B & D \\
	$p_6$ & C & D \\
	\hline
\end{ntutab}

\noindent One of the advantages of the pyramid algorithm is that it employs 4 stars to build the feature vector compared to only 3 stars of the Liebe algorithm. Compared to Liebe’s, this method is more robust since it makes the star recognition process more accurate as six features are utilized for identification purpose compared to only three features used by the Liebe algorithm\cite{HETE}. \\

\noindent However, in a tradeoff, more memory space is needed since it requires to store at least 6 pairs of each starID entry this will lead to increase the memory required to store the star pattern database and the processing time will be increased due to the increase in pattern storage and comparisons. The time complexity is also a significant consideration. To solve this problem, the k-vector search has been introduced in\cite{citation-241677739,citation-26584290}. The time complexity has been reduced significantly which is equivalent to the Liebe searching method. \\

\noindent Moreover, the pyramid star recognition algorithm has not yet solved the mismatch problem caused by missing stars. In the case of one or more neighboring stars of the reference, the star is missing the algorithm will fail and do not produce a correct result. \\

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Section 2.5
\section{Geometric Voting algorithm}

To overcome the weakness of Liebe and Pyramid star recognition algorithm, the Geometric Voting is proposed based on voting of radial distances\cite{edseee.456019820080101}. The Geometric Voting method considers all the nearby stars of the reference star appeared in the star image. Thanks to all stars in the image are employed, the Pyramid algorithm becomes more robust than the first two algorithms.

% Figure 2.7
\ntuepsfig[scale=0.7]{2_7}{Geometric Voting star pattern}

% Equation 2.5
\noindent The feature vector is now not a fixed number of elements as in equation~\ref{eq:2_5}.
\begin{equation}
	f = \{r_1, r_2, ...,r_n\}
	\label{eq:2_5}
\end{equation}

\noindent After capturing the image, $r_1, r_2,…,r_n$ are calculated based on the distance from the closest star to the centre which is the reference star to all other stars within the FOV of the star sensor. Then all the distances from the feature vector are compared to the predefined neighboring distances of every star ID in the SPD. With each distance is matched, a voting value of the star ID is increased. After the comparing distance stage processed, the star ID which has the highest vote is recognized as the correct star ID candidate. \\

\noindent For the advantage of this recognition method, firstly it employs all the data presenting in the image. As a result, it reduces the mismatching issued caused by lack of data proposed by Liebe and Pyramid method. Thus, it is the most robust star recognition method compared to the first two introduced methods. \\

\noindent The critical drawback of this method is the enormous space complexity needed to store the Star Pattern Database since each star ID entry must store the information of all of its neighboring stars. It leads to a requirement that a large memory must be used to store the Star Pattern Database to trade off the accuracy and robustness. Thus, the processing time for returning a star ID is increasing due to the increase in data processing and comparisons through the whole database.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Section 2.6
\section{Star Identification Algorithm with Optimized database}

In a quick review and analysis of the 3 prestigious and famous star recognition, we can come up with a conclusion that there is a trade-off between accuracy and robustness with the space complexity and processing time required. For the star tracker system, the choice of algorithm to be implemented on will depend on the scale of the satellite project. For military satellite, we favor the accuracy and robustness over the complexity of time and space. Thus, the computer system on those satellites must be fast enough to handle the complexity. \\

\noindent For the implementation on the nanosatellites, the computer system is a small embedded processor with limited memory and processing ability which can not handle a large number of computations. Therefore, we need an optimized algorithm that is accurate, robust and can be implemented on a concise computer system. \\

\noindent The chosen star tracking algorithm is conducted by the research “An Autonomous Star Recognition Algorithm with Optimized Star Catalogue for Fast Search Performance” M.D. Pham, K.S. Low and S.H. Chen\cite{edselc.2-52.0-8487677997120120101,edseee.655799920130101}. The research introduces a novel star pattern identification using an optimized database and proposes a search tree data structure for quick and advanced parallel search. \\

\noindent Due to the advance of the previous research have been proven, this star tracking algorithm will be chosen to be implemented on the hardware. \\

\noindent This star identification algorithm employs all the star appeared in the FOV like the geometric voting algorithm. The distances from the reference star to its neighboring stars are considered, and thus, another field is added to yield the star pattern, the number of stars appeared within the FOV of the star sensor. \\

% Figure 2.8
\ntuepsfig[scale=0.7]{2_8}{Star Identification Algorithm with Optimized database star pattern}

\noindent The feature vector is described in Figure~\ref{fig:2_8}.
\begin{center}
	\begin{itemize}
		\item N: Number of stars appeared within the FOV of the star sensor.
		\item $D_1, D_2, D_3…, D_n$: Distance from the reference star to all of its neighbors.
	\end{itemize}
\end{center}

\noindent To search and match the star pattern vector with the database, a special database structure is pre-built. The tree is built with multiple levels, the first level is N-Number of stars in the FOV, next layers will be the distances from the reference stars to all of its neighbors which are sorted ascendingly from nearest neighboring star to the farthest. \\

\noindent In the searching and matching stage, each parameter from the star pattern is dispatched and matched to the equivalent level. If the matching succeeds, the next layer is considered. If all layers are matched the correct star ID will be returned; otherwise, we return a statement that the star pattern is a false pattern, no stars were matched. In this case, depend on the attitude determination system on the satellite, the star identification algorithm would be rerun or skipped to proceed the next star image.

% Figure 2.9
\ntuepsfig[scale=0.7]{2_9}{A star pattern database tree-styled structure}

### 2018-07-16 thesis/2_chapters/chap3.tex
Update 16/7/2018

% Chapter 3
\chapter{Hardware and Software Co-processing – Implementation of the Algorithm}
\label{chap:HSC}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Section 3.1
\section{Overview}

% Subsection 3.1.2
\subsection{FPGA - Programmable Logic - IP Block}

FPGA (Field Programmable Gate Array) provides a general purpose digital logic with great flexibility and utility. The fundamental logic cells of an FPGA work using look up tables (LUTs). The performance of an FPGA design depends on the area using and routing of LUTs\cite{Dummies}. \\

\noindent \textbf{LUTs}: FPGAs were first designed to imitate Gate Arrays – integrated circuits with a sea of gates that were connected by added metal layers (wire routing) to define the functionality of the device. However, instead of implementing the logic using transistor gates, the logic was in many cases implemented by memory fashioned as look up tables. \\

\ntuepsfig[width=\textwidth]{3_LUT}{A 4-input logic implemented by a Look up table (LUT)\cite{Coursera}}

\noindent \textbf{Routing}: The routing in an FPGA is hierarchical. At the lowest level, we have a routing switch that is controlled by a bit of SRAM, or a FLASH bit, or a fuse. There are many routing switches in the local routing to connect various logic elements or blocks. The FPGA is made of a sea of these logic blocks. Groups of the blocks are connected by long lines or very long lines. Common signals like clocks are routed on special routing networks called global networks. \\

\ntuepsfig[width=\textwidth]{3_Routing}{FPGA Routing Architecture\cite{Coursera}}

\noindent \textbf{FPGA design flow}: The design begins with design entry, continues with simulation to verify the logic is implemented as expected, and then the tool will perform synthesis (also called mapping) to map the logic to the device architecture. Next the tool will create the interconnection between cells by place and routing (or fitting) the design. Another simulation after the fitting is done is a good practice. If this looks good, the next step to use the tool to create a programming file, which is then downloaded into the FPGA device for testing\cite{Coursera}. \\

\ntuepsfig[width=\textwidth]{3_DesignFlow}{FPGA Development Process Design Flow\cite{Coursera}}

\noindent \textbf{Programmable Logic}: In Xilinx architecture, the FPGA part of the design is called Programmable Logic (PL). Some of the specialized components in the architecture include:
\begin{itemize}
	\item \textbf{Configurable Logic Blocks (CLBs)} contain flexible Look-Up Tables (LUTs) that implement logic plus storage elements used as flip-flops or latches.
	\item \textbf{Input/Output Blocks (IOBs)} control the flow of data between the I/O pins and the internal logic of the device. IOBs support bidirectional data flow plus 3-state operation. They support a variety of signal standards, including several high-performance differential standards. Double Data-Rate (DDR) registers are included.
	\item \textbf{Block RAM} provides data storage in the form of 18-Kbit dual-port blocks.
	\item \textbf{Multiplier Blocks} accept two 18-bit binary numbers as inputs and calculate the product.
	\item \textbf{Digital Clock Manager (DCM) Blocks} provide self-calibrating, fully digital solutions for distributing, delaying, multiplying, dividing, and phase-shifting clock signals.
\end{itemize}

\noindent These elements are organized as shown in Figure~\ref{fig:3_spartan}. A dual ring of staggered IOBs surrounds a regular array of CLBs. Each device has two columns of block RAM. Each RAM column consists of several 18-Kbit RAM blocks. Each block RAM is associated with a dedicated multiplier. The DCMs are positioned in the center with two at the top and two at the bottom of the device. The design has two DCMs in the middle of the two columns of block RAM and multipliers. \\

\noindent The Xilinx Programmable Logic features a rich network of traces that interconnect all five functional elements, transmitting signals among them. Each functional element has an associated switch matrix that permits multiple connections to the routing\cite{spartan}. \\

\ntuepsfig[width=\textwidth]{3_spartan}{Xilinx Spartan-3AN Family Architecture\cite{spartan}}

\noindent \textbf{Intellectual property core}, IP core, or IP block is a reusable unit of logic, cell, or integrated circuit (commonly called a "chip") layout design that is the intellectual property of one party. IP cores may be licensed to another party or can be owned and used by a single party alone. The term is derived from the licensing of the patent and/or source code copyright that exist in the design. IP cores can be used as building blocks within application-specific integrated circuit (ASIC) designs or field-programmable gate array (FPGA) logic designs\cite{ipcore}.

\pagebreak 
\subsection{System-on-a-chip}

System-on-a-chip (SoC) is anatomy in embedded system which considers a processing board integrated with processor and hardware peripherals and memory for a specific function like digital, analog signal processing\cite{12457872420171101}. \\

\noindent Traditional SoC board is a fixed Application Specific Integrated Circuit (ASIC) with is prebuilt for only one particular function or task. The processing time of ASIC board is speedy and high-efficiency due to the unique hardware prebuilt for this task. In the trade-off, the development time of an ASIC board takes much time due to multiple stages of hardware synthesis, testing and verification and the cost of development is enormous. ASIC board is only suitable for mass-production strategy with over 1 million products per a development cycle. \\

% Figure 3.1
\ntuepsfig[width=\textwidth]{3_1}{An ASIC board}

\noindent Another approach is using an embedded processor for the implementation. All stages of the development are equivalent to a software development process. This approach brings some advantages like low-cost development, flexibility, easy to fix and testing, short-time-development, and short-time-to-market. On the downside, the approach of using multipurpose processors causes high power consumption, low efficiency in the product operation. \\

% Figure 3.2
\ntuepsfig[width=\textwidth]{3_2}{An ARM embedded processor}

\noindent Programmable-System-on-a-chip (PSoC) is a hybrid way approach of SoC embedded system. It replaced the traditional ASIC by a Programmable Logic (FPGA) interfacing and embedded multipurpose processor with an integrated Processing system (usually a hard processor) through a high-speed bus. For zynq PSoC, the Advanced eXtensible Interface (AXI) is this high speed communicating bus. The PSoC cannot achieve the high-efficiency as the traditional ASIC approach but thanks to the modern technology and the short development time, the PSoC approach is the most suitable candidate for research and development projects which is below 1000 products for a cycle. \\

% Figure 3.3
\ntuepsfig[width=\textwidth]{3_3}{PS and PL connected through AXI}

\noindent The PSoC board which is used to implement Star Tracking algorithm in this project is the Zynq zedboad illustrated in Figure~\ref{fig:3_4}. The defining feature of Zynq is that it combines a dual-core ARM-A9 processor with traditional FPGA logic fabric\cite{Xilinx}. Although dedicated processors have been coupled with FPGAs before, it has never been quite the same proposition. In Zynq, the ARM Cortex-A9 is an application grade processor, capable of running full operating systems such as Linux, while the programmable logic is based on Xilinx 7-series FPGA architecture. \\

% Figure 3.4
\ntuepsfig[width=\textwidth]{3_4}{A Zedboard Programmable System on Chip}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Section 3.2
\section{Partition and Profiling}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% subsection 3.2.1
\subsection{Partition}

Partitioning is the first stage of PSoC development. The algorithm or the program will be partitioned into suitable-size submodules. These submodules are later decided to implement on which side of the PSoC: Programmable Logics or Processing System. How the program partitioned is decided by the designer. \\

% Figure 3.5
\ntuepsfig[width=\textwidth]{3_5}{Module partitioning\cite{Zynqbook}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% subsection 3.2.2
\subsection{Profiling}

Profiling is a practical analysis that measures and analyze the space and time complexity of an algorithm or a submodule of an algorithm. By examine the profiling result, we can specify the most critical time-consuming part or module of the system. Then based on the profiling and asymptotic analysis stated above, we can decide correctly which parts or submodules can be implemented in hardware instead of software. \\

\noindent All the submodules are implemented on Processing System side by software approach then determined which submodules take the most time to run. These modules then are optimized and designed as Intellectual Property core by Hardware description language (HDL) on Programmable Logics side. \\

% Figure 3.6
\ntuepsfig[width=\textwidth]{3_6}{Profiling steps}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% subsection 3.2.3
\subsection{Partitioning and profiling results}

The star tracking algorithm is partitioned into 4 submodules shown in Figure~\ref{fig:3_7}. The 4 submodules include:
\begin{itemize}
	\item \textbf{Centroiding}: Takes the star image and reproduce the star coordinates in the image.
	\item \textbf{Choose the reference star}: From the list of star coordinates, proceeds to choose the reference star.
	\item \textbf{Find the star pattern}: From the reference star, generates the feature vector of the image.
	\item \textbf{Pattern searching}: Search and match the feature vector to the prebuilt tree database to get the starID of the reference star.
\end{itemize}

% Figure 3.7
\ntuepsfig[width=\textwidth]{3_7}{Star tracking algorithm submodules partitioned.}

\noindent After partitioning, all submodules are implemented on the Processing system side to examine the runtime of each submodules. The result of profiling stage in Figure~\ref{fig:3_8}. \\

% Figure 3.8
\ntuepsfig[width=\textwidth]{3_8}{Profiling result.}

% Table 3.1
\noindent Table~\ref{tab:profiling}.

\begin{ntutab}{|c|c|}{profiling}{Module Profiling Result}
	\hline
	\textbf{Modules} & \textbf{Runtime(nanoseconds)} \\
	\hline
	Centroiding & 17688 \\
	\hline
	Choose Reference Star & 54 \\
	\hline
	Find the star pattern & 30 \\
	\hline
	Pattern matching (with tree database) & 20 \\
	\hline
\end{ntutab}

\noindent Apparently, the most time-consuming submodule is the centroiding module. It can be explained because the centroiding stage is an image processing stage. Implementation of an image processing algorithm on general purpose processors is more costly and less effective than any other parallel processing approach like using a graphics processing unit (GPU), in this thesis, we design an IP core in the Programmable Logic side instead.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Section 3.3
\section{Module implementation}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% subsection 3.3.1
\subsection{Centroiding}

%%%%%%%%%
% subsubsection 3.3.1.1
\subsubsection{Thresholding}

In the first stage, the sky is captured by a Charge-coupled device(CCD) through lens then discretized into digital star images. In which, Each pixel is an 8-bit integer value which represents the intensity or brightness of a pixel(0 represent darkest pixel and 255 represents the brightest pixel). The star image is usually contaminated with noise as a result of dark current noise and non-star stellar object. Dark current noise arises from thermal energy within the silicon lattice. It can be represented as a background image generated by a certain period of exposure with the shutter closed\cite{MDP}. To eliminate the noise and separate star clusters from the background, we apply thresholding technique. The threshold level can be chosen by averaging all pixel intensities. The pixel which has a higher value than threshold level belongs to a star cluster while the pixel which has a lower value than the threshold belongs to the background. Figure~\ref{fig:3_10} shows how to separate star clusters from the background, the threshold, in this case, is 70.

\ntuepsfig[scale=0.7]{3_10}{Thresholding separates star cluster pixels and background pixels}

%%%%%%%%%
% subsubsection 3.3.1.2
\subsubsection{The connected-components problem in centroiding}

The raw image is contaminated with noises and other non-stellar objects. These noises can be canceled by setting a threshold level. If a pixel Intensity is less than the threshold level, we will set its value to 0(the background level) to differentiate from star cluster pattern. After all false star noises are canceled, the centroiding algorithm proceeds. \\

\noindent The technique to determine star centroids in a star image employs the connected component finding. The traditional approach of connected component finding is considering each pixel in the star image as a vertex in a graph. If a group of pixels belongs to a star cluster pattern, those vertices are connected. Therefore we can determine each independent star clusters by using graph traversing technique like Depth-First-Search (DFS) or Bread-First-Search (BFS). However, this submodule of the star tracking algorithm is implemented as an IP core by Hardware Description Language (HDL) which lack abilities to implement a recursive function or advanced data structure like Queue, Stack. \\

\noindent The emergence of FPGAs with enough capacity to perform complex image processing tasks also led to high-performance architectures for connected component labeling\cite{CCA}. Most of these architectures utilize the one-pass scan algorithm, because of the limited memory resources available on an FPGA. These types of connected component labeling architectures are able to process several image pixels in parallel, thereby enabling a high throughput at low processing latency to be achieved\cite{000384075100011n.d.}. \\

% Figure 3.9
\ntuepsfig[scale=0.2]{3_9}{Star clusters represented as a connected-components problem}

\noindent Figure~\ref{fig:3_9} represents the star centroid finding problem as finding a connected-components problem. The same star cluster pixels are neighboring to each other. To determine the centroid of each star cluster, we must label the pixels into their corresponding star clusters(groups) then calculate each star cluster centroid of each cluster. \\

%%%%%%%%%
% subsubsection 3.3.1.3
\subsubsection{The one-pass scan algorithm}

The one-pass scan algorithm is a connected component labeling approach which performs a scanning throughout the star image. A pixel in a star cluster will be put into an equivalent independent subset if two subsets having pixels connected to each other will be merged into one big set by the applying the following rules. \\

\noindent We maintain a disjoint set data structure when scanning performed if a pixel P is non-background, we consider its left and above pixels as in Figure~\ref{fig:3_11}. There are 3 cases:

\begin{enumerate}
	\item \textbf{Case 1 - Both are background pixels}: Label the pixel (P) with a new number. Create a new subset.
	\item \textbf{Case 2 - One(either pixel) is labeled, the other is not or both are labeled with the same number}: Label the pixel (P) with this number.
	\item \textbf{Case 3 - Both are labeled with different numbers}: Label the pixel (P) with any number from the left or above pixels, merge the set of the above pixel into the set of the left pixel.
\end{enumerate}

% Figure 3.11
\ntuepsfig[scale=0.2]{3_11}{Left and above pixels of the current considering pixel.}

\noindent An example of the one-pass scan algorithm applied to label 2-star clusters: In Figure~\ref{fig:3_12_2}, the first non-background pixel P has been scanned and comes into case 1(both left and above pixels are background pixels), so we create a new disjoint set(set 1) and add this pixel to set 1.

% Figure 3.10
\ntuepsfig[scale=0.35]{3_12_2}{one-pass scan algorithm applied to label 2-star clusters - 1}

\noindent Next, we scan the pixel in Figure~\ref{fig:3_12_3}, the above pixel is a background pixel, and its left pixel is in set 1. Therefore, we apply case 2 of the algorithm, set this pixel to the same set as its left pixel which is set 1.

\ntuepsfig[scale=0.35]{3_12_3}{one-pass scan algorithm applied to label 2-star clusters - 2}

\noindent After skipping background pixels, we consider the pixel shown in Figure~\ref{fig:3_12_4}, both above and left pixels of this pixel are background pixels(case 1). We create a new disjoint set(set 2) and add this pixel to set 2.

\ntuepsfig[scale=0.35]{3_12_4}{one-pass scan algorithm applied to label 2-star clusters - 3}

\noindent The next pixel in Figure~\ref{fig:3_12_5} belongs to case 3, so we merge 2 disjoint sets 1 and 2 and label this pixel as belonging to set 2.

\ntuepsfig[scale=0.35]{3_12_5}{one-pass scan algorithm applied to label 2-star clusters - 4}

\noindent At the final stage in Figure~\ref{fig:3_12_26}, we successfully find the 2 connected-component which are the pixels belongs to set 1,2, and the pixels belongs to set 3,4.

\ntuepsfig[scale=0.35]{3_12_26}{one-pass scan algorithm applied to label 2-star clusters - 5}

\noindent After detecting the star clusters, we calculate the centroids of each star cluster by equation~\ref{eq:3_1}

% Equation 3.1
\begin{equation}
	x = \frac{\displaystyle\sum_{i=1}^{n} \displaystyle\sum_{j=1}^{m} (i * I_{ij})} {\displaystyle\sum_{i=1}^{n} \displaystyle\sum_{j=1}^{m} I_{ij}}, y = \frac{\displaystyle\sum_{i=1}^{n} \displaystyle\sum_{j=1}^{m} (j * I_{ij})} {\displaystyle\sum_{i=1}^{n} \displaystyle\sum_{j=1}^{m} I_{ij}}
	\label{eq:3_1}
\end{equation}

\noindent The reason to choose the one-pass scan algorithm is that an image can not be loaded into the hardware processing unit as a matrix or tensor but as a pixel stream. We only know the previous pixels of the current receiving pixel.

%%%%%%%%%
% subsubsection 3.3.1.4
\subsubsection{IP core design for the one-pass scan algorithm}

\textbf{An image as streamed pixels} \\
\noindent From the one-pass scan algorithm, we need to design an IP core for faster hardware processing. The input of the module is a stream of pixels, and the output is the centroid coordinates of the stars in this image as shown in Figure~\ref{fig:3_18}.

\ntuepsfig[width=\textwidth]{3_18}{IP core design purpose}

\noindent In figure~\ref{fig:3_17}, the pixel coordinates(i,j) in 2D images would be represented by the stream order(k). The reason we need to have a converting framework is that we need to look up the above and left pixels of a considering pixel in the one-pass scan algorithm. \\

\ntuepsfig[width=\textwidth]{3_17}{Stream an image into a pixel stream}

\noindent The converting equations:
	$$k = i*ImgHeight + j$$
	$$i = k / ImgHeight$$
	$$j = k mod ImgHeight$$

\textbf{IP core submodules} \\

\noindent The centroiding again is partitioned into submodules for specific purposes as Figure~\ref{fig:3_19}.

\ntuepsfig[width=\textwidth]{3_19}{IP core submodules}

\begin{itemize}
	\item \textbf{stream processing}: The submodule task is to process the one-pass scan algorithm after receiving a pixel from the stream. The submodule also in responsibility of maintaining and updating the labels and disjoint sets data structures stored in the BRAM. The pseudo codes of the implementation are shown in Figure~\ref{fig:3_20} and Figure~\ref{fig:3_21}
	\item \textbf{centroid calculating}: The submodule task is to calculate the centroid coordinates after the stream processing stage is completed based on Equation~\ref{eq:2_1}. The inputs of the centroid calculating submodule is the disjoint sets data structures. The pseudo codes of the implementation are shown in Figure~\ref{fig:3_22}
	\item \textbf{BRAM}: served as the memory for the IP core. Stored the temporal data structures like: labels and disjoint sets and the final results(star centroid list).
\end{itemize}

\ntuepsfig[scale=0.6]{3_20}{Get above and left pixel functions}

\ntuepsfig[scale=0.6]{3_21}{Stream processing submodule}

\ntuepsfig[scale=0.6]{3_22}{centroid calculating submodule}

\ntuepsfig[scale=0.6]{3_23}{The complete IP core module}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% subsection 3.3.2
\subsection{Choose the reference star}

Figure~\ref{fig:3_13} shows a basic star image which then will be processed through the “Choose the reference star” stage. The first Image in an example is a typical star image. The outer circle represents the FOV of the star Image, and the small blue dots represent the star clusters.

\ntuepsfig[scale=0.35]{3_13}{Distances from the centre of the image to all stars}

\noindent From the centre of the star Image, we calculate the distances from each star cluster to the centre by Euclidean distance as equation~\ref{eq:3_2}. The star which is nearest to the centre (have the minimum distance value) will be chosen as the reference star.

% Equation 3.2
\begin{equation}
	d_{centre\_to\_star} = \sqrt{(x_{star} - x_{centre})^2 + (y_{star} - y_{centre})^2}
	\label{eq:3_2}
\end{equation}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% subsection 3.3.3
\subsection{Find the star pattern}

After we have the reference star, the next stage is to generate the star pattern. The number of stars in the image is counted, and their distances to the reference star are calculated as equation~\ref{eq:3_3} to form a feature vector $f = \{N, D_1, D_2, D_3, … D_n\}$

% Equation 3.3
\begin{equation}
	d_{centroid\_to\_star} = \sqrt{(x_{star} - x_{centroid})^2 + (y_{star} - y_{centroid})^2}
	\label{eq:3_3}
\end{equation}

\ntuepsfig[scale=0.35]{3_14}{Distances from the reference star to its neighbors}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% subsection 3.3.4
\subsection{Pattern searching}

In the last stage, the feature vector is matched to the prebuilt tree pattern database. The feature vector from the “Generate feature vector stage” will be compared to the prebuilt tree structured star pattern database(SPD) to find the correct star cluster ID. Figure~\ref{fig:3_15} shows how a star vector is compared and match with the SPD. \\

\ntuepsfig[width=\textwidth]{3_15}{Star pattern matching}

\noindent In case of mismatching, a tolerance will be added to research for another star ID. This search can be performed parallel to increase the searching speed due to the specific tree structure of the prebuilt SPD as in Figure~\ref{fig:3_16}.

\ntuepsfig[width=\textwidth]{3_16}{Star pattern matching with tolerance}

### 2018-07-16 thesis/2_chapters/chap4.tex
Update 16/7/2018

% Chapter 4
\chapter{Experimental Results}
\label{chap:result}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Section 4.1
\section{Hardware design}

\subsection{Components and Design Flow}

The hardware components shown in Figure~\ref{fig:4_1} includes:
\begin{itemize}
    \item Processing system.
    \item Centroiding IP core.
    \item Direct Memory Access controlling system.
    \item BRAM
    \item Hardware timer
    \item Interrupt controller
\end{itemize}

% Figure 4.1
\ntuepsfig[width=\textwidth]{4_1}{Hardware design diagram}

\noindent \textbf{Data path} \\
\noindent The pixel data are streamed directly into memory by DMA module. The IP core is designed for centroiding processing the algorithm as soon as the first pixel data arrived. After the centroiding algorithm finishing, the IP core store the results of centroiding algorithm into BRAM and informs the PS by an interrupt signal. PS then takes the results from BRAM and process other stages. The data path is implemented through AXI. \\

\noindent \textbf{Control signals} \\
\noindent The PS and PL side communicate through an interrupt controller. The interrupt controller informs the PS if the centroiding algorithm or hardware timer has finished, informs the DMA controller if the memory is full, the DMA controller then flush the old data to free the memory. BRAM controller is a dual channel BRAM which is readable from PS side and writable from PL side. \\

% Figure 4.2
\ntuepsfig[width=\textwidth]{4_2}{Hardware design block}

\noindent The graph~\ref{fig:4_3} shows the percentage of hardware resources used over available resources from the zedboard. We still have more spare resources of the FPGA for other tasks.

% Table 4.1
\begin{ntutab}{|c|c|c|c|}{resource}{Hardware resource consumption}
    \hline
    \textbf{Resource} & \textbf{Used} & \textbf{Available} & \textbf{Percentage (\%)} \\
    \hline
    BRAM\_18K & 17 & 280 & 6.07 \\
    \hline
    DSP48E & 20 & 220 & 9.09 \\
    \hline
    FlipFlops & 9278 & 106400 & 8.72 \\
    \hline
    Lookup Tables & 13387 & 53200 & 25.16 \\
    \hline
\end{ntutab}

% Figure 4.3
\ntuepsfig[width=\textwidth]{4_3}{Hardware resource consumption}

\newpage \subsection{Power Analysis}

\begin{ntutab}{|c|c|}{environment}{Environment condition}
    \hline
    \textbf{Condition} & \textbf{value} \\
    \hline
    Ambient temperature &  \\
    \hline
    Airflow & 250 LFM \\
    \hline
    heat sink & medium \\
    \hline
    board temperature & $25.0^oC$ \\
    \hline
\end{ntutab}

\ntuepsfig[width=\textwidth]{power_sum}{Power consumption summary}

\ntuepsfig[width=\textwidth]{power}{Power consumption by components}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Section 4.2
\section{Runtime experiments}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Star data analysis}

\noindent The main factors affect the runtime of the designed system are:
\begin{itemize}
    \item Image resolution
    \item Number of stars in one image
    \item Star area (in pixels) of one star
\end{itemize}

The images simulated are based on the SSAO star catalog and the standard ESO star map. Randomized distribution false stars are added to each image. For each resolution dataset, we have 12530 simulated images. \\

% Figure 4.4
\ntuepsfig[scale=1.0]{4_4}{Number of stars in one image distribution}

% Figure 4.5
\ntuepsfig[scale=1.0]{4_5}{Star area distribution}

\noindent The algorithm runtime performance is then compared between the implementation run on the embedded processor and the application executed on software-hardware co-processing strategy.

%%%%%%%%%
% subsubsection 4.2.2.1
\newpage \subsection{512x512 dataset}

The star tracker is configured as Table~\ref{tab:4_2}

% Table 4.2
\begin{ntutab}{|c|c|}{4_2}{Star tracker configuration}
    \hline
    \textbf{Parameters} & \textbf{Value} \\
    \hline
    Field of View (FOV) & J2000 \\
    \hline
    Inertial frame & 8.0 degrees full cone \\
    \hline
    Visual magnitude threshold & 5.0 \\
    \hline
    Number of samples & 12530 \\
    \hline
\end{ntutab}

%%%
\textbf{Software runtime}

% Table 4.3
\begin{ntutab}{|c|c|c|}{4_3}{Software runtime}
    \hline
     & \textbf{Average} & \textbf{Worst case} \\
    \hline
    \textbf{Centroiding} & 17688 & 18061 \\
    \hline
    \textbf{Choosing Reference Star} & 54 & 105 \\
    \hline
    \textbf{Finding Star Pattern} & 30 & 109 \\
    \hline
    \textbf{Pattern Matching} & 83 & 155 \\
    \hline
\end{ntutab}

% Figure 4.6
\ntuepsfig[width=\textwidth]{4_6}{Software runtime}

\noindent The average runtime is 17855 us (about 17.86 ms)

%%%
\newpage
\noindent \textbf{Hardware – Software Co-processing runtime}

% Table 4.4
\begin{ntutab}{|c|c|c|}{4_4}{Hardware – Software Co-processing runtime}
    \hline
     & \textbf{Average} & \textbf{Worst case} \\
    \hline
    \textbf{IP core Initiation} & 6 & 6 \\
    \hline
    \textbf{DMA Data Streaming} & 2460 & 2485 \\
    \hline
    \textbf{Centroiding} & 3719 & 3806 \\
    \hline
    \textbf{Choosing Reference Star} & 54 & 145 \\
    \hline
    \textbf{Finding Star Pattern} & 30 & 109 \\
    \hline
    \textbf{Pattern Matching} & 83 & 155 \\
    \hline
\end{ntutab}

% Figure 4.7
\ntuepsfig[width=\textwidth]{4_7}{Software-Hardware co-processing runtime}

\noindent The average runtime is 6352 us(about 6.35 ms)

%%%%%%%%%
\newpage \subsection{1024x1024 dataset}

\noindent The images are captured by the star tracker SST-20S described by Table~\ref{tab:4_7}

% Table 4.7
\begin{ntutab}{|c|c|}{4_7}{Specifications of the SST-20S star tracker and the real image\cite{8374923}}
    \hline
    \textbf{Parameter} & Value \\
    \hline
    \textbf{Field of View (FOV)} & $15^o * 15^o$ \\
    \hline
    \textbf{Sensitivity (Mv)} & 6.3 \\
    \hline
    \textbf{Star catalog} & SAO J2000\cite{myers1997sky2000} \\
    \hline
    \textbf{Resolution (w * h)} & 1024 x 1024 pixels \\
    \hline
    \textbf{Pixel size ($\rho$)} & 13 µm \\
    \hline
    \textbf{Focal length (f)} & 50 mm \\
    \hline
    \textbf{Bits per pixel} & 8 \\
    \hline
    \textbf{Position accuracy} & 40 arcsec \\
    \hline
\end{ntutab}

\textbf{Software runtime}

% Table 4.5
\begin{ntutab}{|c|c|c|}{4_5}{Software runtime}
    \hline
     & \textbf{Average} & \textbf{Worst case} \\
    \hline
    \textbf{Centroiding} & 70527 & 70561 \\
    \hline
    \textbf{Choosing Reference Star} & 63 & 108 \\
    \hline
    \textbf{Finding Star Pattern} & 54 & 115 \\
    \hline
    \textbf{Pattern Matching} & 136 & 155 \\
    \hline
\end{ntutab}

% Figure 4.8
\ntuepsfig[width=\textwidth]{4_8}{Software runtime}

\noindent The average runtime is 70780 us (about 70.78 ms)

%%%
\newpage
\noindent \textbf{Hardware – Software Co-processing runtime}

% Table 4.6
\begin{ntutab}{|c|c|c|}{4_6}{Hardware – Software Co-processing runtime}
    \hline
     & \textbf{Average} & \textbf{Worst case} \\
    \hline
    \textbf{IP core Initiation} & 6 & 6 \\
    \hline
    \textbf{DMA Data Streaming} & 9834 & 9838 \\
    \hline
    \textbf{Centroiding} & 3543 & 3598 \\
    \hline
    \textbf{Choosing Reference Star} & 63 & 108 \\
    \hline
    \textbf{Finding Star Pattern} & 54 & 115 \\
    \hline
    \textbf{Pattern Matching} & 136 & 155 \\
    \hline
\end{ntutab}

% Figure 4.9
\ntuepsfig[width=\textwidth]{4_9}{Hardware – Software Co-processing runtime}

\noindent The average runtime is 13636 us (about 13.64 ms)

%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% subsection 4.2.3
\newpage \subsection{Runtime Comparison}

\begin{ntutab}{|c|c|c|}{4_7}{Runtime comparison}
    \hline
     & \textbf{Average(ms)} & \textbf{Worst case(ms)} \\
    \hline
    \textbf{Liebe method} & 190.6 & 304.7 \\
    \hline
    \textbf{Geometric voting method SW} & 958.4 & 1044.7 \\
    \hline
    \textbf{Pyramid method SW} & 352.3 & 576.6 \\
    \hline
    \textbf{Proposed method SW} & 70.8 & 70.9 \\
    \hline
    \textbf{Proposed method SW-HW coprocessing} & 13.6 & 13.8 \\
    \hline
\end{ntutab}

\ntuepsfig[width=\textwidth]{4_10}{Runtime comparison}

### 2018-07-16 thesis/2_chapters/chap5.tex
Update 16/7/2018

% Chapter 5
\chapter{Conclusion and Future Works}
\label{chap:conclusion}

\section{Summary}

The purpose of this research topic is to implement a system evaluating a star tracking algorithm proposed by Mr. Minh Duc Pham\cite{MDP,edselc.2-52.0-8487677997120120101,edseee.655799920130101}, my senior and an ex post-graduated NTU student. In my thesis, I have summarized three traditional methods and one state-of-the-art star tracking method proposed in the literature review section. Then in the Hardware and Software Co-processing – Implementation of the Algorithm section, I introduced the hardware system, deeply analyze the algorithm. I also proposed an adaptive algorithm based on the proposed algorithm that is suitable for the software-hardware co-processing implementation in the system. In the final section Experimental Results, I suggested my hardware architecture design for this project, carry out some experiments to evaluate the implementation and their results. \\

\noindent All of my work includes the simulation image generator, image datasets, hardware IP core design, system architecture, software algorithms and source code, results of the experiments, quick documentations are dedicated in this repository: https://github.com/dangkhoadl/Master-Thesis-Star-Tracking-System

\section{Conclusion}

\section{Future Works}

### 2018-07-16 CodesForThesis/ConnectedComponentLabeling_SW/CCLabeling4.cpp

@@ -1,0 +1,231 @@
+
+#include <cstdio>
+#include <vector>
+#include <iostream>
+using namespace std;
+
+/*******************************************************************************************/
+#define MAX_IMG_HEIGHT 1024
+#define MAX_IMG_WIDTH 1024
+#define MAXTHPIXEL 1024
+#define THRESHOLD 70
+#define MAX 999
+#define MAX_STAR_DATA_SIZE 40
+#define MAX_SET_SIZE 40
+#define MAX_CENTROID_DATA 40
+
+unsigned Image[MAXTHPIXEL];
+unsigned mark[MAXTHPIXEL];
+unsigned lbImage[MAXTHPIXEL];
+
+unsigned set[MAX_SET_SIZE];
+
+bool status[MAX_STAR_DATA_SIZE];
+unsigned totalIntensity[MAX_STAR_DATA_SIZE];
+unsigned x[MAX_STAR_DATA_SIZE];
+unsigned y[MAX_STAR_DATA_SIZE];
+
+/*********************************** TEMP ********************************************************/
+void readImage(FILE *&fileIn, unsigned streamImage[MAX_IMG_HEIGHT * MAX_IMG_WIDTH], unsigned imgHeight, unsigned imgWidth) {
+	for (unsigned i = 0; i < imgHeight; ++i) for (unsigned j = 0; j < imgWidth; ++j) {
+		fscanf(fileIn, "%d", &streamImage[i*imgHeight + j]);
+	}
+}
+
+void printResult(FILE *fileOut, unsigned centroidDataCount, unsigned X[MAX_CENTROID_DATA], unsigned Y[MAX_CENTROID_DATA]) {
+	for (unsigned i = 0; i < centroidDataCount; ++i) {
+		fprintf(fileOut, "Star[%d]: x = %d, y = %d\n", i + 1, X[i], Y[i]);
+	}
+}
+/**************************************** TEMP ***************************************************************/
+unsigned find(unsigned id) {
+	int temp;
+	temp = id;
+	while (temp != set[temp]) {
+#pragma HLS PIPELINE
+		temp = set[temp];
+	}
+	return temp;
+}
+
+int binarySearch(unsigned data, unsigned pixNum) {
+	int left = 0;
+	int right = pixNum - 1;
+	int mid = 0;
+	while (true) {
+#pragma HLS PIPELINE
+		mid = left + (right - left) / 2;
[…]

### 2018-07-16 CodesForThesis/ConnectedComponentLabeling_SW/CCLabeling4_INT.cpp

@@ -1,0 +1,236 @@
+#ifdef _MSC_VER
+#define _CRT_SECURE_NO_WARNINGS
+#endif
+
+#define DEBUG
+
+#include <cstdio>
+#include <vector>
+#include <iostream>
+using namespace std;
+
+/*******************************************************************************************/
+#define MAX_IMG_HEIGHT 1024
+#define MAX_IMG_WIDTH 1024
+#define MAXTHPIXEL 1024
+#define THRESHOLD 70
+#define MAX 999
+#define MAX_STAR_DATA_SIZE 40
+#define MAX_SET_SIZE 40
+#define MAX_CENTROID_DATA 40
+
+int Image[MAXTHPIXEL];
+int mark[MAXTHPIXEL];
+int lbImage[MAXTHPIXEL];
+
+int set[MAX_SET_SIZE];
+
+bool status[MAX_STAR_DATA_SIZE];
+int totalIntensity[MAX_STAR_DATA_SIZE];
+int x[MAX_STAR_DATA_SIZE];
+int y[MAX_STAR_DATA_SIZE];
+
+/*********************************** TEMP ********************************************************/
+void readImage(FILE *&fileIn, int streamImage[MAX_IMG_HEIGHT * MAX_IMG_WIDTH], int imgHeight, int imgWidth) {
+	for (int i = 0; i < imgHeight; ++i) for (int j = 0; j < imgWidth; ++j) {
+		fscanf(fileIn, "%d", &streamImage[i*imgHeight + j]);
+	}
+}
+
+void printResult(FILE *fileOut, int centroidDataCount, int X[MAX_CENTROID_DATA], int Y[MAX_CENTROID_DATA]) {
+	for (int i = 0; i < centroidDataCount; ++i) {
+		fprintf(fileOut, "Star[%d]: x = %d, y = %d\n", i + 1, X[i], Y[i]);
+	}
+}
+/**************************************** TEMP ***************************************************************/
+int find(int id) {
+	int temp;
+	temp = id;
+	while (temp != set[temp]) {
+#pragma HLS PIPELINE
+		temp = set[temp];
+	}
+	return temp;
+}
+
+int binarySearch(int data, int pixNum) {
+	int left = 0;
+	int right = pixNum - 1;
+	int mid = 0;
+	while (true) {
+#pragma HLS PIPELINE
+		mid = left + (right - left) / 2;
+		if (data == mark[mid]) {
[…]

### 2018-07-16 CodesForThesis/ConnectedComponentLabeling_SW/multiIMGtoMats.py

@@ -1,0 +1,55 @@
+#!/usr/bin/python3
+import sys
+sys.stdout = open('output.out', 'w')
+
+IMG_HEIGHT = 1024
+IMG_WIDTH = 1024
+path = 'D:\\Dropbox\\DangKhoa\\CEE_Cache\\GitHub\\StarTrackingProject\\StarSimulation_Matlab\\TestPattern\\'
+
+a = 1
+a_ = 1
+b = 1
+b_ = 1
+
+def readIMG(i, j):
+    '''
+    IMG_i_j
+    '''
+    Image = []
+    with open(path + 'IMG_{}_{}.bin'.format(i, j), 'r') as inFile:
+        for line in inFile:
+            [Image.append(e) for e in [int(float(x)) for x in line.split()]]
+    return Image
+
+
+def writeOutput(i, j):
+    img = readIMG(i, j)
+    with open('Image.h', 'a') as outFile:
+        outFile.write('\t{')
+        for index, e in enumerate(img):
+            outFile.write('{}, '.format(e)) if index != len(img)-1 else outFile.write('{}'.format(e))
+        outFile.write('},\n') if (i != a_ or j != b_)  else outFile.write('}\n};')
+
+
+def main():
+    with open('Image.h', 'w') as outFile:
+        total_files = (a_- a + 1) * (b_ - b + 1)
+        outFile.write('#ifndef IMAGE_H_\n')
+        outFile.write('#define IMAGE_H_\n')
+        outFile.write('#define IMG_HEIGHT {}\n'.format(IMG_HEIGHT))
+        outFile.write('#define IMG_WIDTH {}\n'.format(IMG_WIDTH))
+        outFile.write('#define IMG_NUM {}\n'.format(total_files))
+        outFile.write('unsigned inputIMGs[{}][IMG_HEIGHT * IMG_WIDTH] = {{\n'.format(total_files))
+
+    # Read all images
+    for i in range(a, a_+1):
+        for j in range(b, b_+1):
+            writeOutput(i, j)
+
+    with open('Image.h', 'a') as outFile:
+        outFile.write('\n\n#endif\n')
+
+
+if __name__ == "__main__":
+    main()
+

### 2018-07-16 CodesForThesis/ConnectedComponents/main.cpp

@@ -1,0 +1,219 @@
+
+#include <cstdio>
+#include <vector>
+#include <cmath>
+#include <iostream>
+using namespace std;
+
+/*******************************************************************************************/
+#define MAX_IMG_HEIGHT 512
+#define MAX_IMG_WIDTH 512
+#define MAXTHPIXEL 512
+#define THRESHOLD 70
+#define MAX 999
+#define MAX_STAR_DATA_SIZE 40
+#define MAX_SET_SIZE 40
+#define MAX_CENTROID_DATA 40
+
+int Image[MAXTHPIXEL];
+int mark[MAXTHPIXEL];
+int lbImage[MAXTHPIXEL];
+
+int set[MAX_SET_SIZE];
+
+bool status[MAX_STAR_DATA_SIZE];
+int totalIntensity[MAX_STAR_DATA_SIZE];
+int x[MAX_STAR_DATA_SIZE];
+int y[MAX_STAR_DATA_SIZE];
+
+/*********************************** TEMP ********************************************************/
+void readImage(FILE *&fileIn, int streamImage[MAX_IMG_HEIGHT * MAX_IMG_WIDTH], int imgHeight, int imgWidth) {
+    for (int i = 0; i < imgHeight; ++i) for (int j = 0; j < imgWidth; ++j) {
+        fscanf(fileIn, "%d", &streamImage[i*imgHeight + j]);
+    }
+}
+
+void printResult(FILE *fileOut, int centroidDataCount, int X[MAX_CENTROID_DATA], int Y[MAX_CENTROID_DATA]) {
+    for (int i = 0; i < centroidDataCount; ++i) {
+        fprintf(fileOut, "Star[%d]: x = %d, y = %d\n", i + 1, X[i], Y[i]);
+    }
+}
+/**************************************** TEMP ***************************************************************/
+int find(int id) {
+    int temp;
+    temp = id;
+    while (temp != set[temp]) {
+        temp = set[temp];
+    }
+    return temp;
+}
+
+int binarySearch(int data, int pixNum) {
+    int left = 0;
+    int right = pixNum - 1;
+    int mid = 0;
+    while (true) {
+        mid = left + (right - left) / 2;
+        if (data == mark[mid]) {
+            return mid;
+        }
+
+        if (left > right || data < mark[left] || data > mark[right])
+            return -1;
+
+        if (data > mark[mid])
+            left = mid + 1;
+        else
+            right = mid - 1;
+    }
+    return -1;
+}
+
[…]

### 2018-07-16 CodesForThesis/ProposedAlgo_Cpp/Catalogs/catalogGen.py

@@ -1,170 +1,0 @@
-#!/usr/bin/python3
-import sys
-sys.stdout = open('output.out', 'w')
-
-
-# Parameters
-IMG_HEIGHT = 512
-IMG_WIDTH = 512
-PIXEL_SIZE = 7e-3
-FOV = 20
-
-SAOCATALOGIN = "SKY2000_Magnitude5_doublestar.txt"
-CATALOGOUT = "proposedAlgo_catalog.txt"
-TREELEVEL = 3
-
-
-import pandas as pd
-def readCatalog():
-    f = open(SAOCATALOGIN, 'r')
-    data = {
-        'SKYMAP_No' : [],
-        'star_RA' : [],
-        'star_DEC' : [],
-        'star_MAG' : []
-    }
-    for line in f.readlines():
-        col = line.split()
-        data['SKYMAP_No'].append(col[0])
-        data['star_RA'].append(col[1])
-        data['star_DEC'].append(col[2])
-        data['star_MAG'].append(col[3])
-    f.close()
-    return pd.DataFrame(data)
-
-
-import sympy as sp
-import numpy as np
-import math
-def rad(deg):
-    return float(deg) * math.pi / 180.0 
-
-
-def Convert_Axis_2_AttitudeMatrix(RA,DEC):
-    axis = [sp.cos(rad(DEC))*sp.cos(rad(RA)), sp.cos(rad(DEC))*sp.sin(rad(RA)),  sp.sin(rad(DEC))]
-
-    # Calculate rotation matrix
-    # The z axis of camera
-    c2 = np.array(axis);
-
-    # The x axis of the camera
-    c0x = c2[1]/math.sqrt((c2[0]**2)+(c2[1]**2))
-    c0y = -c2[0]/math.sqrt((c2[0]**2)+(c2[1]**2))
-    c0z = 0
-    c0 = np.array([c0x, c0y, c0z])
-
-    # The y axis of the cam = z cross x
-    c1 = np.cross(c2, c0)
-
-    return [c0,c1,c2]
-
-
-# Si is coordiante of star in Earth reference frame, 
-# the 3 column are X, Y,and Z
-def buildSi():
-    data = []
-    for (index,entry) in SAOCatalog.iterrows():
-        DEC = entry['star_DEC']
-        RA = entry['star_RA']
-        # Convert RA, and DEC into ECI unit vector
[…]

### 2018-07-16 CodesForThesis/ProposedAlgo_Cpp/Libs/Algorithm.cpp

@@ -1,37 +1,0 @@
-#include "Algorithm.h"
-
-StarPattern getStarPattern(std::vector<Star> &starList,int FOV) {
-    StarPattern starPattern;
-
-    //Calculate the star distance to starRef
-    Star starRef = starList.front();
-    std::pop_heap(starList.begin(), starList.end(), [](const Star &a, const Star &b) {return a.starDistance2Centre > b.starDistance2Centre; });
-    starList.pop_back();
-
-    for (int i = 0; i < starList.size(); ++i) {
-        starList[i].starDistance2StarRef = sqrt((starRef.X - starList[i].X)*(starRef.X - starList[i].X) + (starRef.Y - starList[i].Y)*(starRef.Y - starList[i].Y));
-    }
-    std::make_heap(starList.begin(), starList.end(), [](const Star &a, const Star &b) {return a.starDistance2StarRef > b.starDistance2StarRef; });
-
-    //Traverse through the sorted list to get star pattern
-    int count = 0;
-    float distance[3] = { 0,0,0 };
-
-    while (!starList.empty()) {
-        if (starList.front().starDistance2StarRef > FOV / 2) break;
-        if (count < 3) distance[count] = starList.front().starDistance2StarRef;
-
-        std::pop_heap(starList.begin(), starList.end(), [](const Star &a, const Star &b) {return a.starDistance2StarRef > b.starDistance2StarRef; });
-        starList.pop_back();
-        ++count;
-    }
-        
-    //Update Starpattern
-    starPattern.N = count;
-    starPattern.d1 = distance[0];
-    starPattern.d2 = distance[1];
-    starPattern.d3 = distance[2];
-
-    return starPattern;
-}
-

### 2018-07-16 CodesForThesis/ProposedAlgo_Cpp/Libs/Algorithm.h

@@ -1,17 +1,0 @@
-#pragma once
-
-#include <vector>
-#include <iostream>
-#include <algorithm>
-#include "Centroider.h"
-
-struct StarPattern {
-    int N;
-    int d1;
-    int d2;
-    int d3;
-    int starID;
-    float sqError;
-};
-
-StarPattern getStarPattern(std::vector<Star> &starList, int FOV);

### 2018-07-16 CodesForThesis/ProposedAlgo_Cpp/Libs/Centroider.cpp

@@ -1,98 +1,0 @@
-#include "Centroider.h"
-
-std::vector<Star> centroider(const std::vector<std::vector<int>> &IMG, int levelThreshold, int areaThreshold, int &numberOfStar) {
-    //Declare refIMG 
-    int img_height = IMG.size();
-    int img_width = IMG[0].size();
-    std::vector<std::vector<bool>> refIMG(img_height, std::vector<bool>(img_width, 0));
-
-    //Declare variables
-    int count = 0;
-    //Init the Star Sorted Linked List
-    std::vector<Star> list;
-
-    //scan and perform search
-    for (int i = 0; i < img_height; i++) {
-        for (int j = 0; j < img_width; j++) {
-            //If this pixel is not checked && > levelThreshold
-            if (!refIMG[i][j] && IMG[i][j] > levelThreshold) {
-                //Declare stardata
-                StarData *data = new StarData;
-                data->sumOfXproduct = 0;
-                data->sumOfYproduct = 0;
-                data->sum = 0;
-                data->area = 0;
-
-                //Perform a recursive search
-                search(i, j, img_height, img_width, levelThreshold, data, IMG, refIMG);
-
-                //Create and Add star to a Sorted Linked List
-                insert2List(list, img_height, img_width, data->sumOfXproduct / data->sum, data->sumOfYproduct / data->sum, data->area);
-                ++count;
-
-                //Free stardata
-                delete data;
-            }
-        }
-    }
-
-    //Update number Of Stars
-    numberOfStar = count;
-
-    //return the list
-    return list;
-}
-
-void search(int pixelHeight, int pixelWidth, int img_height, int img_width, int levelThreshold, StarData *data, const std::vector<std::vector<int>> &IMG, std::vector<std::vector<bool>> &refIMG) {
-    //Search pattern of 8 neighbor pixels
-    //     6   7   0
-    //     5   *   1
-    //     4   3   2
-    int dHeight[8] = { -1, 0, 1, 1, 1, 0, -1, -1 };
-    int dWidth[8] = { 1, 1, 1, 0, -1, -1, -1, 0 };
-
-    //Mark this Pixel as checked
-    refIMG[pixelHeight][pixelWidth] = true;
-
-    //Update stardata
-    /* IMPORTANT:
-        pixelHeight <----SWAP----> pixelWidth if the IMG is transpose or not
[…]

### 2018-07-16 CodesForThesis/ProposedAlgo_Cpp/Libs/Centroider.h

@@ -1,24 +1,0 @@
-#pragma once
-#include <vector>
-#include <iostream>
-#include <cmath>
-#include <algorithm>
-
-struct Star {
-    int X;
-    int Y;
-    int area;
-    float starDistance2Centre;
-    float starDistance2StarRef;
-};
-
-struct StarData {
-    int sumOfXproduct;
-    int sumOfYproduct;
-    int sum;
-    int area;
-};
-
-std::vector<Star> centroider(const std::vector<std::vector<int>> &IMG, int levelThreshold,int areaThreshold, int &numberOfStar);
-void search(int pixelHeight, int pixelWidth, int img_height, int img_width, int levelThreshold, StarData *data, const std::vector<std::vector<int>> &IMG, std::vector<std::vector<bool>> &refIMG);
-void insert2List(std::vector<Star> &list, int img_height, int img_width, int XCoordinate, int YCoordinate, int starArea);

### 2018-07-16 CodesForThesis/ProposedAlgo_Cpp/Libs/InOut.cpp

@@ -1,15 +1,0 @@
-#include "InOut.h"
-
-void readIMG(std::ifstream &FileIn, std::vector<std::vector<int>> &IMG) {
-	double pixel;
-	int img_height = IMG.size();
-	int img_width = IMG[0].size();
-	for (int i = 0; i < img_height; i++) {
-		for (int j = 0; j < img_width; j++) {
-			FileIn >> pixel;
-			IMG[i][j] = (int)pixel;
-			//FileIn.seekg(1, SEEK_CUR); // skip " "
-		}
-	}
-	FileIn.close();
-}

### 2018-07-16 CodesForThesis/ProposedAlgo_Cpp/Libs/InOut.h

@@ -1,7 +1,0 @@
-#pragma once
-#include <iostream>
-#include <vector>
-#include <string>
-#include <fstream>
-
-void readIMG(std::ifstream &FileIn, std::vector<std::vector<int>> &IMG);

### 2018-07-16 CodesForThesis/ProposedAlgo_Cpp/Libs/PatternMatching.h

@@ -1,171 +1,0 @@
-#include <iostream>
-#include <vector>
-#include <memory>
-#include <algorithm>
-#include <fstream>
-#include <sstream>
-
-/**************************************** DATASTRUCT ***************************************************/
-struct dataStruct {
-    int N;
-    int d1;
-    int d2;
-    int d3;
-    int id;
-};
-
-/***************************************** READ CATALOG **************************************************/
-std::vector<dataStruct> readCatalog(std::ifstream &fileIn) {
-    std::vector<dataStruct> database;
-    std::string line;
-    while (std::getline(fileIn, line)) {
-        std::stringstream lineStream(line);
-        int Nt, d1t, d2t, d3t, idt;
-        lineStream >> Nt >> d1t >> d2t >> d3t >> idt;
-        database.push_back({ Nt,d1t,d2t,d3t,idt });
-    }
-    return database;
-}
-
-/***************************************** lINEAR SEARCH **************************************************/
-int searchLin(std::vector<dataStruct> database, int tor, int N, int D1, int D2, int D3) {
-    int error = 999;
-    int cid = -1;
-    for (int i = 0; i < database.size(); ++i) {
-        if (database[i].N >= N - tor && database[i].N <= N + tor &&
-            database[i].d1 >= D1 - tor && database[i].d1 <= D1 + tor &&
-            database[i].d2 >= D2 - tor && database[i].d2 <= D2 + tor &&
-            database[i].d3 >= D3 - tor && database[i].d3 <= D3 + tor)
-        {
-            int temp = (N - database[i].N) * (N - database[i].N) + (D1 - database[i].d1) * (D1 - database[i].d1) + (D2 - database[i].d2) * (D2 - database[i].d2) + (D3 - database[i].d3) * (D3 - database[i].d3);
-            if (error > temp) {
-                error = temp;
-                cid = database[i].id;
-            }
-        }
-    }
-    return cid;
-}
-
-/******************************************* TREE SEARCH ************************************************/
-class Node;
-typedef std::shared_ptr<Node> NodePtr;
-class Node {
-public:
-    int key_;
-    NodePtr parent_;
-    std::vector<NodePtr> children_;
-
-    struct CompareKey {
-        CompareKey(const int &val) : val_(val) {}
-        bool operator()(const NodePtr &element) const {
-            return val_ == element->key_;
-        }
-    private:
[…]

### 2018-07-16 CodesForThesis/ProposedAlgo_Cpp/script.py

@@ -1,44 +1,0 @@
-#!/usr/bin/python3
-import sys
-sys.stdout = open('report.txt', 'w')
-
-
-PROGRAM = ".//starTracking.exe"
-
-
-def getArg(i,j):
-    return "Inputs//IMG_" + str(i) + '_' + str(j) + ".bin"
-
-
-import timeit
-import subprocess
-def getOutput(program, arg):
-    results = []
-
-    start = timeit.default_timer()
-    proc = subprocess.Popen([program,arg],stdout=subprocess.PIPE)
-    stop = timeit.default_timer()
-
-    while True:
-        line = proc.stdout.readline()
-        if line != b'':
-            line = str(line)
-            line = line[line.index("\'") + 1:line.rindex("\\")]
-            results.append(int(line))
-        else:
-            break
-    return (results,stop-start)
-
-import time
-if __name__ == '__main__':
-    res = []
-    cnt = 0
-    for i in range(1,71,1):
-        for j in range(179):
-            cnt += 1
-            (results, runtime) = getOutput(PROGRAM,getArg(i,j))
-            # time.sleep(1)
-            res.append([results[0], runtime])
-
-    for r in res:
-        print(r[0], r[1])

### 2018-07-16 CodesForThesis/ProposedAlgo_Cpp/starTracking.cpp

@@ -1,106 +1,0 @@
-﻿
-#include "./Libs/InOut.h"
-#include "./Libs/Centroider.h"
-#include "./Libs/Algorithm.h"
-#include "./Libs/PatternMatching.h"
-
-//Initialize camera parameter
-#define img_height 512
-#define img_width 512
-
-//#define pixelsize 7e-3
-#define FOV 256
-//sensor magnitude threshold 5M
-
-//SPD parameters
-#define TSIZE 14
-#define NUMBEROFENTRIES 1500
-
-//Centroiding parameter
-#define THRESHOLDINGLEVEL 77 
-#define AREATHRESHOLD 1
-
-// Database
-#define CATALOG "./Catalogs/proposedAlgo_catalog2.txt"
-
-using namespace std;
-
-// #define DEBUG
-
-#ifdef DEBUG
-#include <bits/stdc++.h>
-#define sz(a) (int)(a).size()
-#define REP(a) for(int iii=0, _a=(a); iii < _a; ++iii)
-#define FOR(iii,start,end) for(int iii=(start), _end=(end); iii < _end; ++iii)               // [start, end)
-#define FORD(iii,start,end) for(int iii=(start), _end=(end); iii > _end; --iii)              // [start, end)
-#define for_it(A) for(auto it = (A.begin()), _end(A.end()); it != _end; ++it)
-#define quit exit(0);
-#define nl cerr<<endl;
-template<typename T,typename TT> inline ostream& operator<<(ostream &s,pair<T,TT> t) {return s<<"("<<t.first<<","<<t.second<<")";}
-#define pr(args...) { vector<string> _v = split(#args, ','); err(_v.begin(), args); cerr << endl;}
-vector<string> split(const string& s, char c) {vector<string> v;stringstream ssss_(s);string x;while(getline(ssss_, x, c)) {v.emplace_back(x);}return move(v);}
-void err(vector<string>::iterator it) {}
-template<typename T, typename... Args> void err(vector<string>::iterator it, T a, Args... args) {cerr << it -> substr((*it)[0] == ' ', it->length()) << " = " << a << ", ";err(++it, args...);}
-#define pra(A, start, end) {cerr << #A << '[' << start << ',' << (end - 1) << "] = ";FOR(_,start, end) cerr << A[_] << ' '; cerr << endl; }
[…]

### 2018-07-16 CodesForThesis/pseudocode.py

@@ -1,0 +1,68 @@
+
+
+
+def get_above_pixel(k):
+	return k - imgHeight + (k mod imgHeight)
+
+
+def get_left_pixel(k):
+	return k + (k mod imgHeight) - 1
+
+
+def stream_processing(current_pixel, disjoint_sets, labels):
+	# get all pixel postions
+	above_pixel = get_above_pixel(current_pixel)
+	left_pixel = get_left_pixel(current_pixel)
+
+	# Apply the one-pass scan algorithm
+	## Case 1: Both are background pixels
+	if (above_pixel == BACKGROUND) and (left_pixel == BACKGROUND):
+		cur_label = labels.create_new_label()
+		current_pixel.set_label(cur_label)
+		disjoint_sets.create(cur_label)
+
+	## Case 2:  One(either pixel) is labeled, the other is not or
+	##			both are labeled with the same number
+	else if isLabeled(above_pixel) or isLabeled(left_pixel) or
+			get_label(above_pixel) == get_label(left_pixel):
+		cur_label = labels.get_label(above_pixel)
+		current_pixel.set_label(cur_label)
+
+	## Case 3:  Both are labeled with different numbers
+	else if get_label(above_pixel) != get_label(left_pixel):
+		above_pixel_label = labels.get_label(above_pixel)
+		left_pixel_label = labels.get_label(left_pixel)
+		cur_label = above_pixel_label
+		current_pixel.set_label(cur_label)
+		disjoint_sets.join(above_pixel_label, left_pixel_label)
+
+
+def calculate_centroid():
+	centroidList = list()
+	for each set in disjoint_sets:
+		total_intensity = 0
+		(x,y) = (0,0)
+		for each pixel in set:
+			x += pixel.x() * pixel.Intensity()
+			y += pixel.y() * pixel.Intensity()
+			total_intensity += pixel.Intensity()
+		X = x / total_intensity
+		Y = y / total_intensity
+		centroidList.add(X,Y)
+
+	return centroidList
+
+def centroiding():
+	# Initate
+	disjoint_sets.Initiate()
+	labels.Initiate()
+
+	# submodule: Process stream
+	while(receiving_input_pixel() and not timeout()):
+		current_pixel = receiving_input_pixel()
+		stream_processing(current_pixel, disjoint_sets, labels)
+
+	# submodule: calculate centroids
+	centroidList = calculate_centroid(disjoint_sets)
+
+	return centroidList

### 2018-07-16 ConnectedComponentLabeling_SDK/CCLabelling/src/AxiTimerHelper.cpp

@@ -1,56 +1,0 @@
-/*
- * AxiTimerHelper.cpp
- *
- *  Created on: 06/07/2015
- *      Author: laraujo
- */
-
-#include "AxiTimerHelper.h"
-
-AxiTimerHelper::AxiTimerHelper() {
-	// Initialize the timer hardware...
-	 XTmrCtr_Initialize(&m_AxiTimer, XPAR_TMRCTR_0_DEVICE_ID);
-
-	 //XTmrCtr_SetOptions(&m_AxiTimer, 0, XTC_AUTO_RELOAD_OPTION);
-
-	 // Get the clock period in seconds
-	 m_timerClockFreq = (double) XPAR_AXI_TIMER_0_CLOCK_FREQ_HZ;
-	 m_clockPeriodSeconds = (double)1/m_timerClockFreq;
-
-}
-
-AxiTimerHelper::~AxiTimerHelper() {
-	// TODO Auto-generated destructor stub
-}
-
-unsigned int AxiTimerHelper::getElapsedTicks() {
-	return m_tickCounter2 - m_tickCounter1;
-}
-
-unsigned int AxiTimerHelper::startTimer() {
-	// Start timer 0 (There are two, but depends how you configured in vivado)
-	XTmrCtr_Reset(&m_AxiTimer,0);
-	m_tickCounter1 =  XTmrCtr_GetValue(&m_AxiTimer, 0);
-	XTmrCtr_Start(&m_AxiTimer, 0);
-	return m_tickCounter1;
-}
-
-unsigned int AxiTimerHelper::stopTimer() {
-	XTmrCtr_Stop(&m_AxiTimer, 0);
-	m_tickCounter2 =  XTmrCtr_GetValue(&m_AxiTimer, 0);
-	return m_tickCounter2 - m_tickCounter1;
-}
-
-double AxiTimerHelper::getElapsedTimerInSeconds() {
-	double elapsedTimeInSeconds = (double)(m_tickCounter2 - m_tickCounter1) * m_clockPeriodSeconds;
-	return elapsedTimeInSeconds;
-}
-
-double AxiTimerHelper::getClockPeriod() {
-	return m_clockPeriodSeconds;
-}
-
-double AxiTimerHelper::getTimerClockFreq() {
-	return m_timerClockFreq;
-}
-

### 2018-07-16 ConnectedComponentLabeling_SDK/CCLabelling/src/main.cc

@@ -1,287 +1,0 @@
-#include <stdio.h>
-#include <math.h>
-#include <xparameters.h>
-#include "xCCLabel.h"
-#include "xaxidma.h"
-#include "platform.h"
-#include "AxiTimerHelper.h"
-#include "Image.h"
-
-unsigned int float_to_u32(float val) {
-	unsigned int result;
-	union float_bytes {
-		float v;
-		unsigned char bytes[4];
-	} data;
-
-	data.v = val;
-	result = (data.bytes[3] << 24) + (data.bytes[2] << 16) + (data.bytes[1] << 8) + (data.bytes[0]);
-	return result;
-}
-
-/********************************************** HARDWARE ****************************************************************/
-XCclabel cCLabel;
-XCclabel_Config *cCLabel_cfg;
-XAxiDma axiDMA;
-XAxiDma_Config *axiDMA_cfg;
-
-//BRAM addresses
-int *XHW = (int *)0x40000000;
-int *YHW = (int *)0x40010000;
-
-//DMA addresses
-#define MEM_BASE_ADDR 0x01000000
-#define TX_BUFFER_BASE (MEM_BASE_ADDR + 0x00100000)
-
-
-void init_core() {
-	int status = 0;
-
-	// init CC core
-	cCLabel_cfg = XCclabel_LookupConfig(XPAR_CCLABEL_0_DEVICE_ID);
-	if (!cCLabel_cfg) {
-		xil_printf("Error loading config\r\n");
-	}
-	else {
-		status = XCclabel_CfgInitialize(&cCLabel,cCLabel_cfg);
-		if (status != XST_SUCCESS) {
-			xil_printf("Error initializing CC core\r\n");
-		}
-	}
-
-	//init DMA
-	axiDMA_cfg = XAxiDma_LookupConfig(XPAR_AXIDMA_0_DEVICE_ID);
-	if(axiDMA_cfg) {
-		status = XAxiDma_CfgInitialize(&axiDMA, axiDMA_cfg);
-		if(status != XST_SUCCESS) {
-			xil_printf("Error initializing DMA\r\n");
-		}
-	}
-
-	//Disable Interrupts
-	XAxiDma_IntrDisable(&axiDMA, XAXIDMA_IRQ_ALL_MASK, XAXIDMA_DEVICE_TO_DMA);
-	XAxiDma_IntrDisable(&axiDMA, XAXIDMA_IRQ_ALL_MASK, XAXIDMA_DMA_TO_DEVICE);
-}
-
-
[…]

### 2018-07-16 ConnectedComponentLabeling_SDK/CCLabelling_bsp/ps7_cortexa9_0/include/xparameters.h

@@ -1,602 +1,0 @@
-/* Definition for CPU ID */
-#define XPAR_CPU_ID 0
-
-/* Definitions for peripheral PS7_CORTEXA9_0 */
-#define XPAR_PS7_CORTEXA9_0_CPU_CLK_FREQ_HZ 666666687
-
-
-/******************************************************************/
-
-/* Canonical definitions for peripheral PS7_CORTEXA9_0 */
-#define XPAR_CPU_CORTEXA9_0_CPU_CLK_FREQ_HZ 666666687
-
-
-/******************************************************************/
-
-#include "xparameters_ps.h"
-
-#define STDIN_BASEADDRESS 0xE0001000
-#define STDOUT_BASEADDRESS 0xE0001000
-
-/******************************************************************/
-
-/* Definitions for driver AXIDMA */
-#define XPAR_XAXIDMA_NUM_INSTANCES 1
-
-/* Definitions for peripheral AXI_DMA_0 */
-#define XPAR_AXI_DMA_0_DEVICE_ID 0
-#define XPAR_AXI_DMA_0_BASEADDR 0x40400000
-#define XPAR_AXI_DMA_0_HIGHADDR 0x4040FFFF
-#define XPAR_AXI_DMA_0_SG_INCLUDE_STSCNTRL_STRM 0
-#define XPAR_AXI_DMA_0_INCLUDE_MM2S_DRE 1
-#define XPAR_AXI_DMA_0_INCLUDE_S2MM_DRE 0
-#define XPAR_AXI_DMA_0_INCLUDE_MM2S 1
-#define XPAR_AXI_DMA_0_INCLUDE_S2MM 0
-#define XPAR_AXI_DMA_0_M_AXI_MM2S_DATA_WIDTH 32
-#define XPAR_AXI_DMA_0_M_AXI_S2MM_DATA_WIDTH 32
-#define XPAR_AXI_DMA_0_INCLUDE_SG 0
-#define XPAR_AXI_DMA_0_ENABLE_MULTI_CHANNEL 0
-#define XPAR_AXI_DMA_0_NUM_MM2S_CHANNELS 1
-#define XPAR_AXI_DMA_0_NUM_S2MM_CHANNELS 1
[…]

### 2018-07-16 ConnectedComponentLabeling_SDK/CCLabelling_bsp/ps7_cortexa9_0/include/xtmrctr_i.h

@@ -1,79 +1,0 @@
-/******************************************************************************
-*
-* Copyright (C) 2002 - 2014 Xilinx, Inc.  All rights reserved.
-*
-* Permission is hereby granted, free of charge, to any person obtaining a copy
-* of this software and associated documentation files (the "Software"), to deal
-* in the Software without restriction, including without limitation the rights
-* to use, copy, modify, merge, publish, distribute, sublicense, and/or sell
-* copies of the Software, and to permit persons to whom the Software is
-* furnished to do so, subject to the following conditions:
-*
-* The above copyright notice and this permission notice shall be included in
-* all copies or substantial portions of the Software.
-*
-* Use of the Software is limited solely to applications:
-* (a) running on a Xilinx device, or
-* (b) that interact with a Xilinx device through a bus or interconnect.
-*
-* THE SOFTWARE IS PROVIDED "AS IS", WITHOUT WARRANTY OF ANY KIND, EXPRESS OR
-* IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES OF MERCHANTABILITY,
-* FITNESS FOR A PARTICULAR PURPOSE AND NONINFRINGEMENT. IN NO EVENT SHALL THE
-* XILINX CONSORTIUM BE LIABLE FOR ANY CLAIM, DAMAGES OR OTHER LIABILITY,
-* WHETHER IN AN ACTION OF CONTRACT, TORT OR OTHERWISE, ARISING FROM, OUT OF
-* OR IN CONNECTION WITH THE SOFTWARE OR THE USE OR OTHER DEALINGS IN THE
-* SOFTWARE.
-*
-* Except as contained in this notice, the name of the Xilinx shall not be used
-* in advertising or otherwise to promote the sale, use or other dealings in
-* this Software without prior written authorization from Xilinx.
-*
-******************************************************************************/
-/*****************************************************************************/
-/**
-*
-* @file xtmrctr_i.h
-*
-* This file contains data which is shared between files internal to the
-* XTmrCtr component. It is intended for internal use only.
-*
-* <pre>
-* MODIFICATION HISTORY:
-*
-* Ver   Who  Date     Changes
-* ----- ---- -------- -----------------------------------------------
-* 1.00b jhl  02/06/02 First release
-* 1.10b mta  03/21/07 Updated to new coding style
-* 2.00a ktn  10/30/09 _m is removed from all the macro definitions.
-* </pre>
-*
[…]

### 2018-07-16 ConnectedComponentLabeling_SDK/CCLabelling_bsp/ps7_cortexa9_0/libsrc/cclabel_v1_0/src/xcclabel.c

@@ -1,176 +1,0 @@
-// ==============================================================
-// File generated by Vivado(TM) HLS - High-Level Synthesis from C, C++ and SystemC
-// Version: 2014.4
-// Copyright (C) 2014 Xilinx Inc. All rights reserved.
-// 
-// ==============================================================
-
-/***************************** Include Files *********************************/
-#include "xcclabel.h"
-
-/************************** Function Implementation *************************/
-#ifndef __linux__
-int XCclabel_CfgInitialize(XCclabel *InstancePtr, XCclabel_Config *ConfigPtr) {
-    Xil_AssertNonvoid(InstancePtr != NULL);
-    Xil_AssertNonvoid(ConfigPtr != NULL);
-
-    InstancePtr->Crtls_BaseAddress = ConfigPtr->Crtls_BaseAddress;
-    InstancePtr->IsReady = XIL_COMPONENT_IS_READY;
-
-    return XST_SUCCESS;
-}
-#endif
-
-void XCclabel_Start(XCclabel *InstancePtr) {
-    u32 Data;
-
-    Xil_AssertVoid(InstancePtr != NULL);
-    Xil_AssertVoid(InstancePtr->IsReady == XIL_COMPONENT_IS_READY);
-
-    Data = XCclabel_ReadReg(InstancePtr->Crtls_BaseAddress, XCCLABEL_CRTLS_ADDR_AP_CTRL) & 0x80;
-    XCclabel_WriteReg(InstancePtr->Crtls_BaseAddress, XCCLABEL_CRTLS_ADDR_AP_CTRL, Data | 0x01);
-}
-
-u32 XCclabel_IsDone(XCclabel *InstancePtr) {
-    u32 Data;
-
-    Xil_AssertNonvoid(InstancePtr != NULL);
-    Xil_AssertNonvoid(InstancePtr->IsReady == XIL_COMPONENT_IS_READY);
-
-    Data = XCclabel_ReadReg(InstancePtr->Crtls_BaseAddress, XCCLABEL_CRTLS_ADDR_AP_CTRL);
-    return (Data >> 1) & 0x1;
-}
-
[…]

### 2018-07-16 ConnectedComponentLabeling_SDK/CCLabelling_bsp/ps7_cortexa9_0/libsrc/cclabel_v1_0/src/xcclabel.h

@@ -1,108 +1,0 @@
-// ==============================================================
-// File generated by Vivado(TM) HLS - High-Level Synthesis from C, C++ and SystemC
-// Version: 2014.4
-// Copyright (C) 2014 Xilinx Inc. All rights reserved.
-// 
-// ==============================================================
-
-#ifndef XCCLABEL_H
-#define XCCLABEL_H
-
-#ifdef __cplusplus
-extern "C" {
-#endif
-
-/***************************** Include Files *********************************/
-#ifndef __linux__
-#include "xil_types.h"
-#include "xil_assert.h"
-#include "xstatus.h"
-#include "xil_io.h"
-#else
-#include <stdint.h>
-#include <assert.h>
-#include <dirent.h>
-#include <fcntl.h>
-#include <stdio.h>
-#include <stdlib.h>
-#include <string.h>
-#include <sys/mman.h>
-#include <unistd.h>
-#include <stddef.h>
-#endif
-#include "xcclabel_hw.h"
-
-/**************************** Type Definitions ******************************/
-#ifdef __linux__
-typedef uint8_t u8;
-typedef uint16_t u16;
-typedef uint32_t u32;
-#else
-typedef struct {
-    u16 DeviceId;
-    u32 Crtls_BaseAddress;
-} XCclabel_Config;
-#endif
-
-typedef struct {
-    u32 Crtls_BaseAddress;
-    u32 IsReady;
-} XCclabel;
-
-/***************** Macros (Inline Functions) Definitions *********************/
-#ifndef __linux__
-#define XCclabel_WriteReg(BaseAddress, RegOffset, Data) \
-    Xil_Out32((BaseAddress) + (RegOffset), (u32)(Data))
-#define XCclabel_ReadReg(BaseAddress, RegOffset) \
-    Xil_In32((BaseAddress) + (RegOffset))
-#else
-#define XCclabel_WriteReg(BaseAddress, RegOffset, Data) \
-    *(volatile u32*)((BaseAddress) + (RegOffset)) = (u32)(Data)
-#define XCclabel_ReadReg(BaseAddress, RegOffset) \
-    *(volatile u32*)((BaseAddress) + (RegOffset))
-
-#define Xil_AssertVoid(expr)    assert(expr)
[…]

### 2018-07-16 ConnectedComponentLabeling_SDK/CCLabelling_bsp/ps7_cortexa9_0/libsrc/cclabel_v1_0/src/xcclabel_sinit.c

@@ -1,46 +1,0 @@
-// ==============================================================
-// File generated by Vivado(TM) HLS - High-Level Synthesis from C, C++ and SystemC
-// Version: 2014.4
-// Copyright (C) 2014 Xilinx Inc. All rights reserved.
-// 
-// ==============================================================
-
-#ifndef __linux__
-
-#include "xstatus.h"
-#include "xparameters.h"
-#include "xcclabel.h"
-
-extern XCclabel_Config XCclabel_ConfigTable[];
-
-XCclabel_Config *XCclabel_LookupConfig(u16 DeviceId) {
-	XCclabel_Config *ConfigPtr = NULL;
-
-	int Index;
-
-	for (Index = 0; Index < XPAR_XCCLABEL_NUM_INSTANCES; Index++) {
-		if (XCclabel_ConfigTable[Index].DeviceId == DeviceId) {
-			ConfigPtr = &XCclabel_ConfigTable[Index];
-			break;
-		}
-	}
-
-	return ConfigPtr;
-}
-
-int XCclabel_Initialize(XCclabel *InstancePtr, u16 DeviceId) {
-	XCclabel_Config *ConfigPtr;
-
-	Xil_AssertNonvoid(InstancePtr != NULL);
-
-	ConfigPtr = XCclabel_LookupConfig(DeviceId);
-	if (ConfigPtr == NULL) {
-		InstancePtr->IsReady = 0;
-		return (XST_DEVICE_NOT_FOUND);
-	}
-
-	return XCclabel_CfgInitialize(InstancePtr, ConfigPtr);
-}
-
-#endif
-

### 2018-07-16 ConnectedComponentLabeling_SDK/CCLabelling_bsp/ps7_cortexa9_0/libsrc/gpiops_v2_2/src/xgpiops_g.c

@@ -1,55 +1,0 @@
-
-/*******************************************************************
-*
-* CAUTION: This file is automatically generated by HSM.
-* Version: 
-* DO NOT EDIT.
-*
-* Copyright (C) 2010-2017 Xilinx, Inc. All Rights Reserved.*
-*Permission is hereby granted, free of charge, to any person obtaining a copy
-*of this software and associated documentation files (the Software), to deal
-*in the Software without restriction, including without limitation the rights
-*to use, copy, modify, merge, publish, distribute, sublicense, and/or sell
-*copies of the Software, and to permit persons to whom the Software is
-*furnished to do so, subject to the following conditions:
-*
-*The above copyright notice and this permission notice shall be included in
-*all copies or substantial portions of the Software.
-* 
-* Use of the Software is limited solely to applications:
-*(a) running on a Xilinx device, or
-*(b) that interact with a Xilinx device through a bus or interconnect.
-*
-*THE SOFTWARE IS PROVIDED AS IS, WITHOUT WARRANTY OF ANY KIND, EXPRESS OR
-*IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES OF MERCHANTABILITY,
-*FITNESS FOR A PARTICULAR PURPOSE AND NONINFRINGEMENT. IN NO EVENT SHALL THE
-*XILINX CONSORTIUM BE LIABLE FOR ANY CLAIM, DAMAGES OR OTHER LIABILITY,
-*WHETHER IN AN ACTION OF CONTRACT, TORT OR OTHERWISE, ARISING FROM, OUT
-*OF OR IN CONNECTION WITH THE SOFTWARE OR THE USE OR OTHER DEALINGS IN THE SOFTWARE.
-*
-*Except as contained in this notice, the name of the Xilinx shall not be used
-*in advertising or otherwise to promote the sale, use or other dealings in
-*this Software without prior written authorization from Xilinx.
-*
-
-* 
-* Description: Driver configuration
-*
-*******************************************************************/
-
-#include "xparameters.h"
-#include "xgpiops.h"
-
-/*
-* The configuration table for devices
-*/
-
-XGpioPs_Config XGpioPs_ConfigTable[] =
-{
-	{
-		XPAR_PS7_GPIO_0_DEVICE_ID,
-		XPAR_PS7_GPIO_0_BASEADDR
-	}
-};
-
-

### 2018-07-16 ConnectedComponentLabeling_SDK/CCLabelling_bsp/ps7_cortexa9_0/libsrc/tmrctr_v3_0/src/xtmrctr_options.c

@@ -1,214 +1,0 @@
-/******************************************************************************
-*
-* Copyright (C) 2002 - 2014 Xilinx, Inc.  All rights reserved.
-*
-* Permission is hereby granted, free of charge, to any person obtaining a copy
-* of this software and associated documentation files (the "Software"), to deal
-* in the Software without restriction, including without limitation the rights
-* to use, copy, modify, merge, publish, distribute, sublicense, and/or sell
-* copies of the Software, and to permit persons to whom the Software is
-* furnished to do so, subject to the following conditions:
-*
-* The above copyright notice and this permission notice shall be included in
-* all copies or substantial portions of the Software.
-*
-* Use of the Software is limited solely to applications:
-* (a) running on a Xilinx device, or
-* (b) that interact with a Xilinx device through a bus or interconnect.
-*
-* THE SOFTWARE IS PROVIDED "AS IS", WITHOUT WARRANTY OF ANY KIND, EXPRESS OR
-* IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES OF MERCHANTABILITY,
-* FITNESS FOR A PARTICULAR PURPOSE AND NONINFRINGEMENT. IN NO EVENT SHALL THE
-* XILINX CONSORTIUM BE LIABLE FOR ANY CLAIM, DAMAGES OR OTHER LIABILITY,
-* WHETHER IN AN ACTION OF CONTRACT, TORT OR OTHERWISE, ARISING FROM, OUT OF
-* OR IN CONNECTION WITH THE SOFTWARE OR THE USE OR OTHER DEALINGS IN THE
-* SOFTWARE.
-*
-* Except as contained in this notice, the name of the Xilinx shall not be used
-* in advertising or otherwise to promote the sale, use or other dealings in
-* this Software without prior written authorization from Xilinx.
-*
-******************************************************************************/
-/*****************************************************************************/
-/**
-*
-* @file xtmrctr_options.c
-*
-* Contains configuration options functions for the XTmrCtr component.
-*
-* <pre>
-* MODIFICATION HISTORY:
-*
-* Ver   Who  Date     Changes
-* ----- ---- -------- -----------------------------------------------
-* 1.00b jhl  02/06/02 First release
-* 1.10b mta  03/21/07 Updated to new coding style
[…]

### 2018-07-16 ConnectedComponentLabeling_SDK/CCLabelling_bsp/ps7_cortexa9_0/libsrc/tmrctr_v3_0/src/xtmrctr_selftest.c

@@ -1,163 +1,0 @@
-/******************************************************************************
-*
-* Copyright (C) 2002 - 2014 Xilinx, Inc.  All rights reserved.
-*
-* Permission is hereby granted, free of charge, to any person obtaining a copy
-* of this software and associated documentation files (the "Software"), to deal
-* in the Software without restriction, including without limitation the rights
-* to use, copy, modify, merge, publish, distribute, sublicense, and/or sell
-* copies of the Software, and to permit persons to whom the Software is
-* furnished to do so, subject to the following conditions:
-*
-* The above copyright notice and this permission notice shall be included in
-* all copies or substantial portions of the Software.
-*
-* Use of the Software is limited solely to applications:
-* (a) running on a Xilinx device, or
-* (b) that interact with a Xilinx device through a bus or interconnect.
-*
-* THE SOFTWARE IS PROVIDED "AS IS", WITHOUT WARRANTY OF ANY KIND, EXPRESS OR
-* IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES OF MERCHANTABILITY,
-* FITNESS FOR A PARTICULAR PURPOSE AND NONINFRINGEMENT. IN NO EVENT SHALL THE
-* XILINX CONSORTIUM BE LIABLE FOR ANY CLAIM, DAMAGES OR OTHER LIABILITY,
-* WHETHER IN AN ACTION OF CONTRACT, TORT OR OTHERWISE, ARISING FROM, OUT OF
-* OR IN CONNECTION WITH THE SOFTWARE OR THE USE OR OTHER DEALINGS IN THE
-* SOFTWARE.
-*
-* Except as contained in this notice, the name of the Xilinx shall not be used
-* in advertising or otherwise to promote the sale, use or other dealings in
-* this Software without prior written authorization from Xilinx.
-*
-******************************************************************************/
-/*****************************************************************************/
-/**
-*
-* @file xtmrctr_selftest.c
-*
-* Contains diagnostic/self-test functions for the XTmrCtr component.
-*
-* <pre>
-* MODIFICATION HISTORY:
-*
-* Ver   Who  Date     Changes
-* ----- ---- -------- -----------------------------------------------
-* 1.00b jhl  02/06/02 First release
[…]

### 2018-07-16 ConnectedComponentLabeling_SDK/CCLabelling_bsp/ps7_cortexa9_0/libsrc/usbps_v2_2/src/xusbps_g.c

@@ -1,55 +1,0 @@
-
-/*******************************************************************
-*
-* CAUTION: This file is automatically generated by HSM.
-* Version: 
-* DO NOT EDIT.
-*
-* Copyright (C) 2010-2017 Xilinx, Inc. All Rights Reserved.*
-*Permission is hereby granted, free of charge, to any person obtaining a copy
-*of this software and associated documentation files (the Software), to deal
-*in the Software without restriction, including without limitation the rights
-*to use, copy, modify, merge, publish, distribute, sublicense, and/or sell
-*copies of the Software, and to permit persons to whom the Software is
-*furnished to do so, subject to the following conditions:
-*
-*The above copyright notice and this permission notice shall be included in
-*all copies or substantial portions of the Software.
-* 
-* Use of the Software is limited solely to applications:
-*(a) running on a Xilinx device, or
-*(b) that interact with a Xilinx device through a bus or interconnect.
-*
-*THE SOFTWARE IS PROVIDED AS IS, WITHOUT WARRANTY OF ANY KIND, EXPRESS OR
-*IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES OF MERCHANTABILITY,
-*FITNESS FOR A PARTICULAR PURPOSE AND NONINFRINGEMENT. IN NO EVENT SHALL THE
-*XILINX CONSORTIUM BE LIABLE FOR ANY CLAIM, DAMAGES OR OTHER LIABILITY,
-*WHETHER IN AN ACTION OF CONTRACT, TORT OR OTHERWISE, ARISING FROM, OUT
-*OF OR IN CONNECTION WITH THE SOFTWARE OR THE USE OR OTHER DEALINGS IN THE SOFTWARE.
-*
-*Except as contained in this notice, the name of the Xilinx shall not be used
-*in advertising or otherwise to promote the sale, use or other dealings in
-*this Software without prior written authorization from Xilinx.
-*
-
-* 
-* Description: Driver configuration
-*
-*******************************************************************/
-
-#include "xparameters.h"
-#include "xusbps.h"
-
-/*
-* The configuration table for devices
-*/
-
-XUsbPs_Config XUsbPs_ConfigTable[] =
-{
-	{
-		XPAR_PS7_USB_0_DEVICE_ID,
-		XPAR_PS7_USB_0_BASEADDR
-	}
-};
-
-

### 2018-07-16 ConnectedComponentLabeling_SDK/StarTracking/src/Algorithm.h

@@ -1,66 +1,0 @@
-#ifndef ALGORITHM_
-#define ALGORITHM_
-#include <vector>
-#include <cmath>
-#include <algorithm>
-struct Star {
-	int X;
-	int Y;
-	double starDistance2Centre;
-	double starDistance2StarRef;
-};
-
-struct StarPattern {
-	int N;
-	int d1;
-	int d2;
-	int d3;
-	int starID;
-	double sqError;
-};
-
-std::vector<Star> chooseStarRef(int *X, int *Y, unsigned centroidCount, int imgHeight, int imgWidth) {
-	std::vector<Star> starList;
-	for(int i = 0; i < (int)centroidCount; ++i)
-		starList.push_back({X[i], Y[i], sqrt((X[i] - imgHeight/2)*(X[i] - imgHeight/2) + (Y[i] - imgWidth/2)*(Y[i] - imgWidth/2)),0});
-	std::make_heap(starList.begin(), starList.end(), [](const Star &a, const Star &b) {return a.starDistance2Centre > b.starDistance2Centre; });
-	return starList;
-}
-
-StarPattern getStarPattern(std::vector<Star> &starList,int FOV) {
-	StarPattern starPattern;
-
-	//Calculate the star distance to starRef
-	Star starRef = starList.front();
-	std::pop_heap(starList.begin(), starList.end(), [](const Star &a, const Star &b) {return a.starDistance2Centre > b.starDistance2Centre; });
-	starList.pop_back();
-
-	for (int i = 0; i < (int)starList.size(); ++i)
-		starList[i].starDistance2StarRef = sqrt((starRef.X - starList[i].X)*(starRef.X - starList[i].X) + (starRef.Y - starList[i].Y)*(starRef.Y - starList[i].Y));
-	std::make_heap(starList.begin(), starList.end(), [](const Star &a, const Star &b) {return a.starDistance2StarRef > b.starDistance2StarRef; });
-
-	//Traverse through the sorted list to get star pattern
-	int count = 0;
-	float distance[3] = { 0,0,0 };
-
-	while (!starList.empty()) {
-		if (starList.front().starDistance2StarRef > FOV / 2) break;
-		if (count < 3) distance[count] = starList.front().starDistance2StarRef;
-
-		std::pop_heap(starList.begin(), starList.end(), [](const Star &a, const Star &b) {return a.starDistance2StarRef > b.starDistance2StarRef; });
[…]

### 2018-07-16 ConnectedComponentLabeling_SDK/StarTracking/src/CentroiderHW.h

@@ -1,58 +1,0 @@
-#ifndef CCLABEL_H_
-#define CCLABEL_H_
-
-XCclabel cCLabel;
-XCclabel_Config *cCLabel_cfg;
-XAxiDma axiDMA;
-XAxiDma_Config *axiDMA_cfg;
-
-//BRAM addresses
-int *XHW = (int *)0x40000000;
-int *YHW = (int *)0x40010000;
-
-//DMA addresses
-#define MEM_BASE_ADDR 0x01000000
-#define TX_BUFFER_BASE (MEM_BASE_ADDR + 0x00100000)
-
-
-void init_core() {
-	int status = 0;
-
-	// init CC core
-	cCLabel_cfg = XCclabel_LookupConfig(XPAR_CCLABEL_0_DEVICE_ID);
-	if (!cCLabel_cfg) {
-		xil_printf("Error loading config\r\n");
-	}
-	else {
-		status = XCclabel_CfgInitialize(&cCLabel,cCLabel_cfg);
-		if (status != XST_SUCCESS) {
-			xil_printf("Error initializing CC core\r\n");
-		}
-	}
-
-	//init DMA
-	axiDMA_cfg = XAxiDma_LookupConfig(XPAR_AXIDMA_0_DEVICE_ID);
-	if(axiDMA_cfg) {
-		status = XAxiDma_CfgInitialize(&axiDMA, axiDMA_cfg);
-		if(status != XST_SUCCESS) {
-			xil_printf("Error initializing DMA\r\n");
-		}
-	}
-
-	//Disable Interrupts
-	XAxiDma_IntrDisable(&axiDMA, XAXIDMA_IRQ_ALL_MASK, XAXIDMA_DEVICE_TO_DMA);
-	XAxiDma_IntrDisable(&axiDMA, XAXIDMA_IRQ_ALL_MASK, XAXIDMA_DMA_TO_DEVICE);
-}
-
-bool verifyResult(u32 centroidCountSW, int *XSW, int *YSW, u32 centroidCountHW, int *XHW, int *YHW) {
-	if(centroidCountSW == centroidCountHW) {
-		for(int i = 0; i < (int)centroidCountHW; ++i) {
-			if(XSW[i] == XHW[i] && YSW[i] == YHW[i])
-				continue;
-			return false;
-		}
-		return true;
-	}
-	return false;
-}
-#endif

### 2018-07-16 ConnectedComponentLabeling_SDK/StarTracking/src/CentroiderSW.h

@@ -1,164 +1,0 @@
-#ifndef CENTROIDERSW_H_
-#define CENTROIDERSW_H_
-
-#include "Image.h"
-#include <cmath>
-
-#define THRESHOLD 70
-#define MAX 999
-#define MAX_STAR_DATA_SIZE 100
-#define MAX_SET_SIZE 100
-#define MAX_CENTROID_DATA 100
-
-unsigned lbImage[IMG_HEIGHT * IMG_WIDTH];
-unsigned set[MAX_SET_SIZE];
-
-bool status[MAX_STAR_DATA_SIZE];
-unsigned totalIntensity[MAX_STAR_DATA_SIZE];
-unsigned x[MAX_STAR_DATA_SIZE];
-unsigned y[MAX_STAR_DATA_SIZE];
-
-int XSW[MAX_CENTROID_DATA];
-int YSW[MAX_CENTROID_DATA];
-
-void preProcess(unsigned Image[IMG_HEIGHT*IMG_WIDTH]) {
-	unsigned i = 0,j = 0;
-	for (i = 0; i < IMG_HEIGHT; ++i) {
-		for (j = 0; j < IMG_WIDTH; ++j) {
-			if (Image[i*IMG_HEIGHT + j] < THRESHOLD)
-				lbImage[i*IMG_HEIGHT + j] = 0;
-			else
-				lbImage[i*IMG_HEIGHT + j] = 1;
-		}
-	}
-}
-
-unsigned find(unsigned id) {
-	unsigned temp = id;
-	while (temp != set[temp]) {
-		temp = set[temp];
-	}
-	return temp;
-}
-
-unsigned firstPass(unsigned Image[IMG_HEIGHT*IMG_WIDTH]) {
-	unsigned i = 0, j = 0;
-	unsigned label = 0;
-	unsigned prevAbove = 0;
-	unsigned prevLeft = 0;
-	unsigned setCount = 1;
-	unsigned min = 0;
-	unsigned max = MAX;
-	for (i = 0; i < IMG_HEIGHT; ++i) {
-		for (j = 0; j < IMG_WIDTH; ++j) {
-			if (lbImage[i*IMG_HEIGHT + j] != 0) {
-				if(i != 0 && lbImage[(i - 1)*IMG_HEIGHT + j] != 0) {
-					prevAbove = lbImage[(i - 1)*IMG_HEIGHT + j];
-				}
-				else {
-					prevAbove = MAX;
-				}
[…]

### 2018-07-16 ConnectedComponentLabeling_SDK/StarTracking/src/StarPatternDatabase.h

@@ -1,1514 +1,0 @@
-#ifndef STARPATTERNDATABASE_H_
-#define STARPATTERNDATABASE_H_
-
-#define DATABASESIZE 1500
-struct dataStruct {
-	int N;
-	int d1;
-	int d2;
-	int d3;
-	int id;
-};
-int database [DATABASESIZE][5] = {
-	{0, 0, 0, 0, 10},
-	{0, 0, 0, 0, 11},
-	{0, 0, 0, 0, 20},
-	{0, 0, 0, 0, 33},
-	{0, 0, 0, 0, 34},
-	{0, 0, 0, 0, 41},
-	{0, 0, 0, 0, 46},
-	{0, 0, 0, 0, 71},
-	{0, 0, 0, 0, 79},
-	{0, 0, 0, 0, 83},
-	{0, 0, 0, 0, 94},
-	{0, 0, 0, 0, 99},
-	{0, 0, 0, 0, 105},
-	{0, 0, 0, 0, 107},
-	{0, 0, 0, 0, 116},
-	{0, 0, 0, 0, 132},
-	{0, 0, 0, 0, 156},
-	{0, 0, 0, 0, 165},
-	{0, 0, 0, 0, 179},
-	{0, 0, 0, 0, 199},
-	{0, 0, 0, 0, 206},
-	{0, 0, 0, 0, 209},
-	{0, 0, 0, 0, 246},
-	{0, 0, 0, 0, 259},
-	{0, 0, 0, 0, 273},
-	{0, 0, 0, 0, 277},
-	{0, 0, 0, 0, 335},
-	{0, 0, 0, 0, 356},
-	{0, 0, 0, 0, 375},
-	{0, 0, 0, 0, 377},
-	{0, 0, 0, 0, 386},
-	{0, 0, 0, 0, 396},
-	{0, 0, 0, 0, 401},
-	{0, 0, 0, 0, 405},
-	{0, 0, 0, 0, 406},
-	{0, 0, 0, 0, 412},
-	{0, 0, 0, 0, 424},
-	{0, 0, 0, 0, 433},
-	{0, 0, 0, 0, 445},
-	{0, 0, 0, 0, 451},
-	{0, 0, 0, 0, 471},
-	{0, 0, 0, 0, 473},
-	{0, 0, 0, 0, 480},
-	{0, 0, 0, 0, 503},
-	{0, 0, 0, 0, 513},
-	{0, 0, 0, 0, 520},
-	{0, 0, 0, 0, 542},
[…]

### 2018-07-16 ConnectedComponentLabeling_SDK/StarTracking/src/main.cpp

@@ -1,121 +1,0 @@
-#include <xparameters.h>
-#include "xCCLabel.h"
-#include "xaxidma.h"
-#include "platform.h"
-#include "AxiTimerHelper.h"
-#include "Image.h"
-#include "CentroiderSW.h"
-#include "CentroiderHW.h"
-#include "Algorithm.h"
-#include "Database.h"
-#include "StarPatternDatabase.h"
-
-#define FOV 256
-#define TOLERANCE 5
-
-int main() {
-	//Timer
-	AxiTimerHelper timer;
-
-	//Init board
-	init_platform();
-
-	//Initialize
-	init_core();
-	
-	XCclabel_EnableAutoRestart(&cCLabel);
-	
-
-	/********************************************** CC Labeling SW ****************************************************************/
-	timer.startTimer();
-	u32 centroidCountSW = softwareCCLabel(inputIMG, XSW, YSW);
-	timer.stopTimer();
-	double swCCLabeltime = timer.getElapsedTimerInSeconds();
-	
-
-	/********************************************** CC Labeling HW ****************************************************************/
-	//Set parameters
-	XCclabel_Set_imgHeight(&cCLabel, IMG_HEIGHT);
-	XCclabel_Set_imgWidth(&cCLabel, IMG_WIDTH);
-	
-	//Flush the cache of the buffers
-	timer.startTimer();
-	Xil_DCacheFlushRange((u32)inputIMG, IMG_HEIGHT * IMG_WIDTH * sizeof(int));
-	
-	//Send data to IP core
-	XAxiDma_SimpleTransfer(&axiDMA, (u32)inputIMG, IMG_HEIGHT * IMG_WIDTH * sizeof(int), XAXIDMA_DMA_TO_DEVICE);
-	timer.stopTimer();
-	double dmatrans = timer.getElapsedTimerInSeconds();
-	
-	//Start IP core
-	XCclabel_Start(&cCLabel);
-	
-	// Wait until it's done
-	timer.startTimer();
-	while(!XCclabel_IsDone(&cCLabel));
-	
-	timer.stopTimer();
-	double hwCCLabeltime = timer.getElapsedTimerInSeconds();
-
-	//Output
-	u32 centroidCountHW = XCclabel_Get_return(&cCLabel);
-
-	/********************************************** Algorithm ****************************************************************/
-	
-	timer.startTimer();
-	std::vector<Star> starList = chooseStarRef(XHW, XHW, centroidCountHW, IMG_HEIGHT, IMG_WIDTH);
[…]

### 2018-07-16 ConnectedComponentLabeling_SDK/design_1_wrapper_hw_platform_0/ps7_init.h

@@ -1,137 +1,0 @@
-
-/******************************************************************************
-*
-* (c) Copyright 2010-2014 Xilinx, Inc. All rights reserved.
-*
-* Permission is hereby granted, free of charge, to any person obtaining a copy of this
-* software and associated documentation files (the "Software"), to deal in the Software
-* without restriction, including without limitation the rights to use, copy, modify, merge,
-* publish, distribute, sublicense, and/or sell copies of the Software, and to permit
-* persons to whom the Software is furnished to do so, subject to the following conditions:
-* 
-* The above copyright notice and this permission notice shall be included in all copies or 
-* substantial portions of the Software.
-* 
-* Use of the Software is limited solely to applications: (a) running on a Xilinx device, or 
-* (b) that interact with a Xilinx device through a bus or interconnect.  
-* 
-* THE SOFTWARE IS PROVIDED "AS IS", WITHOUT WARRANTY OF ANY KIND, EXPRESS OR IMPLIED, INCLUDING 
-* BUT NOT LIMITED TO THE WARRANTIES OF MERCHANTABILITY, FITNESS FOR A PARTICULAR PURPOSE AND 
-* NONINFRINGEMENT. IN NO EVENT SHALL THE X CONSORTIUM BE LIABLE FOR ANY CLAIM, DAMAGES OR OTHER
-* LIABILITY, WHETHER IN AN ACTION OF CONTRACT, TORT OR OTHERWISE, ARISING FROM, OUT OF OR IN 
-* CONNECTION WITH THE SOFTWARE OR THE USE OR OTHER DEALINGS IN THE SOFTWARE.
-* 
-* Except as contained in this notice, the name of the Xilinx shall not be used in advertising or 
-* otherwise to promote the sale, use or other dealings in this Software without prior written 
-* authorization from Xilinx.
-* 
-*******************************************************************************/
-/****************************************************************************/
-/**
-*
-* @file ps7_init.h
-*
-* This file can be included in FSBL code
-* to get prototype of ps7_init() function
-* and error codes
-*
[…]

### 2018-07-16 ConnectedComponentLabeling_SW/CCLabeling4.cpp

@@ -1,236 +1,0 @@
-#ifdef _MSC_VER
-#define _CRT_SECURE_NO_WARNINGS
-#endif
-
-#define DEBUG
-
-#include <cstdio>
-#include <vector>
-#include <iostream>
-using namespace std;
-
-/*******************************************************************************************/
-#define MAX_IMG_HEIGHT 1024
-#define MAX_IMG_WIDTH 1024
-#define MAXTHPIXEL 1024
-#define THRESHOLD 70
-#define MAX 999
-#define MAX_STAR_DATA_SIZE 40
-#define MAX_SET_SIZE 40
-#define MAX_CENTROID_DATA 40
-
-unsigned Image[MAXTHPIXEL];
-unsigned mark[MAXTHPIXEL];
-unsigned lbImage[MAXTHPIXEL];
-
-unsigned set[MAX_SET_SIZE];
-
-bool status[MAX_STAR_DATA_SIZE];
-unsigned totalIntensity[MAX_STAR_DATA_SIZE];
-unsigned x[MAX_STAR_DATA_SIZE];
-unsigned y[MAX_STAR_DATA_SIZE];
-
-/*********************************** TEMP ********************************************************/
-void readImage(FILE *&fileIn, unsigned streamImage[MAX_IMG_HEIGHT * MAX_IMG_WIDTH], unsigned imgHeight, unsigned imgWidth) {
-	for (unsigned i = 0; i < imgHeight; ++i) for (unsigned j = 0; j < imgWidth; ++j) {
-		fscanf(fileIn, "%d", &streamImage[i*imgHeight + j]);
-	}
-}
-
-void printResult(FILE *fileOut, unsigned centroidDataCount, unsigned X[MAX_CENTROID_DATA], unsigned Y[MAX_CENTROID_DATA]) {
-	for (unsigned i = 0; i < centroidDataCount; ++i) {
-		fprintf(fileOut, "Star[%d]: x = %d, y = %d\n", i + 1, X[i], Y[i]);
-	}
-}
-/**************************************** TEMP ***************************************************************/
-unsigned find(unsigned id) {
-	int temp;
-	temp = id;
-	while (temp != set[temp]) {
-#pragma HLS PIPELINE
-		temp = set[temp];
-	}
-	return temp;
-}
-
-int binarySearch(unsigned data, unsigned pixNum) {
-	int left = 0;
-	int right = pixNum - 1;
-	int mid = 0;
[…]

### 2018-07-16 ConnectedComponentLabeling_SW/CCLabeling4_INT.cpp

@@ -1,236 +1,0 @@
-#ifdef _MSC_VER
-#define _CRT_SECURE_NO_WARNINGS
-#endif
-
-#define DEBUG
-
-#include <cstdio>
-#include <vector>
-#include <iostream>
-using namespace std;
-
-/*******************************************************************************************/
-#define MAX_IMG_HEIGHT 1024
-#define MAX_IMG_WIDTH 1024
-#define MAXTHPIXEL 1024
-#define THRESHOLD 70
-#define MAX 999
-#define MAX_STAR_DATA_SIZE 40
-#define MAX_SET_SIZE 40
-#define MAX_CENTROID_DATA 40
-
-int Image[MAXTHPIXEL];
-int mark[MAXTHPIXEL];
-int lbImage[MAXTHPIXEL];
-
-int set[MAX_SET_SIZE];
-
-bool status[MAX_STAR_DATA_SIZE];
-int totalIntensity[MAX_STAR_DATA_SIZE];
-int x[MAX_STAR_DATA_SIZE];
-int y[MAX_STAR_DATA_SIZE];
-
-/*********************************** TEMP ********************************************************/
-void readImage(FILE *&fileIn, int streamImage[MAX_IMG_HEIGHT * MAX_IMG_WIDTH], int imgHeight, int imgWidth) {
-	for (int i = 0; i < imgHeight; ++i) for (int j = 0; j < imgWidth; ++j) {
-		fscanf(fileIn, "%d", &streamImage[i*imgHeight + j]);
-	}
-}
-
-void printResult(FILE *fileOut, int centroidDataCount, int X[MAX_CENTROID_DATA], int Y[MAX_CENTROID_DATA]) {
-	for (int i = 0; i < centroidDataCount; ++i) {
-		fprintf(fileOut, "Star[%d]: x = %d, y = %d\n", i + 1, X[i], Y[i]);
-	}
-}
-/**************************************** TEMP ***************************************************************/
-int find(int id) {
-	int temp;
-	temp = id;
-	while (temp != set[temp]) {
-#pragma HLS PIPELINE
-		temp = set[temp];
-	}
-	return temp;
-}
-
-int binarySearch(int data, int pixNum) {
-	int left = 0;
-	int right = pixNum - 1;
-	int mid = 0;
-	while (true) {
-#pragma HLS PIPELINE
-		mid = left + (right - left) / 2;
-		if (data == mark[mid]) {
[…]

### 2018-07-16 StarSimulation_Matlab/Plot_sky_images.m

@@ -26,7 +26,7 @@ c2= R_camera_to_earth(2,:);
 c3= R_camera_to_earth(3,:);
 
 %% Read star coordinates in Earth reference frame from star catalog
-file_path='D:\\Dropbox\\DangKhoa\\CEE_Cache\\StarTrackingProject\\StarSimulation_Matlab\\SKY2000_Magnitude5_doublestar.txt';
+file_path='D:\\Dropbox\\DangKhoa\\CEE_Cache\\GitHub\\StarTrackingProject\\StarSimulation_Matlab\\SKY2000_Magnitude5_doublestar.txt';
 [SKYMAP_No,star_RA,star_DEC,star_MAG]= textread(file_path,'%d %f %f %f');
 
 % Si is coordiante of star in Earth reference frame, 

### 2018-07-16 StarSimulation_Matlab/SkySimulator.m

@@ -25,7 +25,7 @@ star_generated=zeros(test,test);
 for RA = 1 :1: 360 
     for DEC = -89:1:89
         % Generate sky image at predetermined attitude
-        cd('D:\\Dropbox\\DangKhoa\\CEE_Cache\\StarTrackingProject\\StarSimulation_Matlab');
+        cd('D:\\Dropbox\DangKhoa\\CEE_Cache\\GitHub\\StarTrackingProject\\StarSimulation_Matlab');
         C = Convert_Axis_2_AttitudeMatrix(RA,DEC,angle);
         [ R_camera_to_earth,star_matrix,I]= Plot_sky_images( C, FOV, img_height, img_width, pixelsize);
         %figure(1);
@@ -39,7 +39,7 @@ for RA = 1 :1: 360
                I(i,j) =  round(temp * 255);
            end
         end
-        baseFileName = sprintf('D:\\Dropbox\\DangKhoa\\CEE_Cache\\StarTrackingProject\\StarSimulation_Matlab\\TestPattern\\IMG_%d_%d.bin',RA,DEC+89);
+        baseFileName = sprintf('.\\TestPattern\\IMG_%d_%d.bin',RA,DEC+89);
         dlmwrite(baseFileName,I,'delimiter',' ');
         % Store number of star generated every test
         star_generated(RA,DEC+91) = size(star_matrix,1); 

### 2018-07-26 thesis/2_chapters/chap4.tex
thesis submitted

@@
 
+The power consumption of the design is measured based on the condition described in Table~\ref{tab:environment}.
+
 \begin{ntutab}{|c|c|}{environment}{Environment condition}
@@
     \hline
-    Ambient temperature &  \\
+    Ambient temperature & $30.0^oC$ \\
     \hline
@@
 
+\noindent As in Figure~\ref{fig:power_sum} and Figure~\ref{fig:power}, the Processing System(the ARM A9 processor) consumes 77\% of the power supplied while other hardware components like the IP core, BRAM consume less power.
+This is due to the fact that generic processors are designed for multiple purpose tasks; hence they are not optimal for power consumption as the hardware solution for a specific task.
+
 \ntuepsfig[width=\textwidth]{power_sum}{Power consumption summary}
@@
 % Section 4.2
+\newpage
 \section{Runtime experiments}

### 2018-07-26 thesis/2_chapters/chap5.tex
thesis submitted

@@
 % Chapter 5
-\chapter{Conclusion and Future Works}
+\chapter{Summary and Future Works}
 \label{chap:conclusion}
@@
 
-\section{Conclusion}
+\section{Future Works}
 
-\section{Future Works}
+Currently, the system can not handle a high throughput image data streaming.
+In my experiments, I have to handle the images one-by-one to feed into the system.
+Hence, I suggest implementing an input-processing module with can manage a large stream amount of image data(around 9.8 GBs) autonomously.
+\\
+
+\noindent Moreover, the first dataset is generated by sky simulation with slightly normal distribution noise added, the second dataset is captured by a star tracker from the ground.
+In space, there are more noises affect the quality of the images from the electromagnetic field, Solar noise, Cosmic noise, etc.
+A noise cancellation module implemented in the PL would be needed.

### 2019-01-16 thesis/2_chapters/chap1.tex
Fix typo chap 1

@@
 
-\noindent Nanosatellite is a small artificial satellite with a wet mass between 1 – 10 kg.
-Nanosatellites are cheap but capable of performing commercial missions and has lead researchers and scientist to explore the new way to use the Nanosatellites in LEO\cite{network}.
+\noindent Nanosatellite is a small artificial satellite with a wet mass(the total mass of the hardware plus fuel and oxidizer) between 1 – 10 kg.
+Nanosatellites are cheap but capable of performing commercial missions and has led researchers and scientists to explore the new way to use the Nanosatellites in LEO\cite{network}.
 Their designs are only comprised of low-cost components.
@@
 \noindent A satellite needs an attitude determination system for navigation and acknowledging orientations.
-Its attitude needed to be calculated and predicted continuously during its operation on the orbit.
-By implying the celestial objects and properties around the satellite, the satellite can autonomously estimate the orientations.
+Its attitude needs to be calculated and predicted continuously during its operation on the orbit.
+By observing the celestial objects and properties around the satellite, the satellite can autonomously estimate the orientations.
 Some of the favorite reference objects are the Sun, the Earth magnetic field, the celestial sphere, and the stars.
@@
 % SubSection 1.1.1
-\subsection{Overview and Motivations}
+\subsection{Introduction to spacecraft attitude determination}
 
@@
 Another way of attitude determination approach is using star trackers.
-Star Tracker is an optical-electronics subsystem comprised of a CCD or CMOS Image sensor attached to an optical lens and a computing system, usually a microprocessor integrated into an ASIC board.
+Star Tracker is an optical-electronics subsystem comprises of a CCD or CMOS Image sensor attached to an optical lens and a computing system, usually a microprocessor integrated into an ASIC board.
 The image sensor will firstly take an image of multiple star clusters at a specific fixed orientation.
 After that, the image is processed through the computing system to extract a particular feature of the model depending on a predefined algorithm.
-Then, the specific feature is compared which a prebuilt pattern or feature database stored in the memory.
+Then, the specific feature is compared with a prebuilt pattern or feature database stored in the memory.
 The output of the algorithm is often a star ID, which has a specific attitude, this attitude is again used to determine the attitude(orientation) of the spacecraft.
@@
 \noindent The star tracker is a preferred attitude determination approach because of its high accuracy compared to other sensors\cite{ntu.19915319780101}.
-However, the star tracker approach is less low cost and more power consumption than traditional approach by sun sensor and IMU.
-To achieve the best accuracy, the star tracker depends on the many factors such as the quality of the image sensor, the quality of the optical lens, most importantly the processing time of the computing subsystem, the runtime of the star tracking Algorithm.
+However, the star tracker approach is high cost and more power consumption than the traditional approach by sun sensor and IMU.
+To achieve the best accuracy, the star tracker depends on the many factors such as the quality of the image sensor, the quality of the optical lens, and most importantly the processing time of the computing subsystem, and the runtime of the star tracking Algorithm.
 \\
@@
 \section{Objectives}
-The essential goals of this research project are followed.
+The essential goals of this research project are as followed.
 \begin{itemize}
-	\item To analyze several star tracking algorithms especially in Lost in space (LIS) mode.
+	\item To analyze several star tracking algorithms especially in Lost in space (LIS) mode, the state that the spacecraft first time entering the orbit without any knowledge about its prior orientations compared to Tracking mode which is the state that the star tracker has been operating for a while, and its current orientations can be computed based on the prior information.
 	\item To implement and evaluate the performance of a star tracking algorithm on specific hardware using hardware and software co-processing approach.
-	\item To benchmark and optimize the algorithm on the terms of power consumption, the area of transistor implementation.
+	\item To benchmark and optimize the algorithm in terms of the power consumption and the area of transistor implementation.
 \end{itemize}
@@
 	\item Chapter 2: Introduces the basis of star tracking operation, reviews some of the state of the art star tracking algorithms and the chosen algorithm to be implemented by the software-hardware co-processing approach.
-	\item Chapter 3: Introduces and analyze a proposed algorithm going to be implemented on the hardware.
-	\item Chapter 4: Discuss the result of the implementation regarding runtime performance, hardware resources.
+	\item Chapter 3: Introduces and analyzes a proposed algorithm to be implemented on the hardware.
+	\item Chapter 4: Discusses the result of the implementation regarding runtime performance and hardware resources.
 \end{itemize}

### 2019-01-19 thesis/2_chapters/chap2.tex
Fix all typos

@@
 % Chapter 2
-\chapter{Literature preview}
+\chapter{Literature Review}
 \label{chap:lit_review}
@@
 	\item LIS mode: the initial attitude is unknown, the star tracker must determine it which is the most critical part of the star tracking operation.
-LIS mode is operated at the time when the power system on or resets after an attitude determination attempt from tracking mode failed\cite{edselc.2-52.0-8487677997120120101}.
+LIS mode is operated at the time when the power system is switched on or reset after an attitude determination attempt from tracking mode failed\cite{edselc.2-52.0-8487677997120120101}.
 	\item Tracking mode: after the initial attitude is recognized.
@@
 
-\noindent On this research topic, we will only focus on the LIS mode operation. The LIS mode operation of a star tracker is generalize in Figure~\ref{fig:2_1} included in 3 main algorithms:
+\noindent On this research topic, we will only focus on the LIS mode operation. The LIS mode operation of a star tracker is generalized in Figure~\ref{fig:2_1} which includes 3 main algorithms:
 \begin{itemize}
@@
 The Star ID will be looked up again in the SAO catalog to extract the information about its attitude.
-Then a group of star attitude is still used to calculate the attitude of the satellite.
+Then a group of star attitude is used to calculate the attitude of the satellite.
 Some of the well-known Attitude Determination methods are the QUEST and TRIAD.
@@
 The first step is to acquire the image which is accomplished by the image sensor.
-The image acquired has to be processed for estimating the coordinate of the stars in the image plane.
+The image acquired has to be processed for estimating the coordinates of the stars in the image plane.
 This is completed by applying the centroiding process on the image.
-The input of this step is a star image with multiple star clusters, the output is the coordinates of every stars presenting.
+The input of this step is a star image with multiple star clusters.
+The output is the coordinate of every star presenting.
 Due to distributed energy surface, a star projection is spread over a 3x3 to 11x11 square area\cite{ntu.54658220060101}, the star projection is a group of connected pixels.
@@
 % Table 2.1
-\noindent Table~\ref{tab:starList}. \\
+\noindent Table~\ref{tab:starList} .\\
 
@@
 % Section 2.3
-\section{Liebe Star Recognition algorithm}
+\section{Liebe Star Recognition Algorithm}
 
@@
 % Equation 2.2
-\noindent The star triplet will form 2 angular distance $\theta_1, \theta_2$ and 1 angular angle $\theta$ which are defined by Equation~\ref{eq:2_2}
+\noindent The star triplet will form 2 angular distances $\theta_1, \theta_2$ and 1 angular angle $\theta$ which are defined by Equation~\ref{eq:2_2}
 \begin{equation}
@@
 
-\noindent The weakness of this algorithm is the weak robustness due to the limitation of star utilizing.
-It only employs the three nearest stars to the centre and discards other stars which will then lead to a mismatch if the 2 predefined nearest neighboring star does not appear in the star image.
+\noindent The weakness of this algorithm is the weak robustness due to the limitation of star utilization.
+It only employs the three nearest stars to the centre and discards other stars which will then lead to a mismatch if the 2 predefined nearest neighboring stars does not appear in the star image.
 Besides, if the reference star appears in the final entry of the Star Pattern Database.
@@
 % Section 2.4
-\section{Pyramid star recognition algorithm}
+\section{Pyramid Star Recognition Algorithm}
 
@@
 \noindent Moreover, the pyramid star recognition algorithm has not yet solved the mismatch problem caused by missing stars.
-In the case of one or more neighboring stars of the reference, the star is missing the algorithm will fail and do not produce a correct result.
+In the case of one or more neighboring stars of the reference are missing, the algorithm will fail and do not produce a correct result.
 \\
@@
 
-To overcome the weakness of Liebe and Pyramid star recognition algorithm, the Geometric Voting is proposed based on voting of radial distances\cite{edseee.456019820080101}.
+To overcome the weaknesses of Liebe and Pyramid star recognition algorithms, the Geometric Voting is proposed based on voting of radial distances\cite{edseee.456019820080101}.
 The Geometric Voting method considers all the nearby stars of the reference star appeared in the star image.
@@
 
-\noindent After capturing the image, $r_1, r_2,…,r_n$ are calculated based on the distance from the closest star to the centre which is the reference star to all other stars within the FOV of the star sensor.
+\noindent After capturing the image, $r_1, r_2,...,r_n$ are calculated based on the distance from the closest star to the centre which is the reference star for all other stars within the Field of View(FOV) of the star sensor.
 Then all the distances from the feature vector are compared to the predefined neighboring distances of every star ID in the SPD.
@@
 
-\noindent For the advantage of this recognition method, firstly it employs all the data presenting in the image.
+\noindent The advantage of this recognition method is that it employs all the data presenting in the image.
 As a result, it reduces the mismatching issued caused by lack of data proposed by Liebe and Pyramid method.
@@
 \noindent The critical drawback of this method is the enormous space complexity needed to store the Star Pattern Database since each star ID entry must store the information of all of its neighboring stars.
-It leads to a requirement that a large memory must be used to store the Star Pattern Database to trade off the accuracy and robustness.
+It leads to the requirement that a large memory must be used to store the Star Pattern Database to trade off of the accuracy and robustness.
 Thus, the processing time for returning a star ID is increasing due to the increase in data processing and comparisons through the whole database.
@@
 
-In a quick review and analysis of the 3 prestigious and famous star recognition, we can come up with a conclusion that there is a trade-off between accuracy and robustness with the space complexity and processing time required.
+In a quick review and analysis of the 3 prestigious and famous star recognition algorithms, we can come up with a conclusion that there is a trade-off between accuracy and robustness with the space complexity and processing time required.
 For the star tracker system, the choice of algorithm to be implemented on will depend on the scale of the satellite project.
@@
 \noindent For the implementation on the nanosatellites, the computer system is a small embedded processor with limited memory and processing ability which can not handle a large number of computations.
-Therefore, we need an optimized algorithm that is accurate, robust and can be implemented on a concise computer system.
+Therefore, we need an optimized algorithm that is accurate, robust and can be implemented on a small computer system.
 \\
 
-\noindent The chosen star tracking algorithm is conducted by the research “An Autonomous Star Recognition Algorithm with Optimized Star Catalogue for Fast Search Performance” M.D.
+\noindent The chosen star tracking algorithm is from the paper “An Autonomous Star Recognition Algorithm with Optimized Star Catalogue for Fast Search Performance” by M.D.
 Pham, K.S.
@@
 Chen\cite{edselc.2-52.0-8487677997120120101,edseee.655799920130101}.
-The research introduces a novel star pattern identification using an optimized database and proposes a search tree data structure for quick and advanced parallel search.
+The algorithm introduces a novel star pattern identification using an optimized database and proposes a search tree data structure for quick and advanced parallel search.
 \\
@@
 		\item N: Number of stars appeared within the FOV of the star sensor.
-		\item $D_1, D_2, D_3…, D_n$: Distance from the reference star to all of its neighbors.
+		\item $D_1, D_2, D_3, ..., D_n$: Distances from the reference star to all of its neighbors.
 	\end{itemize}
@@
 \noindent To search and match the star pattern vector with the database, a special database structure is pre-built.
-The tree is built with multiple levels, the first level is N-Number of stars in the FOV, next layers will be the distances from the reference stars to all of its neighbors which are sorted ascendingly from nearest neighboring star to the farthest.
+The tree structure is built with multiple levels, the first level is N-Number of stars in the FOV, next layers will be the distances from the reference stars to all of its neighbors which are sorted ascendingly from nearest neighboring star to the farthest.
 \\
@@
 If all layers are matched the correct star ID will be returned; otherwise, we return a statement that the star pattern is a false pattern, no stars were matched.
-In this case, depend on the attitude determination system on the satellite, the star identification algorithm would be rerun or skipped to proceed the next star image.
+In this case, depend on the attitude determination system on the satellite, the star identification algorithm would be rerun or skipped to proceed to the next star image.
 

### 2019-01-19 thesis/2_chapters/chap3.tex
Fix all typos

@@
 \noindent \textbf{FPGA design flow}: The design begins with design entry, continues with simulation to verify the logic is implemented as expected, and then the tool will perform synthesis (also called mapping) to map the logic to the device architecture.
-Next the tool will create the interconnection between cells by place and routing (or fitting) the design.
+Next the tool will create the interconnection between cells by placing and routing (or fitting) the design.
 Another simulation after the fitting is done is a good practice.
@@
 
-\noindent Traditional SoC board is a fixed Application Specific Integrated Circuit (ASIC) with is prebuilt for only one particular function or task.
-The processing time of ASIC board is speedy and high-efficiency due to the unique hardware prebuilt for this task.
-In the trade-off, the development time of an ASIC board takes much time due to multiple stages of hardware synthesis, testing and verification and the cost of development is enormous.
-ASIC board is only suitable for mass-production strategy with over 1 million products per a development cycle.
+\noindent Traditional SoC board is a fixed Application Specific Integrated Circuit (ASIC) which is prebuilt for only one particular function or task.
+The processing time of ASIC board is fast and highly efficient due to the unique hardware prebuilt for this task.
+In the trade-off, the development time of an ASIC board takes much longer due to multiple stages of hardware synthesis, testing and verification and the cost of development is enormous.
+ASIC board is only suitable for mass-production strategy with over 1 million products per development cycle.
 \\
@@
 The algorithm or the program will be partitioned into suitable-size submodules.
-These submodules are later decided to implement on which side of the PSoC: Programmable Logics or Processing System.
-How the program partitioned is decided by the designer.
+These submodules are later decided to be implemented on which side of the PSoC: Programmable Logics or Processing System.
+How the program is partitioned, decided by the designer.
 \\
@@
 
-The star tracking algorithm is partitioned into 4 submodules shown in Figure~\ref{fig:3_7}. The 4 submodules include:
+The star tracking algorithm is partitioned into 4 submodules as shown in Figure~\ref{fig:3_7}. The 4 submodules include:
 \begin{itemize}
@@
 
-\noindent After partitioning, all submodules are implemented on the Processing system side to examine the runtime of each submodules. The result of profiling stage in Figure~\ref{fig:3_8}. \\
+\noindent After partitioning, all submodules are implemented on the Processing system side to examine the runtime of each submodule. The result of profiling stage is shown in Figure~\ref{fig:3_8}. \\
 
@@
 It can be explained because the centroiding stage is an image processing stage.
-Implementation of an image processing algorithm on general purpose processors is more costly and less effective than any other parallel processing approach like using a graphics processing unit (GPU), in this thesis, we design an IP core in the Programmable Logic side instead.
+Implementation of an image processing algorithm on general purpose processors is more costly and less effective than any other parallel processing approach like using a graphics processing unit (GPU), in this thesis, we design the centroiding module as an IP core in the Programmable Logic side instead.
 
@@
 In the first stage, the sky is captured by a Charge-coupled device(CCD) through lens then discretized into digital star images.
-In which, Each pixel is an 8-bit integer value which represents the intensity or brightness of a pixel(0 represent darkest pixel and 255 represents the brightest pixel).
+In which, each pixel is an 8-bit integer value which represents the intensity or brightness of a pixel(0 represents darkest pixel and 255 represents the brightest pixel).
 The star image is usually contaminated with noise as a result of dark current noise and non-star stellar object.
@@
 If a pixel Intensity is less than the threshold level, we will set its value to 0(the background level) to differentiate from star cluster pattern.
-After all false star noises are canceled, the centroiding algorithm proceeds.
+After all false star noise is canceled, the centroiding algorithm proceeds.
 \\
@@
 If a group of pixels belongs to a star cluster pattern, those vertices are connected.
-Therefore we can determine each independent star clusters by using graph traversing technique like Depth-First-Search (DFS) or Bread-First-Search (BFS).
-However, this submodule of the star tracking algorithm is implemented as an IP core by Hardware Description Language (HDL) which lack abilities to implement a recursive function or advanced data structure like Queue, Stack.
+Therefore we can determine each independent star cluster by using a graph traversing technique like Depth-First-Search (DFS) or Bread-First-Search (BFS).
+However, this submodule of the star tracking algorithm is implemented as an IP core by Hardware Description Language (HDL) which lack abilities to implement a recursive function or advanced data structure like Queue and Stack.
 \\
@@
 
-\noindent The centroiding again is partitioned into submodules for specific purposes as Figure~\ref{fig:3_19}.
+\noindent The centroiding again is partitioned into submodules for specific purposes as shown in Figure~\ref{fig:3_19}.
 
@@
 	\item \textbf{stream processing}: The submodule task is to process the one-pass scan algorithm after receiving a pixel from the stream.
-The submodule also in responsibility of maintaining and updating the labels and disjoint sets data structures stored in the BRAM.
+The submodule also is in the responsibility of maintaining and updating the labels and disjoint sets data structures stored in the BRAM.
 The pseudo codes of the implementation are shown in Figure~\ref{fig:3_20} and Figure~\ref{fig:3_21}
@@
 
-Figure~\ref{fig:3_13} shows a basic star image which then will be processed through the “Choose the reference star” stage.
-The first Image in an example is a typical star image.
+Figure~\ref{fig:3_13} shows a basic star image which will be processed through the “Choose the reference star” stage.
+The first Image in the example is a typical star image.
 The outer circle represents the FOV of the star Image, and the small blue dots represent the star clusters.
@@
 
-\noindent From the centre of the star Image, we calculate the distances from each star cluster to the centre by Euclidean distance as equation~\ref{eq:3_2}.
+\noindent We calculate the distances from each star cluster to the centre by Euclidean distance as given in equation~\ref{eq:3_2}.
 The star which is nearest to the centre (have the minimum distance value) will be chosen as the reference star.
@@
 After we have the reference star, the next stage is to generate the star pattern.
-The number of stars in the image is counted, and their distances to the reference star are calculated as equation~\ref{eq:3_3} to form a feature vector $f = \{N, D_1, D_2, D_3, … D_n\}$
+The number of stars in the image is counted, and their distances to the reference star are calculated using equation~\ref{eq:3_3} to form a feature vector $f = \{N, D_1, D_2, D_3, … D_n\}$
 
@@
 \noindent In case of mismatching, a tolerance will be added to research for another star ID.
-This search can be performed parallel to increase the searching speed due to the specific tree structure of the prebuilt SPD as in Figure~\ref{fig:3_16}.
+This search can be performed in parallel to increase the searching speed due to the specific tree structure of the prebuilt SPD as shown in Figure~\ref{fig:3_16}.
 

### 2019-01-19 thesis/2_chapters/chap4.tex
Fix all typos

@@
 \noindent The pixel data are streamed directly into memory by DMA module.
-The IP core is designed for centroiding processing the algorithm as soon as the first pixel data arrived.
-After the centroiding algorithm finishing, the IP core store the results of centroiding algorithm into BRAM and informs the PS by an interrupt signal.
-PS then takes the results from BRAM and process other stages.
+The IP core is designed for processing the centroiding algorithm as soon as the first pixel data arrived.
+After finishing the centroiding algorithm, the IP core stores the results of centroiding algorithm into BRAM and informs the PS by an interrupt signal.
+PS then takes the results from BRAM and processes the other stages.
 The data path is implemented through AXI.
@@
 \noindent The PS and PL side communicate through an interrupt controller.
-The interrupt controller informs the PS if the centroiding algorithm or hardware timer has finished, informs the DMA controller if the memory is full, the DMA controller then flush the old data to free the memory.
+The interrupt controller informs the PS if the centroiding algorithm or hardware timer has finished, informs the DMA controller if the memory is full.
+The DMA controller then flushes the old data to free the memory.
 BRAM controller is a dual channel BRAM which is readable from PS side and writable from PL side.
@@
 
-\noindent The graph~\ref{fig:4_3} shows the percentage of hardware resources used over available resources from the zedboard. We still have more spare resources of the FPGA for other tasks.
+\noindent Figure~\ref{fig:4_3} shows the percentage of hardware resources used over the available resources from the zedboard. We still have spare resources of the FPGA for other tasks.
 
@@
 \noindent As in Figure~\ref{fig:power_sum} and Figure~\ref{fig:power}, the Processing System(the ARM A9 processor) consumes 77\% of the power supplied while other hardware components like the IP core, BRAM consume less power.
-This is due to the fact that generic processors are designed for multiple purpose tasks; hence they are not optimal for power consumption as the hardware solution for a specific task.
+This is due to the fact that generic processors are designed for multiple purpose tasks; hence they are not optimal for power consumption compared to the hardware solution for a specific task.
 
@@
 
-The images simulated are based on the SSAO star catalog and the standard ESO star map.
-Randomized distribution false stars are added to each image.
+\noindent The images simulated are based on the SSAO star catalog and the standard ESO star map.
+Randomized distribution of false stars are added to each image.
 For each resolution dataset, we have 12530 simulated images.
@@
 
-The star tracker is configured as Table~\ref{tab:4_2}
+The star tracker is configured as shown in Table~\ref{tab:4_2}
 

### 2019-02-07 thesis/2_chapters/chap1.tex
Update thesis Feb 7

@@
 
-\noindent Nanosatellite is a small artificial satellite with a wet mass(the total mass of the hardware plus fuel and oxidizer) between 1 – 10 kg.
+\noindent Nanosatellite is a small artificial satellite with a wet mass(the total mass of the hardware plus fuel and oxidizer) between 1 - 10 kg.
 Nanosatellites are cheap but capable of performing commercial missions and has led researchers and scientists to explore the new way to use the Nanosatellites in LEO\cite{network}.
@@
 
-Another way of attitude determination approach is using star trackers.
+Another way of attitude determination approach is using star trackers\cite{edseee.38797119950101}.
 Star Tracker is an optical-electronics subsystem comprises of a CCD or CMOS Image sensor attached to an optical lens and a computing system, usually a microprocessor integrated into an ASIC board.
@@
 \section{Major contributions}
-The following are the significant contributions of this research project.
+The major contributions of this research project are summarized as follows:
 \begin{itemize}
-	\item Investigates and Analyses the star tracking algorithms on the advantages and weaknesses of traditional methods.
-	\item Reviews and examines in details the proposed algorithm by precedent research.
-	\item Implements the proposed method in term of hardware and software co-processing approach on an embedded system for star tracker.
+	\item First, we review three classic star tracking algorithms which are applying in commercial star trackers.
+Analyzing and comparing their strengths and weaknesses.
+We then discuss the novel star tracking algorithm presented in ``An Autonomous Star Recognition Algorithm with Optimized Star Catalogue for Fast Search Performance'' by M.D.
+Pham, K.S.
+Low and S.H.
+Chen\cite{edselc.2-52.0-8487677997120120101,edseee.655799920130101}, introduce the steps of the algorithm and explain why the algorithm is suitable for applying in nano-satellites compared to the three classic star tracking algorithms and chosen to be implemented by the hardware-software co-processing approach.
+	\item Based on the algorithm analysis, we partition the algorithm into submodules and propose which part should be implemented on the software part or the hardware part.
+Our main contribute includes (a) an optimized star tracking algorithm for hardware-software co-processing approach, (b) a star tracking embedded system for nano-satellites.
 \end{itemize}
@@
 	\item Chapter 4: Discusses the result of the implementation regarding runtime performance and hardware resources.
+	\item Chapter 5: Summarizes the work and proposes future research topics.
 \end{itemize}

### 2019-02-07 thesis/2_chapters/chap2.tex
Update thesis Feb 7

@@
 	\item LIS mode: the initial attitude is unknown, the star tracker must determine it which is the most critical part of the star tracking operation.
-LIS mode is operated at the time when the power system is switched on or reset after an attitude determination attempt from tracking mode failed\cite{edselc.2-52.0-8487677997120120101}.
+LIS mode is operated at the time when the power system is switched on or reset after an attitude determination attempt if tracking mode failed\cite{edselc.2-52.0-8487677997120120101}.
 	\item Tracking mode: after the initial attitude is recognized.
@@
 The first step is to acquire the image which is accomplished by the image sensor.
-The image acquired has to be processed for estimating the coordinates of the stars in the image plane.
+The image acquired has to be processed for estimating the coordinates of the stars in the image plane as shown in Figure~\ref{fig:2_2}.
 This is completed by applying the centroiding process on the image.
@@
 The output is the coordinate of every star presenting.
-Due to distributed energy surface, a star projection is spread over a 3x3 to 11x11 square area\cite{ntu.54658220060101}, the star projection is a group of connected pixels.
-Therefore, the best way to identify the star clusters is to apply the ‘connected component’ algorithm.
+Due to distributed energy surface, a star projection is spread over a 3x3 to 11x11 square area\cite{ntu.54658220060101}, and the star projection is a group of connected pixels.
+Therefore, the best way to identify the star clusters is to apply the connected component algorithm.
 
@@
 % Table 2.1
-\noindent Table~\ref{tab:starList} .\\
+\noindent Table~\ref{tab:starList} shows how star centroids in an image, as in Figure~\ref{fig:2_4} are stored under a list of Cartesian coordinates.
+Besides, star trackers may use other coordinate systems like the Polar coordinate system, Cylindrical or Spherical coordinate systems.\\
 
@@
 
+% Equation 2.1
 \noindent A star pattern is spread over an area so we can calculate its centroid by applying the weighted pixel intensity technique.
-Assume that (i, j) is the horizontal and vertical centroid coordinate of a star, $I_{ij}$ is each pixel intensity of the star pattern, i and j are the horizontal and vertical coordinates of each pixel of the star pattern.
+Equation~\ref{eq:2_1} shows how to calculate a star centroid in Cartesian coordinate.
+Assume that (x, y) is the horizontal and vertical centroid coordinate of a star cluster, $I_{ij}$ is each pixel intensity of the star pattern, i and j are the horizontal and vertical coordinates of each pixel within this star cluster.
 
@@
 \ntuepsfig[width=\textwidth]{2_3}{Star clusters represented in a 2D image plane}
-
-% Equation 2.1
-\noindent Equation~\ref{eq:2_1}
 
@@
 % Equation 2.2
-\noindent The star triplet will form 2 angular distances $\theta_1, \theta_2$ and 1 angular angle $\theta$ which are defined by Equation~\ref{eq:2_2}
+\noindent The star triplet will form 2 angular distances $\theta_1, \theta_2$ and 1 angular angle $\theta$ which are defined by Equation~\ref{eq:2_2}.
+$V_A, V_B, V_C$ are the Euclidean vectors connecting each star in the star triplet with the star tracker(or the spacecraft), $V_{AB}$ is the Euclidean vector connecting star A and star B.
+Therefore, we have the Euclidean vector connecting star A and star C denoted by $V_{AC}$.
 \begin{equation}
@@
 
-\noindent The star triplet will form 2 angular distance $\theta_1, \theta_2$ and 1 angular angle $\theta$ which are defined by Equation~\ref{eq:2_3}
 \begin{equation}
-	f = \{\theta, \theta_1, \theta_2\}
+	f = \{\theta_1, \theta_2, \theta\}
 	\label{eq:2_3}
@@
 % Table 2.2
-\noindent Table~\ref{tab:Liebe_SPD}.
+\noindent Table~\ref{tab:Liebe_SPD} shows an example of Liebe star pattern database.
+Each feature vector $f = \{\theta_1, \theta_2, \theta\}$ would return a corresponding star ID which identify the identification of the reference star.
+Thus, The table is sorted for quick searching purpose.
+\\
 
-\begin{ntutab}{|c|c|c|}{Liebe_SPD}{An example of Liebe star pattern database}
+\begin{ntutab}{|c|c|c|c|}{Liebe_SPD}{An example of Liebe star pattern database}
 	\hline
-	$\theta_1$ & $\theta_2$ & $\theta$ \\
+	$\theta_1$ & $\theta_2$ & $\theta$ & Star ID \\
 	\hline
-	54 & 80 & 32 \\
-	54 & 80 & 33 \\
-	54 & 81 & 32 \\
-	54 & 81 & 33 \\
-	54 & 82 & 32 \\
-	54 & 82 & 33 \\
-	55 & 80 & 32 \\
-	55 & 80 & 33 \\
-	55 & 81 & 32 \\
-	55 & 81 & 33 \\
-	55 & 82 & 32 \\
-	55 & 82 & 33 \\
-	56 & 80 & 32 \\
-	56 & 80 & 33 \\
-	56 & 81 & 32 \\
-	56 & 81 & 33 \\
-	56 & 82 & 32 \\
-	56 & 82 & 33 \\
+	54 & 80 & 32 & 55 \\
+	54 & 80 & 33 & 631 \\
+	54 & 81 & 32 & 114 \\
+	54 & 81 & 33 & 1297 \\
+	54 & 82 & 32 & 611 \\
+	54 & 82 & 33 & 168 \\
+	55 & 80 & 32 & 284 \\
+	55 & 80 & 33 & 811 \\
+	55 & 81 & 32 & 1289 \\
+	55 & 81 & 33 & 6 \\
+	55 & 82 & 32 & 602 \\
+	55 & 82 & 33 & 1165 \\
+	56 & 80 & 32 & 222 \\
+	56 & 80 & 33 & 327 \\
+	56 & 81 & 32 & 470 \\
+	56 & 81 & 33 & 104 \\
+	56 & 82 & 32 & 1058 \\
+	56 & 82 & 33 & 1222 \\
 	\hline
@@
 \noindent The weakness of this algorithm is the weak robustness due to the limitation of star utilization.
-It only employs the three nearest stars to the centre and discards other stars which will then lead to a mismatch if the 2 predefined nearest neighboring stars does not appear in the star image.
-Besides, if the reference star appears in the final entry of the Star Pattern Database.
+It only employs the three nearest stars to the centre and discards other stars which will then lead to a mismatch if the two predefined nearest neighboring stars do not appear in the star image.
+Besides, if the reference star appears in the final entry of the Star Pattern Database, the searching algorithm would fall into the worst case.
 
@@
 
-% Table 2.3
-\noindent Table~\ref{tab:Pyramid_pattern}.
-
 \begin{ntutab}{|c|c|c|}{Pyramid_pattern}{A Pyramid star pattern example}
@@
 \noindent One of the advantages of the pyramid algorithm is that it employs 4 stars to build the feature vector compared to only 3 stars of the Liebe algorithm.
-Compared to Liebe’s, this method is more robust since it makes the star recognition process more accurate as six features are utilized for identification purpose compared to only three features used by the Liebe algorithm\cite{HETE}.
+Compared to Liebe’s, this method is more robust since it makes the star recognition process more accurate as six features (as denoted in Equation~\ref{eq:2_4}) are utilized for identification purpose compared to only three features used by the Liebe algorithm\cite{HETE}.
+The Table~\ref{tab:Pyramid_pattern} describes how the star patterns $p_1, p_2, p_3, p_4, p_5, p_6$ are defined by angular distances between Star 1 and Star 2.
 \\
@@
 
-\noindent The chosen star tracking algorithm is from the paper “An Autonomous Star Recognition Algorithm with Optimized Star Catalogue for Fast Search Performance” by M.D.
+\noindent The chosen star tracking algorithm is from the paper ``An Autonomous Star Recognition Algorithm with Optimized Star Catalogue for Fast Search Performance'' by M.D.
 Pham, K.S.
@@
 \\
-
-\noindent Due to the advance of the previous research have been proven, this star tracking algorithm will be chosen to be implemented on the hardware. \\
 
@@
 
-\noindent To search and match the star pattern vector with the database, a special database structure is pre-built.
-The tree structure is built with multiple levels, the first level is N-Number of stars in the FOV, next layers will be the distances from the reference stars to all of its neighbors which are sorted ascendingly from nearest neighboring star to the farthest.
+\noindent To search and match the star pattern vector with the database, a special the tree structured database is pre-built.
+Figure~\ref{fig:2_9} shows an example of this tree structured database.
+The tree is built with multiple levels, the first level is N-Number of stars in the FOV, next layers will be the distances from the reference stars to all of its neighbors which are sorted ascendingly from nearest neighboring star to the farthest.
 \\

### 2019-02-07 thesis/2_chapters/chap3.tex
Update thesis Feb 7

@@
 However, instead of implementing the logic using transistor gates, the logic was in many cases implemented by memory fashioned as look up tables.
+Figure~\ref{fig:3_LUT} shows an example of a Look up table implementing a 4-input logic function $F = (A \wedge B) \vee (C \wedge \bar{D})$.
+Instead of connecting the logic gates, the Lookup table memorizes the output result corresponding to the input combinations.
 \\
@@
 Common signals like clocks are routed on special routing networks called global networks.
-\\
+The FPGA routing architecture is demonstrated in Figure~\ref{fig:3_Routing}\\
 
@@
 If this looks good, the next step to use the tool to create a programming file, which is then downloaded into the FPGA device for testing\cite{Coursera}.
-\\
+The FPGA design flow is presented in Figure~\ref{fig:3_DesignFlow} \\
 
@@
 
-\ntuepsfig[width=\textwidth]{3_spartan}{Xilinx Spartan-3AN Family Architecture\cite{spartan}}
+\ntuepsfig[width=4in]{3_spartan}{Xilinx Spartan-3AN Family Architecture\cite{spartan}}
 
@@
 
-\pagebreak 
+% \pagebreak 
 \subsection{System-on-a-chip}
@@
 
-\noindent Traditional SoC board is a fixed Application Specific Integrated Circuit (ASIC) which is prebuilt for only one particular function or task.
+\noindent Traditional SoC board is a fixed Application Specific Integrated Circuit (ASIC) (Figure~\ref{fig:3_1}) which is prebuilt for only one particular function or task.
 The processing time of ASIC board is fast and highly efficient due to the unique hardware prebuilt for this task.
@@
 
-\noindent Another approach is using an embedded processor for the implementation.
+\noindent Another approach is using an embedded processor(Figure~\ref{fig:3_2}) for the implementation.
 All stages of the development are equivalent to a software development process.
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 % Section 3.2
@@
 The algorithm or the program will be partitioned into suitable-size submodules.
-These submodules are later decided to be implemented on which side of the PSoC: Programmable Logics or Processing System.
+These submodules are later decided to be implemented on which side of the PSoC: Programmable Logics or Processing System as illustrated in Figure~\ref{fig:3_5}.
 How the program is partitioned, decided by the designer.
@@
 Then based on the profiling and asymptotic analysis stated above, we can decide correctly which parts or submodules can be implemented in hardware instead of software.
-\\
+The profiling steps \\
 
@@
 % Table 3.1
-\noindent Table~\ref{tab:profiling}.
+% \noindent Table~\ref{tab:profiling}.
 
-\begin{ntutab}{|c|c|}{profiling}{Module Profiling Result}
-	\hline
-	\textbf{Modules} & \textbf{Runtime(nanoseconds)} \\
-	\hline
-	Centroiding & 17688 \\
-	\hline
-	Choose Reference Star & 54 \\
-	\hline
-	Find the star pattern & 30 \\
-	\hline
-	Pattern matching (with tree database) & 20 \\
-	\hline
-\end{ntutab}
+% \begin{ntutab}{|c|c|}{profiling}{Module Profiling Result}
+% 	\hline
+% 	\textbf{Modules} & \textbf{Runtime(nanoseconds)} \\
+% 	\hline
+% 	Centroiding & 17688 \\
+% 	\hline
+% 	Choose Reference Star & 54 \\
+% 	\hline
+% 	Find the star pattern & 30 \\
+% 	\hline
+% 	Pattern matching (with tree database) & 20 \\
+% 	\hline
+% \end{ntutab}
 
@@
 The pixel which has a higher value than threshold level belongs to a star cluster while the pixel which has a lower value than the threshold belongs to the background.
-Figure~\ref{fig:3_10} shows how to separate star clusters from the background, the threshold, in this case, is 70.
+Figure~\ref{fig:3_10} shows how to separate star clusters from the background.
+\\
+
+\noindent Most of the star images are affected by noise.
+Sometimes, the star tracker misleads the noise as a star which often leads to a mismatch.
+Therefore, the threshold should be carefully chosen.
+If we set the threshold too low, it would lead to mismatches.
+Otherwise, if we set the threshold too high, some stars would be missing from the image.
+Between 0-255, we choose the threshold value 70 which mostly produce high matching accuracy.
 
@@
 The one-pass scan algorithm is a connected component labeling approach which performs a scanning throughout the star image.
-A pixel in a star cluster will be put into an equivalent independent subset if two subsets having pixels connected to each other will be merged into one big set by the applying the following rules.
+Each star cluster is equivalent to each disjoint set.
+While scanning the picture, we try to identify which star pixel is corresponding to which disjoint set by applying the following rules.
 \\
 
-\noindent We maintain a disjoint set data structure when scanning performed if a pixel P is non-background, we consider its left and above pixels as in Figure~\ref{fig:3_11}. There are 3 cases:
+\noindent If the pixel value is higher than the defined threshold which distinguish between the star pixel and the background of the image, we consider its left and above pixels as in Figure~\ref{fig:3_11}.
+There are 3 cases:
 
@@
 \noindent In figure~\ref{fig:3_17}, the pixel coordinates(i,j) in 2D images would be represented by the stream order(k).
-The reason we need to have a converting framework is that we need to look up the above and left pixels of a considering pixel in the one-pass scan algorithm.
+The reason we need to have a converting framework is that we need to look up the above and left pixels of the pixel in the one-pass scan algorithm.
 \\
@@
 	$$i = k / ImgHeight$$
-	$$j = k mod ImgHeight$$
+	$$j = k\ mod\ ImgHeight$$
 

### 2019-02-07 thesis/2_chapters/chap4.tex
Update thesis Feb 7

@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% Section 4.1
+\section{Star data analysis}
+
+\noindent The main factors affect the runtime of the designed system are:
+\begin{itemize}
+    \item Image resolution
+    \item Number of stars in one image
+    \item Star area (in pixels) of one star
+\end{itemize}
+
+\noindent If the resolution of the star image is large, the runtime and complexity of the algorithm will increase.
+Therefore, more optimizations are needed in both the hardware and the software of the system.
+Number of stars in one image is another aspect that we should consider.
+Since we need to maintain a disjoint set data structure on hardware, we need to know the maximum and the average number of stars in one image.
+As shown in Figure~\ref{fig:4_4}, the maximum number of star in one image is 24.
+Therefore, we should pre-allocate around 50 disjoint sets.
+We also expect to see an average of 10-11 stars with an average of pixel area around 18-19 pixels over one star as in Figure~\ref{fig:4_5}.
+This information helps us to pre-allocate the hardware memory BRAM and optimize it if needed.
+\\
+
+\noindent The images simulated are based on the SSAO star catalog and the standard ESO star map.
+Randomized distribution of false stars are added to each image.
+For each resolution dataset, we have 12530 simulated images.
+\\
+
+% Figure 4.4
+\ntuepsfig[scale=1.0]{4_4}{Number of stars in one image distribution}
+
+% Figure 4.5
+\ntuepsfig[scale=1.0]{4_5}{Star area distribution}
+
+\noindent The algorithm runtime performance is then compared between the implementation run on the embedded processor and the application executed on software-hardware co-processing strategy.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% Section 4.1
+% Section 4.2
 \section{Hardware design}
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection{Components and Design Flow}
 
-The hardware components shown in Figure~\ref{fig:4_1} includes:
+The system design are shown in Figure~\ref{fig:4_1}. The IP modules as represented by Xilinx Vivado software are illustrated in Figure~\ref{fig:4_2}. The system includes several components such as:
 \begin{itemize}
@@
 
-\noindent Figure~\ref{fig:4_3} shows the percentage of hardware resources used over the available resources from the zedboard. We still have spare resources of the FPGA for other tasks.
+\noindent Table~\ref{tab:resource} shows the percentage of hardware resources used over the available resources from the zedboard. We still have spare resources of the FPGA for other tasks.
 
@@
 % Figure 4.3
-\ntuepsfig[width=\textwidth]{4_3}{Hardware resource consumption}
+% \ntuepsfig[width=\textwidth]{4_3}{Hardware resource consumption}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% Section 4.2
+% Section 4.3
 \newpage
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Star data analysis}
-
-\noindent The main factors affect the runtime of the designed system are:
-\begin{itemize}
-    \item Image resolution
-    \item Number of stars in one image
-    \item Star area (in pixels) of one star
-\end{itemize}
-
-\noindent The images simulated are based on the SSAO star catalog and the standard ESO star map.
-Randomized distribution of false stars are added to each image.
-For each resolution dataset, we have 12530 simulated images.
-\\
-
-% Figure 4.4
-\ntuepsfig[scale=1.0]{4_4}{Number of stars in one image distribution}
-
-% Figure 4.5
-\ntuepsfig[scale=1.0]{4_5}{Star area distribution}
-
-\noindent The algorithm runtime performance is then compared between the implementation run on the embedded processor and the application executed on software-hardware co-processing strategy.
-
 %%%%%%%%%
 % subsubsection 4.2.2.1
-\newpage \subsection{512x512 dataset}
+\subsection{512x512 dataset}
 
-The star tracker is configured as shown in Table~\ref{tab:4_2}
+The first dataset is generated by a MATLAB sky simulator software.
+It simulates the star images captured by the star tracker at specific attitudes.
+A simulated star tracker is configured as Table~\ref{tab:4_2}.
+It has $20^o$ field of view (FOV) and can capture the stars that have magnitude threshold Mv less than 5.0.
+The star camera's attitude is rotated from 0 to $360^o$ right ascension and from $-90^o$ to $90^o$ declinations with an angle increment of $2^o$ to perform a full scan of all the stars from the SAO SKY 2000 star catalogue.
+The dataset has total 12530 sky images.
 
@@
     \hline
-    Field of View (FOV) & J2000 \\
-    \hline
-    Inertial frame & 8.0 degrees full cone \\
+    Field of View (FOV) & $20^o * 20^o$ \\
     \hline
     Visual magnitude threshold & 5.0 \\
+    \hline
+    Star catalogue & SAO SKY 2000 \\
     \hline
@@
 %%%
-\textbf{Software runtime}
+\noindent \textbf{A. Software runtime}
+
+\noindent The algorithm is developed on the zedboard processing system which runs on an 1.0 GHz ARM-A9 CPU with 512 MB DDR3 RAM.
+The algorithm software performance is described in Table~\ref{tab:4_3} and visualized by Figure~\ref{fig:4_6}.
+The runtime of 4 modules are measured in both average and worst-case over 12530 sky images.
+\\
+
+\noindent As we know from the profiling stage, the runtime of the centroiding module is the most critical time-consuming part.
+It can be explained that this stage deals with image processing which is the highest complexity in computation compared to the 3 remaining stages.
+\\
+
+\noindent Thus, the worstcase runtimes are not far from the averages.
+This pattern can be explained by the number of stars in one Image and the star area distribution.
+The distributions are approximately uniform with low standard deviations.
+Therefore, our system can run stably despite different configuration.
+\\
+
+\noindent Overall, The average runtime is 17855 us (about 17.86 ms) on each image.
 
@@
 
-\noindent The average runtime is 17855 us (about 17.86 ms)
-
 %%%
 \newpage
-\noindent \textbf{Hardware – Software Co-processing runtime}
+\noindent \textbf{B. Hardware - Software co-processing runtime}
+
+\noindent The algorithm is re-developed on the zedboard in both the processing system(software) and the programmable logic(hardware).
+The processing system runs on an 1.0 GHz ARM-A9 CPU with 512 MB DDR3 RAM while the programmable logic runs on the FPGA fabric with 100 MHz Clock rate and a total of 560KB BRAM (Block RAM).
+The algorithm is partitioned into 6 submodules.
+The first 3 submodules: IP core Initiation, DMA Data Streaming and Centroiding are implemented on the programmable logic side.
+The 3 remaining submodules: Choosing Reference Star, Finding Star Pattern and Pattern Matching are implemented on the processing system.
+The system performance is described in Table~\ref{tab:4_4} and visualized by Figure~\ref{fig:4_7}.
+\\
+
+\noindent The Centroiding software submodule is replaced by 3 equivalent hardware submodules. The runtime is significantly improved from nearly 17 ms to nearly 6.2 ms. \\
+
+\noindent The average total runtime is 6352 us(about 6.35 ms).
 
@@
 % Figure 4.7
-\ntuepsfig[width=\textwidth]{4_7}{Software-Hardware co-processing runtime}
-
-\noindent The average runtime is 6352 us(about 6.35 ms)
+\ntuepsfig[width=\textwidth]{4_7}{Software - Hardware co-processing runtime}
 
@@
 
-\noindent The images are captured by the star tracker SST-20S described by Table~\ref{tab:4_7}
+\noindent Next, we perform a study on 1019 star images are captured by the star tracker SST-20S currently mounted on a low earth orbit satellite, VELOX-CI\cite{8374923}.
+The specifications of the SST-20S star tracker is described by Table~\ref{tab:4_7}.
 
@@
 
-\textbf{Software runtime}
+\noindent \textbf{A. Software runtime}
+
+\noindent The algorithm is examined again on the zedboard processing system (1.0 GHz ARM-A9 CPU, 512 MB DDR3 RAM).
+Its performance is listed in Table~\ref{tab:4_5} and visualized by Figure~\ref{fig:4_8}.
+The runtime of 4 modules is measured in both average and worst-case over 1019 sky images.
+\\
+
+\noindent As the image size increased, the runtime of the Centroiding part increases and other module runtimes remain approximately the same.
+We can explain that the runtime of the centroiding part is proportional to the complexity of the image processing task, while other module complexities depend on the properties of the images which are the number of stars, the brightness of the star catalog threshold.
+\\
+
+\noindent The average runtime is 70780 us (about 70.78 ms). The runtime has increased 4 times (70 ms compared to 17 ms). \\
 
@@
 
-\noindent The average runtime is 70780 us (about 70.78 ms)
+%%%
+\noindent \textbf{B. Hardware - Software Co-processing runtime}
 
-%%%
-\newpage
-\noindent \textbf{Hardware – Software Co-processing runtime}
+\noindent We again tested the algorithm on the large dataset with the Zedboard System-on-a-chip Processing System and Programmable Logic (PS - PL).
+The system performance is described in Table~\ref{tab:4_6} and visualized by Figure~\ref{fig:4_9}.
+\\
+
+\noindent The total runtime of the Centroiding module is around 13.3 ms.
+Compared to 6.35 ms of the small dataset runtime (512x512), the Hardware-Software Centroiding submodule runtime only increases 2 times.
+As we look further into each submodule, the DMA Data Streaming submodule runtime has a significant change (2.4 ms to 9.8 ms) while the Centroiding submodule runtime is stable (3.7 ms and 3.5 ms).
+This can be explained by the hardware design has been proposed and introduced in Chapter 4.2 ``Hardware design''.
+The DMA Data Streaming submodule streams the image pixels into the system memory, it is the only submodule that affected by the image size complexity.
+Because the Hardware-Software Centroiding submodule takes the pixel coordinates as inputs, this architecture design helps our system run stably despite the changing of the image size.
+\\
+
+\noindent The total average runtime is 13636 us (about 13.64 ms).
 
 % Table 4.6
-\begin{ntutab}{|c|c|c|}{4_6}{Hardware – Software Co-processing runtime}
+\begin{ntutab}{|c|c|c|}{4_6}{Hardware - Software Co-processing runtime}
     \hline
@@
 % Figure 4.9
-\ntuepsfig[width=\textwidth]{4_9}{Hardware – Software Co-processing runtime}
-
-\noindent The average runtime is 13636 us (about 13.64 ms)
+\ntuepsfig[width=\textwidth]{4_9}{Hardware - Software Co-processing runtime}
 
@@
 % subsection 4.2.3
-\newpage \subsection{Runtime Comparison}
+\subsection{Runtime Comparison}
+
+Lastly, we perform the final test to compare the runtimes of the 3 classic algorithms and the proposed algorithm by software processing against the proposed algorithm by software-hardware co-processing.
+The experiment results are benchmarked in Table~\ref{tab:4_7} and visualized by Figure~\ref{fig:4_10}.
+\\
+
+\noindent The software system is implemented on the zedboard with a 1.0 GHz ARM-A9 CPU and 512 MB DDR3 RAM.
+The hardware-software co-processing system is executed on the zedboard Processing system -Programmable Logic with a 1.0 GHz ARM-A9 CPU, 512 MB DDR3 RAM (PS) and the FPGA fabric with 100 MHz Clock rate, 560KB BRAM (PL).
+\\
+
+\noindent The experimental results show that the implementation of the proposed method by software-hardware co-processing has successfully reduced the runtime of the Lost-in-Space star tracking algorithm.
 
@@
     \hline
-    \textbf{Liebe method} & 190.6 & 304.7 \\
+    \textbf{Liebe method SW} & 190.6 & 304.7 \\
     \hline

### 2019-04-02 thesis_supports/Response_Reviewer1/Response_Reviewer1.tex
Add supports

\documentclass[dvips,a4paper,12pt]{report}
\usepackage{xcolor}
\usepackage[
    top=0.6in,
    bottom=0.6in,
    right=0.6in,
    left=0.6in]{geometry}

\begin{document}
\pagenumbering{arabic}

% ----------------------------------------- Begin content --------------------------------------------- %
%%% letter
\noindent Respected Examiner,

\noindent Thank you for reviewing my thesis.

\begin{center}
    \textbf{Thesis Title: Implementation of an Autonomous Star Recognition Algorithm using Hardware-Software Co-processing Approach} 
\end{center}

\noindent Firstly, I would like to thank you for your insightful comments. These excellent comments have helped significantly improve my thesis. This letter addresses each of the raised points and notes precisely how I have responded and included the comments into my revised thesis. \\

\vspace{0.5in}

\noindent Sincerely yours,

\noindent Dang Le Dang Khoa

%%% Q&A
\newpage

\color{blue}
\noindent \large{\textbf{Examiner: 1}}

\begin{enumerate}
    \color{blue}
    \item There are some obvious typos and format problems in the thesis. For example, in Page 7, the caption ‘table 2.1’ is written, but the whole table is given in Page 8. Please check and correct them.

    \color{black}
    Answer

    \color{blue}
    \item In this thesis, the author shows some figures such as Fig. 2.2, 2.3 without any explanation. Please add some explanation to these figures in the thesis content.

    \color{black}
    Answer

    \color{blue}
    \item In Chapter 3.3.1, the author applied thresholding technique in order to eliminate the noise and separate star clusters from the background. But the author did not explain how to choose the threshold.

    \color{black}
    Answer

    \color{blue}
    \item The author claimed that the proposed prebuilt tree structured star pattern database (SPD) was able to reduce space complexity while maintaining high accuracy and robustness, so this optimized algorithm could be used for nanosatellites which have limited memory. However, there is no comparison between the SPD algorithm and traditional algorithm on accuracy, storage consumption, and robustness in this thesis.

    \color{black}
    Answer

    \color{blue}
    \item In Chapter 4.2, the author compares runtime spent by traditional methods and the proposed method in this thesis. He lists specific software runtime and hardware – software co-processing runtime when the same image dataset is used. Details of images used in experiments are also provided. However, the author only lists tables and figures to show image specifications and runtime. He does not give even one word to explain or conclude his experiment results.

    \color{black}
    Answer

    \color{blue}
    \item In Chapter 4.1, the author gives experiment results showing hardware consumption and power consumption when the proposed method is applied. But he does not give comparison on consumption between traditional methods and his own method, therefore, readers do not know how to evaluate his experiment results. If he could add experiment results about power and hardware consumption when traditional methods are used (under the same experimental conditions), and then give a comparison between traditional methods and his method, the advantages of his proposed method would be clearer.

    \color{black}
    Answer

\end{enumerate}

% ----------------------------------------- End content --------------------------------------------- %
\end{document}

### 2019-04-02 thesis_supports/Response_Reviewer2/Response_Reviewer2.tex
Add supports

--- 2019-04-02 thesis_supports/Response_Reviewer1/Response_Reviewer1.tex
@@
 \usepackage{xcolor}
+\usepackage{enumitem}
 \usepackage[
@@
 \color{blue}
-\noindent \large{\textbf{Examiner: 1}}
+\noindent \large{\textbf{Examiner: 2}}
 
@@
     \color{blue}
-    \item There are some obvious typos and format problems in the thesis.
-For example, in Page 7, the caption ‘table 2.1’ is written, but the whole table is given in Page 8.
-Please check and correct them.
+    \item There are many careless mistakes in the thesis.
+Tables and figures are not explained in the body of the thesis, equations are given without explanations, unfinished sentences, etc.
+All these are indicated on the relevant pages in the thesis.
+Please correct and give explanations as requested.
 
@@
     \color{blue}
-    \item In this thesis, the author shows some figures such as Fig. 2.2, 2.3 without any explanation. Please add some explanation to these figures in the thesis content.
+    \item Page 29. Please explain why the threshold is chosen to be 70 to separate star clusters from the background. That will happen if the threshold is reduced or increase?
 
@@
     \color{blue}
-    \item In Chapter 3.3.1, the author applied thresholding technique in order to eliminate the noise and separate star clusters from the background.
-But the author did not explain how to choose the threshold.
+    \item Conclusion must be made for the study, so I would like to see a chapter on conclusion which includes the following:
+    \begin{enumerate}[label=(\alph*)]
+        \color{blue}
+        \item One of the objective of the candidate's thesis is to implement and evaluate the performance of a star tracking algorithm, so what is the conclusion of the evaluation of the performance?
+Can it be used for the attitude determination sensor mounted on a spacecraft?
 
@@
         \color{blue}
-    \item The author claimed that the proposed prebuilt tree structured star pattern database (SPD) was able to reduce space complexity while maintaining high accuracy and robustness, so this optimized algorithm could be used for nanosatellites which have limited memory.
-However, there is no comparison between the SPD algorithm and traditional algorithm on accuracy, storage consumption, and robustness in this thesis.
+        \item Another objecttive of the thesis is to benchmark and optimize the algorithm in terms of the poer consumption and the area of transistor implementation.
+What is the conclusion?
+What is the benchmark now?
+Did the candidate do optimization?
+What I got from the thesis are just the results of the power consumed, but it is necessary that the candidate describes how he did the optimization.
 
@@
         Answer
-
-    \color{blue}
-    \item In Chapter 4.2, the author compares runtime spent by traditional methods and the proposed method in this thesis.
-He lists specific software runtime and hardware – software co-processing runtime when the same image dataset is used.
-Details of images used in experiments are also provided.
-However, the author only lists tables and figures to show image specifications and runtime.
-He does not give even one word to explain or conclude his experiment results.
-
-    \color{black}
-    Answer
-
-    \color{blue}
-    \item In Chapter 4.1, the author gives experiment results showing hardware consumption and power consumption when the proposed method is applied.
-But he does not give comparison on consumption between traditional methods and his own method, therefore, readers do not know how to evaluate his experiment results.
-If he could add experiment results about power and hardware consumption when traditional methods are used (under the same experimental conditions), and then give a comparison between traditional methods and his method, the advantages of his proposed method would be clearer.
-
-    \color{black}
-    Answer
+    \end{enumerate}
 

### 2019-04-02 thesis/1_foreword/originality.tex
Add supports

\addcontentsline{toc}{chapter}{Statement of Originality}
\begin{center}
	\textbf{\large Statement of Originality}
\end{center}

\noindent I hereby certify that the work embodied in this thesis is the result of original research, is free of plagiarised materials, and has not been submitted for a higher degree to any other University or Institution. \\

\vspace{2in}

\begin{multicols}{2}
    \begin{flushleft}
        ........................ \\
        \textbf{Date}
    \end{flushleft}

    \columnbreak

    \begin{flushright}
        ........................ \\
        \textbf{Dang Le Dang Khoa} \\
    \end{flushright}
\end{multicols}

### 2019-04-02 thesis/1_foreword/supervisor.tex
Add supports

\addcontentsline{toc}{chapter}{Supervisor Declaration Statement}
\begin{center}
	\textbf{\large Supervisor Declaration Statement}
\end{center}

\noindent I have reviewed the content and presentation style of this thesis and declare it is free of plagiarism and of sufficient grammatical clarity to be examined. To the best of my knowledge, the research and writing are those of the candidate except as acknowledged in the Author Attribution Statement. I confirm that the investigations were conducted in accord with the ethics policies and integrity standards of Nanyang Technological University and that the research data are presented honestly and without prejudice.

\vspace{2in}

\begin{multicols}{2}
    \begin{flushleft}
        ........................ \\
        \textbf{Date}
    \end{flushleft}

    \columnbreak

    \begin{flushright}
        ........................ \\
        \textbf{Assoc Prof Chen Shoushun} \\
    \end{flushright}
\end{multicols}

### 2019-04-03 thesis_supports/Response_Reviewer2/Response_Reviewer2.tex
Pre Final check

@@
 \usepackage{xcolor}
+\usepackage{float}
 \usepackage{enumitem}
+\usepackage{graphicx}
+    \graphicspath{ {./img/} }
 \usepackage[
@@
     \color{black}
-    Answer
+    Thanks for pointing these out in your ``Additional Document'' file. I have checked and fixed them all. I also have amended detailed explanations and restructured Chapter 3 and 4. \\
 
     \color{blue}
-    \item Page 29. Please explain why the threshold is chosen to be 70 to separate star clusters from the background. That will happen if the threshold is reduced or increase?
+    \item Page 29. Please explain why the threshold is chosen to be 70 to separate star clusters from the background. What will happen if the threshold is reduced or increase?
 
     \color{black}
-    Answer
+    I have amended a precise explanation to chapter 3.3.1 Centroiding (pages: 28,29,30). To summarize how to choose the threshold value:
+
+    \begin{itemize}
+        \item Firstly, I perform an analysis by averaging and counting the occurences of all pixel values in the star image dataset. 
+        \item The result of the analysis would form a pattern which is shown like the below image.
+It includes 2 significant clusters: the first cluster is the background pixel values which formed near 0 Intensity value and the second cluster is the star pixel value which formed near the 255 Intensity value and scattered data points in between(which represent the noise)
+        \item Based on the analysis, We know the range of threshold value is in between the noise values and the star pixel cluster.
+        \item Finally, while carrying out experiments on the test dataset, we fine-tune and optimize the threshold value to produce the highest possible accuracy.
+    \end{itemize}
+
+    \begin{figure}[H]
+        \centering
+        \includegraphics[width=1.0\textwidth]{4}
+    \end{figure}
+
+    If we set the threshold too low, it would lead to mismatches. Otherwise, if we set the threshold too high, some stars would be missing from the image.
 
@@
     \item Conclusion must be made for the study, so I would like to see a chapter on conclusion which includes the following:
+
     \begin{enumerate}[label=(\alph*)]
@@
         \color{black}
-        Answer
+        I have amended some details to the summary and future works in Chapter 5.
+For the question ``Can it be used for the attitude determination sensor mounted on a spacecraft?'', based on the final Runtime Comparison results, the answer is yes since the runtime meet the requirements.
+In the future works section, I suggested a depth study on noise to implement a hardware module that performs the noise cancellation efficiently since my implementation only deals with basic noise.
+Furthermore, we need an autonomous input-processing module that can manage a large stream amount of images to meet the processing rate and improve the throughput.
+(This task would be depended on each specific spacecraft).
+\\
 
         \color{blue}
-        \item Another objecttive of the thesis is to benchmark and optimize the algorithm in terms of the poer consumption and the area of transistor implementation.
+        \item Another objective of the thesis is to benchmark and optimize the algorithm in terms of the power consumption and the area of transistor implementation.
 What is the conclusion?
@@
         \color{black}
-        Answer
+        I have amended some details to Chapter Hardware design(restructured to Chapter 4.2 from page 45 to page 48).
+I have added a conclusion that the hardware-software co-processing approach is advantageous than the software-only approach in term of power consumption.
+
+        The hardware design is written on a high-level language and relied on specific Xilinx design rules and optimizations like Loop pipelining to enhance the processing speed.
+My optimization was mostly done in the algorithmic level like transfer dependant loops to independent loops, transfer array index to a stream and indexing by the binary search to reduce BRAM storages.
+Since they are technical and specific, I would not prefer to include in the thesis.
+An optimization has been mentioned in the thesis is using the one-pass scan algorithm to solve the connected component problem without using complicated data structures to reduce the hardware runtime.
+\\
+
     \end{enumerate}

### 2019-04-03 thesis/2_chapters/chap3.tex
Pre Final check

@@
 % Figure 3.2
-\ntuepsfig[width=\textwidth]{3_2}{An ARM embedded processor}
+% \ntuepsfig[width=\textwidth]{3_2}{An ARM embedded processor}
 
@@
 To eliminate the noise and separate star clusters from the background, we apply thresholding technique.
-The threshold level can be chosen by averaging all pixel intensities.
+The threshold level can be chosen by the Average Pixel Intensity technique.
 The pixel which has a higher value than threshold level belongs to a star cluster while the pixel which has a lower value than the threshold belongs to the background.
@@
 Otherwise, if we set the threshold too high, some stars would be missing from the image.
-Between 0-255, we choose the threshold value 70 which mostly produce high matching accuracy.
 
 \ntuepsfig[scale=0.7]{3_10}{Thresholding separates star cluster pixels and background pixels}
+
+\noindent The Average Pixel Intensity technique is applied to choose the threshold value.
+Firstly, we perform an analysis by averaging and counting the occurrences of all the pixel values in the star image dataset.
+The pattern of the analysis is simulated as in Figure~\ref{fig:3_24}.
+It includes 2 significant clusters: the first cluster is the background pixel values which formed near 0 Intensity value and the second cluster is the star pixel value which formed near the 255 Intensity value.
+There will be some scattered data points in between which represent the noise values.
+Based on the pattern we may know the range of the threshold value.
+To select the threshold value precisely, while running the algorithm on the test dataset, we fine-tune the threshold value again within the range to achieve the best accuracy.
+After performing the analysis and carrying out the algorithm on the test dataset, we choose the threshold value 70 which mostly produce high matching accuracy.
+\\
+
+\ntuepsfig[width=\textwidth]{3_24}{Clustering pixel values}
 
@@
 The raw image is contaminated with noises and other non-stellar objects.
-These noises can be canceled by setting a threshold level.
+The noise can be canceled by setting a threshold level.
 If a pixel Intensity is less than the threshold level, we will set its value to 0(the background level) to differentiate from star cluster pattern.

### 2019-04-08 thesis_supports/thesis_amended/Response_Reviewer1/Response_Reviewer1.tex
Add thesis_submission and thesis_amended

--- 2019-04-02 thesis_supports/Response_Reviewer1/Response_Reviewer1.tex
@@
 \usepackage{xcolor}
+\usepackage{float}
+\usepackage{graphicx}
+    \graphicspath{ {./img/} }
 \usepackage[
@@
     \color{black}
-    Answer
+    Thanks for pointing these out. In my previous submission, while fixing some typos, I forgot to check the configuration of the LaTeX compiler leads to missing table captions.
+
+    I have checked and fixed them all. \\
+
+    \begin{figure}[H]
+        \centering
+        \includegraphics[width=0.6\textwidth]{1}
+    \end{figure}
 
@@
     \color{black}
-    Answer
+    Thanks for pointing out again. I have added explanations of those figures in pages 7 and 8
+
+    \begin{figure}[H]
+        \centering
+        \includegraphics[width=0.6\textwidth]{2}
+    \end{figure}
+
+    \begin{figure}[H]
+        \centering
+        \includegraphics[width=0.6\textwidth]{3}
+    \end{figure}
 
@@
     \color{black}
-    Answer
+    I have amended a precise explanation to chapter 3.3.1 Centroiding (pages: 28,29,30). To summarize how to choose the threshold value:
+
+    \begin{itemize}
+        \item Firstly, I perform an analysis by averaging and counting the occurences of all pixel values in the star image dataset. 
+        \item The result of the analysis would form a pattern which is shown like the below image.
+It includes 2 significant clusters: the first cluster is the background pixel values which formed near 0 Intensity value and the second cluster is the star pixel value which formed near the 255 Intensity value and scattered data points in between(which represent the noise)
+        \item Based on the analysis, We know the range of threshold value is in between the noise values and the star pixel cluster.
+        \item Finally, while carrying out experiments on the test dataset, we fine-tune and optimize the threshold value to produce the highest possible accuracy.
+    \end{itemize}
+
+    \begin{figure}[H]
+        \centering
+        \includegraphics[width=1.0\textwidth]{4}
+    \end{figure}
 
@@
     \color{black}
-    Answer
+    The advantages of the proposed prebuilt tree structured star pattern database (SPD) over traditional algorithms in terms of space complexity, accuracy and robustness have been studied and proved by the previous research ``An Autonomous Star Recognition Algorithm with Optimized Star Catalogue for Fast Search Performance''[1]
 
@@
     \color{black}
-    Answer
+    I have amended detailed explanations to Chapter ``Runtime experiments'' (restructured to Chapter 4.3) from page 49 to page 56.
 
@@
     \color{black}
-    Answer
+    In Chapter Hardware design(restructured to Chapter 4.2 from page 45 to page 48), I have performed a Power Analysis of the design and proved that the Processing System (the ARM A9 processor) consumes 77\% of the power supplied while the Programmable Logic consumes 23\% of the total power.
+To clarify, the power consumption is measured indirectly through the number of hardware components (Logic gates, Lookup Tables, BRAM, etc.) used for the implementation and the specification of the processor (ARM A9), not directly through experiments.
+Therefore, I can only compare the power consumption between running an algorithm on hardware and running an algorithm on software.
+Based on the Power Analysis of the design, we can imply the hardware-software co-processing approach is advantageous than the software-only approach in term of power consumption.
+\\
+    In my thesis, the parts I implemented on hardware are the DMA Data Streaming and the Centroiding modules which are the common tasks for all star tracking algorithms.
+Therefore, A comparison in term of power consumption between the traditional methods and the proposed method is redundant.
 
@@
 
+\color{black}
+\noindent \large{\textbf{Reference}}
+
+\noindent[1] M D Pham, K S Low, Shoushun Chen, and Y T Xing.
+A star pattern recognition algorithm for satellite attitude determination.
+In ISIEA 2012 - 2012 IEEE Symposium on Industrial Electronics and Applications, number ISIEA 2012 - 2012 IEEE Symposium on Industrial Electronics and Applications, pages 236–241, School of Electrical and Electronic Engineering, Nanyang Technological University, 2012.
+
 % ----------------------------------------- End content --------------------------------------------- %

### 2019-04-09 thesis/1_foreword/authorship.tex
Add Signed thesis

--- 2019-04-02 thesis/1_foreword/originality.tex
@@
-\addcontentsline{toc}{chapter}{Statement of Originality}
+\addcontentsline{toc}{chapter}{Authorship Attribution Statement}
 \begin{center}
-	\textbf{\large Statement of Originality}
+    \textbf{\large Authorship Attribution Statement}
 \end{center}
 
-\noindent I hereby certify that the work embodied in this thesis is the result of original research, is free of plagiarised materials, and has not been submitted for a higher degree to any other University or Institution.
-\\
+\noindent This thesis \textbf{does not} contain any materials from papers published in peer-reviewed journals or from papers accepted at conferences in which I am listed as an author.
 

### 2019-04-11 thesis_supports/thesis_amended/Response_Reviewer1/Response_Reviewer1.tex
Clean and Reconfig Latex

@@
-\documentclass[dvips,a4paper,12pt]{report}
+\documentclass[dvips,a4paper,12pt]{article}
+    % \renewcommand\bibname{References} % report: Reference new page
+    \renewcommand\refname{Reference} % article: Reference same page
 \usepackage{xcolor}
@@
     \color{black}
-    The advantages of the proposed prebuilt tree structured star pattern database (SPD) over traditional algorithms in terms of space complexity, accuracy and robustness have been studied and proved by the previous research ``An Autonomous Star Recognition Algorithm with Optimized Star Catalogue for Fast Search Performance''[1]
+    The advantages of the proposed prebuilt tree structured star pattern database (SPD) over traditional algorithms in terms of space complexity, accuracy and robustness have been studied and proved by the previous research ``An Autonomous Star Recognition Algorithm with Optimized Star Catalogue for Fast Search Performance''\cite{MDP}.
 
@@
 
+    \newpage
     \color{blue}
@@
 
+%%% References
 \color{black}
-\noindent \large{\textbf{Reference}}
-
-\noindent[1] M D Pham, K S Low, Shoushun Chen, and Y T Xing.
-A star pattern recognition algorithm for satellite attitude determination.
-In ISIEA 2012 - 2012 IEEE Symposium on Industrial Electronics and Applications, number ISIEA 2012 - 2012 IEEE Symposium on Industrial Electronics and Applications, pages 236–241, School of Electrical and Electronic Engineering, Nanyang Technological University, 2012.
+\bibliography{bib_reference}
+\bibliographystyle{plain}
 
